---
title: "REFMAP Listening test 2 analysis: Bayesian mixed models for inferential explanation"
output: html_document
date: "2026-05-07"
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(easystats)
library(conflicted)
library(here)
library(brms)
library(bayestestR)
library(tidybayes)
library(bayesplot)
library(tidyverse)
library(DHARMa)
library(tictoc)
library(future)
library(future.apply)
library(mice)
library(marginaleffects)
library(priorsense)
library(posterior)
library(loo)
library(shinystan)
library(shinybrms)
library(ggdist)
library(brmsmargins)
library(viridis)
library(ggnewscale)
library(patchwork)
library(ggpmisc)
library(gginnards)
library(ggridges)
library(purrr)

# set package parameters
theme_set(theme_bw())

# CAUTION: calculations in this notebook assume 12 cores available from total of 16
# parallelised processing settings would need to be amended throughout the notebook if
# a different number of cores are available
n_cores <- max(1, parallelly::availableCores() - 4)
future::plan(future::multisession, workers = n_cores)

options(marginaleffects_parallel_inferences = TRUE)
options(marginaleffects_parallel = TRUE)
options(marginaleffects_parallel_packages = c("marginaleffects", "brms"))
options(marginaleffects_posterior_interval = "eti")
options(marginaleffects_posterior_center = mean)

set.seed(808)

```

## Set parameters

```{r}

# plot colour scheme

mycolourlist = list(c(0, 102, 255), c(0, 204, 153), c(255, 0, 102), c(74, 111, 152), c(251, 164, 49), c(204, 153, 255), c(90, 192, 255), c(80, 245, 233), c(255, 90, 192), c(164, 201, 242), c(255, 254, 139), c(255, 243, 255))
mycolours = matrix()

for (ii in 1:length(mycolourlist)){
  mycolours[ii] = rgb(mycolourlist[[ii]][1]/255,
                      mycolourlist[[ii]][2]/255,
                      mycolourlist[[ii]][3]/255)
}

# toggle to save plots
saveplots = TRUE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption=r"(Select output folder to save plots: 03 Experiment\Experiment 2\Analysis\Plots)")
  
  if (!dir.exists(file.path(outFigPath, "svg"))){dir.create(file.path(outFigPath, "svg"))}
  if (!dir.exists(file.path(outFigPath, "pdf"))){dir.create(file.path(outFigPath, "pdf"))}
  
}

# toggle to save data
savedata = TRUE

if (savedata){
  # set output plot directory
  if (saveplots==FALSE){
    choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  }
  outDataPath <- utils::choose.dir(caption=r"(Select output folder to save data: 03 Experiment\Experiment 2\Analysis\R)")
}

# set global number of draws and new subjects for Bayesian model predictions 
ndraws_pred <- 500
nnew_pred <- 150

# set flag whether to reloo models with Pareto k > 0.7
reloo_flag = FALSE


```

# Functions

## Beta distribution transform from arbitrary scale to (0, 1) or back again

```{r}

betaTransform <- function(x, scaleMin, scaleMax,
                          direction=c('forward', 'reverse')[1],
                          squeeze=c('none', 'basic', 'smithson')[1],
                          basic_val=1e-6){
  "Squeeze algorithm 'smithson' is from:
  Smithson, M & Verkuilen, J, 2006. A better lemon squeezer? Maximum-likelihood
  regression with beta-distributed dependent variables. Psychological Methods,
  11(1), 54-71."
  
  if (direction == 'forward') {
    # transform from original scale to (0,1)
    x_scale <- (x - scaleMin) / (scaleMax - scaleMin)
    
    if (squeeze == 'smithson') {
      
      N = length(x_scale)
      x_out <- (x_scale*(N - 1) + 0.5) / N
      
    } else if (squeeze == 'basic') {
      
      x_out <- x_scale*(1 - 2*basic_val) + basic_val
      
    } else {
      
      x_out <- x_scale
      
    }

  } else if (direction == 'reverse') {
    # transform from (0, 1) back to original scale
    x_scale <- x * (scaleMax - scaleMin) + scaleMin
    
    if (squeeze == 'smithson') {
      
      N = length(x_scale)
      x_out <- (x_scale*N - 0.5)/(N - 1)
      
    } else if (squeeze == 'basic') {
      
      x_out <- (x_scale - basic_val)/(1 - 2*basic_val)
      
    } else {
      
      x_out <- x_scale
      
    }

  } else {
    
    stop("Invalid direction argument: must be 'forward' or 'reverse'")
    
  }
  
  return(x_out)
  
}


```

## Bayesian version of McKelvey and Zavoina's pseudo-R2

From https://discourse.mc-stan.org/t/r-2-calculation-for-brm-model-with-cumulative-family-type/14752/2

```{R}
# Bayesian McKelvey-Zavoina R2 ------------------------------------------------
# Bayesian version of McKelvey and Zavoina's pseudo-R2 for binary and ordinal
# brms models (McKelvey and Zavoina, 1975). See also Gelman et al. (2018). This
# pseudo-R2 closely approximates the R2 that would have been obtained if a
# linear model had have been run on observations of the continuous latent
# variable underlying the discrete responses (Veall and Zimmermann, 1992; Hagle
# and Mitchell, 1992; Veall and Zimmermann, 1994).
Bayes_R2_MZ <- function(fit, ...) {
  y_pred <- fitted(fit, scale = "linear", summary = FALSE, ...)
  var_fit <- apply(y_pred, 1, stats::var)
  if (fit$formula$family$family == "cumulative" ||
      fit$formula$family$family == "bernoulli") {
    if (fit$formula$family$link == "probit" || 
        fit$formula$family$link == "probit_approx") {
      var_res <- 1
    }
    else if (fit$formula$family$link == "logit") {
      var_res <- pi^2 / 3 
    }
  } 
  else {
    sum_fit <- summary(fit)
    sig_res <- sum_fit$spec_pars["sigma", "Estimate"]
    var_res <- sig_res^2
  } 
  R2_MZ <- var_fit / (var_fit + var_res)
  print(
    data.frame(
      Estimate = mean(R2_MZ), 
      Est.Error = stats::sd(R2_MZ), 
      "l-95% CI" = quantile(R2_MZ, 0.025),
      "u-95% CI" = quantile(R2_MZ, 0.975),
      row.names = "Bayes_R2_MZ", 
      check.names = FALSE), 
    digits = 3)
}

```

## Rescale ggplot tick marks for variables

```{r}

rescaleTicks <- function(dataVar, dataVarScl, sep=3, ax='x'){
  
  if (ax == 'x'){
    outAx <- scale_x_continuous(breaks=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep) -
                                  (max(dataVar) - max(dataVarScl)),
                                labels=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep))

  } else if (ax == 'y'){
    outAx <- scale_y_continuous(breaks=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep) -
                                  (max(dataVar) - max(dataVarScl)),
                                labels=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep))
  } else {
    stop("Invalid axis argument")
  }
 
  return(outAx) 
}


```

## Scaling multiple dataframes

```{r}

#' Standardise selected columns across a list of data frames
#'
#' Applies \code{datawizard::standardise()} to user-specified columns in each
#' data frame of a list, adding the result as new columns with "Scl"
#' appended to the original column name. Standardisation can be switched on
#' or off per variable via the \code{scale} argument.
#'
#' @param df_list A list of data frames.
#' @param vars    Character vector of column names to (optionally) standardise.
#' @param scale   Controls which variables get full standardisation vs.
#'                centering only:
#'                \itemize{
#'                  \item A single logical (default \code{TRUE}) applied to all \code{vars}.
#'                  \item An unnamed logical vector the same length as \code{vars},
#'                        matched by position.
#'                  \item A named logical vector, e.g. \code{c(height = TRUE, weight = FALSE)}.
#'                        Any variable in \code{vars} not named here defaults to \code{TRUE}.
#'                }
#'                Variables with \code{scale = TRUE} are run through
#'                \code{datawizard::standardise()} (centered AND scaled to SD = 1).
#'                Variables with \code{scale = FALSE} are run through
#'                \code{datawizard::center()} instead, so they are still
#'                mean-centered but left on their original scale (SD unchanged).
#'                Either way the new "Scl" column is always created.
#' @param ...     Additional arguments passed on to \code{datawizard::standardise()}
#'                and \code{datawizard::center()} (e.g. \code{robust}).
#'                Note: only arguments valid for both functions can safely be
#'                passed this way (see Details).
#'
#' @return A list of data frames (same length/order as \code{df_list}), each
#'         with new "<var>Scl" columns added.
#'
#' @examples
#' \dontrun{
#' library(datawizard)
#'
#' df1 <- data.frame(height = rnorm(10, 170, 10), weight = rnorm(10, 70, 15))
#' df2 <- data.frame(height = rnorm(10, 165, 8),  weight = rnorm(10, 65, 12))
#'
#' dfs <- list(df1, df2)
#'
#' # Standardise both variables in every data frame
#' out <- standardise_list(dfs, vars = c("height", "weight"))
#'
#' # Fully standardise height, but only center weight (weightScl keeps its
#' # original SD, just shifted to a mean of 0)
#' out2 <- standardise_list(dfs, vars = c("height", "weight"),
#'                           scale = c(height = TRUE, weight = FALSE))
#' }
#'
#' @export
standardise_list <- function(df_list, vars, scale = TRUE, ...) {

  # --- Input checks --------------------------------------------------------
  if (!is.list(df_list) || !all(vapply(df_list, is.data.frame, logical(1)))) {
    stop("`df_list` must be a list of data frames.")
  }
  if (!is.character(vars) || length(vars) == 0) {
    stop("`vars` must be a non-empty character vector of column names.")
  }
  if (!is.logical(scale)) {
    stop("`scale` must be logical (TRUE/FALSE), optionally named.")
  }

  # --- Expand `scale` into a named logical vector aligned with `vars` -----
  if (length(scale) == 1) {
    scale <- stats::setNames(rep(scale, length(vars)), vars)
  } else {
    if (is.null(names(scale))) {
      if (length(scale) != length(vars)) {
        stop("`scale` must be length 1, named, or the same length as `vars`.")
      }
      names(scale) <- vars
    }
    # Any vars not explicitly named in `scale` default to TRUE
    missing_vars <- setdiff(vars, names(scale))
    if (length(missing_vars) > 0) {
      scale <- c(scale, stats::setNames(rep(TRUE, length(missing_vars)), missing_vars))
    }
    scale <- scale[vars]  # align order, drop any extras not in `vars`
  }

  # --- Apply to each data frame --------------------------------------------
  lapply(df_list, function(df) {

    present_vars <- intersect(vars, names(df))
    absent_vars  <- setdiff(vars, names(df))

    if (length(absent_vars) > 0) {
      warning("Columns not found and skipped: ", paste(absent_vars, collapse = ", "))
    }

    for (v in present_vars) {
      new_name <- paste0(v, "Scl")

      if (isTRUE(scale[[v]])) {
        df[[new_name]] <- datawizard::standardise(df[[v]], ...)
      } else {
        df[[new_name]] <- datawizard::center(df[[v]], ...)
      }
    }

    df
  })
}

```

## estimate calculation grid memory size requirement

```{r}

estimate_size_gb <- function(newdata, ndraws, n_counterfactual_levels = 1) {
  bytes <- as.numeric(nrow(newdata)) * ndraws * n_counterfactual_levels * 8
  gb <- bytes / 1e9
  cat(sprintf("Estimated matrix size: %.1f GB (%s rows x %d draws x %d levels)\n",
              gb, format(nrow(newdata), big.mark = ","), ndraws, n_counterfactual_levels))
  gb
}

```


## avg_comparisons_slopes

Generated by Claude AI (Sonnet 5): https://claude.ai/chat/febecbdd-ea0b-491b-b736-9d2e9a52e55c

```{r}

source(here("src/R/avg_comparisons_slopes.R"))

```

## Bayesian R2 table extraction function

```{r}

get_Br2_table <- function(...) {
  model_names <- match.call(expand.dots = FALSE)$... |> as.character()
  models <- list(...)
  
  # Helper to safely extract metrics or return NAs matching the column shape
  get_metric <- function(model, type) {
    metric <- model$criteria[[type]]
    
    if (!is.null(metric)) {
      return(as_tibble(metric))
    }
    
    # Dynamically find column names from a model that actually has data
    valid_mod <- keep(models, ~ !is.null(.x$criteria[[type]])) |> first()
    col_names <- if (!is.null(valid_mod)) colnames(valid_mod$criteria[[type]]) else c("Estimate", "Est.Error", "Q2.5", "Q97.5")
    
    # Return a single row of NAs with correct columns
    as_tibble(matrix(NA_real_, nrow = 1, ncol = length(col_names), dimnames = list(NULL, col_names)))
  }
  
  # Loop through models, extract, flatten to one row, and sort
  map2_dfr(models, model_names, function(mod, name) {
    bind_rows(
      get_metric(mod, "bayes_R2_marginal")    |> add_column(Type = "Marginal", .before = 1),
      get_metric(mod, "bayes_R2_conditional") |> add_column(Type = "Conditional", .before = 1)
    ) |> 
    add_column(Model = name, .before = 1)
  }) |> 
    # Pivot columns wider so each model has exactly one row
    pivot_wider(
      names_from = Type, 
      values_from = -c(Model, Type),
      names_glue = "{Type}_{.value}"
    ) |> 
    
    # Reorder columns so Marginal statistics block together, then Conditional block together
    relocate(starts_with("Marginal"), .after = Model) |> 
    
    # Reorder rows by the marginal R2 Estimate descending
    arrange(desc(Marginal_Estimate))
}

```

# Import data

```{r}

subjDataPath <- utils::choose.files(caption=r"(Select refmap_listest2_testdata_BySubj.csv from 03 Experiment\Experiment 2\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest2_testdata_BySubj.csv", "refmap_listest2_testdata_BySubj.csv"), ncol=2))

subjData <- read.csv(subjDataPath, header=TRUE)

stimDataPath <- utils::choose.files(caption=r"(Select refmap_listest2_testdata_ByStim.csv from 03 Experiment\Experiment 2\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest2_testdata_ByStim.csv", "refmap_listest2_testdata_ByStim.csv"), ncol=2))

stimData <- read.csv(stimDataPath, header=TRUE, row.names=1)

```

## wrangle

```{r}

# rename variables for ease
subjData <- subjData |> dplyr::rename(TrialNumber = Trial)

subjData$AmbientEnvCore <- subjData$AmbientEnv |>
  dplyr::recode("Park (high)" = "Park",
                "Highway (low)" = "Highway") |>
  factor(levels=c("Park", "Residential", "Streetside square", "Highway"))

subjData$AmbientVariant <- factor(dplyr::case_when(
  subjData$AmbientEnv == "Park (high)" ~ "ParkHigh",
  subjData$AmbientEnv == "Highway (low)" ~ "HighwayLow",
  TRUE ~ "Standard"
  ), levels = c("Standard", "ParkHigh", "HighwayLow"))

stimData$AmbientEnvCore <- stimData$AmbientEnv |>
  dplyr::recode("Park (high)" = "Park",
                "Highway (low)" = "Highway") |>
  factor(levels=c("Park", "Residential", "Streetside square", "Highway"))

stimData$AmbientVariant <- factor(dplyr::case_when(
  stimData$AmbientEnv == "Park (high)" ~ "ParkHigh",
  stimData$AmbientEnv == "Highway (low)" ~ "HighwayLow",
  TRUE ~ "Standard"
  ), levels = c("Standard", "ParkHigh", "HighwayLow"))

# definition of ordinal variable levels
UASOpCats <- c("Baseline", "Overflight", "Delivery")
UASTypeCats <- c("Baseline", "H520", "T150")
UASStart <- c("Baseline", "Left", "Right")

# encode factors
subjData$ID <- factor(subjData$ID)
subjData$UASOperation <- factor(subjData$UASOperation, levels=UASOpCats)
subjData$UASType <- factor(subjData$UASType, levels=UASTypeCats)
subjData$UASStart <- factor(subjData$UASStart, levels=UASStart)
subjData$AmbientEnv <- factor(subjData$AmbientEnv, levels=c("Park", "Residential", "Park (high)",
                                                            "Highway (low)", "Streetside square", "Highway"))
subjData$AAMAttitude <- factor(subjData$AAMAttitude)
subjData$HomeArea <- factor(subjData$HomeArea)
subjData$SoundscapeArea <- factor(subjData$SoundscapeArea)
subjData$Nationality <- factor(subjData$Nationality)
subjData$UKNational <- factor(subjData$UKNational)


# recode AAM_attitude to 2 groups
subjData <- subjData |> dplyr::mutate(AAM_attitude2 = dplyr::recode_values(AAMAttitude,
                                                                    "Supportive" ~ "Supportive",
                                                                    c("Ambivalent",
                                                                      "Concerned",
                                                                      "Neutral") ~ "Ambiv_Concern_Neutral"))
subjData$AAM_attitude2 <- factor(subjData$AAM_attitude2, levels=c("Supportive", "Ambiv_Concern_Neutral"))


# recode NationGeo to 3 groups
subjData <- subjData |> dplyr::mutate(NationGeo3 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia") ~ "Africa_SAsia",
                                                                 c("EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "NotAnswered") ~ "Other"))
subjData$NationGeo3 <- factor(subjData$NationGeo3)

# recode NationGeo to 2 groups
subjData <- subjData |> dplyr::mutate(NationGeo2 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia",
                                                                   "Australasia",
                                                                   "EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "") ~ "Other"))
subjData$NationGeo2 <- factor(subjData$NationGeo2)

# recode Area of residence to 2 groups
subjData <- subjData |> dplyr::mutate(Home_Area2 = dplyr::recode_values(HomeArea,
                                                         "Urban" ~ "Urban",
                                                         c("Suburban",
                                                           "Rural") ~ "Suburban_Rural"))
subjData$Home_Area2 <- factor(subjData$Home_Area2)


# recode Area soundscape to 2 groups
subjData <- subjData |> dplyr::mutate(Area_soundscape2 = dplyr::recode_values(SoundscapeArea,
                                                                       c("Calm",
                                                                         "Vibrant") ~ "Pleasant",
                                                                       c("Chaotic",
                                                                         "Monotonous") ~ "Unpleasant"))

subjData$Area_soundscape2 <- factor(subjData$Area_soundscape2, levels=c("Unpleasant", "Pleasant"))

subjData <- subjData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
subjData <- subjData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)

stimData <- stimData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
stimData <- stimData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)

# Log other variables
subjData$PartLoudSHMPowAvgLog <- log(subjData$PartLoudSHMPowAvg)
stimData$PartLoudSHMPowAvgLog <- log(stimData$PartLoudSHMPowAvg)

# reorder by participant ID and trial number
subjData <- subjData[with(subjData, order(ID, TrialNumber)), ]

# add a rescaled dAnnoyance variable
subjData <- subjData |>
  dplyr::mutate(AnnoyanceOrdBetaScl = betaTransform(Annoyance, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyanceOrdBetaScl = betaTransform(dAnnoyance, -10, 10,
                                                     direction='forward', squeeze='none'))

# add a rescaled dAnnoyance variable
stimData <- stimData |>
  dplyr::mutate(AnnoyMeanOrdBetaScl = betaTransform(AnnoyanceMean, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyMeanOrdBetaScl = betaTransform(dAnnoyanceMean, -10, 10,
                                                     direction='forward', squeeze='none'))

# omit ambient-only stimuli
subjDataNoAmb <- subjData |> dplyr::filter(UASStart != "Baseline")
stimDataNoAmb <- stimData |> dplyr::filter(UASStart != "Baseline")

```

## rescaling variables

```{r}

# rescale variables

centre_vars = c("UASLAeqMaxLR", "UASLAEMaxLR", "UASEPNLMaxLR", "UASLAF50ExMaxLR")

out <- standardise_list(list(subjData, subjDataNoAmb, stimData, stimDataNoAmb),
                        vars = centre_vars,
                        scale = FALSE)

subjData <- out[[1]]
subjDataNoAmb <- out[[2]]
stimData <- out[[3]]
stimDataNoAmb <- out[[4]]


out <- standardise_list(list(subjData, subjDataNoAmb),
                        vars = c("TrialNumber"),
                        scale = TRUE)

subjData <- out[[1]]
subjDataNoAmb <- out[[2]]

# rescale trial number variables
subjData <- rbind(subjData |>
                    dplyr::mutate(TrialNumberScl = datawizard::standardise(TrialNumber, scale=TRUE))) |>
  droplevels()

subjDataNoAmb <- rbind(subjDataNoAmb |>
                         dplyr::mutate(TrialNumberScl = datawizard::standardise(TrialNumber, scale=TRUE))) |>
  droplevels()


```

# dAnnoyance

## m0: minimal ordbeta model

### Formula

```{R}

m0formula <- dAnnoyanceOrdBetaScl ~ 1 + TrialNumberScl +
                    UASProximity +
                    UASLAEMaxLRScl + I(log10(UASEvents)) +
                   AmbientEnvCore + UASOperation +
                   AmbientVariant + UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + UASProximity + UASLAEMaxLRScl + AmbientEnvCore +
                      I(log10(UASEvents)) + AmbientVariant +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

m0Data <- subjDataNoAmb[, all.vars(m0formula), drop=FALSE]

```

### run model 0

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

priors0 <- c(
  # mean model
  set_prior("normal(0, 2)", class='b', dpar='mu'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl', dpar='mu'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl', dpar='mu'),

  # precision model
  brms::prior(normal(0, 1), class = 'Intercept', dpar = 'phi'),
  brms::prior(normal(0, 0.5), class = 'b', dpar = 'phi')
)

tic()
m0 <- brms::brm(brms::bf(m0formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0 <- brms::add_criterion(m0, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0))
m0$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0, re_formula=NA))
m0$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0PostCheck <- brms::pp_check(m0, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheck

m0PostCheckEnv <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckEnv

m0PostCheckEnv <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckEnv

m0PostCheckEvt <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckEvt

m0PostCheckType <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckType

m0PostCheckOp <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckOp

m0PostCheckProx <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckProx

```


#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCorePark",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare"))



```

#### performance

```{R}

loo::pareto_k_table(loo::loo(m0))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0)

```

## m0b: medial ordbeta model

### Formula

```{R}

m0bformula <- dAnnoyanceOrdBetaScl ~
  # within-subjects fixed
  1 + TrialNumberScl + UASProximity +
  AmbientEnvCore*UASType + AmbientEnvCore*UASOperation + AmbientVariant +
  UASLAEMaxLRScl*I(log10(UASEvents)) +
  # between subjects fixed
  NationGeo2 + AAM_attitude2 + Home_Area2 +
  Age + Sex + NoiseSensitivity + Area_soundscape2 +
  # random effects
  (1 + UASProximity + UASLAEMaxLRScl + AmbientEnvCore + I(log10(UASEvents)) +
     AmbientVariant + UASOperation + UASType | ID) + (1 | StimID)

```

### run model 0b

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0b <- brms::brm(brms::bf(m0bformula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0b <- brms::add_criterion(m0b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0b))
m0b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0b, re_formula=NA))
m0b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0b, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0bPostCheck <- brms::pp_check(m0b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheck

m0bPostCheckEnv <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckEnv

m0bPostCheckEnv <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckEnv

m0bPostCheckEvt <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckEvt

m0bPostCheckType <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckType

m0bPostCheckOp <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckOp

m0bPostCheckProx <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0b)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0b), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCorePark",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare"))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0b))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b)

m0b_loo <- loo::loo_compare(m0, m0b, criterion='loo')
m0b_loo

```

## m0c: medial ordbeta model with decorrelated UASProximity

### Formula

```{R}

m0cformula <- dAnnoyanceOrdBetaScl ~
  # within-subjects fixed
  1 + TrialNumberScl + UASProximity +
  AmbientEnvCore*UASType + AmbientEnvCore*UASOperation + AmbientVariant +
  UASLAEMaxLRScl*I(log10(UASEvents)) +
  # between subjects fixed
  NationGeo2 + AAM_attitude2 + Home_Area2 +
  Age + Sex + NoiseSensitivity + Area_soundscape2 +
  # random effects
  (1 + UASLAEMaxLRScl + AmbientEnvCore + I(log10(UASEvents)) +
     AmbientVariant + UASOperation + UASType | ID) +
  (0 + UASProximity | ID) +
  (1 | StimID)

```

### run model 0c

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0c <- brms::brm(brms::bf(m0cformula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0c <- brms::add_criterion(m0c, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0c$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0c))
m0c$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0c, re_formula=NA))
m0c$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0c, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0cPostCheck <- brms::pp_check(m0c, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheck

m0cPostCheckEnv <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckEnv

m0cPostCheckEnv <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckEnv

m0cPostCheckEvt <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckEvt

m0cPostCheckType <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckType

m0cPostCheckOp <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckOp

m0cPostCheckProx <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0c)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0c), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCorePark",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare"))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0c))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b, m0c)

m0c_loo <- loo::loo_compare(m0, m0b, m0c, criterion='loo')
m0c_loo

```

## m1: maximal ordbeta model

### Formula

```{R}

m1formula <- dAnnoyanceOrdBetaScl ~ 1 + TrialNumberScl +
                    UASProximity +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnvCore*UASOperation +
                   UASLAEMaxLRScl*AmbientEnvCore*UASType +
                   AmbientVariant*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + UASProximity + UASLAEMaxLRScl + AmbientEnvCore +
                      I(log10(UASEvents)) + AmbientVariant +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

m1Data <- subjDataNoAmb[, all.vars(m1formula), drop=FALSE]

```

### run model 1

```{r}

chains <- 4

future::plan(future::multisession, workers = chains)

priors1 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(gamma(2, 0.1), class='phi')
)

tic()
m1Priors <- brms::brm(m1formula,
                 data=m1Data,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors1, control=list(adapt_delta=0.95),
                 sample_prior='only', seed=808,
                 chains=chains, iter=2000, warmup=1000)
toc()

m1PriorCheck <- brms::pp_check(m1Priors, ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PriorCheck

tic()
m1 <- brms::brm(m1formula, data=m1Data,
                family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1, control=list(adapt_delta=0.95),
               threads = threading(threads = 3, static = TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1 <- brms::add_criterion(m1, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag,
                          overwrite=TRUE,
                          chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                          backend='cmdstanr',
                          future_args=list(future.seed=TRUE))
toc()

m1$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1))
m1$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1, re_formula=NA))
m1$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1PostCheck <- brms::pp_check(m1, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheck

m1PostCheckEnv <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckEnv

m1PostCheckEnv <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckEnv

m1PostCheckEvt <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckEvt

m1PostCheckType <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckType

m1PostCheckOp <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckOp

m1PostCheckProx <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m1)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m1), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCorePark",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare"))



```

### run model 1b

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

priors1b <- c(
  # mean model
  set_prior("normal(0, 2)", class='b', dpar='mu'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl', dpar='mu'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl', dpar='mu'),
  # precision model
  brms::prior(normal(0, 1), class = 'Intercept', dpar = 'phi'),
  brms::prior(normal(0, 0.5), class = 'b', dpar = 'phi')
)

tic()
m1b <- brms::brm(brms::bf(m1formula, phi ~ 1 + AmbientEnvCore),
                data=m1Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1b <- brms::add_criterion(m1b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m1b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1b))
m1b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1b, re_formula=NA))
m1b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1b, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1bPostCheck <- brms::pp_check(m1b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheck

m1bPostCheckEnv <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckEnv

m1bPostCheckEnv <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckEnv

m1bPostCheckEvt <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckEvt

m1bPostCheckType <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckType

m1bPostCheckOp <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckOp

m1bPostCheckProx <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckProx

```

#### compare

```{R}

loo::pareto_k_table(loo::loo(m1b))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m1, m1b)

m1b_loo <- loo::loo_compare(m1, m1b, criterion='loo')
m1b_loo

```

### run model 1c

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m1c <- brms::brm(brms::bf(m1formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType),
                data=m1Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1c <- brms::add_criterion(m1c, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m1c$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1c))
m1c$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1c, re_formula=NA))
m1c$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1c, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1cPostCheck <- brms::pp_check(m1c, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheck

m1cPostCheckEnv <- brms::pp_check(m1c, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheckEnv

m1cPostCheckEnv <- brms::pp_check(m1c, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheckEnv

m1cPostCheckEvt <- brms::pp_check(m1c, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheckEvt

m1cPostCheckType <- brms::pp_check(m1c, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheckType

m1cPostCheckOp <- brms::pp_check(m1c, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheckOp

m1cPostCheckProx <- brms::pp_check(m1c, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1cPostCheckProx

```

#### compare

```{R}

loo::pareto_k_table(loo::loo(m1c))

get_Br2_table(m1, m1b, m1c)

m1c_loo <- loo::loo_compare(m1, m1b, m1c, criterion='loo')
m1c_loo

```

### run model 1d

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m1d <- brms::brm(brms::bf(m1formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + (1 | ID)),
                data=m1Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1d <- brms::add_criterion(m1d, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m1d$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1d))
m1d$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1d, re_formula=NA))
m1d$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1d, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1dPostCheck <- brms::pp_check(m1d, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheck

m1dPostCheckEnv <- brms::pp_check(m1d, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheckEnv

m1dPostCheckEnv <- brms::pp_check(m1d, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheckEnv

m1dPostCheckEvt <- brms::pp_check(m1d, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheckEvt

m1dPostCheckType <- brms::pp_check(m1d, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheckType

m1dPostCheckOp <- brms::pp_check(m1d, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheckOp

m1dPostCheckProx <- brms::pp_check(m1d, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1dPostCheckProx

```

#### compare

```{R}


loo::pareto_k_table(loo::loo(m1d))

get_Br2_table(m1, m1b, m1c, m1d)

m1d_loo <- loo::loo_compare(m1, m1b, m1c, m1d, criterion='loo')
m1d_loo

```

### run model 1e

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m1e <- brms::brm(brms::bf(m1formula, phi ~ 1 + AmbientEnvCore + AmbientVariant +
                            UASOperation + UASType + (1 | ID)),
                data=m1Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1e <- brms::add_criterion(m1e, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m1e$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1e))
m1e$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1e, re_formula=NA))
m1e$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1e, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1ePostCheck <- brms::pp_check(m1e, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheck

m1ePostCheckEnv <- brms::pp_check(m1e, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheckEnv

m1ePostCheckEnv <- brms::pp_check(m1e, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheckEnv

m1ePostCheckEvt <- brms::pp_check(m1e, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheckEvt

m1ePostCheckType <- brms::pp_check(m1e, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheckType

m1ePostCheckOp <- brms::pp_check(m1e, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheckOp

m1ePostCheckProx <- brms::pp_check(m1e, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1ePostCheckProx

```

#### compare

```{R}

loo::pareto_k_table(loo::loo(m1e))

get_Br2_table(m1, m1b, m1c, m1d, m1e)

m1e_loo <- loo::loo_compare(m1, m1b, m1c, m1d, m1e, criterion='loo')
m1e_loo

```

### run model 1f

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m1f <- brms::brm(brms::bf(m1formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m1Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1f <- brms::add_criterion(m1f, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m1f$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1f))
m1f$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1f, re_formula=NA))
m1f$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1f, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1fPostCheck <- brms::pp_check(m1f, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheck

m1fPostCheckEnv <- brms::pp_check(m1f, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheckEnv

m1fPostCheckEnv <- brms::pp_check(m1f, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheckEnv

m1fPostCheckEvt <- brms::pp_check(m1f, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheckEvt

m1fPostCheckType <- brms::pp_check(m1f, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheckType

m1fPostCheckOp <- brms::pp_check(m1f, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheckOp

m1fPostCheckProx <- brms::pp_check(m1f, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1fPostCheckProx

```

#### compare

```{R}

loo::pareto_k_table(loo::loo(m1f))

get_Br2_table(m1, m1b, m1c, m1d, m1e, m1f)

m1f_loo <- loo::loo_compare(m1, m1b, m1c, m1d, m1e, m1f, criterion='loo')
m1f_loo

```

### analyse m1f results

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m1f_bCI_range <- bayestestR::hdi(m1f, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m1f_bCI_wsf <- m1f_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASProximityNear", 
                                 "b_UASTypeT150", 
                                 "b_UASOperationDelivery",
                                 "b_AmbientEnvCorePark",
                                 "b_AmbientEnvCoreResidential",
                                 "b_AmbientEnvCoreStreetsidesquare",
                                 "b_AmbientVariantParkHigh",
                                 "b_AmbientVariantHighwayLow"))
p_m1f_bCI_wsf <- plot(m1f_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1f_bCI_wsf

filename <- "dAnnoyMnCatModbCI_brmsOb_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m1f_bCI_wsfi <- m1f_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvCorePark:UASOperationDelivery",
                                 "b_AmbientEnvCoreResidential:UASOperationDelivery",
                                 "b_AmbientEnvCoreStreetsidesquare:UASOperationDelivery",
                                 "b_AmbientEnvCorePark:UASTypeT150",
                                 "b_AmbientEnvCoreResidential:UASTypeT150",
                                 "b_AmbientEnvCoreStreetsidesquare:UASTypeT150",
                                 "b_UASTypeT150:AmbientVariantParkHigh",
                                 "b_UASTypeT150:AmbientVariantHighwayLow",
                                 "b_UASOperationDelivery:UASTypeT150"))
p_m1f_bCI_wsfi <- plot(m1f_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1f_bCI_wsfi

filename <- "dAnnoyMnCatModbCI_brmsOb_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m1f_bCI_wsc <- m1f_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m1f_bCI_wsc <- plot(m1f_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1f_bCI_wsc

filename <- "dAnnoyMnCatModbCI_brmsOb_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m1f_bCI_wscfi <- m1f_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvCorePark",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreResidential",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreStreetsidesquare",
                                 "b_UASLAEMaxLRScl:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvCorePark:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreResidential:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreStreetsidesquare:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:AmbientEnvCorePark:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreResidential:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreStreetsidesquare:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m1f_bCI_wscfi <- plot(m1f_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1f_bCI_wscfi

filename <- "dAnnoyMnCatModbCI_brmsOb_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m1f_bCI_bsf <- m1f_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Unpleasant"))
p_m1f_bCI_bsf <- plot(m1f_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1f_bCI_bsf

filename <- "dAnnoyMnCatModbCI_brmsOb_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m1f_bCI_bsc <- m1f_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NoiseSensitivity"))
p_m1f_bCI_bsc <- plot(m1f_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1f_bCI_bsc

filename <- "dAnnoyMnCatModbCI_brmsOb_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### analyse population-averaged effects (not conditional effects) using marginaleffects

```{R}
# create base datagrid
m1fDataFit <- insight::get_data(m1f)

# get unique combinations of the predictors
base_unique <- m1fDataFit |>
    dplyr::distinct(ID, UASProximity, UASType, UASEvents, AmbientEnvCore, AmbientVariant, UASOperation,
                    NationGeo2, AAM_attitude2, Home_Area2,
                    Age, Sex, NoiseSensitivity, Area_soundscape2,
                    .keep_all = TRUE) |>
    dplyr::group_by(ID, UASProximity, UASType, UASEvents, AmbientEnvCore, AmbientVariant, UASOperation) |>
    dplyr::ungroup()
# include mean trial number
base_unique$TrialNumberScl <- mean(m1fDataFit$TrialNumberScl)

# expand grid over LAE
lae_step <- seq(min(stimDataNoAmb$UASLAEMaxLRScl), max(stimDataNoAmb$UASLAEMaxLRScl), length.out = 13)
base_expanded <- marginaleffects::datagrid(
  newdata = base_unique,
  UASLAEMaxLRScl = lae_step,
  grid_type = "counterfactual"
)

lae_step2 <- c(-10, -8, -6, 4, 6, 8)
base_expanded2 <- marginaleffects::datagrid(
  newdata = base_unique,
  UASLAEMaxLRScl = lae_step2,
  grid_type = "counterfactual"
)

# set up marginal grids with new subject and stimulus IDs
grid_marg <- base_expanded[rep(seq_len(nrow(base_expanded)), each = nnew_pred), ]
new_idx <- rep(seq_len(nnew_pred), times = nrow(base_expanded))
grid_marg$ID     <- paste0("new_id_", new_idx)
grid_marg$StimID <- paste0("new_stim_", new_idx)

grid_marg2<- base_expanded2[rep(seq_len(nrow(base_expanded2)), each = nnew_pred), ]
new_idx2 <- rep(seq_len(nnew_pred), times = nrow(base_expanded2))
grid_marg2$ID     <- paste0("new_id_", new_idx2)
grid_marg2$StimID <- paste0("new_stim_", new_idx2)

set.seed(999)
m1fpredProx <- marginaleffects::avg_predictions(m1f, newdata=subset(grid_marg,
                                                             UASEvents==1, 
                                                             AmbientVariant=="Standard"),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASProximity",
                                                       "UASType",
                                                       "UASOperation",
                                                       "AmbientEnvCore"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredType <- marginaleffects::avg_predictions(m1f, newdata=subset(grid_marg,
                                                             UASEvents==1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

# force it to match brms's internal string representation
newdata_test <- m1fDataFit
newdata_test$ID <- as.character(newdata_test$ID)
newdata_test$StimID <- as.character(newdata_test$StimID)   # same risk applies here

m1fpredTypeTest <- marginaleffects::avg_predictions(m1f, newdata=subset(newdata_test, UASEvents == 1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredOp <- marginaleffects::avg_predictions(m1f, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "UASOperation",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                              re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredEnv <- marginaleffects::avg_predictions(m1f, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                                re_formula = NULL,
                                               allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredEvt <- marginaleffects::avg_predictions(m1f, newdata=subset(grid_marg,
                                                                 UASProximity=="Far" &
                                                                 UASOperation=="Overflight" &
                                                                   AmbientVariant=="Standard"),
                                            by=c("UASLAEMaxLRScl",
                                                 "AmbientEnvCore",
                                                 "UASEvents",
                                                 "UASOperation"),
                                            re_formula = NULL,
                                            allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                          transform=\(x) betaTransform(x, -10, 10,
                                                                       direction='reverse',
                                                                       squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredEvt2 <- marginaleffects::avg_predictions(m1f, newdata=subset(grid_marg2,
                                                                  UASProximity=="Far" &
                                                                  UASOperation=="Overflight" &
                                                                    AmbientVariant=="Standard"),
                                              by=c("UASLAEMaxLRScl",
                                                   "AmbientEnvCore",
                                                   "UASEvents",
                                                   "UASOperation"),
                                                re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                            transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredAtt <- marginaleffects::avg_predictions(m1f, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "AAM_attitude2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredAoR <- marginaleffects::avg_predictions(m1f, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Home_Area2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredScp <- marginaleffects::avg_predictions(m1f, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Area_soundscape2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredSex <- marginaleffects::avg_predictions(m1f, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Sex"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1fpredNat <- marginaleffects::avg_predictions(m1f, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "NationGeo2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

```

#### visualise plots of PA effects

```{R}

p1 <- ggplot(data=subset(m1fpredType, UASEvents==1)) +
               theme(panel.grid = element_blank(), aspect.ratio=1.35,
                     text = element_text(family = "serif", size=16),
                     axis.text=element_text(family = "serif", size=14)) +
               
               geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyanceMean,
                                                  colour=UASType, shape=UASType),
                          alpha=0.35, size=2) +
               
               geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASType),
                           alpha=0.15) +
               
               geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASType), linewidth=1) +
               
               scale_color_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
               scale_fill_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
               scale_shape_manual(values=c(10, 11, 12)) +
               
               guides(colour=guide_legend(title="UAS type", reverse=FALSE),
                      fill=guide_legend(title="UAS type", reverse=FALSE),
                      shape=guide_legend(title="UAS type", reverse=FALSE)) +
             
               rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                              stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
               
               scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-6, 8)) +
               
               labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance") +
               facet_wrap(vars(AmbientEnvCore))

p2 <- ggplot(data=subset(m1fpredOp, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                                                 colour=UASOperation, shape=UASOperation),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASOperation),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASOperation), linewidth=1) +
              
              scale_color_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(9, 6, 2)) +
              
              guides(colour=guide_legend(title="UAS operation", reverse=TRUE),
                     fill=guide_legend(title="UAS operation", reverse=TRUE),
                     shape=guide_legend(title="UAS operation", reverse=TRUE)) +
              
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance") +
              facet_grid(rows = vars(AmbientEnv))

p3 <- ggplot(data=subset(m1fpredEnv, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14),
                    axis.title.x=element_blank(),
                    axis.text.x=element_blank(),
                    axis.ticks.x=element_blank()) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyanceMean,
                                                 colour=AmbientEnvCore, shape=AmbientEnvCore),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AmbientEnvCore),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AmbientEnvCore), linewidth=1) +
              
              scale_color_viridis(option='magma', direction=-1, discrete=TRUE, begin=0.2, end=0.8) +
              scale_fill_viridis(option='magma', direction=-1, discrete=TRUE, begin=0.2, end=0.8) +
              scale_shape_manual(values=c(1, 3, 5, 7)) +
              
              guides(colour=guide_legend(title="Amb. env.", reverse=FALSE),
                     fill=guide_legend(title="Amb. env.", reverse=FALSE),
                     shape=guide_legend(title="Amb. env.", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(y="Mean change in annoyance")

p4 <- ggplot(data=subset(m1fpredEvt, AmbientEnv=='Park' & UASOperation=='Overflight')) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' & UASOperation=='Overflight'),
                         aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                             colour=factor(UASEvents), shape=factor(UASEvents)),
                         alpha=0.55, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=factor(UASEvents)),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=factor(UASEvents)), linewidth=1) +
              
              scale_color_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(4, 5, 7, 8)) +
              
              guides(colour=guide_legend(title="UAS events", reverse=TRUE),
                     fill=guide_legend(title="UAS events", reverse=TRUE),
                     shape=guide_legend(title="UAS events", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(min(2, min(m1fpredEvt$conf.low)), 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

(p1 | p2) + (p3 / p4)

filename <- "PtsABdAnnoyMnCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# add faint dashed grey major grid lines to p1, p2, p3, p4 and remove minor grid lines and point data
p1b <- p1 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                  panel.grid.minor = element_blank())
p1b <- gginnards::delete_layers(p1b, "GeomPoint")
p2b <- p2 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p2b <- gginnards::delete_layers(p2b, "GeomPoint")
p3b <- p3 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p3b <- gginnards::delete_layers(p3b, "GeomPoint")
p4b <- p4 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p4b <- gginnards::delete_layers(p4b, "GeomPoint")

(p1b | p2b) + (p3b / p4b)

filename <- "PtsABdAnnoyMnCatModGrid_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p3c <- p3 + theme(axis.title.x=element_text(family = "serif", size=14),
                  axis.text.x=element_text(family = "serif", size=14),
                  axis.ticks.x=element_line(colour="black", linewidth=1)) + 
        labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)))

filename <- "PtsABdAnnoyMnCatModEnv_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=5, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=5, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p5 <- ggplot(data=subset(m1fpredEvt2, UASOperation=="Overflight" & AmbientEnv=="Park")) +
              theme(panel.grid = element_blank(), aspect.ratio=0.8,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' &
                                       UASOperation=='Overflight' & SessionPart=='B'),
                         aes(x=UASEvents, y=dAnnoyMean,
                             colour=UASLAEMaxLR, shape=UASType),
                         alpha=0.35, size=2) +
  
              scale_color_viridis(option='inferno', direction=1, discrete=FALSE, begin = 0.2, end = 0.8,
                                  breaks=c(73, 79)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE)) +
  
              ggnewscale::new_scale_color() +
  
              geom_ribbon(aes(x=UASEvents, ymin=conf.low, ymax=conf.high, fill=factor(UASLAEMaxLRScl)),
                          alpha=0.05) +
  
              geom_line(aes(x=UASEvents, y=estimate, colour=factor(UASLAEMaxLRScl)), linewidth=1, alpha=0.5) +

              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_shape_manual(values=c(10, 11, 12)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     fill=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     shape=guide_legend(title="UAS type", reverse=FALSE)) +
            
              scale_x_continuous(breaks=c(1, 3, 5, 9), labels=c(1, 3, 5, 9)) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(2, 7)) +
              
              labs(x="Number of UAS Overflight events", y="Mean change in annoyance")

p5

filename <- "PtsABdAnnoyMnCatModEvt2_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p6 <- ggplot(data=m1fpredAtt) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AAM_attitude2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AAM_attitude2), linewidth=1) +
              
              scale_color_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="AAM attitude", reverse=TRUE),
                     fill=guide_legend(title="AAM attitude", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p7 <- ggplot(data=m1fpredAoR) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Home_Area2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Home_Area2), linewidth=1) +
              
              scale_color_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Area of residence", reverse=FALSE),
                     fill=guide_legend(title="Area of residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p8 <- ggplot(data=m1fpredScp) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Area_soundscape2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Area_soundscape2), linewidth=1) +
              
              scale_color_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Soundscape at residence", reverse=FALSE),
                     fill=guide_legend(title="Soundscape at residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p9 <- ggplot(data=m1fpredSex) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Sex), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Sex), linewidth=1) +
              
              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Sex", reverse=TRUE),
                     fill=guide_legend(title="Sex", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p10 <- ggplot(data=m1fpredNat) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=NationGeo2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=NationGeo2), linewidth=1) +
              
              scale_color_viridis(option='cividis', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='cividis', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="National region", reverse=TRUE),
                     fill=guide_legend(title="National region", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")


(p6 + p7 + p8) / (p9 + p10)

filename <- "PtsABdAnnoyMnAttAoRScpSexNatCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### visualise posterior distributions of group level effects

```{r}

m1f_sd_draws <- as.data.frame(m1f) %>%
    dplyr::select(starts_with("sd_")) %>%
    tidyr::pivot_longer(cols = everything(), names_to = "Parameter", values_to = "Value") %>%
    dplyr::mutate(Parameter = gsub("sd_", "", Parameter)) # Clean up label names

# 2. Plot using ridges with a shared x-axis and normalized curve heights
ggplot(m1f_sd_draws, aes(x = Value, y = Parameter, fill = Parameter)) +
     theme(legend.position = "none",
            panel.grid.major.y = element_blank(),
            text = element_text(family = "serif", size=16)) +
    # stat_density_ridges normalizes the peak height of each curve individually
    ggridges::stat_density_ridges(aes(height = after_stat(density)), 
                        geom = "density_ridges", 
                        alpha = 1, 
                        scale = 1.5,) + # Controls how much curves can overlap vertically
    # Adds the 50%, 89% and 95% credible intervals right beneath each curve
    tidybayes::stat_pointinterval(aes(y = as.numeric(as.factor(Parameter)) - 0.1), 
                       .width = c(0.5, 0.89, 0.95)) +
    scale_fill_manual(values = mycolours) +
    labs(x = "Estimated variation (sd scale)",
         y = "Group parameter")

filename <- "PtsABdAnnoyMnCatModSD_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### test relations

##### setup test grids

```{r}

contrast_grid_base <- marginaleffects::datagrid(
  newdata = base_unique,
  UASLAEMaxLRScl = c(as.numeric(levels(subjDataNoAmb.med$UASLAeq)), 65) + 10*log10(25),
  grid_type = "counterfactual"
)

grid_test <- contrast_grid_base[rep(seq_len(nrow(contrast_grid_base)), each = nnew_pred), ]
new_idx <- rep(seq_len(nnew_pred), times = nrow(contrast_grid_base))
grid_test$ID     <- paste0("new_id_", new_idx)
grid_test$StimID <- paste0("new_stim_", new_idx)

estimate_size_gb(grid_test, ndraws_pred, n_counterfactual_levels = 2)  # 2, since this is a comparison


```

##### run tests

```{r}

set.seed(999)
sex_contrast <- marginaleffects::avg_comparisons(
  m1f, variables = "Sex", newdata = grid_test,
  re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
  ndraws = ndraws_pred,
  transform = \(x) betaTransform(x, -10, 10, direction = 'reverse', squeeze = 'none')
)

```

## m4: maximal ordinal model for dAnnoyance, median imputed

### formula

```{R}

m4formula <- update(m0formula, dAnnoyanceOrd ~ . - SessionPart - TrialNumberScl +
                      PartTrialNumberScl)

# extract the data for the model
m4Data <- subjDataNoAmb.med[, all.vars(m4formula), drop=FALSE]

```

### run model 4

```{r}

emp_thresh4 <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb$dAnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh4 <- emp_thresh4[is.finite(emp_thresh4)]

priors4 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='PartTrialNumberScl'),
  brms::prior_string(paste0("normal(", emp_thresh4,", 1)"), class = "Intercept", coef = 1:length(emp_thresh4))
)


tic()
m4Priors <- brms::brm(m4formula,
                 data=m4Data,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr',
                 prior=priors4, control=list(adapt_delta=0.95),
                 sample_prior='only', seed=808,
                 chains=4, iter=1800, warmup=900)
toc()

m4_ppd <- ppd_ridgeplot(m4Priors, ndraws = 100)
m4_ppd

m4PriorCheck <- brms::pp_check(m4Priors, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance category index")
m4PriorCheck

tic()
m4 <- brms::brm(m4formula,
                 data=m4Data,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr',
                 prior=priors4, control=list(adapt_delta=0.95),
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m4 <- brms::add_criterion(m4, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m4$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m4))
m4$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m4, re_formula=NA))
m4$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m4, re_formula=NULL))
m4$criteria$bayes_R2_MZ <- as.data.frame(Bayes_R2_MZ(m4))

m4PostCheck <- brms::pp_check(m4, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance category index")
m4PostCheck

```

### analyse results

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m4_bCI_range <- bayestestR::hdi(m4, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m4_bCI_wsf <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASTypeM300", "b_UASTypeT150", 
                                 "b_UASOperationLanding", "b_UASOperationTakeoff",
                                 "b_AmbientEnvStreet"))
p_m4_bCI_wsf <- plot(m4_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wsf

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m4_bCI_wsfi <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvStreet:UASOperationLanding",
                                 "b_AmbientEnvStreet:UASOperationTakeoff",
                                 "b_AmbientEnvStreet:UASTypeM300",
                                 "b_AmbientEnvStreet:UASTypeT150",
                                 "b_UASOperationLanding:UASTypeM300",
                                 "b_UASOperationLanding:UASTypeT150"))
p_m4_bCI_wsfi <- plot(m4_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wsfi

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m4_bCI_wsc <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m4_bCI_wsc <- plot(m4_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wsc

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m4_bCI_wscfi <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvStreet",
                                 "b_UASLAEMaxLRScl:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:UASTypeM300",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeM300",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m4_bCI_wscfi <- plot(m4_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wscfi

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m4_bCI_bsf <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Uneventful"))
p_m4_bCI_bsf <- plot(m4_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_bsf

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m4_bCI_bsc <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NoiseSensitivity"))
p_m4_bCI_bsc <- plot(m4_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_bsc

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

## m5: omit stimID group effect from m3b

### Formula

```{R}

m5formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID)

```

### run model 5

```{R}

tic()
m5 <- brms::brm(brms::bf(m5formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m5 <- brms::add_criterion(m5, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m5$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m5))
m5$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m5, re_formula=NA))
m5$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m5, re_formula=NULL))

m5PostCheck <- brms::pp_check(m5, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m5PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)

m5_loo <- loo::loo_compare(m3b, m5, criterion='loo')
m5_loo

```

## m6: omit UASType group effect from m5

### Formula

```{R}

m6formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 6

```{R}

tic()
m6 <- brms::brm(brms::bf(m6formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m6 <- brms::add_criterion(m6, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m6$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m6))
m6$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m6, re_formula=NA))
m6$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m6, re_formula=NULL))

m6PostCheck <- brms::pp_check(m6, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m6PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)

m6_loo <- loo::loo_compare(m3b, m5, m6, criterion='loo')
m6_loo

```

## m7: omit UASLAEMaxLRScl group effect from m6

### Formula

```{R}

m7formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation | ID)

```

### run model 7

```{R}

tic()
m7 <- brms::brm(brms::bf(m7formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m7 <- brms::add_criterion(m7, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m7$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m7))
m7$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m7, re_formula=NA))
m7$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m7, re_formula=NULL))

m7PostCheck <- brms::pp_check(m7, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m7PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)
loo::loo(m7)


m7_loo <- loo::loo_compare(m3b, m5, m6, m7, criterion='loo')
m7_loo

loo::loo_compare(m6, m7, criterion='loo')

```

## m8: omit UASOperation group effect from m7

### Formula

```{R}

m8formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) | ID)

```

### run model 8

```{R}

tic()
m8 <- brms::brm(brms::bf(m8formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m8 <- brms::add_criterion(m8, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m8$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m8))
m8$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m8, re_formula=NA))
m8$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m8, re_formula=NULL))

m8PostCheck <- brms::pp_check(m8, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m8PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)
loo::loo(m7)
loo::loo(m8)


m8_loo <- loo::loo_compare(m3b, m5, m6, m7, m8, criterion='loo')
m8_loo

loo::loo_compare(m7, m8, criterion='loo')

```

## m8b: omit UASOperation group effect from m6

### Formula

```{R}

m8bformula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                     UASLAEMaxLRScl | ID)

```

### run model 8b

```{R}

tic()
m8b <- brms::brm(brms::bf(m8bformula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m8b <- brms::add_criterion(m8b, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m8b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m8b))
m8b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m8b, re_formula=NA))
m8b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m8b, re_formula=NULL))

m8bPostCheck <- brms::pp_check(m8b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m8bPostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)
loo::loo(m7)
loo::loo(m8)
loo::loo(m8b)


m8b_loo <- loo::loo_compare(m3b, m5, m6, m7, m8, m8b, criterion='loo')
m8b_loo

loo::loo_compare(m6, m8b, criterion='loo')

```

## m9: omit population interaction effects from m6

### Formula

```{R}

m9formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 9

```{R}

tic()
m9 <- brms::brm(brms::bf(m9formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m9 <- brms::add_criterion(m9, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m9$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m9))
m9$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m9, re_formula=NA))
m9$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m9, re_formula=NULL))

m9PostCheck <- brms::pp_check(m9, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m9PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)

m9_loo <- loo::loo_compare(m3b, m6, m9, criterion='loo')
m9_loo

loo::loo_compare(m6, m9, criterion='loo')

```

## m10: omit further population interaction effects from m9

### Formula

```{R}

m10formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*UASOperation +
                   AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 10

```{R}

tic()
m10 <- brms::brm(brms::bf(m10formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m10 <- brms::add_criterion(m10, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m10$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m10))
m10$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m10, re_formula=NA))
m10$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m10, re_formula=NULL))

m10PostCheck <- brms::pp_check(m10, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m10PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m10)

m10_loo <- loo::loo_compare(m3b, m6, m9, m10, criterion='loo')
m10_loo

loo::loo_compare(m9, m10, criterion='loo')

```

## m11: omit further population effects from m9

### Formula

```{R}

m11formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Sex + NoiseSensitivity +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 11

```{R}

tic()
m11 <- brms::brm(brms::bf(m11formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m11 <- brms::add_criterion(m11, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m11$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m11))
m11$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m11, re_formula=NA))
m11$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m11, re_formula=NULL))

m11PostCheck <- brms::pp_check(m11, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m11PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)

m11_loo <- loo::loo_compare(m3b, m6, m9, m11, criterion='loo')
m11_loo

loo::loo_compare(m9, m11, criterion='loo')

```

## m12: omit further population effects from m11

### Formula

```{R}

m12formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   Home_Area2 +
                   Sex + NoiseSensitivity +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 12

```{R}

tic()
m12 <- brms::brm(brms::bf(m12formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m12 <- brms::add_criterion(m12, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m12$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m12))
m12$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m12, re_formula=NA))
m12$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m12, re_formula=NULL))

m12PostCheck <- brms::pp_check(m12, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m12PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)
loo::loo(m12)

m12_loo <- loo::loo_compare(m3b, m6, m9, m11, m12, criterion='loo')
m12_loo

loo::loo_compare(m11, m12, criterion='loo')

```

## m13: omit further population effects from m12

### Formula

```{R}

m13formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   Sex +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 13

```{R}

tic()
m13 <- brms::brm(brms::bf(m13formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m13 <- brms::add_criterion(m13, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m13$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m13))
m13$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m13, re_formula=NA))
m13$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m13, re_formula=NULL))

m13PostCheck <- brms::pp_check(m13, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m13PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)
loo::loo(m12)
loo::loo(m13)

m13_loo <- loo::loo_compare(m3b, m6, m9, m11, m12, m13, criterion='loo')
m13_loo

loo::loo_compare(m12, m13, criterion='loo')

```

## m14: omit further population effects from m13

### Formula

```{R}

m14formula <- dAnnoyanceOrdBetaScl ~ 1 + PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 14

```{R}

tic()
m14 <- brms::brm(brms::bf(m14formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=1800, warmup=900)
toc()

tic()
m14 <- brms::add_criterion(m14, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m14$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m14))
m14$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m14, re_formula=NA))
m14$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m14, re_formula=NULL))

m14PostCheck <- brms::pp_check(m14, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m14PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)
loo::loo(m12)
loo::loo(m13)
loo::loo(m14)

m14_loo <- loo::loo_compare(m3b, m6, m9, m11, m12, m13, m14, criterion='loo')
m14_loo

loo::loo_compare(m13, m14, criterion='loo')

```









































