---
title: "REFMAP Listening test 1 analysis: Data analysis with bootstrap estimation (DABEST)"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook analyses the Part A and B data in terms of mean differences between groups using within-subjects paired analysis with bootstrap estimation of confidence intervals.

# Setup

## Load packages and set seed

```{r}
# load packages
library(tidyr)
library(unikn)
library(ggplot2)
library(dabestr)

# set random seed
set.seed(303)

# save plots toggle
saveplots = FALSE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption="Select output folder to save plots")
}
```

## Import data and wrangle

```{r}

subjLongDataApath <- utils::choose.files(caption=r"(Select refmap_listest1_testdataA_BySubj.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                         filters=matrix(data=c("refmap_listest1_testdataA_BySubj.csv", "refmap_listest1_testdataA_BySubj.csv"), ncol=2))

subjLongDataA <- read.csv(subjLongDataApath, header=TRUE)

dfA <- subjLongDataA[c('ID.', 'Recording', 'AmbientEnv', 'UASLAeq', 'SNRlevel', 'UASOperation', 'UASType', 'Annoyance')]

UASLAeqCatsA <- c("No UAS", "42", "48", "54", "60")
SNRCatsA <- c("No UAS", "-16", "-10", "-4", "2", "8")
UASOpCatsA <- c("No UAS", "Flyby", "Landing", "Takeoff")
UASTypeCatsA <- c("No UAS", "H520", "M300", "T150")

dfA$ID. <- factor(dfA$ID.)
dfA$AmbientEnv <- factor(dfA$AmbientEnv)
dfA$UASLAeq <- factor(dfA$UASLAeq, levels=UASLAeqCatsA, order=TRUE)
dfA$SNRlevel <- factor(dfA$SNRlevel, levels=SNRCatsA, order=TRUE)
dfA$UASOperation <- factor(dfA$UASOperation, levels=UASOpCatsA)
dfA$UASType <- factor(dfA$UASType, levels=UASTypeCatsA)

subjLongDataBpath <- utils::choose.files(caption=r"(Select refmap_listest1_testdataB_BySubj.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                         filters=matrix(data=c("refmap_listest1_testdataB_BySubj.csv", "refmap_listest1_testdataB_BySubj.csv"), ncol=2))

subjLongDataB <- read.csv(subjLongDataBpath, header=TRUE)

dfB <- subjLongDataB[c('ID.', 'Recording', 'UASLAeq', 'UASEvents', 'SNRlevel', 'UASType', 'Annoyance')]

UASLAeqCatsB <- c("No UAS", "54", "60")
SNRCatsB <- c("No UAS", "2", "8")
UASTypeCatsB <- c("No UAS", "H520", "T150")

dfB$ID. <- factor(dfB$ID.)
dfB$UASLAeq <- factor(dfB$UASLAeq, levels=UASLAeqCatsB, order=TRUE)
dfB$SNRlevel <- factor(dfB$SNRlevel, levels=SNRCatsB, order=TRUE)
dfB$UASType <- factor(dfB$UASType, levels=UASTypeCatsB)

```

Test for differences between the response to the propagated flyover vs power-scaled flyover:

```{r}

# select all flyover level 2 data
dfA_F_2 <- dfA[grep(pattern="F_2", dfA$Recording),]

dfA_F_2[, 'LvlType'] <- "Modelled"

dfA_F_2$LvlType[grep(pattern="PwrScale", dfA_F_2$Recording)] <- "Scaled"

# assign to processor

dbA_F_2 <- dabestr::load(dfA_F_2,
                         x = LvlType, y = Annoyance,
                         idx = c("Modelled", "Scaled"),
                         paired = "baseline", id_col = ID., colour=AmbientEnv)

dbA_F_2.dmean <- dabestr::mean_diff(dbA_F_2, perm_count=5000)

dbA_F_2_pltmean <- dabestr::dabest_plot(dbA_F_2.dmean, custom_palette='igv',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings", )


if (saveplots){
  svg(filename=file.path(outFigPath, "PtAFlyScaleDabest.svg"), family='serif', width=6, height=5)
  dbA_F_2_pltmean
  dump <- dev.off()
}

dbA_F_2_pltmean
```

Test for differences in Part A between UAS types, segregating by ambient environment.

```{r}
dfA_Park <- dfA[dfA$AmbientEnv == 'Park',]
dfA_Street <- dfA[dfA$AmbientEnv == 'Street',]

dbA_TypePk <- dabestr::load(dfA_Park,
                            x = UASType, y = Annoyance,
                            idx = c("H520", "M300", "T150"),
                            paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_TypePk.dmean <- dabestr::mean_diff(dbA_TypePk, perm_count=5000)

dbA_TypePk_pltmean <- dabestr::dabest_plot(dbA_TypePk.dmean, custom_palette='d3',
                                           raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                           swarm_label="Annoyance ratings",
                                           contrast_ylim=c(-1, 0.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtATypeParkDabest.svg"), family='serif', width=6, height=7.5)
  dbA_TypePk_pltmean
  dump <- dev.off()
}

dbA_TypeSt <- load(dfA_Street,
                   x = UASType, y = Annoyance,
                   idx = c("H520", "M300", "T150"),
                   paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_TypeSt.dmean <- dabestr::mean_diff(dbA_TypeSt, perm_count=5000)

dbA_TypeSt_pltmean <- dabestr::dabest_plot(dbA_TypeSt.dmean, custom_palette='d3',
                                           raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                           swarm_label="Annoyance ratings",
                                           contrast_ylim=c(-1, 0.5))


if (saveplots){
  svg(filename=file.path(outFigPath, "PtATypeStreetDabest.svg"), family='serif', width=6, height=7.5)
  dbA_TypeSt_pltmean
  dump <- dev.off()
}

dbA_TypePk_pltmean
dbA_TypeSt_pltmean

```

Re-test for differences between UAS types, with only top two UAS sound levels

```{r}

dbA_TypePkHi <- dabestr::load(dfA_Park[dfA_Park$UASLAeq %in% c(60), ],
                              x = UASType, y = Annoyance,
                              idx = c("H520", "M300", "T150"),
                              paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_TypePkHi.dmean <- dabestr::mean_diff(dbA_TypePkHi, perm_count=5000)

dbA_TypePkHi_pltmean <- dabestr::dabest_plot(dbA_TypePkHi.dmean, custom_palette='d3',
                                             raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                             swarm_label="Annoyance ratings",
                                             contrast_ylim=c(-2, 0.5))
if (saveplots){
  svg(filename=file.path(outFigPath, "PtATypeParkHiDabest.svg"), family='serif', width=6, height=7.5)
  dbA_TypePkHi_pltmean
  dump <- dev.off()
}

dbA_TypeStHi <- load(dfA_Street[dfA_Street$UASLAeq %in% c(60), ],
                      x = UASType, y = Annoyance,
                      idx = c("H520", "M300", "T150"),
                      paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_TypeStHi.dmean <- dabestr::mean_diff(dbA_TypeStHi, perm_count=5000)

dbA_TypeStHi_pltmean <- dabestr::dabest_plot(dbA_TypeStHi.dmean, custom_palette='d3',
                                              raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                              swarm_label="Annoyance ratings",
                                              contrast_ylim=c(-2, 0.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtATypeStreetHiDabest.svg"), family='serif', width=6, height=7.5)
  dbA_TypeStHi_pltmean
  dump <- dev.off()
}

dbA_TypePkHi_pltmean
dbA_TypeStHi_pltmean

```

Test for differences between UAS operations, segregating by ambient environment.

```{r}

dbA_OpPk <- dabestr::load(dfA_Park[!grepl(pattern="PwrScale", dfA_Park$Recording),],
                          x = UASOperation, y = Annoyance,
                          idx = c("Flyby", "Landing", "Takeoff"),
                          paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_OpPk.dmean <- dabestr::mean_diff(dbA_OpPk, perm_count=5000)

dbA_OpPk_pltmean <- dabestr::dabest_plot(dbA_OpPk.dmean, custom_palette='d3',
                                         raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                         swarm_label="Annoyance ratings",
                                         contrast_ylim=c(-0.5, 1))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtAOpParkDabest.svg"), family='serif', width=6, height=7.5)
  dbA_OpPk_pltmean
  dump <- dev.off()
}

dbA_OpSt <- load(dfA_Street[!grepl(pattern="PwrScale", dfA_Street$Recording),],
                 x = UASOperation, y = Annoyance,
                 idx = c("Flyby", "Landing", "Takeoff"),
                 paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_OpSt.dmean <- dabestr::mean_diff(dbA_OpSt, perm_count=5000)

dbA_OpSt_pltmean <- dabestr::dabest_plot(dbA_OpSt.dmean, custom_palette='d3',
                                         raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                         swarm_label="Annoyance ratings",
                                         contrast_ylim=c(-0.5, 1))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtAOpStreetDabest.svg"), family='serif', width=6, height=7.5)
  dbA_OpSt_pltmean
  dump <- dev.off()
}

dbA_OpPk_pltmean
dbA_OpSt_pltmean

```

Again, filtering for only the top UAS level:

```{r}

dbA_OpPkHi <- dabestr::load(dfA_Park[!grepl(pattern="PwrScale", dfA_Park$Recording) & dfA_Park$UASLAeq %in% c(60),],
                            x = UASOperation, y = Annoyance,
                            idx = c("Flyby", "Landing", "Takeoff"),
                            paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_OpPkHi.dmean <- dabestr::mean_diff(dbA_OpPkHi, perm_count=5000)

dbA_OpPkHi_pltmean <- dabestr::dabest_plot(dbA_OpPkHi.dmean, custom_palette='d3',
                                           raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                           swarm_label="Annoyance ratings",
                                           contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtAOpParkHiDabest.svg"), family='serif', width=6, height=7.5)
  dbA_OpPkHi_pltmean
  dump <- dev.off()
}

dbA_OpStHi <- load(dfA_Street[!grepl(pattern="PwrScale", dfA_Street$Recording) & dfA_Street$UASLAeq %in% c(60), ],
                   x = UASOperation, y = Annoyance,
                   idx = c("Flyby", "Landing", "Takeoff"),
                   paired = "baseline", id_col = ID., colour=UASLAeq)

dbA_OpStHi.dmean <- dabestr::mean_diff(dbA_OpStHi, perm_count=5000)

dbA_OpStHi_pltmean <- dabestr::dabest_plot(dbA_OpStHi.dmean, custom_palette='d3',
                                           raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                           swarm_label="Annoyance ratings",
                                           contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtAOpStreetHiDabest.svg"), family='serif', width=6, height=7.5)
  dbA_OpStHi_pltmean
  dump <- dev.off()
}

dbA_OpPkHi_pltmean
dbA_OpStHi_pltmean

```

Test for differences in Part B for varying event numbers, segregated by UAS type

```{r}
dfB_H520 <- dfB[dfB$UASType == 'H520',]
dfB_T150 <- dfB[dfB$UASType == 'T150',]

dbB_TypeH520b <- dabestr::load(dfB_H520,
                               x = UASEvents, y = Annoyance,
                               idx = c(1, 3, 5, 9),
                               paired = "baseline", id_col = ID., colour=UASLAeq)

dbB_TypeH520s <- dabestr::load(dfB_H520,
                               x = UASEvents, y = Annoyance,
                               idx = c(1, 3, 5, 9),
                               paired = "sequential", id_col = ID., colour=UASLAeq)

dbB_TypeH520b.dmean <- dabestr::mean_diff(dbB_TypeH520b, perm_count=5000)
dbB_TypeH520s.dmean <- dabestr::mean_diff(dbB_TypeH520s, perm_count=5000)

dbB_TypeH520b_pltmean <- dabestr::dabest_plot(dbB_TypeH520b.dmean, custom_palette='d3',
                                              raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                              swarm_label="Annoyance ratings",
                                              contrast_ylim=c(-1, 2.5))
dbB_TypeH520s_pltmean <- dabestr::dabest_plot(dbB_TypeH520s.dmean, custom_palette='d3',
                                              raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                              swarm_label="Annoyance ratings",
                                              contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtBTypeH520DabestBase.svg"), family='serif', width=6, height=7.5)
  dbB_TypeH520b_pltmean
  dump <- dev.off()


  svg(filename=file.path(outFigPath, "PtBTypeH520DabestSeq.svg"), family='serif', width=6, height=7.5)
  dbB_TypeH520s_pltmean
  dump <- dev.off()
}

dbB_TypeT150b <- load(dfB_T150,
                      x = UASEvents, y = Annoyance,
                      idx = c(1, 3, 5, 9),
                      paired = "baseline", id_col = ID., colour=UASLAeq)

dbB_TypeT150s <- load(dfB_T150,
                      x = UASEvents, y = Annoyance,
                      idx = c(1, 3, 5, 9),
                      paired = "sequential", id_col = ID., colour=UASLAeq)

dbB_TypeT150b.dmean <- dabestr::mean_diff(dbB_TypeT150b, perm_count=5000)
dbB_TypeT150s.dmean <- dabestr::mean_diff(dbB_TypeT150s, perm_count=5000)

dbB_TypeT150b_pltmean <- dabestr::dabest_plot(dbB_TypeT150b.dmean, custom_palette='d3',
                                              raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                              swarm_label="Annoyance ratings",
                                              contrast_ylim=c(-1, 2.5))

dbB_TypeT150s_pltmean <- dabestr::dabest_plot(dbB_Type_T150s.dmean, custom_palette='d3',
                                              raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                              swarm_label="Annoyance ratings",
                                              contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtBTypeT150DabestBase.svg"), family='serif', width=6, height=7.5)
  dbB_TypeT150b_pltmean
  dump <- dev.off()
  
  svg(filename=file.path(outFigPath, "PtBTypeT150DabestSeq.svg"), family='serif', width=6, height=7.5)
  dbB_TypeT150s_pltmean
  dump <- dev.off()
}

dbB_TypeH520b_pltmean
dbB_TypeH520s_pltmean
dbB_TypeT150b_pltmean
dbB_TypeT150s_pltmean

```
Test for differences in Part B for varying event numbers, segregated by UAS LAeq

```{r}
dfB_54 <- dfB[dfB$UASLAeq == '54',]
dfB_60 <- dfB[dfB$UASLAeq == '60',]

dbB_54b <- dabestr::load(dfB_54,
                         x = UASEvents, y = Annoyance,
                         idx = c(1, 3, 5, 9),
                         paired = "baseline", id_col = ID., colour=UASType)

dbB_54s <- dabestr::load(dfB_54,
                         x = UASEvents, y = Annoyance,
                         idx = c(1, 3, 5, 9),
                         paired = "sequential", id_col = ID., colour=UASType)

dbB_54b.dmean <- dabestr::mean_diff(dbB_54b, perm_count=5000)
dbB_54s.dmean <- dabestr::mean_diff(dbB_54s, perm_count=5000)

dbB_54b_pltmean <- dabestr::dabest_plot(dbB_54b.dmean, custom_palette='d3',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings",
                                        contrast_ylim=c(-1, 2.5))
dbB_54s_pltmean <- dabestr::dabest_plot(dbB_54s.dmean, custom_palette='d3',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings",
                                        contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtB54DabestBase.svg"), family='serif', width=6, height=7.5)
  dbB_54b_pltmean
  dump <- dev.off()
  
  svg(filename=file.path(outFigPath, "PtB54DabestSeq.svg"), family='serif', width=6, height=7.5)
  dbB_54s_pltmean
  dump <- dev.off()
}

dbB_60b <- load(dfB_60,
                x = UASEvents, y = Annoyance,
                idx = c(1, 3, 5, 9),
                paired = "baseline", id_col = ID., colour=UASType)

dbB_60s <- load(dfB_60,
                x = UASEvents, y = Annoyance,
                idx = c(1, 3, 5, 9),
                paired = "sequential", id_col = ID., colour=UASType)

dbB_60b.dmean <- dabestr::mean_diff(dbB_60b, perm_count=5000)
dbB_60s.dmean <- dabestr::mean_diff(dbB_60s, perm_count=5000)

dbB_60b_pltmean <- dabestr::dabest_plot(dbB_60b.dmean, custom_palette='d3',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings",
                                        contrast_ylim=c(-1, 2.5))

dbB_60s_pltmean <- dabestr::dabest_plot(dbB_60s.dmean, custom_palette='d3',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings",
                                        contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtB60DabestBase.svg"), family='serif', width=6, height=7.5)
  dbB_60b_pltmean
  dump <- dev.off()
  
  svg(filename=file.path(outFigPath, "PtB60DabestSeq.svg"), family='serif', width=6, height=7.5)
  dbB_60s_pltmean
  dump <- dev.off()
}

dbB_54b_pltmean
dbB_54s_pltmean
dbB_60b_pltmean
dbB_60s_pltmean

```

Test for differences in Part B for varying event numbers, unsegregated

```{r}
dbB_b <- dabestr::load(dfB,
                         x = UASEvents, y = Annoyance,
                         idx = c(1, 3, 5, 9),
                         paired = "baseline", id_col = ID., colour=UASLAeq)

dbB_s <- dabestr::load(dfB,
                         x = UASEvents, y = Annoyance,
                         idx = c(1, 3, 5, 9),
                         paired = "sequential", id_col = ID., colour=UASLAeq)

dbB_b.dmean <- dabestr::mean_diff(dbB_b, perm_count=5000)
dbB_s.dmean <- dabestr::mean_diff(dbB_s, perm_count=5000)

dbB_b_pltmean <- dabestr::dabest_plot(dbB_b.dmean, custom_palette='d3',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings",
                                        contrast_ylim=c(-1, 2.5))
dbB_s_pltmean <- dabestr::dabest_plot(dbB_s.dmean, custom_palette='d3',
                                        raw_marker_size = 0.5, raw_marker_alpha = 0.3,
                                        swarm_label="Annoyance ratings",
                                        contrast_ylim=c(-1, 2.5))

if (saveplots){
  svg(filename=file.path(outFigPath, "PtBDabestBase.svg"), family='serif', width=6, height=7.5)
  dbB_b_pltmean
  dump <- dev.off()
  
  svg(filename=file.path(outFigPath, "PtBDabestSeq.svg"), family='serif', width=6, height=7.5)
  dbB_s_pltmean
  dump <- dev.off()
}

dbB_b_pltmean
dbB_s_pltmean
```