---
title: "REFMAP Listening test 2 analysis: Random forest variable importance identification"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook analyses both parts of the data in terms of variable importance, using a random forest model based on conditional inference trees and a conditional permutation variable importance algorithm.

# Setup

## Load packages

```{r}
# load packages
library(tidyr)
library(ggplot2)
library(party)
library(conflicted)
library(tidyverse)
library(openxlsx2)
library(caret)
library(viridis)
library(cowplot)
library(permimp)
# set package parameters
theme_set(theme_bw())

```

```{r}

# plot colour scheme

mycolourlist = list(c(0, 102, 255), c(0, 204, 153), c(255, 0, 102), c(74, 111, 152), c(251, 164, 49), c(204, 153, 255), c(90, 192, 255), c(80, 245, 233), c(255, 90, 192), c(164, 201, 242), c(255, 254, 139), c(255, 243, 255))
mycolours = matrix()

for (ii in 1:length(mycolourlist)){
  mycolours[ii] = rgb(mycolourlist[[ii]][1]/255,
                      mycolourlist[[ii]][2]/255,
                      mycolourlist[[ii]][3]/255)
}

# toggle to save plots
saveplots = TRUE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption="Select output folder to save plots '03 Experiment\\Experiment 2\\Analysis\\Plots'")
  
  if (!dir.exists(file.path(outFigPath, "svg"))){dir.create(file.path(outFigPath, "svg"))}
  if (!dir.exists(file.path(outFigPath, "pdf"))){dir.create(file.path(outFigPath, "pdf"))}
  
}

# toggle to save data
savedata = TRUE

if (savedata){
  # set output plot directory
  if (saveplots==FALSE){
    choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  }
  outDataPath <- utils::choose.dir(caption="Select output folder to save data '03 Experiment\\Experiment 2\\Analysis\\R'")
}
 

```

# Import data and wrangle

```{r}

stimDatapath <- utils::choose.files(caption=r"(Select refmap_listest2_testdata_ByStim.csv from 03 Experiment\Experiment 2\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest2_testdata_ByStim.csv", "refmap_listest2_testdata_ByStim.csv"), ncol=2))

stimData <- utils::read.csv(stimDatapath, header=TRUE)

colnames(stimData)[1] <- "Stimulus"

# make response proportions into percentages
stimData[['HighAnnoyPc']] <- stimData[['HighlyAnnoyedProp']]*100
stimData[['dHighAnnoyPc']] <- stimData[['dHighlyAnnoyedProp']]*100

```

The aggregated data by stimulus are assigned to a dataframe, relevant categorical variables are converted to ordinal, and then the variable subset of interest is selected, NA rows dropped (ie, the 'Baseline' stimuli, as the conditional variable importance algorithm cannot currently handle NA values, which are present in all the UAS dB metrics), and a formula assigned.

```{r}

stimDataUAS <- cbind(Stimulus = stimData[, "Stimulus"],
                     UASEvents = stimData[, "UASEvents"],
                     stimData[, which(colnames(stimData)=="UASLAeqMaxLR"):
                                which(colnames(stimData)=="UASLoudISO305Ex")],
                     stimData[, which(colnames(stimData)=="UASTonalECMAAvg"):
                                which(colnames(stimData)=="UASSharpvBISO105Ex")],
                     stimData[, which(colnames(stimData)=="UASImpulsSHMPowAvg"):
                                which(colnames(stimData)=="UASPsychAnnoyBoucher")],
                     stimData[, which(colnames(stimData)=="IntermitRatioC2MaxLR"):
                                which(colnames(stimData)=="IntermitRatioC5MaxLR")],
                     stimData[, which(colnames(stimData)=="LAeqLAF90diff"):
                                which(colnames(stimData)=="dPsychAnnoyBoucher")],
                     stimData[, which(colnames(stimData)=="AnnoyanceMean"):
                                which(colnames(stimData)=="dHighAnnoyPc")])

stimDataAmb <- cbind(Stimulus = stimData[, "Stimulus"],
                     UASEvents = stimData[, "UASEvents"],
                     stimData[, which(colnames(stimData)=="AmbLAeqMaxLR"):
                                which(colnames(stimData)=="AmbLoudISO305Ex")],
                     stimData[, which(colnames(stimData)=="AmbTonalECMAAvg"):
                                which(colnames(stimData)=="AmbSharpvBISO105Ex")],
                     stimData[, which(colnames(stimData)=="AmbImpulsSHMPowAvg"):
                                which(colnames(stimData)=="AmbPsychAnnoyBoucher")],
                     stimData[, which(colnames(stimData)=="AnnoyanceMean"):
                                which(colnames(stimData)=="dHighAnnoyPc")])


# omit ambient-only stimuli
stimDataUAS <- stimDataUAS |> dplyr::filter(UASEvents != 0)



```

## Load existing results files (if wanted)

```{r}

loadExisting <- FALSE

if (loadExisting){
  # annoy mean results
  resdAnnoyMnFit <- utils::read.csv(file.path(outDataPath, "\\CRFdAnnoyMnOOBFit.csv"), sep = ",", row.names=1)
  
  resdAnnoyMnPermImp <- list()
  wb <- openxlsx2::wb_load(file.path(outDataPath, "\\CRFdAnnoyMnConPermimp.xlsx"))
  sheetNames<- wb_get_sheet_names(wb)

  for (sheet in sheetNames){
    col_name <- names(openxlsx2::wb_to_df(wb, sheet, row_names=TRUE))
    resdAnnoyMnPermImp[[col_name]] <- openxlsx2::wb_to_df(wb, sheet, row_names=TRUE)
  }
  
  # high annoyance results
  resdHiAnnoyFit <- utils::read.csv(file.path(outDataPath, "\\CRFdHiAnnoyOOBFit.csv"), sep = ",", row.names=1)
  
  resdHiAnnoyPermImp <- list()
  wb <- openxlsx2::wb_load(file.path(outDataPath, "\\CRFdHiAnnoyConPermimp.xlsx"))
  sheetNames<- wb_get_sheet_names(wb)

  for (sheet in sheetNames){
    col_name <- names(openxlsx2::wb_to_df(wb, sheet, row_names=TRUE))
    resdHiAnnoyPermImp[[col_name]] <- openxlsx2::wb_to_df(wb, sheet, row_names=TRUE)
  }
}

```

# Random forest functions

Write a function to train a conditional-inference random forest (crf) model on input data according to input formula, iterate over input random seeds, average error and variable importance metrics, and output metrics with plotted

## Averaging over multiple random seeds

```{r}

multi_crfReg <- function(dataIn, iVars, dVar, seeds, ntree, mtry, permImpCondThres=0.95, minsplit=20, minbucket=7, nperm=1){
  # initialise variables
  crfOOBErrAll <- 0
  crfOOBRMSE <- 0
  crfOOBMAE <- 0
  crfOOBErrR2 <- 0
  crfMarPermImpVals <- 0
  crfConPermImpVals <- 0
  crfMarPermImpValsPerTree <- data.frame()
  crfConPermImpValsPerTree <- data.frame()
  
  for (iters in 1:length(seeds)){
    
    # formula for regression
    formVars <- reformulate(iVars, dVar)
    
    # set random seed
    set.seed(seeds[iters])
    # train crf model
    crfModel <- party::cforest(formVars, data=dataIn,
                               controls=party::cforest_unbiased(ntree=ntree,
                                                                mtry=mtry,
                                                                minsplit=minsplit,
                                                                minbucket=minbucket))
    
    # get OOB predictions
    crfModelOOB <- predict(crfModel, OOB=TRUE, type='response')
    
    # get OOB error
    crfModelOOBErr <- as.numeric(as.matrix(as.numeric(as.matrix(crfModelOOB))
                                           - as.numeric(as.matrix(crfModel@data@env$response[[names(crfModel@data@env$response)]]))))

    # OOB RMSE, MAE and Rsquared
    crfOOBRMSE <- crfOOBRMSE + sqrt(mean(crfModelOOBErr^2))
    crfOOBMAE <- crfOOBMAE + mean(abs(crfModelOOBErr))
    crfOOBErrR2 <- crfOOBErrR2 + cor(as.numeric(as.matrix(crfModelOOB)),
                                     as.numeric(as.matrix(crfModel@data@env$response[[names(crfModel@data@env$response)]])))^2

    # set random seed
    set.seed(seeds[iters])

    # set random seed
    set.seed(seeds[iters])
    # conditional variable permutation importance
    crfConPermImp <- permimp::permimp(crfModel, nperm=nperm, conditional=TRUE, threshold=permImpCondThres, progressBar=FALSE)
    
    crfConPermImpVals <- crfConPermImpVals + crfConPermImp$values
    crfConPermImpValsPerTree <- rbind(crfConPermImpValsPerTree, crfConPermImp$perTree)
  }
  
  # average metrics
  crfOOBErrAll <- crfOOBErrAll/length(seeds)
  crfOOBRMSE <- crfOOBRMSE/length(seeds)
  crfOOBMAE <- crfOOBMAE/length(seeds)
  crfOOBErrR2 <- crfOOBErrR2/length(seeds)
  crfConPermImpVals <- data.frame(CondPermImp=sort(crfConPermImpVals/length(seeds), decreasing=TRUE))
  crfConPermImpValsQtl <- data.frame(apply(crfConPermImpValsPerTree, 2, quantile, probs=c(0.25, 0.50, 0.75)))
  
  resultsOut <- list('OOB_RMSE'=crfOOBRMSE, 'OOB_MAE'=crfOOBMAE, 'Rsquared'=crfOOBErrR2, 'conditional_permimp'=crfConPermImpVals,                      'conditional_permimp_perTree'=crfConPermImpValsPerTree, 'conditional_permimp_qtl'=crfConPermImpValsQtl)
  return(resultsOut)
}

```

## Comparing rankings from two seeds 

```{r}

crfReg <- function(dataIn, iVars, dVar, seeds, ntree, mtry, permImpCondThres=0.95, minsplit=20, minbucket=7, nperm=1){
  # initialise variables
  crfOOBErrAll <- 0
  crfOOBRMSE <- 0
  crfOOBMAE <- 0
  crfOOBErrR2 <- 0
  crfMarPermImpVals <- 0
  crfConPermImpVals <- 0
  crfMarPermImpValsPerTree <- data.frame()
  crfConPermImpValsPerTree <- data.frame()

  # formula for regression
  formVars <- reformulate(iVars, dVar)
  
  for (iters in 1:length(seeds)){
  
    # set random seed
    set.seed(seeds[iters])
    # train crf model
    crfModel <- party::cforest(formVars, data=dataIn,
                               controls=party::cforest_unbiased(ntree=ntree,
                                                                mtry=mtry,
                                                                minsplit=minsplit,
                                                                minbucket=minbucket))
    
    # conditional variable permutation importance
    crfConPermImp <- permimp::permimp(crfModel, nperm=nperm, conditional=TRUE, threshold=permImpCondThres, progressBar=FALSE)
    
    crfConPermImpVals <- crfConPermImp$values
    
    if (iters == 1){
      crfConPermImpVals1 <- data.frame(CondPermImp=sort(crfConPermImpVals, decreasing=TRUE))
      crfConPermImpValsPerTree1 <- crfConPermImp$perTree
      crfConPermImpValsQtl1 <- data.frame(apply(crfConPermImpValsPerTree1, 2, quantile, probs=c(0.25, 0.50, 0.75)))
      
      # get OOB predictions
      crfModelOOB <- predict(crfModel, OOB=TRUE, type='response')
      
      # get OOB error
      crfModelOOBErr <- as.numeric(as.matrix(as.numeric(as.matrix(crfModelOOB))
                                              - as.numeric(as.matrix(crfModel@data@env$response[[names(crfModel@data@env$response)]]))))
      
      # OOB RMSE, error quartiles and Rsquared
      crfOOBRMSE <- sqrt(mean(crfModelOOBErr^2))
      crfOOBMAE <- crfOOBMAE + mean(abs(crfModelOOBErr))
      crfOOBErrR2 <- cor(as.numeric(as.matrix(crfModelOOB)),
                                    as.numeric(as.matrix(crfModel@data@env$response[[names(crfModel@data@env$response)]])))^2

      }
    
    else{
      crfConPermImpValsN <- data.frame(CondPermImp=sort(crfConPermImpVals, decreasing=TRUE))
      
      nVarImpChecks <- min(max(sum(crfConPermImpVals1 >= crfConPermImpVals1$CondPermImp[1]*0.1),
                               sum(crfConPermImpValsN >= crfConPermImpValsN$CondPermImp[1]*0.1)), 4)  # number of variable importance values with a value at least 10% of the highest importance
      if (sum(rownames(crfConPermImpVals1)[1:nVarImpChecks] != rownames(crfConPermImpValsN)[1:nVarImpChecks]) > 0){
        warning("Permutation importance rank order within 10% of max differs between seeds: increase number of trees ('ntree') or number of permutations ('nperm'), or subsample of features ('mtry')")
      }
      else{
        resultsOut <- list('OOB_errors'=crfModelOOBErr, 'OOB_RMSE'=crfOOBRMSE, 'OOB_MAE'=crfOOBMAE, 'Rsquared'=crfOOBErrR2, 'conditional_permimp'=crfConPermImpVals1, 'conditional_permimp_perTree'=crfConPermImpValsPerTree1, 'conditional_permpimp_qtl'=crfConPermImpValsQtl1)
        return(resultsOut)
      }
      
    }
    
  }

}

```

## Hyperparameter tuning

```{r, fig.width=12, fig.height=4}
mtryTune <- function(dataIn, iVars, dVar, seeds, ntrees, minsplit=20, minbucket=7){

  formVars <- reformulate(iVars, dVar)
  
  # set mtry values and corresponding iVars/mtry ratios
  if (length(iVars) > 9){
    iVars_mtrys <- c(10.5, 5.25, 3.5, 2.75, 2.25, 1.75, 1.5, 1.25)
    mtrys <- as.integer(length(iVars)/iVars_mtrys)
  }
  else{
    mtrys <- seq(2, length(iVars) - 3, by=1)
    iVars_mtrys <- length(iVars)/mtrys
  }
  iVars_mtrys <- iVars_mtrys[mtrys >= 2]  # remove 0 or 1 values
  mtrys <- mtrys[mtrys >= 2]  # remove 0 or 1 values
  
  # remove any duplicated values
  iVars_mtrys <- iVars_mtrys[!(duplicated(mtrys) | duplicated(mtrys, fromLast = TRUE))]
  mtrys <- mtrys[!(duplicated(mtrys) | duplicated(mtrys, fromLast = TRUE))]

  # ensure mtrys is less than length(iVars)
  iVars_mtrys <- iVars_mtrys[mtrys < length(iVars)]
  mtrys <- mtrys[mtrys < length(iVars)]

  resRMSEMap = matrix(data=0, nrow=length(mtrys), ncol=length(ntrees))
  resRsquaredMap = matrix(data=0, nrow=length(mtrys), ncol=length(ntrees))
  resMAEMap = matrix(data=0, nrow=length(mtrys), ncol=length(ntrees))
  
  
  for (ii in seq(1, length(ntrees))){
    
    tuneMod.results <- data.frame(RMSE=numeric(length(mtrys)),
                                Rsquared=numeric(length(mtrys)),
                                MAE=numeric(length(mtrys)))
    
    for (seed in seeds){
      set.seed(seed)
      ntree = ntrees[ii]
      tuneMod <- caret::train(formVars,
                              data=dataIn,
                              method='cforest',
                              controls=party::cforest_unbiased(ntree=ntree,
                                                               minsplit=minsplit,
                                                               minbucket=minbucket),
                              tuneGrid=data.frame(.mtry=mtrys),
                              trControl = trainControl(method = "oob"))
      
      
      
      # accumulate results
      resRMSEMap[, ii] <- resRMSEMap[, ii] + tuneMod$results$RMSE
      resRsquaredMap[, ii] <- resRsquaredMap[, ii] + tuneMod$results$Rsquared
      resMAEMap[, ii] <- resMAEMap[, ii] + tuneMod$results$MAE
      
      tuneMod.results <- tuneMod.results + tuneMod$results[, which(names(tuneMod$results) != 'mtry')]
    }

    # average results
    tuneMod.results <- tuneMod.results/length(seeds)
    tuneMod.results <- cbind(tuneMod.results, data.frame(mtry=mtrys), data.frame(iVars_mtry=iVars_mtrys))

    print(tuneMod.results)

  }
  
  # average results
  resRMSEMap <- resRMSEMap/length(seeds)
  resRsquaredMap <- resRsquaredMap/length(seeds)
  resMAEMap <- resMAEMap/length(seeds)
  
  
  # convert to data frames with mtry as row names and ntree as column names, and convert to long format using tidyverse
  resdfRMSEMap <- as.data.frame(resRMSEMap)
  rownames(resdfRMSEMap) <- mtrys
  colnames(resdfRMSEMap) <- ntrees
  resdfRsquaredMap <- as.data.frame(resRsquaredMap)
  rownames(resdfRsquaredMap) <- mtrys
  colnames(resdfRsquaredMap) <- ntrees
  resdfMAEMap <- as.data.frame(resMAEMap)
  rownames(resdfMAEMap) <- mtrys
  colnames(resdfMAEMap) <- ntrees
  
  
  # convert dataframes to long format using tidyverse
  resdfRMSEMap <- resdfRMSEMap |>
                      rownames_to_column('mtry') |>
                          gather(key='ntree', value='RMSE', -mtry)
  
  resdfRsquaredMap <- resdfRsquaredMap |>
                          rownames_to_column('mtry') |>
                              gather(key='ntree', value='Rsquared', -mtry)
  
  resdfMAEMap <- resdfMAEMap |>
                    rownames_to_column('mtry') |>
                        gather(key='ntree', value='MAE', -mtry)
  
  # ensure ntree and mtry columns are ordered factors
  resdfRMSEMap$ntree <- factor(resdfRMSEMap$ntree, levels=as.character(ntrees))
  resdfRMSEMap$mtry <- factor(resdfRMSEMap$mtry, levels=as.character(mtrys))
  
  resdfRsquaredMap$ntree <- factor(resdfRsquaredMap$ntree, levels=as.character(ntrees))
  resdfRsquaredMap$mtry <- factor(resdfRsquaredMap$mtry, levels=as.character(mtrys))
  
  resdfMAEMap$ntree <- factor(resdfMAEMap$ntree, levels=as.character(ntrees))
  resdfMAEMap$mtry <- factor(resdfMAEMap$mtry, levels=as.character(mtrys))
  
  # plot heatmaps using ggplot, with extreme (min or max) value plotted as overlaid point using annotate and colourbar scale reversed
  pHeatmapRMSE <- ggplot(resdfRMSEMap) +
                    geom_tile(aes(x=ntree, y=mtry, fill=RMSE)) +
                        scale_fill_viridis(option="viridis", direction=-1) +
                          geom_point(data=resdfRMSEMap[which(resdfRMSEMap$RMSE
                                                             == min(resdfRMSEMap$RMSE),
                                                             arr.ind = TRUE),],
                                     aes(x=ntree, y=mtry), colour="red", size=2) +
                            guides(colour = guide_colourbar(reverse=TRUE)) +
                              labs(x="ntree", y="mtry", fill="RMSE") +
                                theme(text = element_text(family = "serif"))
  
  pHeatmapRsquared <- ggplot(resdfRsquaredMap) +
                        geom_tile(aes(x=ntree, y=mtry, fill=Rsquared)) +
                            scale_fill_viridis(option="viridis", direction=1) +
                              geom_point(data=resdfRsquaredMap[which(resdfRsquaredMap$Rsquared
                                                                     == max(resdfRsquaredMap$Rsquared),
                                                                     arr.ind = TRUE),],
                                         aes(x=ntree, y=mtry), colour="red", size=2) +
                                guides(colour = guide_colourbar(reverse=TRUE)) +
                                  labs(x="ntree", y="mtry", fill="Rsquared") +
                                    theme(text = element_text(family = "serif"))
  
  pHeatmapMAE <- ggplot(resdfMAEMap) +
                    geom_tile(aes(x=ntree, y=mtry, fill=MAE)) +
                        scale_fill_viridis(option="viridis", direction=-1) +
                          geom_point(data=resdfMAEMap[which(resdfMAEMap$MAE
                                                            == min(resdfMAEMap$MAE),
                                                            arr.ind = TRUE),],
                                     aes(x=ntree, y=mtry), colour="red", size=2) +
                            guides(colour = guide_colourbar(reverse=TRUE)) +
                              labs(x="ntree", y="mtry", fill="MAE") +
                                theme(text = element_text(family = "serif"))
  
  p <-  cowplot::plot_grid(pHeatmapRMSE,
                           pHeatmapRsquared,
                           pHeatmapMAE,
                           ncol=3, nrow=1)
  
  return(p)

}  # end of function

```


# Analysis

## Set global parameters

```{r}

permImpCondThres <- 0.95
minsplit <- 20
minbucket <- 7
ntrees <- c(251, 501, 1001, 1501, 2501, 4001, 5501)

```

## Analyse ambient variables

### Initialise results output variables


```{r}

resAmbAnnoyMnFit <- data.frame(RMSE = numeric(),
                               MAE = numeric(),
                               Rsquared = numeric())
resAmbAnnoyMnPermImp <- list()

```

### Set variables

```{r}

iVars <- names(stimDataAmb)[which(names(stimDataAmb) == 'AmbLAeqMaxLR'):which(names(stimDataAmb) == 'AmbPsychAnnoyBoucher')]

dVar <- "AnnoyanceMean"

seeds <- c(65841, 75426, 95421, 546, 856410)

```

### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataAmb, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
              ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)

p

if (saveplots){
  ggsave(filename="AnnoyMnAmbVarsHyperTune.svg", width=12, height=4, path=file.path(outFigPath, "svg"))
  unlink("AnnoyMnAmbVarsHyperTune.svg")

  ggsave(filename="AnnoyMnAmbVarsHyperTune.pdf", width=12, height=4, path=file.path(outFigPath, "pdf"))
  unlink("AnnoyMnAmbVarsHyperTune.pdf")
}

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.5)

```


#### Run model

Train preliminary model

```{r}

nperm <- 10

resultsOutAmb <- crfReg(dataIn=stimDataAmb, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAmb$OOB_RMSE
resultsOutAmb$OOB_MAE
resultsOutAmb$Rsquared

```

Train multiple seeds model

```{r}

resultsOutAmb <- multi_crfReg(dataIn=stimDataAmb, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAmb$OOB_RMSE
resultsOutAmb$OOB_MAE
resultsOutAmb$Rsquared

```

```{r}

# store results
resAmbAnnoyMnFit['Abs vars', 'RMSE'] <- resultsOutAmb$OOB_RMSE
resAmbAnnoyMnFit['Abs vars', 'MAE'] <- resultsOutAmb$OOB_MAE
resAmbAnnoyMnFit['Abs vars', 'Rsquared'] <- resultsOutAmb$Rsquared
resAmbAnnoyMnPermImp$AbsVars <- resultsOutAmb$conditional_permimp

```

#### Plot results

```{r, fig.width=8,fig.height=15}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAmb.conimp <- arrange(resultsOutAmb$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutAmb.conimp) + geom_col(aes(x=factor(rownames(resultsOutAmb.conimp), levels=rownames(resultsOutAmb.conimp)), y=CondPermImp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) +
  coord_flip(ylim=c(0, 0.5))
pBar

filename <- "AnnoyMnAmbVarsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep = ""), width=8, height=15, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep = ""))
  
  ggsave(filename=paste(filename, ".pdf", sep = ""), width=8, height=15, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep = ""))
}
```
These results indicate that the ambient sound quality variables have very little individual influence on the outcome.

Therefore, the ambient can be factored in as a categorical variable to be used in the analysis.

```{r}

# generate a categorical factor for AmbientEnv and cbind it to the stimDataUAS
stimDataNum <- cbind(stimDataUAS, AmbientEnvVar = factor(stimData[stimData$UASEvents != 0,]$AmbientEnv))

```


## Mean change in annoyance

### Set parameters

```{r}

eventVar <- "UASEvents"
ambVar <- "AmbientEnvVar"


```

### Initialise results output variables

```{r}
resdAnnoyMnFit <- data.frame(RMSE = numeric(),
                               MAE = numeric(),
                               Rsquared = numeric())
resdAnnoyMnPermImp <- list()

```


### Absolute variables

#### Set variables

```{r}

iVars <- names(stimDataNum)[which(names(stimDataNum) == 'UASEvents'):which(names(stimDataNum) == 'UASPsychAnnoyBoucher')]

iVars <- c(iVars, "AmbientEnvVar")

dVar <- "dAnnoyanceMean"

seeds <- c(84, 7864, 68541, 541, 83527)

```

#### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
              ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

filename <- "dAnnoyMnAbsVarsHyperTune"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.25)

```

#### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutAbs <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_MAE
resultsOutAbs$Rsquared

```

Train multiple seeds model

```{r}

resultsOutAbs <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_MAE
resultsOutAbs$Rsquared

```


```{r}

# store results
resdAnnoyMnFit['Abs vars', 'RMSE'] <- resultsOutAbs$OOB_RMSE
resdAnnoyMnFit['Abs vars', 'MAE'] <- resultsOutAbs$OOB_MAE
resdAnnoyMnFit['Abs vars', 'Rsquared'] <- resultsOutAbs$Rsquared
resdAnnoyMnPermImp$AbsVars <- resultsOutAbs$conditional_permimp

```

#### Plot results

```{r, fig.width=8,fig.height=15}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbs.conimp <- arrange(resultsOutAbs$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutAbs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp), levels=rownames(resultsOutAbs.conimp)), y=CondPermImp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) +
  coord_flip()
pBar

filename <- "dAnnoyMnAbsVarsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=15, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=15, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```


```{r, fig.width=8,fig.height=12}

# Plot only positive values

resultsOutAbs.conimpPtv <- resultsOutAbs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > 0)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbs.conimpPtv) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimpPtv), levels=rownames(resultsOutAbs.conimpPtv)), y=CondPermImp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar


filename <- "dAnnoyMnAbsVarsConPermimpPtv"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=12, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=12, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

```{r, fig.width=8,fig.height=2.5}

# Plot only values within 1% of the maximum

resultsOutAbs.conimp1pc <- resultsOutAbs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > max(resultsOutAbs.conimp)/100)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbs.conimp1pc) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp1pc), levels=rownames(resultsOutAbs.conimp1pc)), y=CondPermImp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAbsVarsConPermimp1pc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.5, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

absVar <- "UASLAF50ExMaxLR"

```


### SQM analysis

#### Individual SQMs

##### Sharpness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, "UASSharpAurISO3PowAvg", "UASSharpAurISO305Ex", "UASSharpAurSHMPowAvg", "UASSharpAurSHM05Ex", "UASSharpAurISO1PowAvg", "UASSharpAurISO105Ex", "UASSharpvBISO1PowAvg", "UASSharpvBISO105Ex", "UASSharpDINPowAvg", "UASSharpDIN05Ex", "UASSharpAurISO1Med", "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(685410, 485, 20738, 541, 8546)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 10

resultsOutSharp <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSharp <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```


```{r}
# store results
resdAnnoyMnFit['Abs sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resdAnnoyMnFit['Abs sharp', 'MAE'] <- resultsOutSharp$OOB_MAE
resdAnnoyMnFit['Abs sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resdAnnoyMnPermImp$AbsSharp <- resultsOutSharp$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- arrange(resultsOutSharp$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=CondPermImp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnSharpConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4.9, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4.9, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

sharpVar <- "UASSharpvBISO105Ex"

```

##### Tonal loudness and tonality

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", 	"UASTonalAwSHMInt05Ex", "UASTonLdECMAPowAvg", "UASTonLdECMA05Ex", "UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(465., 694851, 987, 2087, 86523)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}
# Tonality with tonal loudness

nperm <- 5

resultsOutTonal1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared

```

Train multiple seeds model

```{r}
# Tonality with tonal loudness

resultsOutTonal1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared

```

```{r}
# store results
resdAnnoyMnFit['Abs tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resdAnnoyMnFit['Abs tonal inc loud', 'MAE'] <- resultsOutTonal1$OOB_MAE
resdAnnoyMnFit['Abs tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resdAnnoyMnPermImp$AbsTonal1 <- resultsOutTonal1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=5}

par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- arrange(resultsOutTonal1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnTonalLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=5, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}
```

Selected metric

```{r}

tonLdVar <- "UASTonLdECMAPowAvg"

```

##### Tonality without tonal loudness or tonal sharpness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", "UASTonalAwSHMInt05Ex",	"UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(648320, 8732, 6489, 41583, 74534)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}
# Tonality

nperm <- 5

resultsOutTonal2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```

Train multiple seeds model

```{r}
# Tonality

resultsOutTonal2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```


```{r}

# store results
resdAnnoyMnFit['Abs tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resdAnnoyMnFit['Abs tonal no loud', 'MAE'] <- resultsOutTonal2$OOB_MAE
resdAnnoyMnFit['Abs tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resdAnnoyMnPermImp$AbsTonal2 <- resultsOutTonal2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- arrange(resultsOutTonal2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("Tonality w/o tonal loudness/sharpness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 2.5))
pBar

filename <- "dAnnoyMnTonalConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

tonalVar <- "UASTonalECMA05Ex"

```

##### Fluctuation strength

###### Set variables

```{r}

# Fluctuation strength
iVars <- c(absVar, eventVar, ambVar, "UASFluctOldSHM10Ex", "UASFluctOldSHM05Ex", "UASFluctECMA10Ex", "UASFluctECMA05Ex", "UASFluctFZ10Ex", "UASFluctFZ05Ex", "UASFluctOV10Ex", "UASFluctOV05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(418659, 365412, 7864, 15, 684)

```


###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 2501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutFluct <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```

Train multiple seeds model

```{r}

resultsOutFluct <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```


```{r}

# store results
resdAnnoyMnFit['Abs fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resdAnnoyMnFit['Abs fluct', 'MAE'] <- resultsOutFluct$OOB_MAE
resdAnnoyMnFit['Abs fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resdAnnoyMnPermImp$AbsFluct <- resultsOutFluct$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=3.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- arrange(resultsOutFluct$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=CondPermImp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnFluctConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=3.5, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=3.5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

fluctVar <- "UASFluctECMA10Ex"

```

##### Roughness

###### Set variables

```{r}

# Roughness
iVars <- c(absVar, eventVar, ambVar, "UASRoughECMA10Ex", "UASRoughECMA05Ex", "UASRoughFZ10Ex", "UASRoughFZ05Ex", "UASRoughDW10Ex", "UASRoughDW05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(481, 9867, 84651, 36541, 2136)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 5501
mtry <- as.integer(length(iVars)/1.5)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutRough <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

Train multiple seeds model

```{r}

resultsOutRough <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

```{r}
# store results
resdAnnoyMnFit['Abs rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resdAnnoyMnFit['Abs rough', 'MAE'] <- resultsOutRough$OOB_MAE
resdAnnoyMnFit['Abs rough', 'Rsquared'] <- resultsOutRough$Rsquared
resdAnnoyMnPermImp$AbsRough <- resultsOutRough$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- arrange(resultsOutRough$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=CondPermImp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnRoughConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.9, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.9, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

roughVar <- "UASRoughECMA10Ex"

```

##### Impulsiveness

###### Set variables

```{r}
# Impulsiveness
iVars <- c(absVar, eventVar, ambVar, "UASImpulsSHMAvg", "UASImpulsSHM05Ex", "UASImpulsSHMPowAvg", "UASImpulsLoudWZAvg", "UASImpulsLoudWZ05Ex", "UASImpulsLoudWZPowAvg", "UASImpulsLoudWECMAAvg", "UASImpulsLoudWECMA05Ex", "UASImpulsLoudWECMAPowAvg")
dVar <- "dAnnoyanceMean"

seeds <- c(41069, 640195, 9485, 46198, 31287)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.25)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutImpuls <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

Train multiple seeds model

```{r}

resultsOutImpuls <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['Abs impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resdAnnoyMnFit['Abs impuls', 'MAE'] <- resultsOutImpuls$OOB_MAE
resdAnnoyMnFit['Abs impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resdAnnoyMnPermImp$AbsImpuls <- resultsOutImpuls$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- arrange(resultsOutImpuls$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=CondPermImp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnImpulsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=3.8, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=3.8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

impulsVar <- "UASImpulsLoudWZAvg"

```

#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

##### Include tonal loudness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, sharpVar, tonLdVar, fluctVar, roughVar, impulsVar)
dVar <- "dAnnoyanceMean"

seeds <- c(486195, 64051, 78465, 84, 31046)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1001
mtry <- as.integer(length(iVars)/1.6)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resdAnnoyMnFit['Abs SQMs inc tonal loud', 'MAE'] <- resultsOutSQMs1$OOB_MAE
resdAnnoyMnFit['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resdAnnoyMnPermImp$AbsSQMs1 <- resultsOutSQMs1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- arrange(resultsOutSQMs1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAbsSQMsTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

##### Exclude tonal loudness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, sharpVar, tonalVar, fluctVar, roughVar, impulsVar)
dVar <- "dAnnoyanceMean"

seeds <- c(84, 410, 846951, 643581, 76823)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.6)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resdAnnoyMnFit['Abs SQMs no tonal loud', 'MAE'] <- resultsOutSQMs2$OOB_MAE
resdAnnoyMnFit['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resdAnnoyMnPermImp$AbsSQMs2 <- resultsOutSQMs2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- arrange(resultsOutSQMs2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAbsSQMsNoTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### Psychoacoustic annoyance metrics

##### Set variables

```{r}

iVars <- c(ambVar, "UASPsychAnnoyWidmann", "UASPsychAnnoyMore", "UASPsychAnnoyDi", "UASPsychAnnoyTorija", "UASPsychAnnoyWillemsen", "UASPsychAnnoyBoucher")
dVar <- "dAnnoyanceMean"

seeds <- c(410685, 648513, 60832, 807324, 783268237)


```

##### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```


Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.75)

```

##### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutPA <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

Train multiple seeds model

```{r}

resultsOutPA <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['Psychoacoustic annoyance', 'RMSE'] <- resultsOutPA$OOB_RMSE
resdAnnoyMnFit['Psychoacoustic annoyance', 'MAE'] <- resultsOutPA$OOB_MAE
resdAnnoyMnFit['Psychoacoustic annoyance', 'Rsquared'] <- resultsOutPA$Rsquared
resdAnnoyMnPermImp$AbsPA <- resultsOutPA$conditional_permimp

```

##### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutPA.conimp <- arrange(resultsOutPA$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutPA.conimp) + geom_col(aes(x=factor(rownames(resultsOutPA.conimp), levels=rownames(resultsOutPA.conimp)), y=CondPermImp), fill=mycolours[10], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 1.8))
pBar


filename <- "dAnnoyMnAbsPAConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

### All variables (absolute and difference)

#### Set variables

```{r}

iVars <- names(stimDataNum)[which(names(stimDataNum) == 'UASEvents'):which(names(stimDataNum) == 'dPsychAnnoyBoucher')]

dVar <- "dAnnoyanceMean"

seeds <- c(650834, 45634110, 78028376, 498, 808365)

```

#### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
              ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

filename <- "dAnnoyMnAllVarsHyperTune"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected hyperparameters

```{r}

ntree <- 5501
mtry <- as.integer(length(iVars)/1.5)

```

#### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutAbsDiffs <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbsDiffs$OOB_RMSE
resultsOutAbsDiffs$OOB_MAE
resultsOutAbsDiffs$Rsquared

```

Train multiple seeds model

```{r}

resultsOutAbsDiffs <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbsDiffs$OOB_RMSE
resultsOutAbsDiffs$OOB_MAE
resultsOutAbsDiffs$Rsquared
```

```{r}
# store results
resdAnnoyMnFit['All vars', 'RMSE'] <- resultsOutAbsDiffs$OOB_RMSE
resdAnnoyMnFit['All vars', 'MAE'] <- resultsOutAbsDiffs$OOB_MAE
resdAnnoyMnFit['All vars', 'Rsquared'] <- resultsOutAbsDiffs$Rsquared
resdAnnoyMnPermImp$AllVars <- resultsOutAbsDiffs$conditional_permimp

```

#### Plot results

```{r, fig.width=8,fig.height=33}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbsDiffs.conimp <- arrange(resultsOutAbsDiffs$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutAbsDiffs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbsDiffs.conimp), levels=rownames(resultsOutAbsDiffs.conimp)), y=CondPermImp), fill=mycolours[9], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar


filename <- "dAnnoyMnAllVarsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=33, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=33, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

```{r, fig.width=8,fig.height=20}

# Plot only positive values

resultsOutAbsDiffs.conimpPtv <- resultsOutAbsDiffs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > 0)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbsDiffs.conimpPtv) + geom_col(aes(x=factor(rownames(resultsOutAbsDiffs.conimpPtv), levels=rownames(resultsOutAbsDiffs.conimpPtv)), y=CondPermImp), fill=mycolours[9], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAllVarsConPermimpPtv"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=20, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=20, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


```

```{r, fig.width=8,fig.height=6}

# Plot only values within 1% of the maximum

resultsOutAbsDiffs.conimp1pc <- resultsOutAbsDiffs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > max(resultsOutAbsDiffs.conimp)/100)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbsDiffs.conimp1pc) + geom_col(aes(x=factor(rownames(resultsOutAbsDiffs.conimp1pc), levels=rownames(resultsOutAbsDiffs.conimp1pc)), y=CondPermImp), fill=mycolours[9], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAllVarsConPermimp1pc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=6, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=6, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}
```

Selected metric

```{r}

allVar <- "Detect0p1dBIntEx50MaxLR"

```

### dSQM analysis

#### Individual SQMs

##### dSharpness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, "dSharpAurISO3PowAvg", "dSharpAurISO305Ex", "dSharpAurSHMPowAvg", "dSharpAurSHM05Ex", "dTonShpAurSHMPowAvg", "dTonShpAurSHM05Ex", "PartTonShpAurSHMPowAvg",
           "PartTonShpAurSHM05Ex", "PartTonShpvBSHMPowAvg",
           "PartTonShpvBSHM05Ex", "PartTonShpWidSHMPowAvg",
           "PartTonShpWidSHM05Ex", "PartSharpAurSHMPowAvg",
           "PartSharpAurSHM05Ex", "PartSharpvBSHMPowAvg",
           "PartSharpvBSHM05Ex", "PartSharpWidSHMPowAvg",
           "PartSharpWidSHM05Ex", "UASSharpAurISO3PowAvg", "UASSharpAurISO305Ex", "UASSharpAurSHMPowAvg", "UASSharpAurSHM05Ex", "UASSharpAurISO1PowAvg", "UASSharpAurISO105Ex", "UASSharpvBISO1PowAvg", "UASSharpvBISO105Ex", "UASSharpDINPowAvg", "UASSharpDIN05Ex", "UASSharpAurISO1Med",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(1230723, 65416854, 44615, 1510, 410865)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <-5501
mtry <- as.integer(length(iVars)/1.5)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSharp <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSharp <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```


```{r}

# store results
resdAnnoyMnFit['All sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resdAnnoyMnFit['All sharp', 'MAE'] <- resultsOutSharp$OOB_MAE
resdAnnoyMnFit['All sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resdAnnoyMnPermImp$AllSharp <- resultsOutSharp$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=7.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- arrange(resultsOutSharp$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=CondPermImp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("All sharpness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar


filename <- "dAnnoyMnAllSharpConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=7.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=7.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allSharpVar <- "PartSharpvBSHMPowAvg"

```

##### dTonal loudness and dtonality

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, "dTonalECMAAvg", "dTonalSHMInt05Ex", "dTonalSHMIntAvg", "dTonalECMA05Ex", "dTonalAwSHMAvg",	"dTonalAwSHM05Ex",	"dTonalAwSHMIntAvg", 	"dTonalAwSHMInt05Ex", "dTonLdECMAPowAvg", "dTonLdECMA05Ex", "dTonShpAurSHMPowAvg",
           "dTonShpAurSHM05Ex", "PartTonShpAurSHMPowAvg",
           "PartTonShpAurSHM05Ex", "PartTonShpvBSHMPowAvg",
           "PartTonShpvBSHM05Ex", "PartTonShpWidSHMPowAvg",
           "PartTonShpWidSHM05Ex", "PartTonLdSHMPowAvg", "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", 	"UASTonalAwSHMInt05Ex", "UASTonLdECMAPowAvg", "UASTonLdECMA05Ex", "UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(82703108, 964851, 451352, 97840, 48516874)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.75)

```

###### Run model

Train preliminary model

```{r}
# Tonality with tonal loudness

nperm <- 5

resultsOutTonal1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared

```

Train multiple seeds model

```{r}
# Tonality with tonal loudness

resultsOutTonal1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared

```

```{r}
# store results
resdAnnoyMnFit['All tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resdAnnoyMnFit['All tonal inc loud', 'MAE'] <- resultsOutTonal1$OOB_MAE
resdAnnoyMnFit['All tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resdAnnoyMnPermImp$AllTonal1 <- resultsOutTonal1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=7}

par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- arrange(resultsOutTonal1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("All tonality inc. tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 2.2))
pBar


filename <- "dAnnoyMnAllTonalLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=7, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allTonLdVar <- "PartTonLdSHMPowAvg"

```

##### dTonality without dtonal loudness or dtonal sharpness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, "dTonalECMAAvg", "dTonalSHMInt05Ex", "dTonalSHMIntAvg", "dTonalECMA05Ex", "dTonalAwSHMAvg",	"dTonalAwSHM05Ex",	"dTonalAwSHMIntAvg", 	"dTonalAwSHMInt05Ex", "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", "UASTonalAwSHMInt05Ex",	"UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(41486, 726318, 390827798, 484659, 86479)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}
# Tonality

nperm <- 5

resultsOutTonal2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
                           ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```

Train multiple seeds model

```{r}
# Tonality

resultsOutTonal2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```


```{r}

# store results
resdAnnoyMnFit['All tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resdAnnoyMnFit['All tonal no loud', 'MAE'] <- resultsOutTonal2$OOB_MAE
resdAnnoyMnFit['All tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resdAnnoyMnPermImp$AllTonal2 <- resultsOutTonal2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=5.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- arrange(resultsOutTonal2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("All tonality w/o tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 3))
pBar

filename <- "dAnnoyMnAllTonalConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=5.8, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=5.8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


```

Selected metric

```{r}

allTonalVar <- "dTonalECMAAvg"

```

##### dFluctuation strength

###### Set variables

```{r}

# Fluctuation strength
iVars <- c(allVar, eventVar, ambVar, "dFluctECMA10Ex", "dFluctECMA05Ex", "dFluctOV10Ex", "dFluctOV05Ex", "UASFluctOldSHM10Ex", "UASFluctOldSHM05Ex", "UASFluctECMA10Ex", "UASFluctECMA05Ex", "UASFluctFZ10Ex", "UASFluctFZ05Ex", "UASFluctOV10Ex", "UASFluctOV05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(76236328, 8645, 48561486, 67321, 532485)

```


###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutFluct <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```
Train multiple seeds model

```{r}

resultsOutFluct <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```


```{r}

# store results
resdAnnoyMnFit['All fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resdAnnoyMnFit['All fluct', 'MAE'] <- resultsOutFluct$OOB_MAE
resdAnnoyMnFit['All fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resdAnnoyMnPermImp$AllFluct <- resultsOutFluct$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- arrange(resultsOutFluct$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=CondPermImp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("All fluctuation strength") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAllFluctConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allFluctVar <- "dFluctOV10Ex"

```


##### dRoughness

###### Set variables

```{r}

# Roughness
iVars <- c(allVar, eventVar, ambVar, "dRoughECMA10Ex", "dRoughECMA05Ex", "dRoughFZ10Ex", "dRoughFZ05Ex", "UASRoughECMA10Ex", "UASRoughECMA05Ex", "UASRoughFZ10Ex", "UASRoughFZ05Ex", "UASRoughDW10Ex", "UASRoughDW05Ex")
dVar <- "dAnnoyanceMean"

seeds <- c(5328723, 4865154, 846, 672310, 203687)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutRough <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

Train multiple seeds model

```{r}

resultsOutRough <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

```{r}
# store results
resdAnnoyMnFit['All rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resdAnnoyMnFit['All rough', 'MAE'] <- resultsOutRough$OOB_MAE
resdAnnoyMnFit['All rough', 'Rsquared'] <- resultsOutRough$Rsquared
resdAnnoyMnPermImp$AllRough <- resultsOutRough$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- arrange(resultsOutRough$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=CondPermImp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("All roughness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dAnnoyMnAllRoughConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allRoughVar <- "dRoughECMA05Ex"

```

##### dImpulsiveness

###### Set variables

```{r}
# Impulsiveness
iVars <- c(allVar, eventVar, ambVar, "dImpulsSHMAvg", "dImpulsSHM05Ex", "dImpulsSHMPowAvg",
           "dImpulsLoudWZAvg", "dImpulsLoudWZ05Ex", "dImpulsLoudWZPowAvg",
           "dImpulsLoudWECMAAvg", "dImpulsLoudWECMA05Ex", "dImpulsLoudWECMAPowAvg", "UASImpulsSHMAvg", "UASImpulsSHM05Ex", "UASImpulsSHMPowAvg", "UASImpulsLoudWZAvg", "UASImpulsLoudWZ05Ex", "UASImpulsLoudWZPowAvg", "UASImpulsLoudWECMAAvg", "UASImpulsLoudWECMA05Ex", "UASImpulsLoudWECMAPowAvg")
dVar <- "dAnnoyanceMean"

seeds <- c(798231, 513615, 78312, 481659, 846)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutImpuls <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

Train multiple seeds model

```{r}

resultsOutImpuls <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['All impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resdAnnoyMnFit['All impuls', 'MAE'] <- resultsOutImpuls$OOB_MAE
resdAnnoyMnFit['All impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resdAnnoyMnPermImp$AllImpuls <- resultsOutImpuls$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=5.6}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- arrange(resultsOutImpuls$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=CondPermImp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + ggtitle("All impulsiveness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar


filename <- "dAnnoyMnAllImpulsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=5.6, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=5.6, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allImpulsVar <- "dImpulsLoudWZAvg"

```

#### dSQM and loudness comparison

Now the highest importance dSQMs are ranked against each other, controlling for loudness difference.

##### Include dtonal loudness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, allSharpVar, allTonLdVar, allFluctVar, allRoughVar, allImpulsVar)
dVar <- "dAnnoyanceMean"

seeds <- c(678321, 9812, 762183, 2378, 20318967)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.6)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['All SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resdAnnoyMnFit['All SQMs inc tonal loud', 'MAE'] <- resultsOutSQMs1$OOB_MAE
resdAnnoyMnFit['All SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resdAnnoyMnPermImp$AllSQMs1 <- resultsOutSQMs1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- arrange(resultsOutSQMs1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 1.5))
pBar


filename <- "dAnnoyMnAllSQMsTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

##### Exclude tonal loudness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, allSharpVar, allTonalVar, allFluctVar, allRoughVar, allImpulsVar)
dVar <- "dAnnoyanceMean"

seeds <- c(6782318, 213321465, 51324, 6614, 71238728)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 2501
mtry <- as.integer(length(iVars)/1.6)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['All SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resdAnnoyMnFit['All SQMs no tonal loud', 'MAE'] <- resultsOutSQMs2$OOB_MAE
resdAnnoyMnFit['All SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resdAnnoyMnPermImp$AllSQMs2 <- resultsOutSQMs2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- arrange(resultsOutSQMs2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 1.5))
pBar

filename <- "dAnnoyMnAllSQMsNoTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### dPsychoacoustic annoyance metrics

##### Set variables

```{r}

iVars <- c(ambVar, "dPsychAnnoyWidmann", "dPsychAnnoyMore", "dPsychAnnoyDi", "dPsychAnnoyTorija", "dPsychAnnoyWillemsen", "dPsychAnnoyBoucher", "UASPsychAnnoyWidmann", "UASPsychAnnoyMore", "UASPsychAnnoyDi", "UASPsychAnnoyTorija", "UASPsychAnnoyWillemsen", "UASPsychAnnoyBoucher")
dVar <- "dAnnoyanceMean"

seeds <- c(873278, 23132180, 76510132, 2932730, 23184)


```

##### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
              ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```


Selected hyperparameters

```{r}

ntree <- 251
mtry <-  as.integer(length(iVars)/2.25)

```

##### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutPA <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

Train multiple seeds model

```{r}

resultsOutPA <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

```{r}

# store results
resdAnnoyMnFit['All Psychoacoustic annoyance', 'RMSE'] <- resultsOutPA$OOB_RMSE
resdAnnoyMnFit['All Psychoacoustic annoyance', 'MAE'] <- resultsOutPA$OOB_MAE
resdAnnoyMnFit['All Psychoacoustic annoyance', 'Rsquared'] <- resultsOutPA$Rsquared
resdAnnoyMnPermImp$AllPA <- resultsOutPA$conditional_permimp

```

##### Plot results

```{r, fig.width=8,fig.height=4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutPA.conimp <- arrange(resultsOutPA$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutPA.conimp) + geom_col(aes(x=factor(rownames(resultsOutPA.conimp), levels=rownames(resultsOutPA.conimp)), y=CondPermImp), fill=mycolours[10], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (mean change in annoyance)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 1))
pBar

filename <- "dAnnoyMnAllPAConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

### Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resdAnnoyMnFit, paste(outDataPath, "\\CRFdAnnoyMnOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resdAnnoyMnPermImp){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resdAnnoyMnPermImp[ii])
    names(temp[[ii]]) <- names(resdAnnoyMnPermImp[ii])
  }
  openxlsx2::write_xlsx(temp, paste(outDataPath, "\\CRFdAnnoyMnConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## (Change to) High annoyance

### Initialise results output variables

```{r}
resdHiAnnoyFit <- data.frame(RMSE = numeric(),
                             MAE = numeric(),
                             Rsquared = numeric())
resdHiAnnoyPermImp <- list()

```

### Absolute variables

#### Set variables

```{r}

iVars <- names(stimDataNum)[which(names(stimDataNum) == 'UASEvents'):which(names(stimDataNum) == 'UASPsychAnnoyBoucher')]

dVar <- "dHighAnnoyPc"

seeds <- c(2612618, 6541, 237, 723075032, 786312)

```

#### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

filename <- "dHiAnnoyAbsVarsHyperTune"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}
```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.25)

```

#### Run model

Train preliminary model

```{r}

nperm <- 10

resultsOutAbs <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_MAE
resultsOutAbs$Rsquared

```
Train multiple seeds model

```{r}

resultsOutAbs <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_MAE
resultsOutAbs$Rsquared

```


```{r}

# store results
resdHiAnnoyFit['Abs vars', 'RMSE'] <- resultsOutAbs$OOB_RMSE
resdHiAnnoyFit['Abs vars', 'MAE'] <- resultsOutAbs$OOB_MAE
resdHiAnnoyFit['Abs vars', 'Rsquared'] <- resultsOutAbs$Rsquared
resdHiAnnoyPermImp$AbsVars <- resultsOutAbs$conditional_permimp

```

#### Plot results

```{r, fig.width=8,fig.height=16}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbs.conimp <- arrange(resultsOutAbs$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutAbs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp), levels=rownames(resultsOutAbs.conimp)), y=CondPermImp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) +
  coord_flip()
pBar

filename <- "dHiAnnoyAbsVarsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=16, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=16, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

```{r, fig.width=8,fig.height=14}

# Plot only positive values
resultsOutAbs.conimpPtv <- resultsOutAbs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > 0)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbs.conimpPtv,) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimpPtv), levels=rownames(resultsOutAbs.conimpPtv)), y=CondPermImp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAbsVarsConPermimpPtv"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=14, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=14, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


```


```{r, fig.width=8,fig.height=4}

# Plot only values within 1% of the maximum
resultsOutAbs.conimp1pc <- resultsOutAbs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > max(resultsOutAbs.conimp)/100)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbs.conimp1pc,) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp1pc), levels=rownames(resultsOutAbs.conimp1pc)), y=CondPermImp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAbsVarsConPermimp1pc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

absVar <- "UASLAF50ExMaxLR"

```

### SQM analysis

#### Individual SQMs

##### Sharpness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, "UASSharpAurISO3PowAvg", "UASSharpAurISO305Ex", "UASSharpAurSHMPowAvg", "UASSharpAurSHM05Ex", "UASSharpAurISO1PowAvg", "UASSharpAurISO105Ex", "UASSharpvBISO1PowAvg", "UASSharpvBISO105Ex", "UASSharpDINPowAvg", "UASSharpDIN05Ex", "UASSharpAurISO1Med",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(832178, 1352546, 6854, 64014, 78523)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p


```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSharp <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSharp <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```


```{r}

# store results
resdHiAnnoyFit['Abs sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resdHiAnnoyFit['Abs sharp', 'MAE'] <- resultsOutSharp$OOB_MAE
resdHiAnnoyFit['Abs sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resdHiAnnoyPermImp$AbsSharp <- resultsOutSharp$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- arrange(resultsOutSharp$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=CondPermImp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoySharpConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4.9, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4.9, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

sharpVar <- "UASSharpvBISO105Ex"

```


##### Tonal loudness and tonality

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", 	"UASTonalAwSHMInt05Ex", "UASTonLdECMAPowAvg", "UASTonLdECMA05Ex", "UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(8654, 6854, 3512864, 418650, 645098)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 5501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}
# Tonality with tonal loudness

nperm <- 5

resultsOutTonal1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared
```

Train multiple seeds model

```{r}
# Tonality with tonal loudness

resultsOutTonal1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared

```

```{r}
# store results
resdHiAnnoyFit['Abs tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resdHiAnnoyFit['Abs tonal inc loud', 'MAE'] <- resultsOutTonal1$OOB_MAE
resdHiAnnoyFit['Abs tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resdHiAnnoyPermImp$AbsTonal1 <- resultsOutTonal1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4.4}

par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- arrange(resultsOutTonal1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 400))
pBar

filename <- "dHiAnnoyTonalLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

tonLdVar <- "UASTonLdECMAPowAvg"

```


##### Tonality without tonal loudness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", "UASTonalAwSHMInt05Ex",	"UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(418659, 654641, 58541, 793265, 846951)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.25)

```


###### Run model

Train preliminary model

```{r}
# Tonality

nperm <- 5

resultsOutTonal2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
                           ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm,
                           minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```

Train multiple seeds model

```{r}
# Tonality

resultsOutTonal2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```


```{r}

# store results
resdHiAnnoyFit['Abs tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resdHiAnnoyFit['Abs tonal no loud', 'MAE'] <- resultsOutTonal2$OOB_MAE
resdHiAnnoyFit['Abs tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resdHiAnnoyPermImp$AbsTonal2 <- resultsOutTonal2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- arrange(resultsOutTonal2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 400))
pBar

filename <- "dHiAnnoyTonalConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=3.8, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=3.8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

tonalVar <- "UASTonalECMA05Ex"

```

##### Fluctuation strength

###### Set variables

```{r}

# Fluctuation strength
iVars <- c(absVar, eventVar, ambVar, "UASFluctOldSHM10Ex", "UASFluctOldSHM05Ex", "UASFluctECMA10Ex", "UASFluctECMA05Ex", "UASFluctFZ10Ex", "UASFluctFZ05Ex", "UASFluctOV10Ex", "UASFluctOV05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(46851, 78220178, 18659, 792530, 312789)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1001
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutFluct <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
                          ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres,
                          nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```
Train multiple seeds model

```{r}

resultsOutFluct <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```


```{r}

# store results
resdHiAnnoyFit['Abs fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resdHiAnnoyFit['Abs fluct', 'MAE'] <- resultsOutFluct$OOB_MAE
resdHiAnnoyFit['Abs fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resdHiAnnoyPermImp$AbsFluct <- resultsOutFluct$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- arrange(resultsOutFluct$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=CondPermImp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyFluctConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.9, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.9, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

fluctVar <- "UASFluctOV10Ex"

```

##### Roughness

###### Set variables

```{r}

# Roughness
iVars <- c(absVar, eventVar, ambVar, "UASRoughECMA10Ex", "UASRoughECMA05Ex", "UASRoughFZ10Ex", "UASRoughFZ05Ex", "UASRoughDW10Ex", "UASRoughDW05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(849651, 105362, 8, 58641, 615)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 5501
mtry <- as.integer(length(iVars)/1.25)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutRough <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

Train multiple seeds model

```{r}

resultsOutRough <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

```{r}
# store results
resdHiAnnoyFit['Abs rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resdHiAnnoyFit['Abs rough', 'MAE'] <- resultsOutRough$OOB_MAE
resdHiAnnoyFit['Abs rough', 'Rsquared'] <- resultsOutRough$Rsquared
resdHiAnnoyPermImp$AbsRough <- resultsOutRough$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- arrange(resultsOutRough$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=CondPermImp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyRoughConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.9, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.9, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

roughVar <- "UASRoughDW05Ex"

```


##### Impulsiveness

###### Set variables

```{r}
# Impulsiveness
iVars <- c(absVar, eventVar, ambVar, "UASImpulsSHMAvg", "UASImpulsSHM05Ex", "UASImpulsSHMPowAvg", "UASImpulsLoudWZAvg", "UASImpulsLoudWZ05Ex", "UASImpulsLoudWZPowAvg", "UASImpulsLoudWECMAAvg", "UASImpulsLoudWECMA05Ex", "UASImpulsLoudWECMAPowAvg")
dVar <- "dHighAnnoyPc"

seeds <- c(23782, 641095, 3526178, 4865, 36512)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.5)

```


###### Run model

Train preliminary model

```{r}

nperm <- 15

resultsOutImpuls <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

Train multiple seeds model

```{r}

resultsOutImpuls <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['Abs impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resdHiAnnoyFit['Abs impuls', 'MAE'] <- resultsOutImpuls$OOB_MAE
resdHiAnnoyFit['Abs impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resdHiAnnoyPermImp$AbsImpuls <- resultsOutImpuls$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- arrange(resultsOutImpuls$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=CondPermImp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyImpulsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

impulsVar <- "UASImpulsLoudWZAvg"

```

#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

##### Include tonal loudness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, sharpVar, tonLdVar, fluctVar, roughVar, impulsVar)
dVar <- "dHighAnnoyPc"

seeds <- c(419865, 6541851, 4532, 320785, 8546)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1001
mtry <- mtry <- as.integer(length(iVars)/1.6)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resdHiAnnoyFit['Abs SQMs inc tonal loud', 'MAE'] <- resultsOutSQMs1$OOB_MAE
resdHiAnnoyFit['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resdHiAnnoyPermImp$AbsSQMs1 <- resultsOutSQMs1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- arrange(resultsOutSQMs1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 120))
pBar


filename <- "dHiAnnoyAbsSQMsTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

##### Exclude tonal loudness

###### Set variables

```{r}

iVars <- c(absVar, eventVar, ambVar, sharpVar, tonalVar, fluctVar, roughVar, impulsVar)
dVar <- "dHighAnnoyPc"

seeds <- c(150864, 698541, 30841, 5406854, 20387)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 501
mtry <- as.integer(length(iVars)/1.6)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resdHiAnnoyFit['Abs SQMs no tonal loud', 'MAE'] <- resultsOutSQMs2$OOB_MAE
resdHiAnnoyFit['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resdHiAnnoyPermImp$AbsSQMs2 <- resultsOutSQMs2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- arrange(resultsOutSQMs2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 120))
pBar

filename <- "dHiAnnoyAbsSQMsNoTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### Psychoacoustic annoyance metrics

##### Set variables

```{r}

iVars <- c(ambVar, "UASPsychAnnoyWidmann", "UASPsychAnnoyMore", "UASPsychAnnoyDi", "UASPsychAnnoyTorija", "UASPsychAnnoyWillemsen", "UASPsychAnnoyBoucher")
dVar <- "dHighAnnoyPc"

seeds <- c(865414, 7180, 6513, 973, 79320)


```

##### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```


Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.75)

```

##### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutPA <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

Train multiple seeds model

```{r}

resultsOutPA <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['Psychoacoustic annoyance', 'RMSE'] <- resultsOutPA$OOB_RMSE
resdHiAnnoyFit['Psychoacoustic annoyance', 'MAE'] <- resultsOutPA$OOB_MAE
resdHiAnnoyFit['Psychoacoustic annoyance', 'Rsquared'] <- resultsOutPA$Rsquared
resdHiAnnoyPermImp$AbsPA <- resultsOutPA$conditional_permimp

```

##### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutPA.conimp <- arrange(resultsOutPA$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutPA.conimp) + geom_col(aes(x=factor(rownames(resultsOutPA.conimp), levels=rownames(resultsOutPA.conimp)), y=CondPermImp), fill=mycolours[10], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 150))
pBar


filename <- "dHiAnnoyAbsPAConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

### All variables (absolute and difference)

#### Set variables

```{r}

iVars <- names(stimDataNum)[which(names(stimDataNum) == 'UASEvents'):which(names(stimDataNum) == 'dPsychAnnoyBoucher')]

dVar <- "dHighAnnoyPc"

seeds <- c(649851, 60, 732, 52537, 160598)

```

#### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
              ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/2.25)

```

#### Run model

Train preliminary model

```{r}

nperm <- 10

resultsOutAbsDiffs <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbsDiffs$OOB_RMSE
resultsOutAbsDiffs$OOB_MAE
resultsOutAbsDiffs$Rsquared

```

Train multiple seeds model

```{r}

resultsOutAbsDiffs <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutAbsDiffs$OOB_RMSE
resultsOutAbsDiffs$OOB_MAE
resultsOutAbsDiffs$Rsquared
```

```{r}
# store results
resdHiAnnoyFit['All vars', 'RMSE'] <- resultsOutAbsDiffs$OOB_RMSE
resdHiAnnoyFit['All vars', 'MAE'] <- resultsOutAbsDiffs$OOB_MAE
resdHiAnnoyFit['All vars', 'Rsquared'] <- resultsOutAbsDiffs$Rsquared
resdHiAnnoyPermImp$AllVars <- resultsOutAbsDiffs$conditional_permimp

```

#### Plot results

```{r, fig.width=8,fig.height=33}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbsDiffs.conimp <- arrange(resultsOutAbsDiffs$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutAbsDiffs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbsDiffs.conimp), levels=rownames(resultsOutAbsDiffs.conimp)), y=CondPermImp), fill=mycolours[9], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllVarsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=33, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=33, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

```{r, fig.width=8,fig.height=24}

# Plot only positive values

resultsOutAbsDiffs.conimpPtv <- resultsOutAbsDiffs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > 0)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbsDiffs.conimpPtv) + geom_col(aes(x=factor(rownames(resultsOutAbsDiffs.conimpPtv), levels=rownames(resultsOutAbsDiffs.conimpPtv)), y=CondPermImp), fill=mycolours[9], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllVarsConPermimpPtv"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=24, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=24, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```


```{r, fig.width=8,fig.height=6.5}

# Plot only values within 1% of the maximum

resultsOutAbsDiffs.conimp1pc <- resultsOutAbsDiffs.conimp |>
                                          rownames_to_column('Metric') |>
                                                filter_if(is.numeric, all_vars(. > max(resultsOutAbsDiffs.conimp)/100)) |>
                                                      column_to_rownames('Metric')

pBar <- ggplot(resultsOutAbsDiffs.conimp1pc) + geom_col(aes(x=factor(rownames(resultsOutAbsDiffs.conimp1pc), levels=rownames(resultsOutAbsDiffs.conimp1pc)), y=CondPermImp), fill=mycolours[9], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar


filename <- "dHiAnnoyAllVarsConPermimp1pc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=12, height=6.5, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=12, height=6.5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allVar <- "UASLoudISO1PowAvg"

```

### dSQM analysis

#### Individual SQMs

##### dSharpness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, "dSharpAurISO3PowAvg", "dSharpAurISO305Ex", "dSharpAurSHMPowAvg", "dSharpAurSHM05Ex", "dTonShpAurSHMPowAvg", "dTonShpAurSHM05Ex", "PartTonShpAurSHMPowAvg",
           "PartTonShpAurSHM05Ex", "PartTonShpvBSHMPowAvg",
           "PartTonShpvBSHM05Ex", "PartTonShpWidSHMPowAvg",
           "PartTonShpWidSHM05Ex", "PartSharpAurSHMPowAvg",
           "PartSharpAurSHM05Ex", "PartSharpvBSHMPowAvg",
           "PartSharpvBSHM05Ex", "PartSharpWidSHMPowAvg",
           "PartSharpWidSHM05Ex", "UASSharpAurISO3PowAvg", "UASSharpAurISO305Ex", "UASSharpAurSHMPowAvg", "UASSharpAurSHM05Ex", "UASSharpAurISO1PowAvg", "UASSharpAurISO105Ex", "UASSharpvBISO1PowAvg", "UASSharpvBISO105Ex", "UASSharpDINPowAvg", "UASSharpDIN05Ex", "UASSharpAurISO1Med",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(9864, 65341, 468951, 410856, 288649, 7419)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 4001
mtry <- as.integer(length(iVars)/1.25)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSharp <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```
Train multiple seeds model

```{r}

resultsOutSharp <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_MAE
resultsOutSharp$Rsquared

```


```{r}
# store results
resdHiAnnoyFit['All sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resdHiAnnoyFit['All sharp', 'MAE'] <- resultsOutSharp$OOB_MAE
resdHiAnnoyFit['All sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resdHiAnnoyPermImp$AllSharp <- resultsOutSharp$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- arrange(resultsOutSharp$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=CondPermImp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("All sharpness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllSharpConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=8, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allSharpVar <- "UASSharpAurISO1Med"

```


##### dTonal loudness and dtonality

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, "dTonalECMAAvg", "dTonalSHMInt05Ex", "dTonalSHMIntAvg", "dTonalECMA05Ex", "dTonalAwSHMAvg",	"dTonalAwSHM05Ex",	"dTonalAwSHMIntAvg", 	"dTonalAwSHMInt05Ex", "dTonLdECMAPowAvg", "dTonLdECMA05Ex", "dTonShpAurSHMPowAvg",
           "dTonShpAurSHM05Ex", "PartTonLdSHMPowAvg", "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", 	"UASTonalAwSHMInt05Ex", "UASTonLdECMAPowAvg", "UASTonLdECMA05Ex", "UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex",
         "UASTonShpAurSHMPowAvg", "UASTonShpAurSHM05Ex")
dVar <- "dHighAnnoyPc"

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

seeds <- c(2184874, 89684, 1065484, 854, 37646541)

```
Selected hyperparameters

```{r}

ntree <- 501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}
# Tonality with tonal loudness

nperm <- 5

resultsOutTonal1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared
```

Train multiple seeds model

```{r}
# Tonality with tonal loudness

resultsOutTonal1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_MAE
resultsOutTonal1$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['All tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resdHiAnnoyFit['All tonal inc loud', 'MAE'] <- resultsOutTonal1$OOB_MAE
resdHiAnnoyFit['All tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resdHiAnnoyPermImp$AllTonal1 <- resultsOutTonal1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=7}

par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- arrange(resultsOutTonal1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("All tonality inc. tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 350))
pBar

filename <- "dHiAnnoyAllTonalLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=7, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allTonLdVar <- "PartTonLdSHMPowAvg"

```

##### dTonality without dtonal loudness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, "dTonalECMAAvg", "dTonalSHMInt05Ex", "dTonalSHMIntAvg", "dTonalECMA05Ex", "dTonalAwSHMAvg",	"dTonalAwSHM05Ex",	"dTonalAwSHMIntAvg", 	"dTonalAwSHMInt05Ex", "UASTonalECMAAvg", "UASTonalSHMInt05Ex", "UASTonalSHMIntAvg", "UASTonalECMA05Ex", "UASTonalAwSHMAvg",	"UASTonalAwSHM05Ex",	"UASTonalAwSHMIntAvg", "UASTonalAwSHMInt05Ex",	"UASTonalAurAvg", "UASTonalAur05Ex", "UASTonalAur10Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(4106985, 188519, 536110, 87964, 986541)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.25)

```


###### Run model

Train preliminary model

```{r}
# Tonality

nperm <- 5

resultsOutTonal2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```

Train multiple seeds model

```{r}
# Tonality

resultsOutTonal2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_MAE
resultsOutTonal2$Rsquared

```


```{r}

# store results
resdHiAnnoyFit['All tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resdHiAnnoyFit['All tonal no loud', 'MAE'] <- resultsOutTonal2$OOB_MAE
resdHiAnnoyFit['All tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resdHiAnnoyPermImp$AllTonal2 <- resultsOutTonal2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- arrange(resultsOutTonal2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=CondPermImp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("All tonality w/o tonal loudness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 400))
pBar


filename <- "dHiAnnoyAllTonalConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=5, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allTonalVar <- "UASTonalAurAvg"

```

##### dFluctuation strength

###### Set variables

```{r}

# Fluctuation strength
iVars <- c(allVar, eventVar, ambVar, "dFluctECMA10Ex", "dFluctECMA05Ex", "dFluctOV10Ex", "dFluctOV05Ex", "UASFluctOldSHM10Ex", "UASFluctOldSHM05Ex", "UASFluctECMA10Ex", "UASFluctECMA05Ex", "UASFluctFZ10Ex", "UASFluctFZ05Ex", "UASFluctOV10Ex", "UASFluctOV05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(841489, 152148, 697280, 1537856, 86541)

```


###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 5501
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutFluct <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```

Train multiple seeds model

```{r}

resultsOutFluct <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_MAE
resultsOutFluct$Rsquared

```


```{r}

# store results
resdHiAnnoyFit['All fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resdHiAnnoyFit['All fluct', 'MAE'] <- resultsOutFluct$OOB_MAE
resdHiAnnoyFit['All fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resdHiAnnoyPermImp$AllFluct <- resultsOutFluct$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- arrange(resultsOutFluct$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=CondPermImp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("All fluctuation strength") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllFluctConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allFluctVar <- "UASFluctFZ05Ex"

```

##### dRoughness

###### Set variables

```{r}

# Roughness
iVars <- c(allVar, eventVar, ambVar, "dRoughECMA10Ex", "dRoughECMA05Ex", "dRoughFZ10Ex", "dRoughFZ05Ex", "UASRoughECMA10Ex", "UASRoughECMA05Ex", "UASRoughFZ10Ex", "UASRoughFZ05Ex", "UASRoughDW10Ex", "UASRoughDW05Ex")
dVar <- "dHighAnnoyPc"

seeds <- c(854196, 4735, 96452, 3651, 48652)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.25)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutRough <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

Train multiple seeds model

```{r}

resultsOutRough <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_MAE
resultsOutRough$Rsquared

```

```{r}
# store results
resdHiAnnoyFit['All rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resdHiAnnoyFit['All rough', 'MAE'] <- resultsOutRough$OOB_MAE
resdHiAnnoyFit['All rough', 'Rsquared'] <- resultsOutRough$Rsquared
resdHiAnnoyPermImp$AllRough <- resultsOutRough$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- arrange(resultsOutRough$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=CondPermImp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("All roughness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllRoughConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allRoughVar <- "UASRoughDW05Ex"

```

##### dImpulsiveness

###### Set variables

```{r}
# Impulsiveness
iVars <- c(allVar, eventVar, ambVar, "dImpulsSHMAvg", "dImpulsSHM05Ex", "dImpulsSHMPowAvg",
           "dImpulsLoudWZAvg", "dImpulsLoudWZ05Ex", "dImpulsLoudWZPowAvg",
           "dImpulsLoudWECMAAvg", "dImpulsLoudWECMA05Ex", "dImpulsLoudWECMAPowAvg", "UASImpulsSHMAvg", "UASImpulsSHM05Ex", "UASImpulsSHMPowAvg", "UASImpulsLoudWZAvg", "UASImpulsLoudWZ05Ex", "UASImpulsLoudWZPowAvg", "UASImpulsLoudWECMAAvg", "UASImpulsLoudWECMA05Ex", "UASImpulsLoudWECMAPowAvg")
dVar <- "dHighAnnoyPc"

seeds <- c(48615, 27684, 58954, 6541346, 98764346)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 251
mtry <- as.integer(length(iVars)/1.5)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutImpuls <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

Train multiple seeds model

```{r}

resultsOutImpuls <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_MAE
resultsOutImpuls$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['All impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resdHiAnnoyFit['All impuls', 'MAE'] <- resultsOutImpuls$OOB_MAE
resdHiAnnoyFit['All impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resdHiAnnoyPermImp$AllImpuls <- resultsOutImpuls$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=5.6}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- arrange(resultsOutImpuls$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=CondPermImp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + ggtitle("All impulsiveness") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllImpulsConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=5.6, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=5.6, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

Selected metric

```{r}

allImpulsVar <- "UASImpulsLoudWZPowAvg"

```

#### dSQM and loudness comparison

Now the highest importance dSQMs are ranked against each other, controlling for loudness difference.

##### Include dtonal loudness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, allSharpVar, allTonLdVar, allFluctVar, allRoughVar, allImpulsVar)
dVar <- "dHighAnnoyPc"

seeds <- c(619845, 541634, 89, 6536541, 1854)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 5501
mtry <- as.integer(length(iVars)/1.6)

```


###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs1 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_MAE
resultsOutSQMs1$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['All SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resdHiAnnoyFit['All SQMs inc tonal loud', 'MAE'] <- resultsOutSQMs1$OOB_MAE
resdHiAnnoyFit['All SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resdHiAnnoyPermImp$AllSQMs1 <- resultsOutSQMs1$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- arrange(resultsOutSQMs1$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 200))
pBar


filename <- "dHiAnnoyAllSQMsTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

##### Exclude tonal loudness

###### Set variables

```{r}

iVars <- c(allVar, eventVar, ambVar, allSharpVar, allTonalVar, allFluctVar, allRoughVar, allImpulsVar)
dVar <- "dHighAnnoyPc"

seeds <- c(418569, 269884, 848116, 4151, 8428)

```

###### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
             ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```

Selected hyperparameters

```{r}

ntree <- 1501
mtry <- as.integer(length(iVars)/1.6)

```

###### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutSQMs2 <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

Train multiple seeds model

```{r}

resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_MAE
resultsOutSQMs2$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['All SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resdHiAnnoyFit['All SQMs no tonal loud', 'MAE'] <- resultsOutSQMs2$OOB_MAE
resdHiAnnoyFit['All SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resdHiAnnoyPermImp$AllSQMs2 <- resultsOutSQMs2$conditional_permimp

```

###### Plot results

```{r, fig.width=8,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- arrange(resultsOutSQMs2$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=CondPermImp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip(ylim=c(0, 200))
pBar


filename <- "dHiAnnoyAllSQMsNoTonLdConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=2.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=2.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### dPsychoacoustic annoyance metrics

##### Set variables

```{r}

iVars <- c(ambVar, "dPsychAnnoyWidmann", "dPsychAnnoyMore", "dPsychAnnoyDi", "dPsychAnnoyTorija", "dPsychAnnoyWillemsen", "dPsychAnnoyBoucher", "UASPsychAnnoyWidmann", "UASPsychAnnoyMore", "UASPsychAnnoyDi", "UASPsychAnnoyTorija", "UASPsychAnnoyWillemsen", "UASPsychAnnoyBoucher")
dVar <- "dHighAnnoyPc"

seeds <- c(9726, 81235, 7235, 320179, 586410)


```

##### Hyperparameter tuning

```{r, fig.width=12, fig.height=4}

p <- mtryTune(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2],
              ntrees=ntrees, minsplit=minsplit, minbucket=minbucket)
p

```


Selected hyperparameters

```{r}

ntree <- 501
mtry <-  as.integer(length(iVars)/1.5)

```

##### Run model

Train preliminary model

```{r}

nperm <- 5

resultsOutPA <- crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds[1:2], ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

Train multiple seeds model

```{r}

resultsOutPA <- multi_crfReg(dataIn=stimDataNum, iVars=iVars, dVar=dVar, seeds=seeds, ntree=ntree, mtry=mtry, permImpCondThres=permImpCondThres, nperm=nperm, minsplit=minsplit, minbucket=minbucket)

# print model prediction results
resultsOutPA$OOB_RMSE
resultsOutPA$OOB_MAE
resultsOutPA$Rsquared

```

```{r}

# store results
resdHiAnnoyFit['All Psychoacoustic annoyance', 'RMSE'] <- resultsOutPA$OOB_RMSE
resdHiAnnoyFit['All Psychoacoustic annoyance', 'MAE'] <- resultsOutPA$OOB_MAE
resdHiAnnoyFit['All Psychoacoustic annoyance', 'Rsquared'] <- resultsOutPA$Rsquared
resdHiAnnoyPermImp$AllPA <- resultsOutPA$conditional_permimp

```

##### Plot results

```{r, fig.width=8,fig.height=4.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutPA.conimp <- arrange(resultsOutPA$conditional_permimp, desc(row_number()))

pBar <- ggplot(resultsOutPA.conimp) + geom_col(aes(x=factor(rownames(resultsOutPA.conimp), levels=rownames(resultsOutPA.conimp)), y=CondPermImp), fill=mycolours[10], width=0.5) + labs(x="Variable", y="Conditional variable permutation importance (% highly annoyed)") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) + coord_flip()
pBar

filename <- "dHiAnnoyAllPAConPermimp"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4.4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))
  
  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4.4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

### Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resdHiAnnoyFit, paste(outDataPath, "\\CRFdHiAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resdHiAnnoyPermImp){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resdHiAnnoyPermImp[ii])
    names(temp[[ii]]) <- names(resdHiAnnoyPermImp[ii])
  }
  openxlsx2::write_xlsx(temp, paste(outDataPath, "\\CRFdHiAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```


## Summary

Summary of results

### With tonal loudness

#### Absolute variables

```{r, fig.width=8, fig.height=4}
# combine the annoyance perm importance results

# convert each result to a tibble with rownames added to a column, renaming the data column to 'dAnnoy' etc.
resdAnnoyMnAbsPermImpTbl <- as.data.frame(resdAnnoyMnPermImp$AbsSQMs1/max(resdAnnoyMnPermImp$AbsSQMs1)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdAnnoyMnAbsPermImpTbl)[2] <- "dAnnoy"

resdHiAnnoyAbsPermImpTbl <- as.data.frame(resdHiAnnoyPermImp$AbsSQMs1/max(resdHiAnnoyPermImp$AbsSQMs1)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdHiAnnoyAbsPermImpTbl)[2] <- "dHiAnnoy"

# merge the dataframes
resAbsPermImpTbl <- list(resdAnnoyMnAbsPermImpTbl, resdHiAnnoyAbsPermImpTbl) |>
  purrr::reduce(merge, by = c('Variable'), all = T)

# rename the columns
colnames(resAbsPermImpTbl)[2:3] <- c("Mean change in annoyance", "%HA | HA' (amb.)")
resAbsPermImpTbl[is.na(resAbsPermImpTbl)] <- 0

resAbs <- tidyr::pivot_longer(resAbsPermImpTbl, cols=-Variable, names_to="Outcome", values_to="Imp")

# reorder res tibble, descending by the variable Imp grouped sum and create column with new group order as a factor
resAbs <- resAbs |> mutate(Variable_sum = sum(Imp), .by=Variable) |> arrange(desc(Variable_sum)) |> group_by(Variable_sum, Variable) |>
   mutate(Order = cur_group_id()) |> mutate(Order = as.factor(Order)) |> arrange(desc(Order))

# Reorder outcome levels
resAbs$Outcome <- factor(resAbs$Outcome, levels=c("Mean change in annoyance", "%HA | HA' (amb.)"))

# plot res as horizontal bar chart, with Imp as y axis, Variable as x axis, Outcome as fill, and Variable_sum as order, relabel x axis with Variable names
pBar <- ggplot(resAbs) + geom_col(aes(fill=Outcome, y=Imp, x=Order), colour='grey35', linewidth=0,  width=0.75, show.legend=TRUE) +
  labs(x="Variable", y="Normalised conditional variable\npermutation importance") +
  theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2)) +
  coord_flip(ylim=c(0, 1.2)) + scale_fill_manual(values=mycolours, labels=c(expression(paste(bar(Delta~A))), "%HA | HA' (amb.)")) +
  scale_x_discrete(labels=unique(rev(resAbs$Variable))) +
  guides(fill=guide_legend(title='Outcome'))

pBar + scale_y_continuous(breaks=seq(0, 1, by=0.5))

filename <- "crfAbsSQMsSummary"

if (saveplots){
  ggsave(filename=paste(filename, ".svg"), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg"))

  ggsave(filename=paste(filename, ".pdf"), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf"))
}

```

```{r, fig.width=4, fig.height=4}
# plot res as horizontal bar chart, with Imp as y axis, Variable as x axis, Outcome as fill, and Variable_sum as order, relabel x axis with Variable names
pBar <- ggplot(resAbs) + geom_col(aes(fill=Outcome, y=Imp, x=Order), colour='grey35', linewidth=0,  width=0.75, show.legend=TRUE) +
  labs(x="Variable", y="Normalised conditional variable\npermutation importance") +
  theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2), legend.position = "top") +
  coord_flip(ylim=c(0, 1.2)) +
  scale_fill_manual(values=mycolours, labels=c(expression(paste(bar(Delta~A))), "%HA | HA' (amb.)")) +
  scale_x_discrete(labels=unique(rev(resAbs$Variable))) +
  guides(fill=guide_legend(title='Outcome', nrow=2, ncol=1))

pBar + scale_y_continuous(breaks=seq(0, 1, by=0.5))

filename <- "crfAbsSQMsSummaryNw"

if (saveplots){
  ggsave(filename=paste(filename, ".svg"), width=4, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg"))

  ggsave(filename=paste(filename, ".pdf"), width=4, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf"))
}

```

#### All variables

```{r, fig.width=8, fig.height=4}
# combine the annoyance perm importance results

# convert each result to a tibble with rownames added to a column, renaming the data column to 'dAnnoy' etc.
resdAnnoyMnAllPermImpTbl <- as.data.frame(resdAnnoyMnPermImp$AllSQMs1/max(resdAnnoyMnPermImp$AllSQMs1)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdAnnoyMnAllPermImpTbl)[2] <- "dAnnoy"

resdHiAnnoyAllPermImpTbl <- as.data.frame(resdHiAnnoyPermImp$AllSQMs1/max(resdHiAnnoyPermImp$AllSQMs1)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdHiAnnoyAllPermImpTbl)[2] <- "dHiAnnoy"

# merge the dataframes
resAllPermImpTbl <- list(resdAnnoyMnAllPermImpTbl, resdHiAnnoyAllPermImpTbl) |>
  purrr::reduce(merge, by = c('Variable'), all = T)

# rename the columns
colnames(resAllPermImpTbl)[2:3] <- c("Mean change in annoyance", "%HA | HA' (amb.)")
resAllPermImpTbl[is.na(resAllPermImpTbl)] <- 0

resAll <- tidyr::pivot_longer(resAllPermImpTbl, cols=-Variable, names_to="Outcome", values_to="Imp")

# reorder res tibble, descending by the variable Imp grouped sum and create column with new group order as a factor
resAll <- resAll |> mutate(Variable_sum = sum(Imp), .by=Variable) |> arrange(desc(Variable_sum)) |> group_by(Variable_sum, Variable) |>
   mutate(Order = cur_group_id()) |> mutate(Order = as.factor(Order)) |> arrange(desc(Order))

# Reorder outcome levels
resAll$Outcome <- factor(resAll$Outcome, levels=c("Mean change in annoyance", "%HA | HA' (amb.)"))

# plot res as horizontal bar chart, with Imp as y axis, Variable as x axis, Outcome as fill, and Variable_sum as order, relabel x axis with Variable names
pBar <- ggplot(resAll) + geom_col(aes(fill=Outcome, y=Imp, x=Order), colour='grey35', linewidth=0,  width=0.75, show.legend=TRUE) +
  labs(x="Variable", y="Normalised conditional variable permutation importance") +
  theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2), legend.position = "right") + coord_flip(ylim=c(-0.1, 1.1)) +
  scale_fill_manual(values=mycolours) +
  scale_x_discrete(labels=unique(rev(resAll$Variable)))

pBar + scale_y_continuous(breaks=seq(0, 1, by=0.5))

filename <- "crfAllSQMsSummary"

if (saveplots){
  ggsave(filename=paste(filename, ".svg"), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg"))

  ggsave(filename=paste(filename, ".pdf"), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf"))
}


```

### No tonal loudness

#### Absolute variables

```{r, fig.width=8, fig.height=4}
# combine the annoyance perm importance results

# convert each result to a tibble with rownames added to a column, renaming the data column to 'dAnnoy' etc.
resdAnnoyMnAbsPermImpNoTonLdTbl <- as.data.frame(resdAnnoyMnPermImp$AbsSQMs2/max(resdAnnoyMnPermImp$AbsSQMs2)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdAnnoyMnAbsPermImpNoTonLdTbl)[2] <- "dAnnoy"

resdHiAnnoyAbsPermImpNoTonLdTbl <- as.data.frame(resdHiAnnoyPermImp$AbsSQMs2/max(resdHiAnnoyPermImp$AbsSQMs2)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdHiAnnoyAbsPermImpNoTonLdTbl)[2] <- "dHiAnnoy"

# merge the dataframes
resAbsPermImpNoTonLdTbl <- list(resdAnnoyMnAbsPermImpNoTonLdTbl, resdHiAnnoyAbsPermImpNoTonLdTbl) |>
  purrr::reduce(merge, by = c('Variable'), all = T)

# rename the columns
colnames(resAbsPermImpNoTonLdTbl)[2:3] <- c("Mean change in annoyance", "%HA | HA' (amb.)")
resAbsPermImpNoTonLdTbl[is.na(resAbsPermImpNoTonLdTbl)] <- 0

resAbsNoTonLd <- tidyr::pivot_longer(resAbsPermImpNoTonLdTbl, cols=-Variable, names_to="Outcome", values_to="Imp")

# reorder res tibble, descending by the variable Imp grouped sum and create column with new group order as a factor
resAbsNoTonLd <- resAbsNoTonLd |> mutate(Variable_sum = sum(Imp), .by=Variable) |> arrange(desc(Variable_sum)) |> group_by(Variable_sum, Variable) |>
   mutate(Order = cur_group_id()) |> mutate(Order = as.factor(Order)) |> arrange(desc(Order))

# Reorder outcome levels
resAbsNoTonLd$Outcome <- factor(resAbsNoTonLd$Outcome, levels=c("Mean change in annoyance", "%HA | HA' (amb.)"))

# plot res as horizontal bar chart, with Imp as y axis, Variable as x axis, Outcome as fill, and Variable_sum as order, relabel x axis with Variable names
pBar <- ggplot(resAbsNoTonLd) + geom_col(aes(fill=Outcome, y=Imp, x=Order), colour='grey35', linewidth=0,  width=0.75, show.legend=TRUE) +
  labs(x="Variable", y="Normalised conditional variable permutation importance") +
  theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2), legend.position = "right") + coord_flip(ylim=c(0, 1.2)) +
  scale_fill_manual(values=mycolours) +
  scale_x_discrete(labels=unique(rev(resAbsNoTonLd$Variable)))

pBar + scale_y_continuous(breaks=seq(0, 1, by=0.5))


filename <- "crfAbsSQMsNoTonLdSummary"

if (saveplots){
  ggsave(filename=paste(filename, ".svg"), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg"))

  ggsave(filename=paste(filename, ".pdf"), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf"))
}

```

#### All variables

```{r, fig.width=8, fig.height=4}
# combine the annoyance perm importance results

# convert each result to a tibble with rownames added to a column, renaming the data column to 'dAnnoy' etc.
resdAnnoyMnAllPermImpNoTonLdTbl <- as.data.frame(resdAnnoyMnPermImp$AllSQMs2/max(resdAnnoyMnPermImp$AllSQMs2)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdAnnoyMnAllPermImpNoTonLdTbl)[2] <- "dAnnoy"

resdHiAnnoyAllPermImpNoTonLdTbl <- as.data.frame(resdHiAnnoyPermImp$AllSQMs2/max(resdHiAnnoyPermImp$AllSQMs2)) |>
  tibble::rownames_to_column(var='Variable')
colnames(resdHiAnnoyAllPermImpNoTonLdTbl)[2] <- "dHiAnnoy"

# merge the dataframes
resAllPermImpNoTonLdTbl <- list(resdAnnoyMnAllPermImpNoTonLdTbl, resdHiAnnoyAllPermImpNoTonLdTbl) |>
  purrr::reduce(merge, by = c('Variable'), all = T)

# rename the columns
colnames(resAllPermImpNoTonLdTbl)[2:3] <- c("Mean change in annoyance", "%HA | HA' (amb.)")
resAllPermImpNoTonLdTbl[is.na(resAllPermImpNoTonLdTbl)] <- 0

resAllNoTonLd <- tidyr::pivot_longer(resAllPermImpNoTonLdTbl, cols=-Variable, names_to="Outcome", values_to="Imp")

# reorder res tibble, descending by the variable Imp grouped sum and create column with new group order as a factor
resAllNoTonLd <- resAllNoTonLd |> mutate(Variable_sum = sum(Imp), .by=Variable) |> arrange(desc(Variable_sum)) |> group_by(Variable_sum, Variable) |>
   mutate(Order = cur_group_id()) |> mutate(Order = as.factor(Order)) |> arrange(desc(Order))

# Reorder outcome levels
resAllNoTonLd$Outcome <- factor(resAllNoTonLd$Outcome, levels=c("Mean change in annoyance", "%HA | HA' (amb.)"))

# plot res as horizontal bar chart, with Imp as y axis, Variable as x axis, Outcome as fill, and Variable_sum as order, relabel x axis with Variable names
pBar <- ggplot(resAllNoTonLd) + geom_col(aes(fill=Outcome, y=Imp, x=Order), colour='grey35', linewidth=0,  width=0.75, show.legend=TRUE) +
  labs(x="Variable", y="Normalised conditional variable permutation importance") + theme(text = element_text(family = "serif"), panel.grid=element_line(color = rgb(235, 235, 235, 100, maxColorValue = 255), linewidth = 0.25, linetype = 2), legend.position = "right") +
  coord_flip(ylim=c(-0.1, 1.1)) +
  scale_fill_manual(values=mycolours) +
  scale_x_discrete(labels=unique(rev(resAllNoTonLd$Variable)))

pBar + scale_y_continuous(breaks=seq(0, 1, by=0.5))


filename <- "crfAllSQMsNoTonLdSummary"

if (saveplots){
  ggsave(filename=paste(filename, ".svg"), width=8, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg"))

  ggsave(filename=paste(filename, ".pdf"), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf"))
}

```

### Save the results outputs to file

```{r}
# Make a list of the summary results
resSummary <- list(resAbs, resAll, resAbsNoTonLd, resAllNoTonLd)

# Save the results
if (savedata){
  ii <- 0
  temp = list()
  for (res in resSummary){
    ii <- ii + 1
    temp[[ii]] <- data.frame(resSummary[ii])
  }
  openxlsx2::write_xlsx(temp, paste(outDataPath, "\\CRFSummary.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```