---
title: "REFMAP Listening test 1 Parts A & B analysis: Bayesian mixed models for inferential explanation"
output: html_document
date: "2026-05-07"
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(easystats)
library(conflicted)
library(brms)
library(bayestestR)
library(tidybayes)
library(bayesplot)
library(tidyverse)
library(DHARMa)
library(tictoc)
library(future)
library(future.apply)
library(mice)
library(marginaleffects)
library(priorsense)
library(posterior)
library(loo)
library(shinystan)
library(shinybrms)
library(ggdist)
library(brmsmargins)
library(viridis)
library(ggnewscale)
library(patchwork)
library(ggpmisc)
library(gginnards)
library(ggridges)

# set package parameters
theme_set(theme_bw())

n_cores <- max(1, parallelly::availableCores() - 4)
future::plan(future::multisession, workers = n_cores)

options(marginaleffects_parallel_inferences = TRUE)
options(marginaleffects_parallel = TRUE)
options(marginaleffects_parallel_packages = c("marginaleffects", "brms"))
options(marginaleffects_posterior_interval = "eti")
options(marginaleffects_posterior_center = mean)

set.seed(808)

```

Set parameters

```{r}

# plot colour scheme

mycolourlist = list(c(0, 102, 255), c(0, 204, 153), c(255, 0, 102), c(74, 111, 152), c(251, 164, 49), c(204, 153, 255), c(90, 192, 255), c(80, 245, 233), c(255, 90, 192), c(164, 201, 242), c(255, 254, 139), c(255, 243, 255))
mycolours = matrix()

for (ii in 1:length(mycolourlist)){
  mycolours[ii] = rgb(mycolourlist[[ii]][1]/255,
                      mycolourlist[[ii]][2]/255,
                      mycolourlist[[ii]][3]/255)
}

# toggle to save plots
saveplots = TRUE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption="Select output folder to save plots")
  
  if (!dir.exists(file.path(outFigPath, "svg"))){dir.create(file.path(outFigPath, "svg"))}
  if (!dir.exists(file.path(outFigPath, "pdf"))){dir.create(file.path(outFigPath, "pdf"))}
  
}

# toggle to save data
savedata = TRUE

if (savedata){
  # set output plot directory
  if (saveplots==FALSE){
    choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  }
  outDataPath <- utils::choose.dir(caption="Select output folder to save data")
}

# set global number of draws for Bayesian model predictions 
ndraws_pred <- 1000

# set flag whether to reloo models with Pareto k > 0.7
reloo_flag = FALSE


```

# Functions

## Prior predictive distribution ppd_ridgeplot
Adapted from: https://bruno.nicenboim.me/posts/posts/2026-01-09-ordinal-models/index.html

```{r}

ppd_ridgeplot <- function(fit, title = "Prior Predictive Distribution", 
                          subtitle = NULL, ndraws = 500) {
  
  yrep <- brms::posterior_predict(fit, ndraws = ndraws)

  # extract observed response categories from model
  response_name <- all.vars(fit$formula$formula)[1]
  
  observed_y <- fit$data[[response_name]]

  # preserve ordinal ordering
  response_levels <- sort(unique(observed_y))

  proportions_per_draw <- lapply(seq_len(nrow(yrep)), function(i) {
    props <- table(factor(yrep[i, ], levels = response_levels)) / ncol(yrep)
    data.frame(
      draw = i,
      response = factor(response_levels,
                        levels = response_levels,
                        ordered = TRUE),
      proportion = as.numeric(props)
    )
  })
  
  ppd_data <- do.call(rbind, proportions_per_draw)
  
  # reference line for equal occupancy
  equal_prob <- 1 / length(response_levels)
  
  ggplot(ppd_data, aes(x = proportion, y = response)) +
    ggridges::geom_density_ridges(fill = "steelblue", alpha = 0.7, scale = 0.9, stat = "binline") +
    scale_x_continuous(breaks = seq(0, 1, by = 0.2), limits = c(0, 1)) +
    geom_vline(xintercept = equal_prob, linetype = "dashed") +
    labs(title = title,
         subtitle = subtitle,
         x = "Predicted category proportion",
         y = "Response category") +
    theme_minimal(base_size = 12) +
    coord_flip()

}

```

## Beta distribution transform from arbitrary scale to (0, 1) or back again

```{r}

betaTransform <- function(x, scaleMin, scaleMax,
                          direction=c('forward', 'reverse')[1],
                          squeeze=c('none', 'basic', 'smithson')[1],
                          basic_val=1e-6){
  "Squeeze algorithm 'smithson' is from:
  Smithson, M & Verkuilen, J, 2006. A better lemon squeezer? Maximum-likelihood
  regression with beta-distributed dependent variables. Psychological Methods,
  11(1), 54-71."
  
  if (direction == 'forward') {
    # transform from original scale to (0,1)
    x_scale <- (x - scaleMin) / (scaleMax - scaleMin)
    
    if (squeeze == 'smithson') {
      
      N = length(x_scale)
      x_out <- (x_scale*(N - 1) + 0.5) / N
      
    } else if (squeeze == 'basic') {
      
      x_out <- x_scale*(1 - 2*basic_val) + basic_val
      
    } else {
      
      x_out <- x_scale
      
    }

  } else if (direction == 'reverse') {
    # transform from (0, 1) back to original scale
    x_scale <- x * (scaleMax - scaleMin) + scaleMin
    
    if (squeeze == 'smithson') {
      
      N = length(x_scale)
      x_out <- (x_scale*N - 0.5)/(N - 1)
      
    } else if (squeeze == 'basic') {
      
      x_out <- (x_scale - basic_val)/(1 - 2*basic_val)
      
    } else {
      
      x_out <- x_scale
      
    }

  } else {
    
    stop("Invalid direction argument: must be 'forward' or 'reverse'")
    
  }
  
  return(x_out)
  
}


```

## Bayesian version of McKelvey and Zavoina's pseudo-R2

From https://discourse.mc-stan.org/t/r-2-calculation-for-brm-model-with-cumulative-family-type/14752/2

```{R}
# Bayesian McKelvey-Zavoina R2 ------------------------------------------------
# Bayesian version of McKelvey and Zavoina's pseudo-R2 for binary and ordinal
# brms models (McKelvey and Zavoina, 1975). See also Gelman et al. (2018). This
# pseudo-R2 closely approximates the R2 that would have been obtained if a
# linear model had have been run on observations of the continuous latent
# variable underlying the discrete responses (Veall and Zimmermann, 1992; Hagle
# and Mitchell, 1992; Veall and Zimmermann, 1994).
Bayes_R2_MZ <- function(fit, ...) {
  y_pred <- fitted(fit, scale = "linear", summary = FALSE, ...)
  var_fit <- apply(y_pred, 1, stats::var)
  if (fit$formula$family$family == "cumulative" ||
      fit$formula$family$family == "bernoulli") {
    if (fit$formula$family$link == "probit" || 
        fit$formula$family$link == "probit_approx") {
      var_res <- 1
    }
    else if (fit$formula$family$link == "logit") {
      var_res <- pi^2 / 3 
    }
  } 
  else {
    sum_fit <- summary(fit)
    sig_res <- sum_fit$spec_pars["sigma", "Estimate"]
    var_res <- sig_res^2
  } 
  R2_MZ <- var_fit / (var_fit + var_res)
  print(
    data.frame(
      Estimate = mean(R2_MZ), 
      Est.Error = stats::sd(R2_MZ), 
      "l-95% CI" = quantile(R2_MZ, 0.025),
      "u-95% CI" = quantile(R2_MZ, 0.975),
      row.names = "Bayes_R2_MZ", 
      check.names = FALSE), 
    digits = 3)
}

```

## Rescale ggplot tick marks for variables

```{r}

rescaleTicks <- function(dataVar, dataVarScl, sep=3, ax='x'){
  
  if (ax == 'x'){
    outAx <- scale_x_continuous(breaks=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep) -
                                  (max(dataVar) - max(dataVarScl)),
                                labels=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep))

  } else if (ax == 'y'){
    outAx <- scale_y_continuous(breaks=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep) -
                                  (max(dataVar) - max(dataVarScl)),
                                labels=seq(floor(min(dataVar)),
                                           ceiling(max(dataVar)),
                                           by=sep))
  } else {
    stop("Invalid axis argument")
  }
 
  return(outAx) 
}


```

## Scaling multiple dataframes

```{r}

#' Standardise selected columns across a list of data frames
#'
#' Applies \code{datawizard::standardise()} to user-specified columns in each
#' data frame of a list, adding the result as new columns with "Scl"
#' appended to the original column name. Standardisation can be switched on
#' or off per variable via the \code{scale} argument.
#'
#' @param df_list A list of data frames.
#' @param vars    Character vector of column names to (optionally) standardise.
#' @param scale   Controls which variables get full standardisation vs.
#'                centering only:
#'                \itemize{
#'                  \item A single logical (default \code{TRUE}) applied to all \code{vars}.
#'                  \item An unnamed logical vector the same length as \code{vars},
#'                        matched by position.
#'                  \item A named logical vector, e.g. \code{c(height = TRUE, weight = FALSE)}.
#'                        Any variable in \code{vars} not named here defaults to \code{TRUE}.
#'                }
#'                Variables with \code{scale = TRUE} are run through
#'                \code{datawizard::standardise()} (centered AND scaled to SD = 1).
#'                Variables with \code{scale = FALSE} are run through
#'                \code{datawizard::center()} instead, so they are still
#'                mean-centered but left on their original scale (SD unchanged).
#'                Either way the new "Scl" column is always created.
#' @param ...     Additional arguments passed on to \code{datawizard::standardise()}
#'                and \code{datawizard::center()} (e.g. \code{robust}).
#'                Note: only arguments valid for both functions can safely be
#'                passed this way (see Details).
#'
#' @return A list of data frames (same length/order as \code{df_list}), each
#'         with new "<var>Scl" columns added.
#'
#' @examples
#' \dontrun{
#' library(datawizard)
#'
#' df1 <- data.frame(height = rnorm(10, 170, 10), weight = rnorm(10, 70, 15))
#' df2 <- data.frame(height = rnorm(10, 165, 8),  weight = rnorm(10, 65, 12))
#'
#' dfs <- list(df1, df2)
#'
#' # Standardise both variables in every data frame
#' out <- standardise_list(dfs, vars = c("height", "weight"))
#'
#' # Fully standardise height, but only center weight (weightScl keeps its
#' # original SD, just shifted to a mean of 0)
#' out2 <- standardise_list(dfs, vars = c("height", "weight"),
#'                           scale = c(height = TRUE, weight = FALSE))
#' }
#'
#' @export
standardise_list <- function(df_list, vars, scale = TRUE, ...) {

  # --- Input checks --------------------------------------------------------
  if (!is.list(df_list) || !all(vapply(df_list, is.data.frame, logical(1)))) {
    stop("`df_list` must be a list of data frames.")
  }
  if (!is.character(vars) || length(vars) == 0) {
    stop("`vars` must be a non-empty character vector of column names.")
  }
  if (!is.logical(scale)) {
    stop("`scale` must be logical (TRUE/FALSE), optionally named.")
  }

  # --- Expand `scale` into a named logical vector aligned with `vars` -----
  if (length(scale) == 1) {
    scale <- stats::setNames(rep(scale, length(vars)), vars)
  } else {
    if (is.null(names(scale))) {
      if (length(scale) != length(vars)) {
        stop("`scale` must be length 1, named, or the same length as `vars`.")
      }
      names(scale) <- vars
    }
    # Any vars not explicitly named in `scale` default to TRUE
    missing_vars <- setdiff(vars, names(scale))
    if (length(missing_vars) > 0) {
      scale <- c(scale, stats::setNames(rep(TRUE, length(missing_vars)), missing_vars))
    }
    scale <- scale[vars]  # align order, drop any extras not in `vars`
  }

  # --- Apply to each data frame --------------------------------------------
  lapply(df_list, function(df) {

    present_vars <- intersect(vars, names(df))
    absent_vars  <- setdiff(vars, names(df))

    if (length(absent_vars) > 0) {
      warning("Columns not found and skipped: ", paste(absent_vars, collapse = ", "))
    }

    for (v in present_vars) {
      new_name <- paste0(v, "Scl")

      if (isTRUE(scale[[v]])) {
        df[[new_name]] <- datawizard::standardise(df[[v]], ...)
      } else {
        df[[new_name]] <- datawizard::center(df[[v]], ...)
      }
    }

    df
  })
}

```

# Import data and wrangle

## Parts A & B combined

```{r}

subjDataPath <- utils::choose.files(caption=r"(Select refmap_listest1_testdata_BySubj.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest1_testdata_BySubj.csv", "refmap_listest1_testdata_BySubj.csv"), ncol=2))

subjData <- read.csv(subjDataPath, header=TRUE)

stimDataPath <- utils::choose.files(caption=r"(Select refmap_listest1_testdata_ByStim.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest1_testdata_ByStim.csv", "refmap_listest1_testdata_ByStim.csv"), ncol=2))

stimData <- read.csv(stimDataPath, header=TRUE, row.names=1)

```

```{r}
# definition of ordinal variable levels
UASLAeqCatsA <- c("Baseline", "42", "48", "54", "60")
SNRCatsA <- c("Baseline", "-16", "-10", "-4", "2", "8")
UASOpCatsA <- c("Baseline", "Overflight", "Landing", "Takeoff")
UASTypeCatsA <- c("Baseline", "H520", "M300", "T150")

# encode factors
subjData$ID <- factor(subjData$ID)
subjData$SessionPart <- factor(subjData$SessionPart)
subjData$UASLAeq <- factor(subjData$UASLAeq, levels=UASLAeqCatsA, order=TRUE)
subjData$SNRlevel <- factor(subjData$SNRlevel, levels=SNRCatsA, order=TRUE)
subjData$UASOperation <- factor(subjData$UASOperation, levels=UASOpCatsA)
subjData$UASType <- factor(subjData$UASType, levels=UASTypeCatsA)
subjData$AmbientEnv <- factor(subjData$AmbientEnv, levels=c("Park", "Street"))
subjData$AAM_attitude <- factor(subjData$AAM_attitude)
subjData$Home_Area <- factor(subjData$Home_Area)
subjData$Area_soundscape <- factor(subjData$Area_soundscape)
subjData$NationGeo <- factor(subjData$NationGeo)

# For Age column in subjData, replace "No answer" with NA, and then convert to numeric using dplyr and pipe
subjData <- subjData |> dplyr::mutate(Age = case_when(Age == "No answer" ~ NA_character_, TRUE ~ Age)) |>
  dplyr::mutate(Age = as.numeric(Age))

# recode AAM_attitude to 3 groups
subjData <- subjData |> dplyr::mutate(AAM_attitude3 = dplyr::recode_values(AAM_attitude,
                                                                    "Supportive" ~ "Supportive",
                                                                    c("Ambivalent",
                                                                      "Concerned") ~ "Ambiv_Concern",
                                                                      "Neutral" ~ "Neutral"))
subjData$AAM_attitude3 <- factor(subjData$AAM_attitude3, levels=c("Supportive", "Ambiv_Concern", "Neutral"))

# recode AAM_attitude to 2 groups
subjData <- subjData |> dplyr::mutate(AAM_attitude2 = dplyr::recode_values(AAM_attitude,
                                                                    "Supportive" ~ "Supportive",
                                                                    c("Ambivalent",
                                                                      "Concerned",
                                                                      "Neutral") ~ "Ambiv_Concern_Neutral"))
subjData$AAM_attitude2 <- factor(subjData$AAM_attitude2, levels=c("Supportive", "Ambiv_Concern_Neutral"))

# recode AAM_attitude to 2 other groups
subjData <- subjData |> dplyr::mutate(AAM_attitude2_2 = dplyr::recode_values(AAM_attitude,
                                                                    c("Supportive",
                                                                      "Ambivalent") ~ "Support_Ambiv",
                                                                    c("Concerned",
                                                                      "Neutral") ~ "Concern_Neutral"))

subjData$AAM_attitude2_2 <- factor(subjData$AAM_attitude2_2, levels=c("Support_Ambiv", "Concern_Neutral"))

# recode NationGeo to 4 groups
subjData <- subjData |> dplyr::mutate(NationGeo4 = dplyr::recode_values(NationGeo,
                                                               "UK" ~ "UK",
                                                               c("Africa",
                                                                 "SouthAsia") ~ "Africa_SAsia",
                                                               c("Australasia",
                                                                 "EastAsia",
                                                                 "Europe",
                                                                 "MidEast",
                                                                 "SouthAmerica") ~ "Other",
                                                               "" ~ "Unspecified"))
subjData$NationGeo4 <- factor(subjData$NationGeo4)

# recode NationGeo to 3 groups
subjData <- subjData |> dplyr::mutate(NationGeo3 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia") ~ "Africa_SAsia",
                                                                 c("Australasia",
                                                                   "EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "") ~ "Other"))
subjData$NationGeo3 <- factor(subjData$NationGeo3)

# recode NationGeo to 2 groups
subjData <- subjData |> dplyr::mutate(NationGeo2 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia",
                                                                   "Australasia",
                                                                   "EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "") ~ "Other"))
subjData$NationGeo2 <- factor(subjData$NationGeo2)


subjData$NationGeo3 <- factor(subjData$NationGeo3)

# recode Area of residence to 2 groups
subjData <- subjData |> dplyr::mutate(Home_Area2 = dplyr::recode_values(Home_Area,
                                                         "Urban" ~ "Urban",
                                                         c("Suburban",
                                                           "Rural") ~ "Suburban_Rural"))
subjData$Home_Area2 <- factor(subjData$Home_Area2)


# recode Area soundscape to 2 groups
subjData <- subjData |> dplyr::mutate(Area_soundscape2 = dplyr::recode_values(Area_soundscape,
                                                                       c("Calm",
                                                                         "Monotonous") ~ "Uneventful",
                                                                       c("Chaotic",
                                                                         "Vibrant") ~ "Eventful"))

subjData$Area_soundscape2 <- factor(subjData$Area_soundscape2)

subjData <- subjData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
subjData <- subjData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)

stimData <- stimData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
stimData <- stimData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)

# Log other variables
subjData$PartLoudMGLT05ExLog <- log(subjData$PartLoudMGLT05Ex)
subjData$PartLoudMGST05ExLog <- log(subjData$PartLoudMGST05Ex)
subjData$PartLoudMGLTPowAvgLog <- log(subjData$PartLoudMGLTPowAvg)
subjData$PartLoudMGSTPowAvgLog <- log(subjData$PartLoudMGSTPowAvg)
subjData$PartLoudSHMPowAvgLog <- log(subjData$PartLoudSHMPowAvg)

stimData$PartLoudMGLT05ExLog <- log(stimData$PartLoudMGLT05Ex)
stimData$PartLoudMGST05ExLog <- log(stimData$PartLoudMGST05Ex)
stimData$PartLoudMGLTPowAvgLog <- log(stimData$PartLoudMGLTPowAvg)
stimData$PartLoudMGSTPowAvgLog <- log(stimData$PartLoudMGSTPowAvg)
stimData$PartLoudSHMPowAvgLog <- log(stimData$PartLoudSHMPowAvg)

# reorder by participant ID and trial number
subjData <- subjData[with(subjData, order(ID, TrialNumber)), ]

# re-encode Annoyance variables as ordinal
subjData <- subjData |> dplyr::mutate(AnnoyanceOrd=factor(Annoyance,
                                                          levels=seq(0, 10, by=1),
                                                          ordered=TRUE),
                                      dAnnoyanceOrd=factor(dAnnoyance,
                                                           levels=seq(-10, 10, by=1),
                                                           ordered=TRUE))

# add a rescaled dAnnoyance variable
subjData <- subjData |>
  dplyr::mutate(AnnoyanceOrdBetaScl = betaTransform(Annoyance, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyanceOrdBetaScl = betaTransform(dAnnoyance, -10, 10,
                                                     direction='forward', squeeze='none'))


# add a rescaled dAnnoyance variable
stimData <- stimData |>
  dplyr::mutate(AnnoyMeanOrdBetaScl = betaTransform(AnnoyMean, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyMeanOrdBetaScl = betaTransform(dAnnoyMean, -10, 10,
                                                     direction='forward', squeeze='none'))

# omit ambient-only stimuli
subjDataNoAmb <- subjData |> dplyr::filter(UASLAeq != "Baseline")
stimDataNoAmb <- stimData |> dplyr::filter(UASLAeq != "Baseline")

```

## filter and impute missing age data

```{R}

# filter data to exclude the missing age participant and the missing response data
subjDataNoAmb.cc <- subjDataNoAmb |> dplyr::filter(!is.na(Age) & !is.na(TrialNumber))

# first create a participant-level dataset
subj_dat <- subjData |> dplyr::select(ID, Age) |> dplyr::distinct()

# create a median imputation for missing age data
subj_dat.med <- subj_dat |> dplyr::mutate(Age = ifelse(is.na(Age),
                                                   median(Age, na.rm=TRUE),
                                                   Age))

# now merge the imputed age data back into the main dataset
subjData.med <- subjData |> dplyr::select(-Age) |> dplyr::left_join(subj_dat.med, by="ID")

# now filter the dataset to exclude ambient-only stimuli
subjDataNoAmb.med <- subjData.med |> dplyr::filter(UASLAeq != "Baseline") |>
  droplevels()

# use multiple imputation to impute missing age data
imp_data <- mice::mice(subj_dat, m=5, method='pmm', seed=808, printFlag=F)

completed_list <- mice::complete(imp_data, action='all')

# merge the completed datasets back into a main dataset list and filter baseline
subjData.imp <- lapply(completed_list,
                       function(df) {subjData |>
                           dplyr::select(-Age) |>
                           dplyr::left_join(df, by="ID")})

subjDataNoAmb.imp <- lapply(subjData.imp,
                            function(df) {subjData |>
                                dplyr::filter(UASLAeq != "Baseline") |>
                                droplevels()
                            } )

```

## rescaling variables

```{r}

out <- standardise_list(list(subjData, subjDataNoAmb, subjDataNoAmb.cc, subjDataNoAmb.med, subjDataNoAmb.imp),
                        vars = c("TrialNumber"),
                        scale = TRUE)

subjData <- out[[1]]
subjDataNoAmb <- out[[2]]
subjDataNoAmb.cc <- out[[3]]
subjDataNoAmb.med <- out[[4]]
subjDataNoAmb.imp <- out[[5]]

# rescale trial number variables separately for each session part
subjData <- rbind(subjData[subjData$SessionPart == "A", ] |>
                    dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)),
                    subjData[subjData$SessionPart == "B", ] |>
                    dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE))) |>
  droplevels()

subjDataNoAmb <- rbind(subjDataNoAmb[subjDataNoAmb$SessionPart == "A", ] |>
                         dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)),
                    subjDataNoAmb[subjDataNoAmb$SessionPart == "B", ] |>
                      dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE))) |>
  droplevels()

subjDataNoAmb.cc <- rbind(subjDataNoAmb.cc[subjDataNoAmb.cc$SessionPart == "A", ] |>
                            dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)),
                    subjDataNoAmb.cc[subjDataNoAmb.cc$SessionPart == "B", ] |>
                      dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE))) |>
  droplevels()

subjDataNoAmb.med <- rbind(subjDataNoAmb.med[subjDataNoAmb.med$SessionPart == "A", ] |>
                             dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)),
                    subjDataNoAmb.med[subjDataNoAmb.med$SessionPart == "B", ] |>
                      dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE))) |>
  droplevels()

subjDataNoAmb.imp <- rbind(subjDataNoAmb.imp[subjDataNoAmb.imp$SessionPart == "A", ] |>
                             dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)),
                    subjDataNoAmb.imp[subjDataNoAmb.imp$SessionPart == "B", ] |>
                      dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE))) |>
  droplevels()

```

# Annoyance

## Model 0 formula

```{R}

m0formula <- AnnoyanceOrd ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

```

## m0a: maximal ordinal model for annoyance, complete cases

```{r}

emp_thresh0a <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb.cc$AnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh0a <- emp_thresh0a[is.finite(emp_thresh0a)]

priors0a <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh0a,", 1)"), class = "Intercept", coef = 1:length(emp_thresh0a))
)

# extract the data for the model
m0aData <- subjDataNoAmb.cc[, all.vars(m0formula), drop=FALSE]

tic()
m0aPriors <- brms::brm(m0formula,
                 data=m0aData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0a,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m0a_ppd <- ppd_ridgeplot(m0aPriors, ndraws = 100)
m0a_ppd

m0aPriorCheck <- brms::pp_check(m0aPriors, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating category index")
m0aPriorCheck

tic()
m0a <- brms::brm(m0formula,
                 data=m0aData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0a,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m0a <- brms::add_criterion(m0a, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m0a$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0a))
m0a$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0a, re_formula=NA))
m0a$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0a, re_formula=NULL))
m0a$criteria$bayes_R2_MZ <- as.data.frame(Bayes_R2_MZ(m0a))

m0aPostCheck <- brms::pp_check(m0a, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating category index")
m0aPostCheck

```

## m0b: maximal ordinal model for annoyance, median imputed

```{r}

emp_thresh0b <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb$AnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh0b <- emp_thresh0b[is.finite(emp_thresh0b)]

priors0b <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh0b,", 1)"), class = "Intercept", coef = 1:length(emp_thresh0b))
)

# extract the data for the model
m0bData <- subjDataNoAmb.med[, all.vars(m0formula), drop=FALSE]

tic()
m0bPriors <- brms::brm(m0formula,
                 data=m0bData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0b,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m0b_ppd <- ppd_ridgeplot(m0bPriors, ndraws = 100)
m0b_ppd

m0bPriorCheck <- brms::pp_check(m0bPriors, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating category index")
m0bPriorCheck

tic()
m0b <- brms::brm(m0formula,
                 data=m0bData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0b,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m0b <- brms::add_criterion(m0b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m0b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0b))
m0b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0b, re_formula=NA))
m0b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0b, re_formula=NULL))
m0b$criteria$bayes_R2_MZ <- as.data.frame(Bayes_R2_MZ(m0b))

m0bPostCheck <- brms::pp_check(m0b, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating category index")
m0bPostCheck

```

## m0c: maximal ordinal model for annoyance, multiple imputed

```{r}

emp_thresh0c <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb$AnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh0c <- emp_thresh0c[is.finite(emp_thresh0c)]

priors0c <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh0c,", 1)"), class = "Intercept", coef = 1:length(emp_thresh0c))
)

# extract the data for the model
m0cData <- lapply(subjDataNoAmb.imp,
                      function(df) {df[, all.vars(m0formula), drop=FALSE]})

tic()
m0cPriors <- brms::brm_multiple(m0formula,
                 data=m0cData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0c,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m0c_ppd <- ppd_ridgeplot(m0cPriors, ndraws = 100)
m0c_ppd

m0cPriorCheck <- brms::pp_check(m0cPriors, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating category index")
m0cPriorCheck

tic()
m0c <- brms::brm_multiple(m0formula,
                 data=m0cData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior = priors0c,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m0c <- brms::add_criterion(m0c, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m0c$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0c))
m0c$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0c, re_formula=NA))
m0c$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0c, re_formula=NULL))
m0c$criteria$bayes_R2_MZ <- as.data.frame(Bayes_R2_MZ(m0c))

m0cPostCheck <- brms::pp_check(m0c, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating category index")
m0cPostCheck

```

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m0c_bCI_range <- bayestestR::hdi(m0c, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m0c_bCI_wsf <- m0c_bCI_range |>
  dplyr::filter(Parameter %in% c("b_SessionPartB", "b_UASTypeM300", "b_UASTypeT150", 
                                 "b_UASOperationLanding", "b_UASOperationTakeoff",
                                 "b_AmbientEnvStreet"))
p_m0c_bCI_wsf <- plot(m0c_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m0c_bCI_wsf

filename <- "PtsABAnnoyMnCatModbCI_brmsCo_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m0c_bCI_wsfi <- m0c_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvStreet:UASOperationLanding",
                                 "b_AmbientEnvStreet:UASOperationTakeoff",
                                 "b_AmbientEnvStreet:UASTypeM300",
                                 "b_AmbientEnvStreet:UASTypeT150",
                                 "b_UASOperationLanding:UASTypeM300",
                                 "b_UASOperationLanding:UASTypeT150"))
p_m0c_bCI_wsfi <- plot(m0c_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m0c_bCI_wsfi

filename <- "PtsABAnnoyMnCatModbCI_brmsCo_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m0c_bCI_wsc <- m0c_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m0c_bCI_wsc <- plot(m0c_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m0c_bCI_wsc

filename <- "PtsABAnnoyMnCatModbCI_brmsCo_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m0c_bCI_wscfi <- m0c_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvStreet",
                                 "b_UASLAEMaxLRScl:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:UASTypeM300",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeM300",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m0c_bCI_wscfi <- plot(m0c_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m0c_bCI_wscfi

filename <- "PtsABAnnoyMnCatModbCI_brmsCo_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m0c_bCI_bsf <- m0c_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Uneventful"))
p_m0c_bCI_bsf <- plot(m0c_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m0c_bCI_bsf

filename <- "PtsABAnnoyMnCatModbCI_brmsCo_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m0c_bCI_bsc <- m0c_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NSSTotal"))
p_m0c_bCI_bsc <- plot(m0c_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m0c_bCI_bsc

filename <- "PtsABAnnoyMnCatModbCI_brmsCo_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

## m1: maximal ordbeta model for annoyance, median imputed

### model 1 formula

```{r}

m1formula <- update(m0formula, AnnoyanceOrdBetaScl ~ .)

```

### run model

```{r}

priors1 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior(gamma(2, 0.1), class='phi')
)

# extract the data for the model
m1Data <- subjDataNoAmb.med[, all.vars(m1formula), drop=FALSE]

tic()
m1Priors <- brms::brm(m1formula,
                 data=m1Data,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors1, sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m1PriorCheck <- brms::pp_check(m1Priors, ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating")
m1PriorCheck

tic()
m1 <- brms::brm(m1formula,
                 data=m1Data,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors1,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m1 <- brms::add_criterion(m1, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m1$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1))
m1$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1, re_formula=NA))
m1$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1, re_formula=NULL))

m1PostCheck <- brms::pp_check(m1, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating")
m1PostCheck

```

### model 1b formula

```{r}

m1bformula <- AnnoyanceOrdBetaScl ~ 1 + SessionPart*PartTrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

```

### run modelb

```{r}

priors1b <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='PartTrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior(gamma(2, 0.1), class='phi')
)

# extract the data for the model
m1bData <- subjDataNoAmb.med[, all.vars(m1bformula), drop=FALSE]

tic()
m1bPriors <- brms::brm(m1bformula,
                 data=m1bData,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors1b, sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m1bPriorCheck <- brms::pp_check(m1bPriors, ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating")
m1bPriorCheck

tic()
m1b <- brms::brm(m1bformula,
                 data=m1bData,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors1b,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m1b <- brms::add_criterion(m1b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m1b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1b))
m1b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1b, re_formula=NA))
m1b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1b, re_formula=NULL))

m1bPostCheck <- brms::pp_check(m1b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean annoyance rating")
m1bPostCheck

```

#### compare

```{R}

loo::loo(m1)
loo::loo(m1b)

m1b_loo <- loo::loo_compare(m1, m1b, criterion='loo')
m1b_loo

```

### analyse results

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m1_bCI_range <- bayestestR::hdi(m1, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m1_bCI_wsf <- m1_bCI_range |>
  dplyr::filter(Parameter %in% c("b_SessionPartB", "b_UASTypeM300", "b_UASTypeT150", 
                                 "b_UASOperationLanding", "b_UASOperationTakeoff",
                                 "b_AmbientEnvStreet"))
p_m1_bCI_wsf <- plot(m1_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1_bCI_wsf

filename <- "PtsABAnnoyMnCatModbCI_brmsOb_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m1_bCI_wsfi <- m1_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvStreet:UASOperationLanding",
                                 "b_AmbientEnvStreet:UASOperationTakeoff",
                                 "b_AmbientEnvStreet:UASTypeM300",
                                 "b_AmbientEnvStreet:UASTypeT150",
                                 "b_UASOperationLanding:UASTypeM300",
                                 "b_UASOperationLanding:UASTypeT150"))
p_m1_bCI_wsfi <- plot(m1_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1_bCI_wsfi

filename <- "PtsABAnnoyMnCatModbCI_brmsOb_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m1_bCI_wsc <- m1_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m1_bCI_wsc <- plot(m1_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1_bCI_wsc

filename <- "PtsABAnnoyMnCatModbCI_brmsOb_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m1_bCI_wscfi <- m1_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvStreet",
                                 "b_UASLAEMaxLRScl:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:UASTypeM300",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeM300",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m1_bCI_wscfi <- plot(m1_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1_bCI_wscfi

filename <- "PtsABAnnoyMnCatModbCI_brmsOb_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m1_bCI_bsf <- m1_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Uneventful"))
p_m1_bCI_bsf <- plot(m1_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1_bCI_bsf

filename <- "PtsABAnnoyMnCatModbCI_brmsOb_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m1_bCI_bsc <- m1_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NSSTotal"))
p_m1_bCI_bsc <- plot(m1_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1_bCI_bsc

filename <- "PtsABAnnoyMnCatModbCI_brmsOb_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### analyse population-averaged effects (not conditional effects) using marginaleffects

```{R}

m1DataFit <- insight::get_data(m1)

m1predType <- marginaleffects::avg_predictions(m1, newdata=subset(m1DataFit,
                                                             UASEvents==1),
                                                  variables=list(UASLAEMaxLRScl=seq(
                                                      min(stimDataNoAmb$UASLAEMaxLRScl),
                                                      max(stimDataNoAmb$UASLAEMaxLRScl),
                                                      length.out=25)),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnv",
                                                       "UASEvents"),
                                               ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, 0, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

m1predOp <- marginaleffects::avg_predictions(m1, newdata=subset(m1DataFit,
                                                        UASEvents==1),
                                                variables=list(UASLAEMaxLRScl=seq(
                                                    min(stimDataNoAmb$UASLAEMaxLRScl),
                                                    max(stimDataNoAmb$UASLAEMaxLRScl),
                                                    length.out=25)),
                                                by=c("UASLAEMaxLRScl",
                                                     "UASOperation",
                                                     "AmbientEnv",
                                                     "UASEvents"),
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, 0, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

m1predEnv <- marginaleffects::avg_predictions(m1, newdata=subset(m1DataFit,
                                                        UASEvents==1),
                                                variables=list(UASLAEMaxLRScl=seq(
                                                    min(stimDataNoAmb$UASLAEMaxLRScl),
                                                    max(stimDataNoAmb$UASLAEMaxLRScl),
                                                    length.out=25)),
                                                by=c("UASLAEMaxLRScl",
                                                     "AmbientEnv",
                                                     "UASEvents"),
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, 0, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))


m1predEvt <- marginaleffects::avg_predictions(m1, newdata=subset(m1DataFit,
                                                                 AmbientEnv=="Park" &
                                                                 UASOperation=="Overflight"),
                                            variables=list(UASLAEMaxLRScl=seq(
                                                min(stimDataNoAmb$UASLAEMaxLRScl),
                                                max(stimDataNoAmb$UASLAEMaxLRScl),
                                                length.out=25)),
                                            by=c("UASLAEMaxLRScl",
                                                 "AmbientEnv",
                                                 "UASEvents",
                                                 "UASOperation"),
                                               ndraws=ndraws_pred,
                                          transform=\(x) betaTransform(x, 0, 10,
                                                                       direction='reverse',
                                                                       squeeze='none'))

m1predEvt2 <- marginaleffects::avg_predictions(m1, newdata=subset(m1DataFit,
                                                                  AmbientEnv=="Park" &
                                                                  UASOperation=="Overflight"),
                                              variables=list(UASLAEMaxLRScl=c(6, 12),
                                                               UASType=c("H520", "T150")),
                                              by=c("UASLAEMaxLRScl",
                                                   "AmbientEnv",
                                                   "UASEvents",
                                                   "UASOperation",
                                                   "SessionPart"),
                                               ndraws=ndraws_pred,
                                            transform=\(x) betaTransform(x, 0, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m1predAtt <- marginaleffects::avg_predictions(m1, newdata=m1DataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "AAM_attitude2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, 0, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m1predAoR <- marginaleffects::avg_predictions(m1, newdata=m1DataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "Home_Area2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, 0, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m1predScp <- marginaleffects::avg_predictions(m1, newdata=m1DataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "Area_soundscape2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, 0, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

```

#### visualise plots of PA effects

```{R}

p1 <- ggplot(data=subset(m1predType, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=AnnoyMean,
                                                 colour=UASType, shape=UASType),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASType),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASType), linewidth=1) +
              
              scale_color_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(10, 11, 12)) +
              
              guides(colour=guide_legend(title="UAS type", reverse=FALSE),
                     fill=guide_legend(title="UAS type", reverse=FALSE),
                     shape=guide_legend(title="UAS type", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean annoyance rating") +
              facet_grid(rows = vars(AmbientEnv))

p2 <- ggplot(data=subset(m1predOp, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=AnnoyMean,
                                                 colour=UASOperation, shape=UASOperation),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASOperation),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASOperation), linewidth=1) +
              
              scale_color_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(9, 6, 2)) +
              
              guides(colour=guide_legend(title="UAS operation", reverse=TRUE),
                     fill=guide_legend(title="UAS operation", reverse=TRUE),
                     shape=guide_legend(title="UAS operation", reverse=TRUE)) +
              
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean annoyance rating") +
              facet_grid(rows = vars(AmbientEnv))

p3 <- ggplot(data=subset(m1predEnv, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14),
                    axis.title.x=element_blank(),
                    axis.text.x=element_blank(),
                    axis.ticks.x=element_blank()) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=AnnoyMean,
                                                 colour=AmbientEnv, shape=AmbientEnv),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AmbientEnv),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AmbientEnv), linewidth=1) +
              
              scale_color_viridis(option='magma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.7) +
              scale_fill_viridis(option='magma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.7) +
              scale_shape_manual(values=c(1, 3)) +
              
              guides(colour=guide_legend(title="Amb. env.", reverse=FALSE),
                     fill=guide_legend(title="Amb. env.", reverse=FALSE),
                     shape=guide_legend(title="Amb. env.", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(y="Mean annoyance rating")


p4 <- ggplot(data=subset(m1predEvt, AmbientEnv=='Park' & UASOperation=='Overflight')) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' & UASOperation=='Overflight'),
                         aes(x=UASLAEMaxLRScl, y=AnnoyMean,
                             colour=factor(UASEvents), shape=factor(UASEvents)),
                         alpha=0.55, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=factor(UASEvents)),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=factor(UASEvents)), linewidth=1) +
              
              scale_color_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(4, 5, 7, 8)) +
              
              guides(colour=guide_legend(title="UAS events", reverse=TRUE),
                     fill=guide_legend(title="UAS events", reverse=TRUE),
                     shape=guide_legend(title="UAS events", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean annoyance rating")

(p1 | p2) + (p3 / p4)

filename <- "PtsABAnnoyMnCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# add faint dashed grey major grid lines to p1, p2, p3, p4 and remove minor grid lines and point data
p1b <- p1 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                  panel.grid.minor = element_blank())
p1b <- gginnards::delete_layers(p1b, "GeomPoint")
p2b <- p2 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p2b <- gginnards::delete_layers(p2b, "GeomPoint")
p3b <- p3 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p3b <- gginnards::delete_layers(p3b, "GeomPoint")
p4b <- p4 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p4b <- gginnards::delete_layers(p4b, "GeomPoint")

(p1b | p2b) + (p3b / p4b)

filename <- "PtsABAnnoyMnCatModGrid_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p3c <- p3 + theme(axis.title.x=element_text(family = "serif", size=14),
                  axis.text.x=element_text(family = "serif", size=14),
                  axis.ticks.x=element_line(colour="black", linewidth=1)) + 
        labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)))

filename <- "PtsABAnnoyMnCatModEnv_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=5, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=5, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p5 <- ggplot(data=subset(m1predEvt2, UASOperation=="Overflight" & AmbientEnv=="Park" & SessionPart=="B")) +
              theme(panel.grid = element_blank(), aspect.ratio=0.8,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' &
                                       UASOperation=='Overflight' & SessionPart=='B'),
                         aes(x=UASEvents, y=AnnoyMean,
                             colour=UASLAEMaxLR, shape=UASType),
                         alpha=0.35, size=2) +
  
              scale_color_viridis(option='inferno', direction=1, discrete=FALSE, begin = 0.2, end = 0.8,
                                  breaks=c(73, 79)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE)) +
  
              ggnewscale::new_scale_color() +
  
              geom_ribbon(aes(x=UASEvents, ymin=conf.low, ymax=conf.high, fill=factor(UASLAEMaxLRScl)),
                          alpha=0.05) +
  
              geom_line(aes(x=UASEvents, y=estimate, colour=factor(UASLAEMaxLRScl)), linewidth=1, alpha=0.5) +

              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_shape_manual(values=c(10, 11, 12)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     fill=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     shape=guide_legend(title="UAS type", reverse=FALSE)) +
            
              scale_x_continuous(breaks=c(1, 3, 5, 9), labels=c(1, 3, 5, 9)) +
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(3, 8)) +
              
              labs(x="Number of UAS Overflight events", y="Mean annoyance rating")

p5

filename <- "PtsABAnnoyMnCatModEvtComp_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p6 <- ggplot(data=m1predAtt) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AAM_attitude2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AAM_attitude2), linewidth=1) +
              
              scale_color_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="AAM attitude", reverse=TRUE),
                     fill=guide_legend(title="AAM attitude", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean annoyance rating")

p7 <- ggplot(data=m1predAoR) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Home_Area2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Home_Area2), linewidth=1) +
              
              scale_color_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Area of residence", reverse=FALSE),
                     fill=guide_legend(title="Area of residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean annoyance rating")


p8 <- ggplot(data=m1predScp) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Area_soundscape2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Area_soundscape2), linewidth=1) +
              
              scale_color_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Soundscape at residence", reverse=FALSE),
                     fill=guide_legend(title="Soundscape at residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(0, 10, by=1), limits=c(0, 10)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean annoyance rating")


p6 + p7 + p8

filename <- "PtsABAnnoyMnAttAoRScpCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```


# dAnnoyance

## m3: maximal ordbeta model

### Formula

```{R}

m3formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

```

### run model 3

```{r}

priors3 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior(gamma(2, 0.1), class='phi')
)

m3Data <- subjDataNoAmb.med[, all.vars(m3formula), drop=FALSE]

tic()
m3Priors <- brms::brm(m3formula,
                 data=m3Data,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors3, sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m3PriorCheck <- brms::pp_check(m3Priors, ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3PriorCheck

tic()
m3 <- brms::brm(m3formula, data=m3Data,
                family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m3 <- brms::add_criterion(m3, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m3$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m3))
m3$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m3, re_formula=NA))
m3$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m3, re_formula=NULL))

m3PostCheck <- brms::pp_check(m3, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3PostCheck

```

```{R, fig.width=16, fig.height=8}

m3PostCheckEnv <- brms::pp_check(m3, type='dens_overlay_grouped', ndraws=100, group='AmbientEnv') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3PostCheckEnv

m3PostCheckEvt <- brms::pp_check(m3, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3PostCheckEvt

m3PostCheckType <- brms::pp_check(m3, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3PostCheckType

m3PostCheckOp <- brms::pp_check(m3, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3PostCheckOp

m3PostCheckLAE <- brms::pp_check(m3, type='dens_overlay_grouped', ndraws=100, group='UASLAEMaxLRScl',) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  facet_wrap(~group, labeller = labeller(group = function(x) round(as.numeric(x), digits=2))) +
  labs(x="Mean change in annoyance")
m3PostCheckLAE

```

### run model 3b

```{R}

priors3b <- c(
  # mean model
  set_prior("normal(0, 2)", class='b', dpar='mu'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl', dpar='mu'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB', dpar='mu'),
  # precision model
  brms::prior(normal(0, 1), class = 'Intercept', dpar = 'phi'),
  brms::prior(normal(0, 0.5), class = 'b', dpar = 'phi')
)

tic()
m3b <- brms::brm(brms::bf(m3formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m3b <- brms::add_criterion(m3b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m3b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m3b))
m3b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m3b, re_formula=NA))
m3b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m3b, re_formula=NULL))

m3bPostCheck <- brms::pp_check(m3b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3bPostCheck

```

```{R, fig.width=16, fig.height=8}

m3bPostCheckEnv <- brms::pp_check(m3b, type='dens_overlay_grouped', ndraws=100, group='AmbientEnv') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3bPostCheckEnv

```

#### compare

```{R}

loo::loo(m3)
loo::loo(m3b)

m3b_loo <- loo::loo_compare(m3, m3b, criterion='loo')
m3b_loo

```

### run model 3c

```{R}

tic()
m3c <- brms::brm(brms::bf(m3formula, phi ~ 1 + AmbientEnv + UASOperation + UASType),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m3c <- brms::add_criterion(m3c, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m3c$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m3c))
m3c$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m3c, re_formula=NA))
m3c$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m3c, re_formula=NULL))

m3cPostCheck <- brms::pp_check(m3c, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m3cPostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m3c)

m3c_loo <- loo::loo_compare(m3, m3b, m3c, criterion='loo')
m3c_loo

```

### analyse m3b results

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m3b_bCI_range <- bayestestR::hdi(m3b, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m3b_bCI_wsf <- m3b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_SessionPartB", "b_UASTypeM300", "b_UASTypeT150", 
                                 "b_UASOperationLanding", "b_UASOperationTakeoff",
                                 "b_AmbientEnvStreet"))
p_m3b_bCI_wsf <- plot(m3b_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m3b_bCI_wsf

filename <- "PtsABdAnnoyMnCatModbCI_brmsOb_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m3b_bCI_wsfi <- m3b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvStreet:UASOperationLanding",
                                 "b_AmbientEnvStreet:UASOperationTakeoff",
                                 "b_AmbientEnvStreet:UASTypeM300",
                                 "b_AmbientEnvStreet:UASTypeT150",
                                 "b_UASOperationLanding:UASTypeM300",
                                 "b_UASOperationLanding:UASTypeT150"))
p_m3b_bCI_wsfi <- plot(m3b_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m3b_bCI_wsfi

filename <- "PtsABdAnnoyMnCatModbCI_brmsOb_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m3b_bCI_wsc <- m3b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m3b_bCI_wsc <- plot(m3b_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m3b_bCI_wsc

filename <- "PtsABdAnnoyMnCatModbCI_brmsOb_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m3b_bCI_wscfi <- m3b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvStreet",
                                 "b_UASLAEMaxLRScl:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:UASTypeM300",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeM300",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m3b_bCI_wscfi <- plot(m3b_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m3b_bCI_wscfi

filename <- "PtsABdAnnoyMnCatModbCI_brmsOb_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m3b_bCI_bsf <- m3b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Uneventful"))
p_m3b_bCI_bsf <- plot(m3b_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m3b_bCI_bsf

filename <- "PtsABdAnnoyMnCatModbCI_brmsOb_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m3b_bCI_bsc <- m3b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NSSTotal"))
p_m3b_bCI_bsc <- plot(m3b_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m3b_bCI_bsc

filename <- "PtsABdAnnoyMnCatModbCI_brmsOb_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### analyse population-averaged effects (not conditional effects) using marginaleffects

```{R}

m3bDataFit <- insight::get_data(m3b)

m3bpredType <- marginaleffects::avg_predictions(m3b, newdata=subset(m3bDataFit,
                                                             UASEvents==1),
                                                  variables=list(UASLAEMaxLRScl=seq(
                                                      min(stimDataNoAmb$UASLAEMaxLRScl),
                                                      max(stimDataNoAmb$UASLAEMaxLRScl),
                                                      length.out=25)),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnv",
                                                       "UASEvents"),
                                               ndraws=ndraws_pred,
                                               re_formula = NULL,
                                               allow_new_levels = TRUE,
                                               sample_new_levels = "gaussian",
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

m3bpredOp <- marginaleffects::avg_predictions(m3b, newdata=subset(m3bDataFit,
                                                        UASEvents==1),
                                                variables=list(UASLAEMaxLRScl=seq(
                                                    min(stimDataNoAmb$UASLAEMaxLRScl),
                                                    max(stimDataNoAmb$UASLAEMaxLRScl),
                                                    length.out=25)),
                                                by=c("UASLAEMaxLRScl",
                                                     "UASOperation",
                                                     "AmbientEnv",
                                                     "UASEvents"),
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

m3bpredEnv <- marginaleffects::avg_predictions(m3b, newdata=subset(m3bDataFit,
                                                        UASEvents==1),
                                                variables=list(UASLAEMaxLRScl=seq(
                                                    min(stimDataNoAmb$UASLAEMaxLRScl),
                                                    max(stimDataNoAmb$UASLAEMaxLRScl),
                                                    length.out=25)),
                                                by=c("UASLAEMaxLRScl",
                                                     "AmbientEnv",
                                                     "UASEvents"),
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))


m3bpredEvt <- marginaleffects::avg_predictions(m3b, newdata=subset(m3bDataFit,
                                                                 AmbientEnv=="Park" &
                                                                 UASOperation=="Overflight"),
                                            variables=list(UASLAEMaxLRScl=seq(
                                                min(stimDataNoAmb$UASLAEMaxLRScl),
                                                max(stimDataNoAmb$UASLAEMaxLRScl),
                                                length.out=25)),
                                            by=c("UASLAEMaxLRScl",
                                                 "AmbientEnv",
                                                 "UASEvents",
                                                 "UASOperation"),
                                               ndraws=ndraws_pred,
                                          transform=\(x) betaTransform(x, -10, 10,
                                                                       direction='reverse',
                                                                       squeeze='none'))

m3bpredEvt2 <- marginaleffects::avg_predictions(m3b, newdata=subset(m3bDataFit,
                                                                  AmbientEnv=="Park" &
                                                                  UASOperation=="Overflight"),
                                              variables=list(UASLAEMaxLRScl=c(6, 12),
                                                               UASType=c("H520", "T150")),
                                              by=c("UASLAEMaxLRScl",
                                                   "AmbientEnv",
                                                   "UASEvents",
                                                   "UASOperation",
                                                   "SessionPart"),
                                               ndraws=ndraws_pred,
                                            transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m3bpredAtt <- marginaleffects::avg_predictions(m3b, newdata=m3bDataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "AAM_attitude2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m3bpredAoR <- marginaleffects::avg_predictions(m3b, newdata=m3bDataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "Home_Area2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m3bpredScp <- marginaleffects::avg_predictions(m3b, newdata=m3bDataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "Area_soundscape2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m3bpredSex <- marginaleffects::avg_predictions(m3b, newdata=m3bDataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "Sex"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

m3bpredNat <- marginaleffects::avg_predictions(m3b, newdata=m3bDataFit,
                                             variables=list(UASLAEMaxLRScl=seq(
                                              min(stimDataNoAmb$UASLAEMaxLRScl),
                                              max(stimDataNoAmb$UASLAEMaxLRScl),
                                              length.out=25)),
                                             by=c("UASLAEMaxLRScl", "NationGeo2"),
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

```

#### visualise plots of PA effects

```{R}

p1 <- ggplot(data=subset(m3bpredType, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                                                 colour=UASType, shape=UASType),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASType),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASType), linewidth=1) +
              
              scale_color_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(10, 11, 12)) +
              
              guides(colour=guide_legend(title="UAS type", reverse=FALSE),
                     fill=guide_legend(title="UAS type", reverse=FALSE),
                     shape=guide_legend(title="UAS type", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance") +
              facet_grid(rows = vars(AmbientEnv))

p2 <- ggplot(data=subset(m3bpredOp, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                                                 colour=UASOperation, shape=UASOperation),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASOperation),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASOperation), linewidth=1) +
              
              scale_color_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(9, 6, 2)) +
              
              guides(colour=guide_legend(title="UAS operation", reverse=TRUE),
                     fill=guide_legend(title="UAS operation", reverse=TRUE),
                     shape=guide_legend(title="UAS operation", reverse=TRUE)) +
              
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance") +
              facet_grid(rows = vars(AmbientEnv))

p3 <- ggplot(data=subset(m3bpredEnv, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14),
                    axis.title.x=element_blank(),
                    axis.text.x=element_blank(),
                    axis.ticks.x=element_blank()) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                                                 colour=AmbientEnv, shape=AmbientEnv),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AmbientEnv),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AmbientEnv), linewidth=1) +
              
              scale_color_viridis(option='magma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.7) +
              scale_fill_viridis(option='magma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.7) +
              scale_shape_manual(values=c(1, 3)) +
              
              guides(colour=guide_legend(title="Amb. env.", reverse=FALSE),
                     fill=guide_legend(title="Amb. env.", reverse=FALSE),
                     shape=guide_legend(title="Amb. env.", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(y="Mean change in annoyance")

p4 <- ggplot(data=subset(m3bpredEvt, AmbientEnv=='Park' & UASOperation=='Overflight')) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' & UASOperation=='Overflight'),
                         aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                             colour=factor(UASEvents), shape=factor(UASEvents)),
                         alpha=0.55, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=factor(UASEvents)),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=factor(UASEvents)), linewidth=1) +
              
              scale_color_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(4, 5, 7, 8)) +
              
              guides(colour=guide_legend(title="UAS events", reverse=TRUE),
                     fill=guide_legend(title="UAS events", reverse=TRUE),
                     shape=guide_legend(title="UAS events", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

(p1 | p2) + (p3 / p4)

filename <- "PtsABdAnnoyMnCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# add faint dashed grey major grid lines to p1, p2, p3, p4 and remove minor grid lines and point data
p1b <- p1 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                  panel.grid.minor = element_blank())
p1b <- gginnards::delete_layers(p1b, "GeomPoint")
p2b <- p2 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p2b <- gginnards::delete_layers(p2b, "GeomPoint")
p3b <- p3 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p3b <- gginnards::delete_layers(p3b, "GeomPoint")
p4b <- p4 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p4b <- gginnards::delete_layers(p4b, "GeomPoint")

(p1b | p2b) + (p3b / p4b)

filename <- "PtsABdAnnoyMnCatModGrid_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p3c <- p3 + theme(axis.title.x=element_text(family = "serif", size=14),
                  axis.text.x=element_text(family = "serif", size=14),
                  axis.ticks.x=element_line(colour="black", linewidth=1)) + 
        labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)))

filename <- "PtsABdAnnoyMnCatModEnv_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=5, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=5, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p5 <- ggplot(data=subset(m3bpredEvt2, UASOperation=="Overflight" & AmbientEnv=="Park" & SessionPart=="B")) +
              theme(panel.grid = element_blank(), aspect.ratio=0.8,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' &
                                       UASOperation=='Overflight' & SessionPart=='B'),
                         aes(x=UASEvents, y=dAnnoyMean,
                             colour=UASLAEMaxLR, shape=UASType),
                         alpha=0.35, size=2) +
  
              scale_color_viridis(option='inferno', direction=1, discrete=FALSE, begin = 0.2, end = 0.8,
                                  breaks=c(73, 79)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE)) +
  
              ggnewscale::new_scale_color() +
  
              geom_ribbon(aes(x=UASEvents, ymin=conf.low, ymax=conf.high, fill=factor(UASLAEMaxLRScl)),
                          alpha=0.05) +
  
              geom_line(aes(x=UASEvents, y=estimate, colour=factor(UASLAEMaxLRScl)), linewidth=1, alpha=0.5) +

              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_shape_manual(values=c(10, 11, 12)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     fill=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     shape=guide_legend(title="UAS type", reverse=FALSE)) +
            
              scale_x_continuous(breaks=c(1, 3, 5, 9), labels=c(1, 3, 5, 9)) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(2, 7)) +
              
              labs(x="Number of UAS Overflight events", y="Mean change in annoyance")

p5

filename <- "PtsABdAnnoyMnCatModEvt2_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p6 <- ggplot(data=m3bpredAtt) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AAM_attitude2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AAM_attitude2), linewidth=1) +
              
              scale_color_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="AAM attitude", reverse=TRUE),
                     fill=guide_legend(title="AAM attitude", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p7 <- ggplot(data=m3bpredAoR) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Home_Area2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Home_Area2), linewidth=1) +
              
              scale_color_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Area of residence", reverse=FALSE),
                     fill=guide_legend(title="Area of residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p8 <- ggplot(data=m3bpredScp) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Area_soundscape2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Area_soundscape2), linewidth=1) +
              
              scale_color_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Soundscape at residence", reverse=FALSE),
                     fill=guide_legend(title="Soundscape at residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p9 <- ggplot(data=m3bpredSex) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Sex), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Sex), linewidth=1) +
              
              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Sex", reverse=TRUE),
                     fill=guide_legend(title="Sex", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p10 <- ggplot(data=m3bpredNat) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=NationGeo2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=NationGeo2), linewidth=1) +
              
              scale_color_viridis(option='cividis', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='cividis', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="National region", reverse=TRUE),
                     fill=guide_legend(title="National region", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")


(p6 + p7 + p8) / (p9 + p10)

filename <- "PtsABdAnnoyMnAttAoRScpSexNatCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### visualise posterior distributions of group level effects

```{r}

m3b_sd_draws <- as.data.frame(m3b) %>%
    dplyr::select(starts_with("sd_")) %>%
    tidyr::pivot_longer(cols = everything(), names_to = "Parameter", values_to = "Value") %>%
    dplyr::mutate(Parameter = gsub("sd_", "", Parameter)) # Clean up label names

# 2. Plot using ridges with a shared x-axis and normalized curve heights
ggplot(m3b_sd_draws, aes(x = Value, y = Parameter, fill = Parameter)) +
     theme(legend.position = "none",
            panel.grid.major.y = element_blank(),
            text = element_text(family = "serif", size=16)) +
    # stat_density_ridges normalizes the peak height of each curve individually
    ggridges::stat_density_ridges(aes(height = after_stat(density)), 
                        geom = "density_ridges", 
                        alpha = 1, 
                        scale = 1.5,) + # Controls how much curves can overlap vertically
    # Adds the 50%, 89% and 95% credible intervals right beneath each curve
    tidybayes::stat_pointinterval(aes(y = as.numeric(as.factor(Parameter)) - 0.1), 
                       .width = c(0.5, 0.89, 0.95)) +
    scale_fill_manual(values = mycolours) +
    labs(x = "Estimated variation (sd scale)",
         y = "Group parameter")

filename <- "PtsABdAnnoyMnCatModSD_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

## m4: maximal ordinal model for dAnnoyance, median imputed

### formula

```{R}

m4formula <- update(m0formula, dAnnoyanceOrd ~ .)

```

### run model 4

```{r}

emp_thresh4 <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb$dAnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh4 <- emp_thresh4[is.finite(emp_thresh4)]

priors4 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh4,", 1)"), class = "Intercept", coef = 1:length(emp_thresh4))
)

# extract the data for the model
m4Data <- subjDataNoAmb.med[, all.vars(m4formula), drop=FALSE]

tic()
m4Priors <- brms::brm(m4formula,
                 data=m4Data,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors4,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

m4_ppd <- ppd_ridgeplot(m4Priors, ndraws = 100)
m4_ppd

m4PriorCheck <- brms::pp_check(m4Priors, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance category index")
m4PriorCheck

tic()
m4 <- brms::brm(m4formula,
                 data=m4Data,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors4,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m4 <- brms::add_criterion(m4, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag)
toc()

m4$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m4))
m4$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m4, re_formula=NA))
m4$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m4, re_formula=NULL))
m4$criteria$bayes_R2_MZ <- as.data.frame(Bayes_R2_MZ(m4))

m4PostCheck <- brms::pp_check(m4, type='bars', ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance category index")
m4PostCheck

```

### analyse results

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m4_bCI_range <- bayestestR::hdi(m4, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m4_bCI_wsf <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_SessionPartB", "b_UASTypeM300", "b_UASTypeT150", 
                                 "b_UASOperationLanding", "b_UASOperationTakeoff",
                                 "b_AmbientEnvStreet"))
p_m4_bCI_wsf <- plot(m4_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wsf

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m4_bCI_wsfi <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvStreet:UASOperationLanding",
                                 "b_AmbientEnvStreet:UASOperationTakeoff",
                                 "b_AmbientEnvStreet:UASTypeM300",
                                 "b_AmbientEnvStreet:UASTypeT150",
                                 "b_UASOperationLanding:UASTypeM300",
                                 "b_UASOperationLanding:UASTypeT150"))
p_m4_bCI_wsfi <- plot(m4_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wsfi

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m4_bCI_wsc <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m4_bCI_wsc <- plot(m4_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wsc

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m4_bCI_wscfi <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvStreet",
                                 "b_UASLAEMaxLRScl:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:UASTypeM300",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationLanding",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASOperationTakeoff",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeM300",
                                 "b_UASLAEMaxLRScl:AmbientEnvStreet:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m4_bCI_wscfi <- plot(m4_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_wscfi

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m4_bCI_bsf <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Uneventful"))
p_m4_bCI_bsf <- plot(m4_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_bsf

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m4_bCI_bsc <- m4_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NSSTotal"))
p_m4_bCI_bsc <- plot(m4_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m4_bCI_bsc

filename <- "PtsABdAnnoyMnCatModbCI_brmsCo_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

## m5: omit stimID group effect from m3b

### Formula

```{R}

m5formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID)

```

### run model 5

```{R}

tic()
m5 <- brms::brm(brms::bf(m5formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m5 <- brms::add_criterion(m5, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m5$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m5))
m5$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m5, re_formula=NA))
m5$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m5, re_formula=NULL))

m5PostCheck <- brms::pp_check(m5, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m5PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)

m5_loo <- loo::loo_compare(m3b, m5, criterion='loo')
m5_loo

```

## m6: omit UASType group effect from m5

### Formula

```{R}

m6formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 6

```{R}

tic()
m6 <- brms::brm(brms::bf(m6formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m6 <- brms::add_criterion(m6, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m6$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m6))
m6$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m6, re_formula=NA))
m6$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m6, re_formula=NULL))

m6PostCheck <- brms::pp_check(m6, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m6PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)

m6_loo <- loo::loo_compare(m3b, m5, m6, criterion='loo')
m6_loo

```

## m7: omit UASLAEMaxLRScl group effect from m6

### Formula

```{R}

m7formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation | ID)

```

### run model 7

```{R}

tic()
m7 <- brms::brm(brms::bf(m7formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m7 <- brms::add_criterion(m7, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m7$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m7))
m7$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m7, re_formula=NA))
m7$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m7, re_formula=NULL))

m7PostCheck <- brms::pp_check(m7, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m7PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)
loo::loo(m7)


m7_loo <- loo::loo_compare(m3b, m5, m6, m7, criterion='loo')
m7_loo

loo::loo_compare(m6, m7, criterion='loo')

```

## m8: omit UASOperation group effect from m7

### Formula

```{R}

m8formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) | ID)

```

### run model 8

```{R}

tic()
m8 <- brms::brm(brms::bf(m8formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m8 <- brms::add_criterion(m8, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m8$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m8))
m8$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m8, re_formula=NA))
m8$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m8, re_formula=NULL))

m8PostCheck <- brms::pp_check(m8, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m8PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)
loo::loo(m7)
loo::loo(m8)


m8_loo <- loo::loo_compare(m3b, m5, m6, m7, m8, criterion='loo')
m8_loo

loo::loo_compare(m7, m8, criterion='loo')

```

## m8b: omit UASOperation group effect from m6

### Formula

```{R}

m8bformula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                     UASLAEMaxLRScl | ID)

```

### run model 8b

```{R}

tic()
m8b <- brms::brm(brms::bf(m8bformula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m8b <- brms::add_criterion(m8b, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m8b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m8b))
m8b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m8b, re_formula=NA))
m8b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m8b, re_formula=NULL))

m8bPostCheck <- brms::pp_check(m8b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m8bPostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m5)
loo::loo(m6)
loo::loo(m7)
loo::loo(m8)
loo::loo(m8b)


m8b_loo <- loo::loo_compare(m3b, m5, m6, m7, m8, m8b, criterion='loo')
m8b_loo

loo::loo_compare(m6, m8b, criterion='loo')

```

## m9: omit population interaction effects from m6

### Formula

```{R}

m9formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 9

```{R}

tic()
m9 <- brms::brm(brms::bf(m9formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m9 <- brms::add_criterion(m9, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m9$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m9))
m9$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m9, re_formula=NA))
m9$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m9, re_formula=NULL))

m9PostCheck <- brms::pp_check(m9, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m9PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)

m9_loo <- loo::loo_compare(m3b, m6, m9, criterion='loo')
m9_loo

loo::loo_compare(m6, m9, criterion='loo')

```

## m10: omit further population interaction effects from m9

### Formula

```{R}

m10formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*UASOperation +
                   AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 10

```{R}

tic()
m10 <- brms::brm(brms::bf(m10formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m10 <- brms::add_criterion(m10, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m10$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m10))
m10$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m10, re_formula=NA))
m10$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m10, re_formula=NULL))

m10PostCheck <- brms::pp_check(m10, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m10PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m10)

m10_loo <- loo::loo_compare(m3b, m6, m9, m10, criterion='loo')
m10_loo

loo::loo_compare(m9, m10, criterion='loo')

```

## m11: omit further population effects from m9

### Formula

```{R}

m11formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Sex + NSSTotal +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 11

```{R}

tic()
m11 <- brms::brm(brms::bf(m11formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m11 <- brms::add_criterion(m11, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m11$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m11))
m11$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m11, re_formula=NA))
m11$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m11, re_formula=NULL))

m11PostCheck <- brms::pp_check(m11, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m11PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)

m11_loo <- loo::loo_compare(m3b, m6, m9, m11, criterion='loo')
m11_loo

loo::loo_compare(m9, m11, criterion='loo')

```

## m12: omit further population effects from m11

### Formula

```{R}

m12formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   Home_Area2 +
                   Sex + NSSTotal +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 12

```{R}

tic()
m12 <- brms::brm(brms::bf(m12formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m12 <- brms::add_criterion(m12, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m12$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m12))
m12$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m12, re_formula=NA))
m12$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m12, re_formula=NULL))

m12PostCheck <- brms::pp_check(m12, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m12PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)
loo::loo(m12)

m12_loo <- loo::loo_compare(m3b, m6, m9, m11, m12, criterion='loo')
m12_loo

loo::loo_compare(m11, m12, criterion='loo')

```

## m13: omit further population effects from m12

### Formula

```{R}

m13formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   Sex +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 13

```{R}

tic()
m13 <- brms::brm(brms::bf(m13formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m13 <- brms::add_criterion(m13, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m13$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m13))
m13$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m13, re_formula=NA))
m13$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m13, re_formula=NULL))

m13PostCheck <- brms::pp_check(m13, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m13PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)
loo::loo(m12)
loo::loo(m13)

m13_loo <- loo::loo_compare(m3b, m6, m9, m11, m12, m13, criterion='loo')
m13_loo

loo::loo_compare(m12, m13, criterion='loo')

```

## m14: omit further population effects from m13

### Formula

```{R}

m14formula <- dAnnoyanceOrdBetaScl ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*UASType +
                   AmbientEnv*UASType +
                   (1 + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASLAEMaxLRScl | ID)

```

### run model 14

```{R}

tic()
m14 <- brms::brm(brms::bf(m14formula, phi ~ 1 + AmbientEnv),
                data=m3Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors3b,
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=4, iter=2000, warmup=1000)
toc()

tic()
m14 <- brms::add_criterion(m14, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag)
toc()

m14$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m14))
m14$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m14, re_formula=NA))
m14$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m14, re_formula=NULL))

m14PostCheck <- brms::pp_check(m14, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m14PostCheck

```

#### compare

```{R}

loo::loo(m3b)
loo::loo(m6)
loo::loo(m9)
loo::loo(m11)
loo::loo(m12)
loo::loo(m13)
loo::loo(m14)

m14_loo <- loo::loo_compare(m3b, m6, m9, m11, m12, m13, m14, criterion='loo')
m14_loo

loo::loo_compare(m13, m14, criterion='loo')

```









































