---
title: "REFMAP Listening test 1 analysis: Random forest variable importance identification"
output: html_notebook
---

This notebook analyses the Part A and B data in terms of variable importance using a random forest model based on conditional inference trees and a conditional permutation variable importance algorithm.

# Setup

## Load packages

```{r}
# load packages
library(tidyr)
library(unikn)
library(ggplot2)
require(flexplot)
library(party)
library(randomForest)

# set package parameters
theme_set(theme_bw())

```

```{r}
# function to enable plot dimension adjustment
set_plot_dimensions <- function(width_choice, height_choice) {
        options(repr.plot.width=width_choice, repr.plot.height=height_choice)
        }
```

## Import data and wrangle

```{r}
stimDataA <- read.csv("C:\\Users\\m_lot\\OneDrive - University of Salford\\REFMAP General\\03 Experiment\\Experiment 1\\Analysis\\PostProcess\\refmap_listest1_testdataA_ByStim.csv", header=TRUE)

subjLongDataA <- read.csv("C:\\Users\\m_lot\\OneDrive - University of Salford\\REFMAP General\\03 Experiment\\Experiment 1\\Analysis\\PostProcess\\refmap_listest1_testdataA_BySubj.csv", header=TRUE)
```

```{r}
# function to encode categorical to ordinal variables
encode_ordinal <- function(x, order=unique(x)) {
  x <- as.numeric(factor(x, levels=order, exclude=NULL))
  x
}

# definition of ordinal variable levels
SNRCats <- c("No UAS", "-16", "-10", "-4", "2", "8")
UASLAeqCats <- c("No UAS", "42", "48", "54", "60")

```

The aggregated data by stimulus are assigned to a dataframe, relevant categorical variables are converted to ordinal, and then the variable subset of interest is selected, NA rows dropped (ie, the 'no UAS' stimuli, as the conditional variable importance algorithm cannot currently handle NA values, which are present in all the UAS dB metrics), and a formula assigned.

```{r}

stimDataANum <- stimDataA

stimDataANum[['SNRlevel']] <- encode_ordinal(stimDataA[['SNRlevel']], order=SNRCats)
stimDataANum[['UASLAeq']] <- encode_ordinal(stimDataA[['UASLAeq']], order=UASLAeqCats)

stimDataANum <- cbind(stimDataANum[, which(colnames(stimDataANum)=="UASLAeq"):
                                     which(colnames(stimDataANum)=="SNRlevel")],
                      stimDataANum[, which(colnames(stimDataANum)=="UASLAeqMaxLR"):
                                     which(colnames(stimDataANum)=="UASImpulsHMS05ExMaxLR")],
                      stimDataANum[, which(colnames(stimDataANum)=="UASLAeqdiffAmbLAF90"):
                                     which(colnames(stimDataANum)=="UASPartLoudGMSTPowAvg")],
                      stimDataANum[, which(colnames(stimDataANum)=="dTonalECMAHMSAvgMaxLR"):
                                     which(colnames(stimDataANum)=="dImpulsHMS05ExMaxLR")])
colSelect = c('ValenceMedian', 'ArousalMedian', 'AnnoyMedian', 'HighAnnoyProportion')
stimDataANum <- cbind(stimDataANum, stimDataA[, colSelect])
stimDataANum <- subset(stimDataANum, select = -c(UASLAEMaxLR))

# drop rows missing with missing values, as conditional variable importance cannot handle these 
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]

includeVarsStim <- names(stimDataANum)[1:which(names(stimDataANum) == 'dImpulsHMS05ExMaxLR')]
formVarStim <- reformulate(includeVarsStim, 'AnnoyMedian')

```

This process is repeated for the disaggregated data by subject.

```{r}

subjDataANum <- subjLongDataA

subjDataANum[['SNRlevel']] <- encode_ordinal(subjLongDataA[['SNRlevel']], order=SNRCats)
subjDataANum[['UASLAeq']] <- encode_ordinal(subjLongDataA[['UASLAeq']], order=UASLAeqCats)

subjDataANum <- cbind(subjDataANum[, which(colnames(subjDataANum)=="UASLAeq"):
                                     which(colnames(subjDataANum)=="SNRlevel")],
                      subjDataANum[, which(colnames(subjDataANum)=="UASLAeqMaxLR"):
                                     which(colnames(subjDataANum)=="UASImpulsHMS05ExMaxLR")],
                      subjDataANum[, which(colnames(subjDataANum)=="UASLAeqdiffAmbLAF90"):
                                     which(colnames(subjDataANum)=="UASPartLoudGMSTPowAvg")],
                      subjDataANum[, which(colnames(subjDataANum)=="dTonalECMAHMSAvgMaxLR"):
                                     which(colnames(subjDataANum)=="dImpulsHMS05ExMaxLR")])
colSelect = c('Valence', 'Arousal', 'Annoyance', 'HighAnnoy')
subjDataANum <- cbind(subjDataANum, subjLongDataA[, colSelect])
subjDataANum <- subset(subjDataANum, select = -c(UASLAEMaxLR))

# drop rows missing with missing values, as conditional variable importance cannot handle these
subjDataANum <- subjDataANum[complete.cases(subjDataANum),]

includeVarsSubj <- names(subjDataANum)[1:which(names(subjDataANum) == 'dImpulsHMS05ExMaxLR')]
formVarSubj <- reformulate(includeVarsSubj, 'Annoyance')

```

## Training the model

### Aggregated data

#### All variables

The random forest modelling is run on the aggregated data, including all the variables.

```{r}
set.seed(909)
crf_AggModel <- party::cforest(formVarStim, data=stimDataANum,
                               controls=party::cforest_unbiased(ntree=1000,
                                                                mtry=as.integer(length(includeVarsStim)/1.25)))

crf_AggModelOOB <- predict(crf_AggModel, OOB=TRUE, type='response')

# Error quantiles
round(quantile(abs(crf_AggModelOOB - data.matrix(crf_AggModel@data@env$response))), digits=3)

cor(crf_AggModelOOB, crf_AggModel@data@env$response)^2  # Rsquared
```

The marginal variable importance is calculated.


```{r}
sort(party::varimp(crf_AggModel), decreasing=TRUE)
```

Now, the conditional variable permutations importance is calculated.

```{r}
# using permimp cpi
start.time <- Sys.time()

pimpCrfAggModel <- permimp::permimp(crf_AggModel, nperm=1, conditional=TRUE,
                                    threshold=0.95, progressBar=FALSE)

end.time <- Sys.time()
time.taken <- round(end.time - start.time, 2)
time.taken

```
```{r}
pimpCrfAggOrdered <- round(sort(pimpCrfAggModel$values, decreasing=F), digits=4)
rev(pimpCrfAggOrdered)
```

```{r, fig.width=10,fig.height=12}
par(mai=c(0,3,0,0))
pimpCrfAggOrdereddf <- data.frame(pimpCrfAggOrdered)
pimpCrfAggOrdereddf <- plyr::rename(pimpCrfAggOrdereddf, c("pimpCrfAggOrdered" = "Variable_importance"))

pBar <- ggplot(pimpCrfAggOrdereddf) + geom_col(aes(x=factor(rownames(pimpCrfAggOrdereddf), levels=rownames(pimpCrfAggOrdereddf)), y=Variable_importance), fill="#076fa2", width=0.5) + labs(x="Variable", y="Conditional variable importance") + theme(text = element_text(family = "serif"))
pBar + coord_flip()
```


```{r, fig.width=10,fig.height=12}
# plot cpi
permimp::plot.VarImp(pimpCrfAggModel, type='box', horizontal=TRUE)

```
#### Remove loudness and level variables

Now a model is run omitting loudness and level variables, while retaining only the top importance loudness variable.

```{r}
```


### Individual data

Next, a new model is run on the disaggregated data:

```{r}
set.seed(909)
crf_IndModel <- party::cforest(formVarSubj, data=subjDataANum,
                               controls=party::cforest_unbiased(ntree=500,
                                                                mtry=as.integer(length(includeVarsSubj)/1.25)))

crf_IndModelOOB <- predict(crf_IndModel, OOB=TRUE, type='response')

# Error quantiles
round(quantile(abs(crf_IndModelOOB - data.matrix(crf_IndModel@data@env$response))), digits=3)

cor(crf_IndModelOOB, crf_IndModel@data@env$response)^2  # Rsquared
```


```{r}
sort(party::varimp(crf_IndModel), decreasing=TRUE)

```

```{r}
start.time <- Sys.time()
impCrfIndModel <- permimp::permimp(crf_IndModel, nperm=1, conditional=TRUE, progressBar=FALSE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time, 2)
time.taken
```

```{r}
impCrfIndOrdered <- sort(impCrfIndModel$values, decreasing=F)
rev(impCrfIndOrdered)
```

```{r, fig.width=10,fig.height=12}
par(mai=c(0,3,0,0))
impCrfIndOrdereddf <- data.frame(impCrfIndOrdered)
impCrfIndOrdereddf <- plyr::rename(impCrfIndOrdereddf, c("impCrfIndOrdered" = "Variable_importance"))

pBar <- ggplot(impCrfIndOrdereddf) + geom_col(aes(x=factor(rownames(impCrfIndOrdereddf), levels=rownames(impCrfIndOrdereddf)), y=Variable_importance), fill="#076fa2", width=0.5) + labs(x="Variable") + theme(text = element_text(family = "serif"))
pBar + coord_flip()
```


Run again, omitting AmbientLAeq variable

```{r}

includeVarsSubj <- c(names(subjDataANum)[1], names(subjDataANum)[3:which(names(subjDataANum) == 'dImpulsHMS05ExMaxLR')])
formVarSubj <- reformulate(includeVarsSubj, 'Annoyance')

set.seed(909)
crf_IndModel <- party::cforest(formVarSubj, data=subjDataANum[, !(names(subjDataANum) %in% "AmbientLAeq")],
                               controls=party::cforest_unbiased(ntree=500,
                                                                mtry=as.integer(length(includeVarsSubj)/1.25)))

crf_IndModelOOB <- predict(crf_IndModel, OOB=TRUE, type='response')

# Error quantiles
round(quantile(abs(crf_IndModelOOB - data.matrix(crf_IndModel@data@env$response))), digits=3)

cor(crf_IndModelOOB, crf_IndModel@data@env$response)^2  # Rsquared
```

```{r}
start.time <- Sys.time()
impCrfIndModel <- permimp::permimp(crf_IndModel, nperm=1, conditional=TRUE, progressBar=FALSE)
end.time <- Sys.time()
time.taken <- round(end.time - start.time, 2)
time.taken
```

```{r, fig.width=10,fig.height=12}
impCrfIndOrdered <- sort(impCrfIndModel$values, decreasing=F)
par(mai=c(0,3,0,0))
impCrfIndOrdereddf <- data.frame(impCrfIndOrdered)
impCrfIndOrdereddf <- plyr::rename(impCrfIndOrdereddf, c("impCrfIndOrdered" = "Variable_importance"))

pBar <- ggplot(impCrfIndOrdereddf) + geom_col(aes(x=factor(rownames(impCrfIndOrdereddf), levels=rownames(impCrfIndOrdereddf)), y=Variable_importance), fill="#076fa2", width=0.5) + labs(x="Variable") + theme(text = element_text(family = "serif"))
pBar + coord_flip()
```

