---
title: "REFMAP Listening test 1 analysis: Random forest variable importance identification"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This notebook analyses the Part A and B data in terms of variable importance using a random forest model based on conditional inference trees and a conditional permutation variable importance algorithm.

# Setup

## Load packages

```{r}
# load packages
library(tidyr)
library(ggplot2)
library(party)
library(conflicted)
library(tidyverse)
library(openxlsx)


# set package parameters
theme_set(theme_bw())

```

```{r}

# plot colour scheme

mycolourlist = list(c(0, 102, 255), c(0, 204, 153), c(255, 0, 102), c(74, 111, 152), c(251, 164, 49), c(204, 153, 255), c(90, 192, 255), c(80, 245, 233), c(255, 90, 192), c(164, 201, 242), c(255, 254, 139), c(255, 243, 255))
mycolours = matrix()

for (ii in 1:length(mycolourlist)){
  mycolours[ii] = rgb(mycolourlist[[ii]][1]/255,
                      mycolourlist[[ii]][2]/255,
                      mycolourlist[[ii]][3]/255)
}

# toggle to save plots
saveplots = TRUE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption="Select output folder to save plots")
}

# toggle to save data
savedata = TRUE

if (savedata){
  # set output plot directory
  if (saveplots==FALSE){
    choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  }
  outDataPath <- utils::choose.dir(caption="Select output folder to save data")
}
 

```

# Part A analysis

## Import data and wrangle

```{r}

stimDataApath <- utils::choose.files(caption=r"(Select refmap_listest1_testdataA_ByStim.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest1_testdataA_ByStim.csv", "refmap_listest1_testdataA_ByStim.csv"), ncol=2))

stimNoticeDataApath <- utils::choose.files(caption=r"(Select refmap_listest1_testdataANoticeFilt_ByStim.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)", filters=matrix(data=c("refmap_listest1_testdataANoticeFilt_ByStim.csv", "refmap_listest1_testdataANoticeFilt_ByStim.csv"), ncol=2))

stimDataA <- utils::read.csv(stimDataApath, header=TRUE)
stimNoticeDataA <- utils::read.csv(stimNoticeDataApath, header=TRUE)

colnames(stimDataA)[1] <- "Recording"
colnames(stimNoticeDataA)[1] <- "Recording"

```

```{r}
# function to encode categorical to ordinal numeric variables
encode_ordinal <- function(x, order=unique(x)) {
  x <- as.numeric(factor(x, levels=order, exclude=NULL, order=TRUE))
  x
}

# definition of ordinal variable levels
SNRCatsA <- c("No UAS", "-16", "-10", "-4", "2", "8")
UASLAeqCatsA <- c("No UAS", "42", "48", "54", "60")

```

The aggregated data by stimulus are assigned to a dataframe, relevant categorical variables are converted to ordinal, and then the variable subset of interest is selected, NA rows dropped (ie, the 'no UAS' stimuli, as the conditional variable importance algorithm cannot currently handle NA values, which are present in all the UAS dB metrics), and a formula assigned.

```{r}

stimDataANum <- data.frame()

stimDataANum <- cbind(stimDataA[, 'Recording'],
                      stimDataA[, which(colnames(stimDataA)=="UASLAeq"):
                                  which(colnames(stimDataA)=="SNRlevel")],
                      stimDataA[, which(colnames(stimDataA)=="UASLAeqMaxLR"):
                                  which(colnames(stimDataA)=="UASImpulsHMS05ExMaxLR")],
                      stimDataA[, which(colnames(stimDataA)=="LAeqdiffLAF90"):
                                  which(colnames(stimDataA)=="PartLoudGMLT05Ex")],
                      stimDataA[, which(colnames(stimDataA)=="dTonalECMAHMSAvgMaxLR"):
                                  which(colnames(stimDataA)=="dImpulsHMS05ExMaxLR")],
                      stimDataA[, which(colnames(stimDataA)=="ValenceMedian"):
                                  which(colnames(stimDataA)=="HighAnnoyProportion")])
  
stimDataANum <- subset(stimDataANum, select = -c(UASLAEMaxLR))

colnames(stimDataANum)[1] <- "Recording"

# make the categorical outcome variables numerical dummy factors
# stimDataANum[['SNRlevel']] <- encode_ordinal(stimDataA[['SNRlevel']], order=SNRCatsA)
# stimDataANum[['UASLAeq']] <- encode_ordinal(stimDataA[['UASLAeq']], order=UASLAeqCatsA)

# make the discrete ordinal outcome variables factors
stimDataANum[['ValenceMedian']] <- factor(stimDataANum[['ValenceMedian']], levels=c(1, 2, 3, 4, 5), order=TRUE)
stimDataANum[['ArousalMedian']] <- factor(stimDataANum[['ArousalMedian']], levels=c(1, 2, 3, 4, 5), order=TRUE)
stimDataANum[['AnnoyMedian']] <- factor(stimDataANum[['AnnoyMedian']], levels=c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10), order=TRUE)
stimDataANum[['dValenceMedian']] <- factor(stimDataANum[['dValenceMedian']], levels=c(-4, -3, -2, -1, 0, 1, 2, 3, 4), order=TRUE)
stimDataANum[['dArousalMedian']] <- factor(stimDataANum[['dArousalMedian']], levels=c(-4, -3, -2, -1, 0, 1, 2, 3, 4), order=TRUE)
stimDataANum[['dAnnoyMedian']] <- factor(stimDataANum[['dAnnoyMedian']], levels=c(-10, -9, -8, -7, -6, -5, -4, -3, -2, -1,
                                                                                 0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10), order=TRUE)
```

```{r}

stimNoticeDataANum <- data.frame()

stimNoticeDataANum <- cbind(stimNoticeDataA[, 'Recording'],
                            stimNoticeDataA[, which(colnames(stimNoticeDataA)=="UASLAeq"):
                                              which(colnames(stimNoticeDataA)=="SNRlevel")],
                            stimNoticeDataA[, which(colnames(stimNoticeDataA)=="UASLAeqMaxLR"):
                                              which(colnames(stimNoticeDataA)=="UASImpulsHMS05ExMaxLR")],
                            stimNoticeDataA[, which(colnames(stimNoticeDataA)=="LAeqdiffLAF90"):
                                              which(colnames(stimNoticeDataA)=="PartLoudGMLT05Ex")],
                            stimNoticeDataA[, which(colnames(stimNoticeDataA)=="dTonalECMAHMSAvgMaxLR"):
                                              which(colnames(stimNoticeDataA)=="dImpulsHMS05ExMaxLR")],
                            stimNoticeDataA[, which(colnames(stimNoticeDataA)=="NoticedTotalFilt"):
                                              which(colnames(stimNoticeDataA)=="HighAnnoyPropFilt")])

stimNoticeDataANum <- subset(stimNoticeDataANum, select = -c(UASLAEMaxLR))

colnames(stimNoticeDataANum)[1] <- "Recording"

# make the categorical outcome variables numerical dummy factors
# stimNoticeDataANum[['SNRlevel']] <- encode_ordinal(stimNoticeDataA[['SNRlevel']], order=SNRCatsA)
# stimNoticeDataANum[['UASLAeq']] <- encode_ordinal(stimNoticeDataA[['UASLAeq']], order=UASLAeqCatsA)

```

## Random forest function

Write a function to train a conditional-inference random forest (crf) model on input data according to input formula, iterate over input random seeds, average error and variable importance metrics, and output metrics with plotted

```{r}

multi_crfReg <- function(dataIn, iVars, dVar, seeds, ntree, mtry, minsplit=20,
                         minbucket=7, nperm=1){
  # initialise variables
  crfOOBErrAll <- 0
  crfOOBRMSE <- 0
  crfOOBErrQ <- 0
  crfOOBErrR2 <- 0
  crfMarVarImpVals <- 0
  crfConPermImpVals <- 0
  
  for (iters in 1:length(seeds)){
    
    # formula for regression
    formVars <- reformulate(iVars, dVar)
    
    # set random seed
    set.seed(seeds[iters])
    # train crf model
    crfModel <- party::cforest(formVars, data=dataIn,
                               controls=party::cforest_unbiased(ntree=ntree,
                                                                mtry=mtry,
                                                                minsplit=minsplit,
                                                                minbucket=minbucket))
    
    # get OOB predictions
    crfModelOOB <- predict(crfModel, OOB=TRUE, type='response')
    
    # get OOB error
    crfModelOOBErr <- as.numeric(as.matrix(as.numeric(as.matrix(crfModelOOB))
                                            - as.numeric(as.matrix(crfModel@data@env$response[[names(crfModel@data@env$response)]]))))

    # cumulative error for averaging
    crfOOBErrAll <- crfOOBErrAll + crfModelOOBErr
    
    # OOB RMSE, error quartiles and Rsquared
    crfOOBRMSE <- crfOOBRMSE + sqrt(mean(crfModelOOBErr^2))
    crfOOBErrQ <- crfOOBErrQ + quantile(abs(crfModelOOBErr),
                                        type=8, names=TRUE)
    crfOOBErrR2 <- crfOOBErrR2 + cor(as.numeric(as.matrix(crfModelOOB)),
                                     as.numeric(as.matrix(crfModel@data@env$response[[names(crfModel@data@env$response)]])))^2

    # set random seed
    set.seed(seeds[iters])
    # marginal variable permutation importance
    crfMarVarImp <- permimp::permimp(crfModel, nperm=nperm, conditional=FALSE, threshold=0.95, progressBar=FALSE)
    
    crfMarVarImpVals <- crfMarVarImpVals + crfMarVarImp$values
    
    # set random seed
    set.seed(seeds[iters])
    # conditional variable permutation importance
    crfConPermImp <- permimp::permimp(crfModel, nperm=nperm, conditional=TRUE, threshold=0.95, progressBar=FALSE)
    
    crfConPermImpVals <- crfConPermImpVals + crfConPermImp$values
    
  }
  
  # average metrics
  crfOOBErrAll <- crfOOBErrAll/length(seeds)
  crfOOBRMSE <- crfOOBRMSE/length(seeds)
  crfOOBErrQ <- crfOOBErrQ/length(seeds)
  crfOOBErrR2 <- crfOOBErrR2/length(seeds)
  crfMarVarImpVals <- sort(crfMarVarImpVals/length(seeds), decreasing=TRUE)
  crfConPermImpVals <- sort(crfConPermImpVals/length(seeds), decreasing=TRUE)
  
  resultsOut <- list('OOB_errors'=crfOOBErrAll, 'OOB_RMSE'=crfOOBRMSE, 'OOB_abserror'=crfOOBErrQ, 'Rsquared'=crfOOBErrR2, 'marginal_permimp'=crfMarVarImpVals, 'conditional_permimp'=crfConPermImpVals)
  return(resultsOut)
}

```

## Annoyance

### Absolute variables


#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]
stimDataANum$UASLAeq <- as.numeric(stimDataANum$UASLAeq)
stimDataANum$SNRlevel <- as.numeric(stimDataANum$SNRlevel)
```

```{r}
resAnnoyMedFit <- data.frame(RMSE = numeric(),
                             Rsquared = numeric(),
                             AEq0 = numeric(),
                             AEq25 = numeric(),
                             AEq50 = numeric(),
                             AEq75 = numeric(),
                             AEq100 = numeric())
resAnnoyMedPermImp <- list()

```

The random forest modelling is run on the aggregated data, including all the absolute variables.

```{r}
iVars <- names(stimDataANum)[which(names(stimDataANum) == 'UASLAeq'):which(names(stimDataANum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbs <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(101, 303, 808, 909, 2486), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_abserror
resultsOutAbs$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs vars', 'RMSE'] <- resultsOutAbs$OOB_RMSE
resAnnoyMedFit['Abs vars', 'Rsquared'] <- resultsOutAbs$Rsquared
resAnnoyMedFit['Abs vars', which(colnames(resAnnoyMedFit) == 'AEq0'):
                           which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutAbs$OOB_abserror
resAnnoyMedPermImp$AbsVars <- resultsOutAbs$conditional_permimp
```


```{r, fig.width=5, fig.height=5}
# set.seed(303)
# xjitter = runif(length(stimDataANum$dAnnoyMedian), 0, 0.2)
# yjitter = runif(length(resultsOutAbs$OOB_predicts), 0, 0.2)
# base::plot(as.numeric(as.character(stimDataANum$AnnoyMedian)) + xjitter, as.numeric(as.character(resultsOutAbs$OOB_predicts)) + yjitter, col=rgb(0, 102/255, 255/255, 0.2),
#            xlim=c(0, 10), ylim=c(0, 10), xlab="Median annoyance rating", ylab="Predicted median annoyance")
```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbs.conimp <- data.frame('Var_imp'=rev(resultsOutAbs$conditional_permimp))

pBar <- ggplot(resultsOutAbs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp), levels=rownames(resultsOutAbs.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoyAbsVarsConPermimp.svg", width=10, height=11.5, path=outFigPath)
  unlink("PtAAnnoyAbsVarsConPermimp.svg")
}

```

### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are replaced, as the SQM analysis can incorporate 0 values (whereas dB metrics cannot be handled in this way).

```{r}

stimDataANum <- rbind(stimDataANum, stimDataA[stimDataA['Recording']
                                              == "A1_CALBIN_Pa.wav",
                                              colnames(stimDataANum)],
                      stimDataA[stimDataA['Recording']
                                              == "A2_CALBIN_Pa.wav",
                                              colnames(stimDataANum)])
stimDataANum <- arrange(stimDataANum, Recording)

```

#### Individual SQMs

Now a model is run omitting loudness and level variables, while retaining only (one of) the top importance loudness variables, and each category of SQM in turn.

```{r}
# Sharpness
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharp <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(222, 1, 606, 66, 98745), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_abserror
resultsOutSharp$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resAnnoyMedFit['Abs sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resAnnoyMedFit['Abs sharp', which(colnames(resAnnoyMedFit) == 'AEq0'):
                            which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutSharp$OOB_abserror
resAnnoyMedPermImp$AbsSharp <- resultsOutSharp$conditional_permimp
```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- data.frame('Var_imp'=rev(resultsOutSharp$conditional_permimp))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoySharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtAAnnoySharpConPermimp.svg")
}

```
Tonality including tonal loudness

```{r}
# Tonality inc tonal loudness
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(8756, 32, 875, 7446, 3), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_abserror
resultsOutTonal1$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs inc tonal loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resAnnoyMedFit['Abs inc tonal loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resAnnoyMedFit['Abs inc tonal loud', which(colnames(resAnnoyMedFit) == 'AEq0'):
                                     which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutTonal1$OOB_abserror
resAnnoyMedPermImp$AbsTonal1 <- resultsOutTonal1$conditional_permimp
```

```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1$conditional_permimp))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.175))

if (saveplots){
  ggsave(filename="PtAAnnoyTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtAAnnoyTonalLdConPermimp.svg")
}

```
Re-run tonality evaluation omitting tonal loudness 

```{r}
# Tonality
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(8756, 32, 875, 7446, 3), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_abserror
resultsOutTonal2$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs no tonal loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resAnnoyMedFit['Abs no tonal loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resAnnoyMedFit['Abs no tonal loud', which(colnames(resAnnoyMedFit) == 'AEq0'):
                                    which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutTonal2$OOB_abserror
resAnnoyMedPermImp$AbsTonal2 <- resultsOutTonal2$conditional_permimp
```

```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2$conditional_permimp))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.175))

if (saveplots){
  ggsave(filename="PtAAnnoyTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtAAnnoyTonalNoLdConPermimp.svg")
}

```


```{r}
# Fluctuation strength
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluct <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(565, 9872, 64, 82645, 337), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_abserror
resultsOutFluct$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resAnnoyMedFit['Abs fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resAnnoyMedFit['Abs fluct', which(colnames(resAnnoyMedFit) == 'AEq0'):
                            which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutFluct$OOB_abserror
resAnnoyMedPermImp$AbsFluct <- resultsOutFluct$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- data.frame('Var_imp'=rev(resultsOutFluct$conditional_permimp))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoyFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtAAnnoyFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRough <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(66745, 711, 4, 6645, 888), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_abserror
resultsOutRough$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resAnnoyMedFit['Abs rough', 'Rsquared'] <- resultsOutRough$Rsquared
resAnnoyMedFit['Abs rough', which(colnames(resAnnoyMedFit) == 'AEq0'):
                            which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutRough$OOB_abserror
resAnnoyMedPermImp$AbsRough <- resultsOutRough$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- data.frame('Var_imp'=rev(resultsOutRough$conditional_permimp))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoyRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtAAnnoyRoughConPermimp.svg")
}

```

```{r}
# Impulsiveness
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpuls <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(3337, 58, 12, 666987, 331), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_abserror
resultsOutImpuls$Rsquared
```

```{r}
# store results
resAnnoyMedFit['Abs impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resAnnoyMedFit['Abs impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resAnnoyMedFit['Abs impuls', which(colnames(resAnnoyMedFit) == 'AEq0'):
                             which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutImpuls$OOB_abserror
resAnnoyMedPermImp$AbsImpuls <- resultsOutImpuls$conditional_permimp

```

```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- data.frame('Var_imp'=rev(resultsOutImpuls$conditional_permimp))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoyImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtAAnnoyImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(12313, 22, 9, 788, 1765), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_abserror
resultsOutSQMs1$Rsquared
```

```{r}

# store results
resAnnoyMedFit['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resAnnoyMedFit['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resAnnoyMedFit['Abs SQMs inc tonal loud', which(colnames(resAnnoyMedFit) == 'AEq0'):
                                          which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutSQMs1$OOB_abserror
resAnnoyMedPermImp$AbsSQMs1 <- resultsOutSQMs1$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.125))

if (saveplots){
  ggsave(filename="PtAAnnoyAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtAAnnoyAbsSQMsTonLdConPermimp.svg")
}

```

Repeated without tonal loudness

```{r}
iVars <- c("UASLoudISO3PowAvgBin", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonalInt05ExMaxLR", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(12313, 22, 9, 788, 1765), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_abserror
resultsOutSQMs2$Rsquared
```

```{r}

# store results
resAnnoyMedFit['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resAnnoyMedFit['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resAnnoyMedFit['Abs SQMs no tonal loud', which(colnames(resAnnoyMedFit) == 'AEq0'):
                                         which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutSQMs2$OOB_abserror
resAnnoyMedPermImp$AbsSQMs2 <- resultsOutSQMs2$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoyAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtAAnnoyAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]
stimDataANum$UASLAeq <- as.numeric(stimDataANum$UASLAeq)
stimDataANum$SNRlevel <- as.numeric(stimDataANum$SNRlevel)
```


```{r}
iVars <- c(names(stimDataANum)[which(colnames(stimDataANum)=="LAeqdiffLAF90"):
                               which(colnames(stimDataANum)=="dImpulsHMS05ExMaxLR")], "SNRlevel")
resultsOutDiffs <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='AnnoyMedian', seeds=c(738, 1928, 7343, 1137, 838), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutDiffs$OOB_RMSE
resultsOutDiffs$OOB_abserror
resultsOutDiffs$Rsquared
```

```{r}

# store results
resAnnoyMedFit['Diff vars', 'RMSE'] <- resultsOutDiffs$OOB_RMSE
resAnnoyMedFit['Diff vars', 'Rsquared'] <- resultsOutDiffs$Rsquared
resAnnoyMedFit['Diff vars', which(colnames(resAnnoyMedFit) == 'AEq0'):
                            which(colnames(resAnnoyMedFit) == 'AEq100')] <- resultsOutDiffs$OOB_abserror
resAnnoyMedPermImp$DiffVars <- resultsOutDiffs$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffs.conimp <- data.frame('Var_imp'=rev(resultsOutDiffs$conditional_permimp))

pBar <- ggplot(resultsOutDiffs.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffs.conimp), levels=rownames(resultsOutDiffs.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAAnnoyDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtAAnnoyDiffVarsConPermimp.svg")
}

```
Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resAnnoyMedFit, paste(outDataPath, "\\ptACRFAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resAnnoyMedPermImp){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resAnnoyMedPermImp[ii])
    names(temp[[ii]]) <- names(resAnnoyMedPermImp[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptACRFAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```
## Change in annoyance

### Absolute variables

Now the response outcome 'change in annoyance' is analysed in the same way.

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]
stimDataANum$UASLAeq <- as.numeric(stimDataANum$UASLAeq)
stimDataANum$SNRlevel <- as.numeric(stimDataANum$SNRlevel)
```

```{r}
resdAnnoyMedFit <- data.frame(RMSE = numeric(),
                              Rsquared = numeric(),
                              AEq0 = numeric(),
                              AEq25 = numeric(),
                              AEq50 = numeric(),
                              AEq75 = numeric(),
                              AEq100 = numeric())
resdAnnoyMedPermImp <- list()

```

```{r}
iVars <- names(stimDataANum)[which(names(stimDataANum) == 'UASLAeq'):which(names(stimDataANum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbs <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(8883, 74645, 3387, 9994, 33), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_abserror
resultsOutAbs$Rsquared
```

```{r}

# store results
resdAnnoyMedFit['Abs vars', 'RMSE'] <- resultsOutAbs$OOB_RMSE
resdAnnoyMedFit['Abs vars', 'Rsquared'] <- resultsOutAbs$Rsquared
resdAnnoyMedFit['Abs vars', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                                       which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutAbs$OOB_abserror
resdAnnoyMedPermImp$AbsVars <- resultsOutAbs$conditional_permimp

```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbs.conimp <- data.frame('Var_imp'=rev(resultsOutAbs$conditional_permimp))

pBar <- ggplot(resultsOutAbs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp), levels=rownames(resultsOutAbs.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoyAbsVarsConPermimp.svg", width=10, height=11.5, path=outFigPath)
  unlink("PtAdAnnoyAbsVarsConPermimp.svg")
}


```

### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are replaced, as the SQM analysis can incorporate 0 values (whereas dB metrics cannot be handled in this way).

```{r}

stimDataANum <- rbind(stimDataANum, stimDataA[stimDataA['Recording']
                                              == "A1_CALBIN_Pa.wav",
                                              colnames(stimDataANum)],
                      stimDataA[stimDataA['Recording']
                                              == "A2_CALBIN_Pa.wav",
                                              colnames(stimDataANum)])
stimDataANum <- arrange(stimDataANum, Recording)

```

#### Individual SQMs


```{r}
# Sharpness
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharp <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(55536, 8224, 1365, 37, 446), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_abserror
resultsOutSharp$Rsquared
```

```{r}
# store results
resdAnnoyMedFit['Abs sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resdAnnoyMedFit['Abs sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resdAnnoyMedFit['Abs sharp', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                             which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutSharp$OOB_abserror
resdAnnoyMedPermImp$AbsSharp <- resultsOutSharp$conditional_permimp

```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- data.frame('Var_imp'=rev(resultsOutSharp$conditional_permimp))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoySharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtAdAnnoySharpConPermimp.svg")
}


```

```{r}
# Tonality with tonal loudness
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(8274, 1313, 885, 64475, 10), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_abserror
resultsOutTonal1$Rsquared
```

```{r}
# store results
resdAnnoyMedFit['Abs tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resdAnnoyMedFit['Abs tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resdAnnoyMedFit['Abs tonal inc loud', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                                      which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutTonal1$OOB_abserror
resdAnnoyMedPermImp$AbsTonal1 <- resultsOutTonal1$conditional_permimp
```


```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1$conditional_permimp))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.18))

if (saveplots){
  ggsave(filename="PtAdAnnoyTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtAdAnnoyTonalLdConPermimp.svg")
}


```

Repeated without tonal loudness

```{r}
# Tonality
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(8274, 1313, 885, 64475, 10), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_abserror
resultsOutTonal2$Rsquared
```

```{r}
# store results
resdAnnoyMedFit['Abs tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resdAnnoyMedFit['Abs tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resdAnnoyMedFit['Abs tonal no loud', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                                     which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutTonal2$OOB_abserror
resdAnnoyMedPermImp$AbsTonal2 <- resultsOutTonal2$conditional_permimp
```


```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2$conditional_permimp))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.18))


if (saveplots){
  ggsave(filename="PtAdAnnoyTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtAdAnnoyTonalNoLdConPermimp.svg")
}


```


```{r}
# Fluctuation strength
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluct <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(5537, 616544, 2247, 302, 3098), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_abserror
resultsOutFluct$Rsquared
```

```{r}

# store results
resdAnnoyMedFit['Abs fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resdAnnoyMedFit['Abs fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resdAnnoyMedFit['Abs fluct', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                             which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutFluct$OOB_abserror
resdAnnoyMedPermImp$AbsFluct <- resultsOutFluct$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- data.frame('Var_imp'=rev(resultsOutFluct$conditional_permimp))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoyFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtAdAnnoyFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRough <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(89668, 782, 94, 613, 64678), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_abserror
resultsOutRough$Rsquared
```

```{r}
# store results
resdAnnoyMedFit['Abs rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resdAnnoyMedFit['Abs rough', 'Rsquared'] <- resultsOutRough$Rsquared
resdAnnoyMedFit['Abs rough', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                             which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutRough$OOB_abserror
resdAnnoyMedPermImp$AbsRough <- resultsOutRough$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- data.frame('Var_imp'=rev(resultsOutRough$conditional_permimp))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  svg(filename=file.path(outFigPath, "PtAdAnnoyRoughConPermimp.svg"), family='serif', width=10, height=7)
  pBar
  dump <- dev.off()
}

if (saveplots){
  ggsave(filename="PtAdAnnoyRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtAdAnnoyRoughConPermimp.svg")
}


```

```{r}
# Impulsiveness
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpuls <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(82724, 187, 93812, 2427, 19), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_abserror
resultsOutImpuls$Rsquared
```

```{r}

# store results
resdAnnoyMedFit['Abs impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resdAnnoyMedFit['Abs impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resdAnnoyMedFit['Abs impuls', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                              which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutImpuls$OOB_abserror
resdAnnoyMedPermImp$AbsImpuls <- resultsOutImpuls$conditional_permimp

```


```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- data.frame('Var_imp'=rev(resultsOutImpuls$conditional_permimp))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoyImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtAdAnnoyImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(7558, 614, 6578, 6139, 15), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_abserror
resultsOutSQMs1$Rsquared
```

```{r}

# store results
resdAnnoyMedFit['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resdAnnoyMedFit['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resdAnnoyMedFit['Abs SQMs inc tonal loud', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                                           which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutSQMs1$OOB_abserror
resdAnnoyMedPermImp$AbsSQMs1 <- resultsOutSQMs1$conditional_permimp

```


```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoyAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtAdAnnoyAbsSQMsTonLdConPermimp.svg")
}

```

Repeated without tonal loudness.

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonalInt05ExMaxLR", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(7558, 614, 6578, 6139, 15), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_abserror
resultsOutSQMs2$Rsquared
```

```{r}

# store results
resdAnnoyMedFit['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resdAnnoyMedFit['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resdAnnoyMedFit['Abs SQMs no tonal loud', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                                          which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutSQMs2$OOB_abserror
resdAnnoyMedPermImp$AbsSQMs2 <- resultsOutSQMs2$conditional_permimp

```


```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoyAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtAdAnnoyAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]
stimDataANum$UASLAeq <- as.numeric(stimDataANum$UASLAeq)
stimDataANum$SNRlevel <- as.numeric(stimDataANum$SNRlevel)
```

```{r}

iVars <- c(names(stimDataANum)[which(colnames(stimDataANum)=="LAeqdiffLAF90"):
                               which(colnames(stimDataANum)=="dImpulsHMS05ExMaxLR")], "SNRlevel")

resultsOutDiffs <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(65, 6568, 548, 49878, 98), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutDiffs$OOB_RMSE
resultsOutDiffs$OOB_abserror
resultsOutDiffs$Rsquared
```

```{r}

# store results
resdAnnoyMedFit['Diff vars', 'RMSE'] <- resultsOutDiffs$OOB_RMSE
resdAnnoyMedFit['Diff vars', 'Rsquared'] <- resultsOutDiffs$Rsquared
resdAnnoyMedFit['Diff vars', which(colnames(resdAnnoyMedFit) == 'AEq0'):
                             which(colnames(resdAnnoyMedFit) == 'AEq100')] <- resultsOutDiffs$OOB_abserror
resdAnnoyMedPermImp$DiffVars <- resultsOutDiffs$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffs.conimp <- data.frame('Var_imp'=rev(resultsOutDiffs$conditional_permimp))

pBar <- ggplot(resultsOutDiffs.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffs.conimp), levels=rownames(resultsOutDiffs.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAdAnnoyDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtAdAnnoyDiffVarsConPermimp.svg")
}

```

Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resdAnnoyMedFit, paste(outDataPath, "\\ptACRFdAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resdAnnoyMedPermImp){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resdAnnoyMedPermImp[ii])
    names(temp[[ii]]) <- names(resdAnnoyMedPermImp[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptACRFdAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## High annoyance

### Absolute variables

Now the response outcome 'high annoyance' is analysed, once more in the same way.

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]
stimDataANum$UASLAeq <- as.numeric(stimDataANum$UASLAeq)
stimDataANum$SNRlevel <- as.numeric(stimDataANum$SNRlevel)
```

```{r}
resHiAnnoyMedFit <- data.frame(RMSE = numeric(),
                               Rsquared = numeric(),
                               AEq0 = numeric(),
                               AEq25 = numeric(),
                               AEq50 = numeric(),
                               AEq75 = numeric(),
                               AEq100 = numeric())
resHiAnnoyMedPermImp <- list()

```

```{r}
iVars <- names(stimDataANum)[which(names(stimDataANum) == 'UASLAeq'):which(names(stimDataANum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbs <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(4645, 5656, 23, 44848, 222), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_abserror
resultsOutAbs$Rsquared
```

```{r, fig.width=5, fig.height=5}
# base::plot(as.numeric(as.character(stimDataANum$HighAnnoyProportion))*100,
#            as.numeric(as.character(resultsOutAbs$OOB_predicts))*100, col=rgb(0, 102/255, 255/255, 0.2),
#            xlim=c(0, 50), ylim=c(0, 50), xlab="% High annoyance", ylab="Predicted % high annoyance")
```

```{r}
# store results
resHiAnnoyMedFit['Abs vars', 'RMSE'] <- resultsOutAbs$OOB_RMSE
resHiAnnoyMedFit['Abs vars', 'Rsquared'] <- resultsOutAbs$Rsquared
resHiAnnoyMedFit['Abs vars', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                             which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutAbs$OOB_abserror
resHiAnnoyMedPermImp$AbsVars <- resultsOutAbs$conditional_permimp

```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbs.conimp <- data.frame('Var_imp'=rev(resultsOutAbs$conditional_permimp))

pBar <- ggplot(resultsOutAbs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp), levels=rownames(resultsOutAbs.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAHiAnnoyAbsVarsConPermimp.svg", width=10, height=7, path=outFigPath)
  unlink("PtAHiAnnoyAbsVarsConPermimp.svg")
}


```
### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are replaced, as the SQM analysis can incorporate 0 values (whereas dB metrics cannot be handled in this way).

```{r}

stimDataANum <- rbind(stimDataANum, stimDataA[stimDataA['Recording']
                                              == "A1_CALBIN_Pa.wav",
                                              colnames(stimDataANum)],
                      stimDataA[stimDataA['Recording']
                                              == "A2_CALBIN_Pa.wav",
                                              colnames(stimDataANum)])
stimDataANum <- arrange(stimDataANum, Recording)

```

#### Individual SQMs

```{r}
# Sharpness
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharp <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(5227, 7174, 47, 4447, 999), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_abserror
resultsOutSharp$Rsquared
```

```{r}
# store results
resHiAnnoyMedFit['Abs sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resHiAnnoyMedFit['Abs sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resHiAnnoyMedFit['Abs sharp', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                              which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutSharp$OOB_abserror
resHiAnnoyMedPermImp$AbsSharp <- resultsOutSharp$conditional_permimp

```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- data.frame('Var_imp'=rev(resultsOutSharp$conditional_permimp))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAHiAnnoySharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtAHiAnnoySharpConPermimp.svg")
}


```
Tonality including tonal loudness

```{r}
# Tonality inc tonal loudness
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(303, 5644, 100, 20, 326), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_abserror
resultsOutTonal1$Rsquared
```

```{r}
# store results
resHiAnnoyMedFit['Abs tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resHiAnnoyMedFit['Abs tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resHiAnnoyMedFit['Abs tonal inc loud', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                                       which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutTonal1$OOB_abserror
resHiAnnoyMedPermImp$AbsTonal1 <- resultsOutTonal1$conditional_permimp
```

```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1$conditional_permimp))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.008))

if (saveplots){
  ggsave(filename="PtAHiAnnoyTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtAHiAnnoyTonalLdConPermimp.svg")
}

```

Tonality without tonal loudness

```{r}
# Tonality without tonal loudness
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(303, 5644, 100, 20, 326), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_abserror
resultsOutTonal2$Rsquared
```

```{r}
# store results
resHiAnnoyMedFit['Abs tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resHiAnnoyMedFit['Abs tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resHiAnnoyMedFit['Abs tonal no loud', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                                      which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutTonal2$OOB_abserror
resHiAnnoyMedPermImp$AbsTonal2 <- resultsOutTonal2$conditional_permimp
```


```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2$conditional_permimp))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.008))

if (saveplots){
  ggsave(filename="PtAHiAnnoyTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtAHiAnnoyTonalNoLdConPermimp.svg")
}

```

```{r}
# Fluctuation strength
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluct <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(7474, 585325, 2524, 2, 4124), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_abserror
resultsOutFluct$Rsquared
```

```{r}

# store results
resHiAnnoyMedFit['Abs fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resHiAnnoyMedFit['Abs fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resHiAnnoyMedFit['Abs fluct', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                                         which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutFluct$OOB_abserror
resHiAnnoyMedPermImp$AbsFluct <- resultsOutFluct$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- data.frame('Var_imp'=rev(resultsOutFluct$conditional_permimp))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAHiAnnoyFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtAHiAnnoyFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRough <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(4141, 412, 974, 757, 752), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_abserror
resultsOutRough$Rsquared
```

```{r}
# store results
resHiAnnoyMedFit['Abs rough', 'RMSE'] <- resultsOutRough$OOB_RMSE
resHiAnnoyMedFit['Abs rough', 'Rsquared'] <- resultsOutRough$Rsquared
resHiAnnoyMedFit['Abs rough', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                              which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutRough$OOB_abserror
resHiAnnoyMedPermImp$AbsRough <- resultsOutRough$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- data.frame('Var_imp'=rev(resultsOutRough$conditional_permimp))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAHiAnnoyRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtAHiAnnoyRoughConPermimp.svg")
}


```

```{r}
# Impulsiveness
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpuls <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(24, 74242, 16576, 717, 33), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_abserror
resultsOutImpuls$Rsquared
```

```{r}

# store results
resHiAnnoyMedFit['Abs impuls', 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resHiAnnoyMedFit['Abs impuls', 'Rsquared'] <- resultsOutImpuls$Rsquared
resHiAnnoyMedFit['Abs impuls', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                               which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutImpuls$OOB_abserror
resHiAnnoyMedPermImp$AbsImpuls <- resultsOutImpuls$conditional_permimp

```


```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- data.frame('Var_imp'=rev(resultsOutImpuls$conditional_permimp))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAHiAnnoyImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtAHiAnnoyImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs1 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(7758, 787, 5875, 686, 59), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_abserror
resultsOutSQMs1$Rsquared
```

```{r}

# store results
resHiAnnoyMedFit['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resHiAnnoyMedFit['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resHiAnnoyMedFit['Abs SQMs inc tonal loud', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                                            which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutSQMs1$OOB_abserror
resHiAnnoyMedPermImp$AbsSQMs1 <- resultsOutSQMs1$conditional_permimp

```


```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.006))

if (saveplots){
  ggsave(filename="PtAHiAnnoyAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtAHiAnnoyAbsSQMsTonLdConPermimp.svg")
}

```
Repeated without tonal loudness

```{r}
iVars <- c("UASLoudISO1PowAvgMaxLR", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonalInt05ExMaxLR", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs2 <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(7758, 787, 5875, 686, 59), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_abserror
resultsOutSQMs2$Rsquared
```

```{r}

# store results
resHiAnnoyMedFit['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resHiAnnoyMedFit['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resHiAnnoyMedFit['Abs SQMs no tonal loud', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                                           which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutSQMs2$OOB_abserror
resHiAnnoyMedPermImp$AbsSQMs2 <- resultsOutSQMs2$conditional_permimp

```


```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.006))

if (saveplots){
  ggsave(filename="PtAHiAnnoyAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtAHiAnnoyAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataANum <- stimDataANum[complete.cases(stimDataANum),]
stimDataANum$UASLAeq <- as.numeric(stimDataANum$UASLAeq)
stimDataANum$SNRlevel <- as.numeric(stimDataANum$SNRlevel)
```

```{r}

iVars <- c(names(stimDataANum)[which(colnames(stimDataANum)=="LAeqdiffLAF90"):
                               which(colnames(stimDataANum)=="dImpulsHMS05ExMaxLR")], "SNRlevel")

resultsOutDiffs <- multi_crfReg(dataIn=stimDataANum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(75465, 42, 273, 32758, 9370), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutDiffs$OOB_RMSE
resultsOutDiffs$OOB_abserror
resultsOutDiffs$Rsquared
```

```{r}

# store results
resHiAnnoyMedFit['Diff vars', 'RMSE'] <- resultsOutDiffs$OOB_RMSE
resHiAnnoyMedFit['Diff vars', 'Rsquared'] <- resultsOutDiffs$Rsquared
resHiAnnoyMedFit['Diff vars', which(colnames(resHiAnnoyMedFit) == 'AEq0'):
                              which(colnames(resHiAnnoyMedFit) == 'AEq100')] <- resultsOutDiffs$OOB_abserror
resHiAnnoyMedPermImp$DiffVars <- resultsOutDiffs$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffs.conimp <- data.frame('Var_imp'=rev(resultsOutDiffs$conditional_permimp))

pBar <- ggplot(resultsOutDiffs.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffs.conimp), levels=rownames(resultsOutDiffs.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtAHiAnnoyDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtAHiAnnoyDiffVarsConPermimp.svg")
}

```

Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resHiAnnoyMedFit, paste(outDataPath, "\\ptACRFHiAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resHiAnnoyMedPermImp){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resHiAnnoyMedPermImp[ii])
    names(temp[[ii]]) <- names(resHiAnnoyMedPermImp[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptACRFHiAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## Noticeability

### Absolute variables

Now the response outcome 'noticeability' is analysed, once more in the same way, but using the truncated N=30 dataset.

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimNoticeDataANum <- stimNoticeDataANum[complete.cases(stimNoticeDataANum),]
stimNoticeDataANum$UASLAeq <- as.numeric(stimNoticeDataANum$UASLAeq)
stimNoticeDataANum$SNRlevel <- as.numeric(stimNoticeDataANum$SNRlevel)
```

```{r}
resNoticeMedFit<- data.frame(RMSE = numeric(),
                             Rsquared = numeric(),
                             AEq0 = numeric(),
                             AEq25 = numeric(),
                             AEq50 = numeric(),
                             AEq75 = numeric(),
                             AEq100 = numeric())
resNoticeMedPermImp <- list()

```

```{r}
iVars <- names(stimNoticeDataANum)[which(names(stimNoticeDataANum) == 'UASLAeq'):which(names(stimNoticeDataANum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbs <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(484, 5494, 8888, 6564, 13268), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutAbs$OOB_RMSE
resultsOutAbs$OOB_abserror
resultsOutAbs$Rsquared
```

```{r}
# store results
resNoticeMedFit['Abs vars', 'RMSE'] <- resultsOutAbs$OOB_RMSE
resNoticeMedFit['Abs vars', 'Rsquared'] <- resultsOutAbs$Rsquared
resNoticeMedFit['Abs vars', which(colnames(resNoticeMedFit) == 'AEq0'):
                            which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutAbs$OOB_abserror
resNoticeMedPermImp$AbsVars <- resultsOutAbs$conditional_permimp

```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbs.conimp <- data.frame('Var_imp'=rev(resultsOutAbs$conditional_permimp))

pBar <- ggplot(resultsOutAbs.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbs.conimp), levels=rownames(resultsOutAbs.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeAbsVarsConPermimp.svg", width=10, height=11.5, path=outFigPath)
  unlink("PtANoticeAbsVarsConPermimp.svg")
}


```
### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are not replaced, as the SQM analysis is using PNL.

```{r}

# stimNoticeDataANum <- rbind(stimNoticeDataANum, stimNoticeDataA[stimNoticeDataA['Recording']
#                                                                 == "A1_CALBIN_Pa.wav",
#                                                                 colnames(stimNoticeDataANum)],
#                             stimNoticeDataA[stimNoticeDataA['Recording']
#                                             == "A2_CALBIN_Pa.wav",
#                                             colnames(stimNoticeDataANum)])
# stimNoticeDataANum <- arrange(stimNoticeDataANum, Recording)

```

#### Individual SQMs

Sharpness

```{r}
# Sharpness
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharp <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(77681, 56, 2326, 9156, 3357), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSharp$OOB_RMSE
resultsOutSharp$OOB_abserror
resultsOutSharp$Rsquared
```

```{r}
# store results
resNoticeMedFit['Abs sharp', 'RMSE'] <- resultsOutSharp$OOB_RMSE
resNoticeMedFit['Abs sharp', 'Rsquared'] <- resultsOutSharp$Rsquared
resNoticeMedFit['Abs sharp', which(colnames(resNoticeMedFit) == 'AEq0'):
                             which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutSharp$OOB_abserror
resNoticeMedPermImp$AbsSharp <- resultsOutSharp$conditional_permimp

```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharp.conimp <- data.frame('Var_imp'=rev(resultsOutSharp$conditional_permimp))

pBar <- ggplot(resultsOutSharp.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharp.conimp), levels=rownames(resultsOutSharp.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeSharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtANoticeSharpConPermimp.svg")
}


```
Tonality including tonal loudness

```{r}
# Tonality
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1 <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(85, 546, 9530, 5024, 146450), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal1$OOB_RMSE
resultsOutTonal1$OOB_abserror
resultsOutTonal1$Rsquared
```

```{r}
# store results
resNoticeMedFit['Abs tonal inc loud', 'RMSE'] <- resultsOutTonal1$OOB_RMSE
resNoticeMedFit['Abs tonal inc loud', 'Rsquared'] <- resultsOutTonal1$Rsquared
resNoticeMedFit['Abs tonal inc loud', which(colnames(resNoticeMedFit) == 'AEq0'):
                                      which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutTonal1$OOB_abserror
resNoticeMedPermImp$AbsTonal1 <- resultsOutTonal1$conditional_permimp
```


```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1$conditional_permimp))

pBar <- ggplot(resultsOutTonal1.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1.conimp), levels=rownames(resultsOutTonal1.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.1))

if (saveplots){
  ggsave(filename="PtANoticeTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtANoticeTonalLdConPermimp.svg")
}

```
Repeated without tonal loudness

```{r}
# Tonality
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2 <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(85, 546, 9530, 5024, 146450), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutTonal2$OOB_RMSE
resultsOutTonal2$OOB_abserror
resultsOutTonal2$Rsquared
```

```{r}
# store results
resNoticeMedFit['Abs tonal no loud', 'RMSE'] <- resultsOutTonal2$OOB_RMSE
resNoticeMedFit['Abs tonal no loud', 'Rsquared'] <- resultsOutTonal2$Rsquared
resNoticeMedFit['Abs tonal no loud', which(colnames(resNoticeMedFit) == 'AEq0'):
                                     which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutTonal2$OOB_abserror
resNoticeMedPermImp$AbsTonal2 <- resultsOutTonal2$conditional_permimp
```


```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2$conditional_permimp))

pBar <- ggplot(resultsOutTonal2.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2.conimp), levels=rownames(resultsOutTonal2.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.1))

if (saveplots){
  ggsave(filename="PtANoticeTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtANoticeTonalNoLdConPermimp.svg")
}

```


```{r}
# Fluctuation strength
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluct <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(50354, 2047, 4524, 872, 27074), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutFluct$OOB_RMSE
resultsOutFluct$OOB_abserror
resultsOutFluct$Rsquared
```

```{r}

# store results
resNoticeMedFit['Abs fluct', 'RMSE'] <- resultsOutFluct$OOB_RMSE
resNoticeMedFit['Abs fluct', 'Rsquared'] <- resultsOutFluct$Rsquared
resNoticeMedFit['Abs fluct', which(colnames(resNoticeMedFit) == 'AEq0'):
                             which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutFluct$OOB_abserror
resNoticeMedPermImp$AbsFluct <- resultsOutFluct$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluct.conimp <- data.frame('Var_imp'=rev(resultsOutFluct$conditional_permimp))

pBar <- ggplot(resultsOutFluct.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluct.conimp), levels=rownames(resultsOutFluct.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtANoticeFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRough <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(7520, 757, 8582, 863, 7757), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutRough$OOB_RMSE
resultsOutRough$OOB_abserror
resultsOutRough$Rsquared
```

```{r}
# store results
resNoticeMedFit["Abs rough", 'RMSE'] <- resultsOutRough$OOB_RMSE
resNoticeMedFit["Abs rough", 'Rsquared'] <- resultsOutRough$Rsquared
resNoticeMedFit["Abs rough", which(colnames(resNoticeMedFit) == 'AEq0'):
                             which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutRough$OOB_abserror
resNoticeMedPermImp$AbsRough <- resultsOutRough$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRough.conimp <- data.frame('Var_imp'=rev(resultsOutRough$conditional_permimp))

pBar <- ggplot(resultsOutRough.conimp) + geom_col(aes(x=factor(rownames(resultsOutRough.conimp), levels=rownames(resultsOutRough.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtANoticeRoughConPermimp.svg")
}


```

```{r}
# Impulsiveness
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpuls <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(557220, 757, 5708, 7864, 2044), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutImpuls$OOB_RMSE
resultsOutImpuls$OOB_abserror
resultsOutImpuls$Rsquared
```

```{r}

# store results
resNoticeMedFit["Abs impuls", 'RMSE'] <- resultsOutImpuls$OOB_RMSE
resNoticeMedFit["Abs impuls", 'Rsquared'] <- resultsOutImpuls$Rsquared
resNoticeMedFit["Abs impuls", which(colnames(resNoticeMedFit) == 'AEq0'):
                              which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutImpuls$OOB_abserror
resNoticeMedPermImp$AbsImpuls <- resultsOutImpuls$conditional_permimp

```


```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpuls.conimp <- data.frame('Var_imp'=rev(resultsOutImpuls$conditional_permimp))

pBar <- ggplot(resultsOutImpuls.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpuls.conimp), levels=rownames(resultsOutImpuls.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtANoticeImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonLdECMAHMS05ExBin", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs1 <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(3830, 77750, 6480, 59297, 42), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs1$OOB_RMSE
resultsOutSQMs1$OOB_abserror
resultsOutSQMs1$Rsquared
```

```{r}

# store results
resNoticeMedFit['Abs SQMS inc loud', 'RMSE'] <- resultsOutSQMs1$OOB_RMSE
resNoticeMedFit['Abs SQMS inc loud', 'Rsquared'] <- resultsOutSQMs1$Rsquared
resNoticeMedFit['Abs SQMS inc loud', which(colnames(resNoticeMedFit) == 'AEq0'):
                                     which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutSQMs1$OOB_abserror
resNoticeMedPermImp$AbsSQMs1 <- resultsOutSQMs1$conditional_permimp

```


```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1.conimp), levels=rownames(resultsOutSQMs1.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtANoticeAbsSQMsTonLdConPermimp.svg")
}

```
Repeated without tonal loudness

```{r}
iVars <- c("UASPNLmaxMaxLR", "AmbientLAeq", "UASSharpAuresISO305ExMaxLR", "UASTonalInt05ExMaxLR", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs2 <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(3830, 77750, 6480, 59297, 42), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutSQMs2$OOB_RMSE
resultsOutSQMs2$OOB_abserror
resultsOutSQMs2$Rsquared
```

```{r}

# store results
resNoticeMedFit['Abs SQMS no loud', 'RMSE'] <- resultsOutSQMs2$OOB_RMSE
resNoticeMedFit['Abs SQMS no loud', 'Rsquared'] <- resultsOutSQMs2$Rsquared
resNoticeMedFit['Abs SQMS no loud', which(colnames(resNoticeMedFit) == 'AEq0'):
                                    which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutSQMs2$OOB_abserror
resNoticeMedPermImp$AbsSQMs2 <- resultsOutSQMs2$conditional_permimp

```


```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2.conimp), levels=rownames(resultsOutSQMs2.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtANoticeAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimNoticeDataANum <- stimNoticeDataANum[complete.cases(stimNoticeDataANum),]
stimNoticeDataANum$UASLAeq <- as.numeric(stimNoticeDataANum$UASLAeq)
stimNoticeDataANum$SNRlevel <- as.numeric(stimNoticeDataANum$SNRlevel)
```

```{r}
iVars <- c(names(stimNoticeDataANum)[which(colnames(stimNoticeDataANum)=="LAeqdiffLAF90"):
                               which(colnames(stimNoticeDataANum)=="dImpulsHMS05ExMaxLR")], "SNRlevel")

resultsOutDiffs <- multi_crfReg(dataIn=stimNoticeDataANum, iVars=iVars, dVar='NoticedPropFilt', seeds=c(3, 782, 560, 995, 46546), ntree=1000, mtry=as.integer(length(iVars)/1.25), nperm=5)

# print model prediction results
resultsOutDiffs$OOB_RMSE
resultsOutDiffs$OOB_abserror
resultsOutDiffs$Rsquared
```

```{r}

# store results
resNoticeMedFit['Diff vars', 'RMSE'] <- resultsOutDiffs$OOB_RMSE
resNoticeMedFit['Diff vars', 'Rsquared'] <- resultsOutDiffs$Rsquared
resNoticeMedFit['Diff vars', which(colnames(resNoticeMedFit) == 'AEq0'):
                             which(colnames(resNoticeMedFit) == 'AEq100')] <- resultsOutDiffs$OOB_abserror
resNoticeMedPermImp$DiffVars <- resultsOutDiffs$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffs.conimp <- data.frame('Var_imp'=rev(resultsOutDiffs$conditional_permimp))

pBar <- ggplot(resultsOutDiffs.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffs.conimp), levels=rownames(resultsOutDiffs.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion UAS noticed)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtANoticeDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtANoticeDiffVarsConPermimp.svg")
}

```

Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resNoticeMedFit, paste(outDataPath, "\\ptACRFNoticeOOBFit.csv", sep=""))

  ii <- 0
  temp = list()
  for (res in resNoticeMedPermImp){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resNoticeMedPermImp[ii])
    names(temp[[ii]]) <- names(resNoticeMedPermImp[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptACRFNoticeConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## Part A summary

Summary of annoyance results for Part A

```{r, fig.width=10, fig.height=7}
# combine the annoyance perm importance results
res = transform(merge(x=as.data.frame(resAnnoyMedPermImp$AbsSQMs1/max(resAnnoyMedPermImp$AbsSQMs1)),
                      y=as.data.frame(resdAnnoyMedPermImp$AbsSQMs1/max(resdAnnoyMedPermImp$AbsSQMs1)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)



res = transform(merge(x=res,
                      y=as.data.frame(resHiAnnoyMedPermImp$AbsSQMs1/max(resHiAnnoyMedPermImp$AbsSQMs1)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

rownames(res) <- c("Ambient env. LAeq", "UAS fluct. str. O-V ^10%", "UAS impuls. HMS mean", "UAS impuls. HMS pow. avg.", "UAS loud. HMS pow. avg.", "UAS loud. ISO 532-1 pow. avg.", "UAS loud. ISO 532-3 pow. avg.", "UAS rough. F&Z ^5%", "UAS sharp. Aures+ISO 532-3 ^5%", "UAS ton. loud. HMS pow. avg.")
colnames(res) <- c("Annoyance", "Change in annoyance", "%HA")
res[is.na(res)] <- 0

res <- tibble::rownames_to_column(res, var="Variable")

res <- tidyr::pivot_longer(res, cols=-Variable, names_to="Outcome", values_to="Imp")

res <- res[order(res$Imp),]

pBar <- ggplot(res[order(res$Imp), ]) + geom_col(aes(fill=Outcome, y=Imp, x=Variable), colour='grey35',  width=0.75, show.legend=TRUE) + labs(x="Variable", y="Normalised variable importance") + theme(text = element_text(family = "serif"), legend.position = "right") + coord_flip(ylim=c(-0.1, 2)) + scale_fill_manual(values=mycolours)
pBar

if (saveplots){
  ggsave(filename="PtAcrfSQMsSummary.svg", width=10, height=7, path=outFigPath)
  unlink("PtAcrfSQMsSummary.svg")
}


# par(mai=c(1, 3, 0.2, 0.5), family='serif')
# pCol <- barplot(as.matrix(t(res[order(res$Annoyance),])), col=mycolours, las=1, xlim=c(0, 3), horiz=TRUE, xlab="Normalised importance", family=windowsFont('serif'))
# legend(x='topright', fill=mycolours, legend=colnames(res))
# 
# if (saveplots){
#   svg(filename=file.path(outFigPath, "PtAcrfSQMsSummary.svg"), family='serif', width=10, height=7)
#   par(mai=c(1, 3, 0.2, 0.5), family='serif')
#   pCol <- barplot(as.matrix(t(res[order(res$Annoyance),])), col=mycolours, las=1, xlim=c(0, 3), horiz=TRUE, xlab="Normalised importance", family=windowsFont('serif'))
#   legend(x='topright', fill=mycolours, legend=colnames(res))
#   dump <- dev.off()
# }


```

```{r, fig.width=10, fig.height=7}
# combine the annoyance perm importance results
res = transform(merge(x=as.data.frame(resAnnoyMedPermImp$AbsSQMs2/max(resAnnoyMedPermImp$AbsSQMs2)),
                      y=as.data.frame(resdAnnoyMedPermImp$AbsSQMs2/max(resdAnnoyMedPermImp$AbsSQMs2)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

res = transform(merge(x=res,
                      y=as.data.frame(resHiAnnoyMedPermImp$AbsSQMs2/max(resHiAnnoyMedPermImp$AbsSQMs2)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

rownames(res) <- c("Ambient env. LAeq", "UAS fluct. str. O-V ^10%", "UAS impuls. HMS mean", "UAS impuls. HMS pow. avg.", "UAS loud. HMS pow. avg.", "UAS loud. ISO 532-1 pow. avg.", "UAS loud. ISO 532-3 pow. avg.", "UAS rough. F&Z ^5%", "UAS sharp. Aures+ISO 532-3 ^5%", "UAS tonality HMS (integ.) ^5%")
colnames(res) <- c("Annoyance", "Change in annoyance", "%HA")
res[is.na(res)] <- 0

res <- tibble::rownames_to_column(res, var="Variable")

res <- tidyr::pivot_longer(res, cols=-Variable, names_to="Outcome", values_to="Imp")

res <- res[order(res$Imp),]

pBar <- ggplot(res[order(res$Imp), ]) + geom_col(aes(fill=Outcome, y=Imp, x=Variable), colour='grey35',  width=0.75, show.legend=TRUE) + labs(x="Variable", y="Normalised variable importance") + theme(text=element_text(family = "serif"), legend.position = "right") + coord_flip(ylim=c(-0.1, 2)) + scale_fill_manual(values=mycolours)
pBar

if (saveplots){
  ggsave(filename="PtAcrfSQMsNoTonLdSummary.svg", width=10, height=7, path=outFigPath)
  unlink("PtAcrfSQMsNoTonLdSummary.svg")
}

# par(mai=c(1, 3, 0.2, 0.5), family='serif')
#   pCol <- barplot(as.matrix(t(res[order(res$Annoyance),])), col=mycolours, las=1, xlim=c(0, 3), horiz=TRUE, xlab="Normalised importance", family=windowsFont('serif'))
#   legend(x='topright', fill=mycolours, legend=colnames(res))
# 
# if (saveplots){
#   svg(filename=file.path(outFigPath, "PtAcrfSQMsNoTonLdSummary.svg"), family='serif', width=10, height=7)
#   par(mai=c(1, 3, 0.2, 0.5), family='serif')
#   pCol <- barplot(as.matrix(t(res[order(res$Annoyance),])), col=mycolours, las=1, xlim=c(0, 3), horiz=TRUE, xlab="Normalised importance", family=windowsFont('serif'))
#   legend(x='topright', fill=mycolours, legend=colnames(res))
#   dump <- dev.off()
# }

```


# Part B analysis

## Import data and wrangle

```{r}

stimDataBpath <- utils::choose.files(caption=r"(Select refmap_listest1_testdataB_ByStim.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)", filters=matrix(data=c("refmap_listest1_testdataB_ByStim.csv", "refmap_listest1_testdataB_ByStim.csv"), ncol=2))

stimDataB <- utils::read.csv(stimDataBpath, header=TRUE)
colnames(stimDataB)[1] <- "Recording"

```

```{r}

# definition of ordinal variable levels
# SNRCatsB <- c("No UAS", "2", "8")
# UASLAeqCatsB <- c("No UAS", "54", "60")

```

```{r}

stimDataBNum <- data.frame()

stimDataBNum <- cbind(stimDataB[, 'Recording'],
                      stimDataB[, which(colnames(stimDataB)=="UASEvents"):
                                which(colnames(stimDataB)=="UASEventDensity")],
                      stimDataB[, which(colnames(stimDataB)=="UASLAeq"):
                                which(colnames(stimDataB)=="SNRlevel")],
                      stimDataB[, which(colnames(stimDataB)=="UASLAeqMaxLR"):
                                which(colnames(stimDataB)=="UASImpulsHMS05ExMaxLR")],
                      stimDataB[, which(colnames(stimDataB)=="LAeqdiffLAF90"):
                                which(colnames(stimDataB)=="PartLoudGMLT05Ex")],
                      stimDataB[, which(colnames(stimDataB)=="dTonalECMAHMSAvgMaxLR"):
                                which(colnames(stimDataB)=="dImpulsHMS05ExMaxLR")],
                      stimDataB[, which(colnames(stimDataB)=="ValenceMedian"):
                                which(colnames(stimDataB)=="HighAnnoyProportion")])
stimDataBNum <- stimDataBNum[, !(colnames(stimDataBNum) %in% c('UASLAEMaxLR', 'UASEventDensity', 'AmbientLAeq'))]

colnames(stimDataBNum)[1] <- "Recording"

# stimDataBNum[['SNRlevel']] <- encode_ordinal(stimDataB[['SNRlevel']], order=SNRCatsB)
# stimDataBNum[['UASLAeq']] <- encode_ordinal(stimDataB[['UASLAeq']], order=UASLAeqCatsB)

# make the discrete ordinal variables factors
stimDataBNum[['UASEvents']] <- factor(stimDataBNum[['UASEvents']], levels=c(0, 1, 3, 5, 9), order=TRUE)
stimDataBNum[['ValenceMedian']] <- factor(stimDataBNum[['ValenceMedian']], levels=c(1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), order=TRUE)
stimDataBNum[['ArousalMedian']] <- factor(stimDataBNum[['ArousalMedian']], levels=c(1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), order=TRUE)
stimDataBNum[['AnnoyMedian']] <- factor(stimDataBNum[['AnnoyMedian']], levels=c(0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5,
                                                                                5.5, 6, 6.5, 7, 7.5, 8, 8.5, 9, 9.5, 10), order=TRUE)
stimDataBNum[['dValenceMedian']] <- factor(stimDataBNum[['dValenceMedian']], levels=c(-4, -3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0,
                                                                                      0.5, 1, 1.5, 2, 2.5, 3, 3.5,  4), order=TRUE)
stimDataBNum[['dArousalMedian']] <- factor(stimDataBNum[['dArousalMedian']], levels=c(-4, -3.5, -3, -2.5, -2, -1.5, -1, -0.5, 0,
                                                                                      0.5, 1, 1.5, 2, 2.5, 3, 3.5,  4), order=TRUE)
stimDataBNum[['dAnnoyMedian']] <- factor(stimDataBNum[['dAnnoyMedian']], levels=c(-10, -9.5, -9, -8.5, -8, -7.5, -7, -6.5, -6, -5.5, -5,
                                                                                  -4.5, -4, -3.5, -3, -2.5, -2, -1.5, -1, -0.5,
                                                                                 0, 0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5,
                                                                                 5.5, 6, 6.5, 7, 7.5, 8, 8.5, 9, 9.5, 10), order=TRUE)


```


## Annoyance

### Absolute variables

The random forest modelling is run on the aggregated data, including all the variables.

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataBNum <- stimDataBNum[complete.cases(stimDataBNum),]

stimDataBNum$UASLAeq <- as.numeric(stimDataBNum$UASLAeq)
stimDataBNum$SNRlevel <- as.numeric(stimDataBNum$SNRlevel)

```

```{r}
resAnnoyMedFitB <- data.frame(RMSE = numeric(),
                               Rsquared = numeric(),
                               AEq0 = numeric(),
                               AEq25 = numeric(),
                               AEq50 = numeric(),
                               AEq75 = numeric(),
                               AEq100 = numeric())
resAnnoyMedPermImpB <- list()

```


```{r}
iVars <- names(stimDataBNum)[which(names(stimDataBNum) == 'UASEvents'):which(names(stimDataBNum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(981, 687, 808, 4596, 2210), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutAbsB$OOB_RMSE
resultsOutAbsB$OOB_abserror
resultsOutAbsB$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs vars', 'RMSE'] <- resultsOutAbsB$OOB_RMSE
resAnnoyMedFitB['Abs vars', 'Rsquared'] <- resultsOutAbsB$Rsquared
resAnnoyMedFitB['Abs vars', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                                       which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutAbsB$OOB_abserror
resAnnoyMedPermImpB$AbsVars <- resultsOutAbsB$conditional_permimp
```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbsB.conimp <- data.frame('Var_imp'=rev(resultsOutAbsB$conditional_permimp))

pBar <- ggplot(resultsOutAbsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbsB.conimp), levels=rownames(resultsOutAbsB.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBAnnoyAbsVarsConPermimp.svg", width=10, height=11.5, path=outFigPath)
  unlink("PtBAnnoyAbsVarsConPermimp.svg")
}

```
### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are replaced, as the SQM analysis can incorporate 0 values (whereas dB metrics cannot be handled in this way).

```{r}

stimDataBNum <- rbind(stimDataBNum, stimDataB[stimDataB['Recording']
                                              == "B2_CALBIN_Pa.wav",
                                              colnames(stimDataBNum)])
stimDataBNum <- arrange(stimDataBNum, Recording)

```


#### Individual SQMs

Now a model is run omitting loudness and level variables, while retaining only (one of) the top importance loudness variables, and each category of SQM in turn.

```{r}
# Sharpness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharpB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(565, 9878, 21, 4546, 64), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSharpB$OOB_RMSE
resultsOutSharpB$OOB_abserror
resultsOutSharpB$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs sharp', 'RMSE'] <- resultsOutSharpB$OOB_RMSE
resAnnoyMedFitB['Abs sharp', 'Rsquared'] <- resultsOutSharpB$Rsquared
resAnnoyMedFitB['Abs sharp', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutSharpB$OOB_abserror
resAnnoyMedPermImpB$AbsSharp <- resultsOutSharpB$conditional_permimp
```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharpB.conimp <- data.frame('Var_imp'=rev(resultsOutSharpB$conditional_permimp))

pBar <- ggplot(resultsOutSharpB.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharpB.conimp), levels=rownames(resultsOutSharpB.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBAnnoySharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtBAnnoySharpConPermimp.svg")
}

```
Tonality including tonal loudness

```{r}
# Tonality inc tonal loudness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(5656, 118848, 5815, 4545, 12313), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutTonal1B$OOB_RMSE
resultsOutTonal1B$OOB_abserror
resultsOutTonal1B$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs inc tonal loud', 'RMSE'] <- resultsOutTonal1B$OOB_RMSE
resAnnoyMedFitB['Abs inc tonal loud', 'Rsquared'] <- resultsOutTonal1B$Rsquared
resAnnoyMedFitB['Abs inc tonal loud', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                                      which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutTonal1B$OOB_abserror
resAnnoyMedPermImpB$AbsTonal1 <- resultsOutTonal1B$conditional_permimp
```

```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1B.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1B$conditional_permimp))

pBar <- ggplot(resultsOutTonal1B.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1B.conimp), levels=rownames(resultsOutTonal1B.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.05))

if (saveplots){
  ggsave(filename="PtBAnnoyTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtBAnnoyTonalLdConPermimp.svg")
}

```
Re-run tonality evaluation omitting tonal loudness 

```{r}
# Tonality
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(5656, 118848, 5815, 4545, 12313), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutTonal2B$OOB_RMSE
resultsOutTonal2B$OOB_abserror
resultsOutTonal2B$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs no tonal loud', 'RMSE'] <- resultsOutTonal2B$OOB_RMSE
resAnnoyMedFitB['Abs no tonal loud', 'Rsquared'] <- resultsOutTonal2B$Rsquared
resAnnoyMedFitB['Abs no tonal loud', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                                     which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutTonal2B$OOB_abserror
resAnnoyMedPermImpB$AbsTonal2 <- resultsOutTonal2B$conditional_permimp
```

```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2B.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2B$conditional_permimp))

pBar <- ggplot(resultsOutTonal2B.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2B.conimp), levels=rownames(resultsOutTonal2B.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.05))

if (saveplots){
  ggsave(filename="PtBAnnoyTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtBAnnoyTonalNoLdConPermimp.svg")
}

```


```{r}
# Fluctuation strength
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluctB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(46446, 121, 54548, 3, 787), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutFluctB$OOB_RMSE
resultsOutFluctB$OOB_abserror
resultsOutFluctB$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs fluct', 'RMSE'] <- resultsOutFluctB$OOB_RMSE
resAnnoyMedFitB['Abs fluct', 'Rsquared'] <- resultsOutFluctB$Rsquared
resAnnoyMedFitB['Abs fluct', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutFluctB$OOB_abserror
resAnnoyMedPermImpB$AbsFluct <- resultsOutFluctB$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluctB.conimp <- data.frame('Var_imp'=rev(resultsOutFluctB$conditional_permimp))

pBar <- ggplot(resultsOutFluctB.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluctB.conimp), levels=rownames(resultsOutFluctB.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBAnnoyFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtBAnnoyFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRoughB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(66, 78716, 8797, 87, 9421), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutRoughB$OOB_RMSE
resultsOutRoughB$OOB_abserror
resultsOutRoughB$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs rough', 'RMSE'] <- resultsOutRoughB$OOB_RMSE
resAnnoyMedFitB['Abs rough', 'Rsquared'] <- resultsOutRoughB$Rsquared
resAnnoyMedFitB['Abs rough', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutRoughB$OOB_abserror
resAnnoyMedPermImpB$AbsRough <- resultsOutRoughB$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRoughB.conimp <- data.frame('Var_imp'=rev(resultsOutRoughB$conditional_permimp))

pBar <- ggplot(resultsOutRoughB.conimp) + geom_col(aes(x=factor(rownames(resultsOutRoughB.conimp), levels=rownames(resultsOutRoughB.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBAnnoyRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtBAnnoyRoughConPermimp.svg")
}

```

```{r}
# Impulsiveness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpulsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(31, 45448, 8441, 546, 6451), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutImpulsB$OOB_RMSE
resultsOutImpulsB$OOB_abserror
resultsOutImpulsB$Rsquared
```

```{r}
# store results
resAnnoyMedFitB['Abs impuls', 'RMSE'] <- resultsOutImpulsB$OOB_RMSE
resAnnoyMedFitB['Abs impuls', 'Rsquared'] <- resultsOutImpulsB$Rsquared
resAnnoyMedFitB['Abs impuls', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutImpulsB$OOB_abserror
resAnnoyMedPermImpB$AbsImpuls <- resultsOutImpulsB$conditional_permimp

```

```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpulsB.conimp <- data.frame('Var_imp'=rev(resultsOutImpulsB$conditional_permimp))

pBar <- ggplot(resultsOutImpulsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpulsB.conimp), levels=rownames(resultsOutImpulsB.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBAnnoyImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtBAnnoyImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASFluctOV10ExMaxLR", "UASRoughFZ10ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs1B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(456, 41546, 7872, 5780, 45640), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSQMs1B$OOB_RMSE
resultsOutSQMs1B$OOB_abserror
resultsOutSQMs1B$Rsquared
```

```{r}

# store results
resAnnoyMedFitB['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1B$OOB_RMSE
resAnnoyMedFitB['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1B$Rsquared
resAnnoyMedFitB['Abs SQMs inc tonal loud', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                                          which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutSQMs1B$OOB_abserror
resAnnoyMedPermImpB$AbsSQMs1 <- resultsOutSQMs1B$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1B.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1B$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1B.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1B.conimp), levels=rownames(resultsOutSQMs1B.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.03))

if (saveplots){
  ggsave(filename="PtBAnnoyAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtBAnnoyAbsSQMsTonLdConPermimp.svg")
}

```

Repeated without tonal loudness

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASTonalAuAvgMaxLR", "UASFluctOV10ExMaxLR", "UASRoughFZ10ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs2B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(456, 41546, 7872, 5780, 45640), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSQMs2B$OOB_RMSE
resultsOutSQMs2B$OOB_abserror
resultsOutSQMs2B$Rsquared
```

```{r}

# store results
resAnnoyMedFitB['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2B$OOB_RMSE
resAnnoyMedFitB['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2B$Rsquared
resAnnoyMedFitB['Abs SQMs no tonal loud', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                                          which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutSQMs2B$OOB_abserror
resAnnoyMedPermImpB$AbsSQMs2 <- resultsOutSQMs2B$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2B.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2B$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2B.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2B.conimp), levels=rownames(resultsOutSQMs2B.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(0, 0.03))

if (saveplots){
  ggsave(filename="PtBAnnoyAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtBAnnoyAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataBNum <- stimDataBNum[complete.cases(stimDataBNum),]
stimDataBNum$UASLAeq <- as.numeric(stimDataBNum$UASLAeq)
stimDataBNum$SNRlevel <- as.numeric(stimDataBNum$SNRlevel)
```

```{r}
iVars <- c(names(stimDataBNum)[which(colnames(stimDataBNum)=="LAeqdiffLAF90"):
                               which(colnames(stimDataBNum)=="dImpulsHMS05ExMaxLR")], "SNRlevel", "UASEvents")
resultsOutDiffsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='AnnoyMedian', seeds=c(7005, 126, 4540, 5465, 840), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutDiffsB$OOB_RMSE
resultsOutDiffsB$OOB_abserror
resultsOutDiffsB$Rsquared
```

```{r}

# store results
resAnnoyMedFitB['Diff vars', 'RMSE'] <- resultsOutDiffsB$OOB_RMSE
resAnnoyMedFitB['Diff vars', 'Rsquared'] <- resultsOutDiffsB$Rsquared
resAnnoyMedFitB['Diff vars', which(colnames(resAnnoyMedFitB) == 'AEq0'):
                            which(colnames(resAnnoyMedFitB) == 'AEq100')] <- resultsOutDiffsB$OOB_abserror
resAnnoyMedPermImpB$DiffVars <- resultsOutDiffsB$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffsB.conimp <- data.frame('Var_imp'=rev(resultsOutDiffsB$conditional_permimp))

pBar <- ggplot(resultsOutDiffsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffsB.conimp), levels=rownames(resultsOutDiffsB.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (median annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBAnnoyDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtBAnnoyDiffVarsConPermimp.svg")
}

```
Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resAnnoyMedFitB, paste(outDataPath, "\\ptBCRFAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resAnnoyMedPermImpB){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resAnnoyMedPermImpB[ii])
    names(temp[[ii]]) <- names(resAnnoyMedPermImpB[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptBCRFAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## Change in annoyance

### Absolute variables

The random forest modelling is run on the aggregated data, including all the variables.

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataBNum <- stimDataBNum[complete.cases(stimDataBNum),]

stimDataBNum$UASLAeq <- as.numeric(stimDataBNum$UASLAeq)
stimDataBNum$SNRlevel <- as.numeric(stimDataBNum$SNRlevel)

```

```{r}
resdAnnoyMedFitB <- data.frame(RMSE = numeric(),
                               Rsquared = numeric(),
                               AEq0 = numeric(),
                               AEq25 = numeric(),
                               AEq50 = numeric(),
                               AEq75 = numeric(),
                               AEq100 = numeric())
resdAnnoyMedPermImpB <- list()

```


```{r}
iVars <- names(stimDataBNum)[which(names(stimDataBNum) == 'UASEvents'):which(names(stimDataBNum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(54654, 15102, 8405, 10, 9174), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutAbsB$OOB_RMSE
resultsOutAbsB$OOB_abserror
resultsOutAbsB$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs vars', 'RMSE'] <- resultsOutAbsB$OOB_RMSE
resdAnnoyMedFitB['Abs vars', 'Rsquared'] <- resultsOutAbsB$Rsquared
resdAnnoyMedFitB['Abs vars', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutAbsB$OOB_abserror
resdAnnoyMedPermImpB$AbsVars <- resultsOutAbsB$conditional_permimp
```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbsB.conimp <- data.frame('Var_imp'=rev(resultsOutAbsB$conditional_permimp))

pBar <- ggplot(resultsOutAbsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbsB.conimp), levels=rownames(resultsOutAbsB.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBdAnnoyAbsVarsConPermimp.svg", width=10, height=11.5, path=outFigPath)
  unlink("PtBdAnnoyAbsVarsConPermimp.svg")
}

```
### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are replaced, as the SQM analysis can incorporate 0 values (whereas dB metrics cannot be handled in this way).

```{r}

stimDataBNum <- rbind(stimDataBNum, stimDataB[stimDataB['Recording']
                                              == "B2_CALBIN_Pa.wav",
                                              colnames(stimDataBNum)])
stimDataBNum <- arrange(stimDataBNum, Recording)

```


#### Individual SQMs

Now a model is run omitting loudness and level variables, while retaining only (one of) the top importance loudness variables, and each category of SQM in turn.

```{r}
# Sharpness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharpB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(8605, 322, 7460, 98, 1984), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSharpB$OOB_RMSE
resultsOutSharpB$OOB_abserror
resultsOutSharpB$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs sharp', 'RMSE'] <- resultsOutSharpB$OOB_RMSE
resdAnnoyMedFitB['Abs sharp', 'Rsquared'] <- resultsOutSharpB$Rsquared
resdAnnoyMedFitB['Abs sharp', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                              which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutSharpB$OOB_abserror
resdAnnoyMedPermImpB$AbsSharp <- resultsOutSharpB$conditional_permimp
```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharpB.conimp <- data.frame('Var_imp'=rev(resultsOutSharpB$conditional_permimp))

pBar <- ggplot(resultsOutSharpB.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharpB.conimp), levels=rownames(resultsOutSharpB.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBdAnnoySharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtBdAnnoySharpConPermimp.svg")
}

```
Tonality including tonal loudness

```{r}
# Tonality inc tonal loudness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(324505, 1324, 5078, 508, 780), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutTonal1B$OOB_RMSE
resultsOutTonal1B$OOB_abserror
resultsOutTonal1B$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs inc tonal loud', 'RMSE'] <- resultsOutTonal1B$OOB_RMSE
resdAnnoyMedFitB['Abs inc tonal loud', 'Rsquared'] <- resultsOutTonal1B$Rsquared
resdAnnoyMedFitB['Abs inc tonal loud', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                                       which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutTonal1B$OOB_abserror
resdAnnoyMedPermImpB$AbsTonal1 <- resultsOutTonal1B$conditional_permimp
```

```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1B.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1B$conditional_permimp))

pBar <- ggplot(resultsOutTonal1B.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1B.conimp), levels=rownames(resultsOutTonal1B.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.005, 0.03))

if (saveplots){
  ggsave(filename="PtBdAnnoyTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtBdAnnoyTonalLdConPermimp.svg")
}

```
Re-run tonality evaluation omitting tonal loudness 

```{r}
# Tonality
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(324505, 1324, 5078, 508, 780), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutTonal2B$OOB_RMSE
resultsOutTonal2B$OOB_abserror
resultsOutTonal2B$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs no tonal loud', 'RMSE'] <- resultsOutTonal2B$OOB_RMSE
resdAnnoyMedFitB['Abs no tonal loud', 'Rsquared'] <- resultsOutTonal2B$Rsquared
resdAnnoyMedFitB['Abs no tonal loud', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                                     which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutTonal2B$OOB_abserror
resdAnnoyMedPermImpB$AbsTonal2 <- resultsOutTonal2B$conditional_permimp
```

```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2B.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2B$conditional_permimp))

pBar <- ggplot(resultsOutTonal2B.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2B.conimp), levels=rownames(resultsOutTonal2B.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.005, 0.03))

if (saveplots){
  ggsave(filename="PtBdAnnoyTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtBdAnnoyTonalNoLdConPermimp.svg")
}

```


```{r}
# Fluctuation strength
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluctB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(724, 2298, 70460, 541, 7456), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutFluctB$OOB_RMSE
resultsOutFluctB$OOB_abserror
resultsOutFluctB$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs fluct', 'RMSE'] <- resultsOutFluctB$OOB_RMSE
resdAnnoyMedFitB['Abs fluct', 'Rsquared'] <- resultsOutFluctB$Rsquared
resdAnnoyMedFitB['Abs fluct', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutFluctB$OOB_abserror
resdAnnoyMedPermImpB$AbsFluct <- resultsOutFluctB$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluctB.conimp <- data.frame('Var_imp'=rev(resultsOutFluctB$conditional_permimp))

pBar <- ggplot(resultsOutFluctB.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluctB.conimp), levels=rownames(resultsOutFluctB.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBdAnnoyFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtBdAnnoyFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRoughB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(1508, 850, 8, 7804, 38), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutRoughB$OOB_RMSE
resultsOutRoughB$OOB_abserror
resultsOutRoughB$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs rough', 'RMSE'] <- resultsOutRoughB$OOB_RMSE
resdAnnoyMedFitB['Abs rough', 'Rsquared'] <- resultsOutRoughB$Rsquared
resdAnnoyMedFitB['Abs rough', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutRoughB$OOB_abserror
resdAnnoyMedPermImpB$AbsRough <- resultsOutRoughB$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRoughB.conimp <- data.frame('Var_imp'=rev(resultsOutRoughB$conditional_permimp))

pBar <- ggplot(resultsOutRoughB.conimp) + geom_col(aes(x=factor(rownames(resultsOutRoughB.conimp), levels=rownames(resultsOutRoughB.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBdAnnoyRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtBdAnnoyRoughConPermimp.svg")
}

```

```{r}
# Impulsiveness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpulsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(50278, 30561, 65740, 21, 155), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutImpulsB$OOB_RMSE
resultsOutImpulsB$OOB_abserror
resultsOutImpulsB$Rsquared
```

```{r}
# store results
resdAnnoyMedFitB['Abs impuls', 'RMSE'] <- resultsOutImpulsB$OOB_RMSE
resdAnnoyMedFitB['Abs impuls', 'Rsquared'] <- resultsOutImpulsB$Rsquared
resdAnnoyMedFitB['Abs impuls', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutImpulsB$OOB_abserror
resdAnnoyMedPermImpB$AbsImpuls <- resultsOutImpulsB$conditional_permimp

```

```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpulsB.conimp <- data.frame('Var_imp'=rev(resultsOutImpulsB$conditional_permimp))

pBar <- ggplot(resultsOutImpulsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpulsB.conimp), levels=rownames(resultsOutImpulsB.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBdAnnoyImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtBdAnnoyImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASFluctFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMS05ExMaxLR")
resultsOutSQMs1B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(4888, 50881, 804, 5470, 257), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSQMs1B$OOB_RMSE
resultsOutSQMs1B$OOB_abserror
resultsOutSQMs1B$Rsquared
```

```{r}

# store results
resdAnnoyMedFitB['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1B$OOB_RMSE
resdAnnoyMedFitB['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1B$Rsquared
resdAnnoyMedFitB['Abs SQMs inc tonal loud', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                                          which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutSQMs1B$OOB_abserror
resdAnnoyMedPermImpB$AbsSQMs1 <- resultsOutSQMs1B$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1B.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1B$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1B.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1B.conimp), levels=rownames(resultsOutSQMs1B.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.01, 0.025))

if (saveplots){
  ggsave(filename="PtBdAnnoyAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtBdAnnoyAbsSQMsTonLdConPermimp.svg")
}

```

Repeated without tonal loudness

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASTonalECMAHMSAvgMaxLR", "UASFluctFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMS05ExMaxLR")
resultsOutSQMs2B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(4888, 50881, 804, 5470, 257), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSQMs2B$OOB_RMSE
resultsOutSQMs2B$OOB_abserror
resultsOutSQMs2B$Rsquared
```

```{r}

# store results
resdAnnoyMedFitB['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2B$OOB_RMSE
resdAnnoyMedFitB['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2B$Rsquared
resdAnnoyMedFitB['Abs SQMs no tonal loud', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                                          which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutSQMs2B$OOB_abserror
resdAnnoyMedPermImpB$AbsSQMs2 <- resultsOutSQMs2B$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2B.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2B$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2B.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2B.conimp), levels=rownames(resultsOutSQMs2B.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.01, 0.025))

if (saveplots){
  ggsave(filename="PtBdAnnoyAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtBdAnnoyAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataBNum <- stimDataBNum[complete.cases(stimDataBNum),]
stimDataBNum$UASLAeq <- as.numeric(stimDataBNum$UASLAeq)
stimDataBNum$SNRlevel <- as.numeric(stimDataBNum$SNRlevel)
```

```{r}
iVars <- c(names(stimDataBNum)[which(colnames(stimDataBNum)=="LAeqdiffLAF90"):
                               which(colnames(stimDataBNum)=="dImpulsHMS05ExMaxLR")], "SNRlevel", "UASEvents")
resultsOutDiffsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='dAnnoyMedian', seeds=c(70765, 3277, 790150, 4308, 8888), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutDiffsB$OOB_RMSE
resultsOutDiffsB$OOB_abserror
resultsOutDiffsB$Rsquared
```

```{r}

# store results
resdAnnoyMedFitB['Diff vars', 'RMSE'] <- resultsOutDiffsB$OOB_RMSE
resdAnnoyMedFitB['Diff vars', 'Rsquared'] <- resultsOutDiffsB$Rsquared
resdAnnoyMedFitB['Diff vars', which(colnames(resdAnnoyMedFitB) == 'AEq0'):
                            which(colnames(resdAnnoyMedFitB) == 'AEq100')] <- resultsOutDiffsB$OOB_abserror
resdAnnoyMedPermImpB$DiffVars <- resultsOutDiffsB$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffsB.conimp <- data.frame('Var_imp'=rev(resultsOutDiffsB$conditional_permimp))

pBar <- ggplot(resultsOutDiffsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffsB.conimp), levels=rownames(resultsOutDiffsB.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (median change in annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBdAnnoyDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtBdAnnoyDiffVarsConPermimp.svg")
}

```
Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resdAnnoyMedFitB, paste(outDataPath, "\\ptBCRFdAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resdAnnoyMedPermImpB){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resdAnnoyMedPermImpB[ii])
    names(temp[[ii]]) <- names(resdAnnoyMedPermImpB[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptBCRFdAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## High annoyance

### Absolute variables

The random forest modelling is run on the aggregated data, including all the variables.

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataBNum <- stimDataBNum[complete.cases(stimDataBNum),]

stimDataBNum$UASLAeq <- as.numeric(stimDataBNum$UASLAeq)
stimDataBNum$SNRlevel <- as.numeric(stimDataBNum$SNRlevel)

```

```{r}
resHiAnnoyMedFitB <- data.frame(RMSE = numeric(),
                                Rsquared = numeric(),
                                AEq0 = numeric(),
                                AEq25 = numeric(),
                                AEq50 = numeric(),
                                AEq75 = numeric(),
                                AEq100 = numeric())
resHiAnnoyMedPermImpB <- list()

```


```{r}
iVars <- names(stimDataBNum)[which(names(stimDataBNum) == 'UASEvents'):which(names(stimDataBNum) == 'UASImpulsHMS05ExMaxLR')]
iVars <- iVars[! iVars %in% 'SNRlevel']
resultsOutAbsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(42757, 31908, 37, 8005, 2), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutAbsB$OOB_RMSE
resultsOutAbsB$OOB_abserror
resultsOutAbsB$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs vars', 'RMSE'] <- resultsOutAbsB$OOB_RMSE
resHiAnnoyMedFitB['Abs vars', 'Rsquared'] <- resultsOutAbsB$Rsquared
resHiAnnoyMedFitB['Abs vars', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                              which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutAbsB$OOB_abserror
resHiAnnoyMedPermImpB$AbsVars <- resultsOutAbsB$conditional_permimp
```

```{r, fig.width=10,fig.height=11.5}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutAbsB.conimp <- data.frame('Var_imp'=rev(resultsOutAbsB$conditional_permimp))

pBar <- ggplot(resultsOutAbsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutAbsB.conimp), levels=rownames(resultsOutAbsB.conimp)), y=Var_imp), fill=mycolours[1], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBHiAnnoyAbsVarsConPermimp.svg", width=10, height=11.5, path=outFigPath)
  unlink("PtBHiAnnoyAbsVarsConPermimp.svg")
}

```
### SQM analysis

#### Replace ambient only stimuli

Here, the 'ambient only' stimuli are replaced, as the SQM analysis can incorporate 0 values (whereas dB metrics cannot be handled in this way).

```{r}

stimDataBNum <- rbind(stimDataBNum, stimDataB[stimDataB['Recording']
                                              == "B2_CALBIN_Pa.wav",
                                              colnames(stimDataBNum)])
stimDataBNum <- arrange(stimDataBNum, Recording)

```


#### Individual SQMs

Now a model is run omitting loudness and level variables, while retaining only (one of) the top importance loudness variables, and each category of SQM in turn.

```{r}
# Sharpness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASSharpAuresISO305ExMaxLR")
resultsOutSharpB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(702, 8, 1415, 15771, 147), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSharpB$OOB_RMSE
resultsOutSharpB$OOB_abserror
resultsOutSharpB$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs sharp', 'RMSE'] <- resultsOutSharpB$OOB_RMSE
resHiAnnoyMedFitB['Abs sharp', 'Rsquared'] <- resultsOutSharpB$Rsquared
resHiAnnoyMedFitB['Abs sharp', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                              which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutSharpB$OOB_abserror
resHiAnnoyMedPermImpB$AbsSharp <- resultsOutSharpB$conditional_permimp
```

```{r, fig.width=10,fig.height=1.7}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSharpB.conimp <- data.frame('Var_imp'=rev(resultsOutSharpB$conditional_permimp))

pBar <- ggplot(resultsOutSharpB.conimp) + geom_col(aes(x=factor(rownames(resultsOutSharpB.conimp), levels=rownames(resultsOutSharpB.conimp)), y=Var_imp), fill=mycolours[2], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Sharpness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBHiAnnoySharpConPermimp.svg", width=10, height=1.7, path=outFigPath)
  unlink("PtBHiAnnoySharpConPermimp.svg")
}

```
Tonality including tonal loudness

```{r}
# Tonality inc tonal loudness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASTonLdECMAHMS05ExBin", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal1B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(50434, 3057, 580, 451, 547), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutTonal1B$OOB_RMSE
resultsOutTonal1B$OOB_abserror
resultsOutTonal1B$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs inc tonal loud', 'RMSE'] <- resultsOutTonal1B$OOB_RMSE
resHiAnnoyMedFitB['Abs inc tonal loud', 'Rsquared'] <- resultsOutTonal1B$Rsquared
resHiAnnoyMedFitB['Abs inc tonal loud', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                                       which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutTonal1B$OOB_abserror
resHiAnnoyMedPermImpB$AbsTonal1 <- resultsOutTonal1B$conditional_permimp
```

```{r, fig.width=10,fig.height=3.8}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal1B.conimp <- data.frame('Var_imp'=rev(resultsOutTonal1B$conditional_permimp))

pBar <- ggplot(resultsOutTonal1B.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal1B.conimp), levels=rownames(resultsOutTonal1B.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Tonality inc. tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.005, 0.03))

if (saveplots){
  ggsave(filename="PtBHiAnnoyTonalLdConPermimp.svg", width=10, height=3.8, path=outFigPath)
  unlink("PtBHiAnnoyTonalLdConPermimp.svg")
}

```
Re-run tonality evaluation omitting tonal loudness 

```{r}
# Tonality
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASTonalECMAHMSAvgMaxLR", "UASTonalECMAHMS05ExMaxLR", "UASTonalIntAvgMaxLR", "UASTonalInt05ExMaxLR", "UASTonalAuAvgMaxLR", "UASTonalAu05ExMaxLR", "UASTonalAu10ExMaxLR")
resultsOutTonal2B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(50434, 3057, 580, 451, 547), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutTonal2B$OOB_RMSE
resultsOutTonal2B$OOB_abserror
resultsOutTonal2B$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs no tonal loud', 'RMSE'] <- resultsOutTonal2B$OOB_RMSE
resHiAnnoyMedFitB['Abs no tonal loud', 'Rsquared'] <- resultsOutTonal2B$Rsquared
resHiAnnoyMedFitB['Abs no tonal loud', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                                     which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutTonal2B$OOB_abserror
resHiAnnoyMedPermImpB$AbsTonal2 <- resultsOutTonal2B$conditional_permimp
```

```{r, fig.width=10,fig.height=3.2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutTonal2B.conimp <- data.frame('Var_imp'=rev(resultsOutTonal2B$conditional_permimp))

pBar <- ggplot(resultsOutTonal2B.conimp) + geom_col(aes(x=factor(rownames(resultsOutTonal2B.conimp), levels=rownames(resultsOutTonal2B.conimp)), y=Var_imp), fill=mycolours[3], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Tonality w/o tonal loudness") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.005, 0.03))

if (saveplots){
  ggsave(filename="PtBHiAnnoyTonalNoLdConPermimp.svg", width=10, height=3.2, path=outFigPath)
  unlink("PtBHiAnnoyTonalNoLdConPermimp.svg")
}

```


```{r}
# Fluctuation strength
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASFluctHMS10ExBin", "UASFluctHMS05ExBin", "UASFluctFZ10ExMaxLR", "UASFluctFZ05ExMaxLR", "UASFluctOV10ExMaxLR", "UASFluctOV05ExMaxLR")
resultsOutFluctB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(82824, 5220, 4, 165, 95941), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutFluctB$OOB_RMSE
resultsOutFluctB$OOB_abserror
resultsOutFluctB$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs fluct', 'RMSE'] <- resultsOutFluctB$OOB_RMSE
resHiAnnoyMedFitB['Abs fluct', 'Rsquared'] <- resultsOutFluctB$Rsquared
resHiAnnoyMedFitB['Abs fluct', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutFluctB$OOB_abserror
resHiAnnoyMedPermImpB$AbsFluct <- resultsOutFluctB$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutFluctB.conimp <- data.frame('Var_imp'=rev(resultsOutFluctB$conditional_permimp))

pBar <- ggplot(resultsOutFluctB.conimp) + geom_col(aes(x=factor(rownames(resultsOutFluctB.conimp), levels=rownames(resultsOutFluctB.conimp)), y=Var_imp), fill=mycolours[4], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Fluctuation strength") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBHiAnnoyFluctConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtBHiAnnoyFluctConPermimp.svg")
}

```

```{r}
# Roughness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASRoughECMAHMS10ExBin", "UASRoughECMAHMS05ExBin", "UASRoughFZ10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASRoughDW10ExMaxLR", "UASRoughDW05ExMaxLR")
resultsOutRoughB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(954, 250, 56565, 480, 543), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutRoughB$OOB_RMSE
resultsOutRoughB$OOB_abserror
resultsOutRoughB$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs rough', 'RMSE'] <- resultsOutRoughB$OOB_RMSE
resHiAnnoyMedFitB['Abs rough', 'Rsquared'] <- resultsOutRoughB$Rsquared
resHiAnnoyMedFitB['Abs rough', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutRoughB$OOB_abserror
resHiAnnoyMedPermImpB$AbsRough <- resultsOutRoughB$conditional_permimp

```

```{r, fig.width=10,fig.height=2.9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutRoughB.conimp <- data.frame('Var_imp'=rev(resultsOutRoughB$conditional_permimp))

pBar <- ggplot(resultsOutRoughB.conimp) + geom_col(aes(x=factor(rownames(resultsOutRoughB.conimp), levels=rownames(resultsOutRoughB.conimp)), y=Var_imp), fill=mycolours[5], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Roughness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBHiAnnoyRoughConPermimp.svg", width=10, height=2.9, path=outFigPath)
  unlink("PtBHiAnnoyRoughConPermimp.svg")
}

```

```{r}
# Impulsiveness
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASImpulsHMSAvgMaxLR", "UASImpulsHMS05ExMaxLR", "UASImpulsHMSPowAvgMaxLR")
resultsOutImpulsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(6525, 6541, 4581, 2216, 5656032), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutImpulsB$OOB_RMSE
resultsOutImpulsB$OOB_abserror
resultsOutImpulsB$Rsquared
```

```{r}
# store results
resHiAnnoyMedFitB['Abs impuls', 'RMSE'] <- resultsOutImpulsB$OOB_RMSE
resHiAnnoyMedFitB['Abs impuls', 'Rsquared'] <- resultsOutImpulsB$Rsquared
resHiAnnoyMedFitB['Abs impuls', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                             which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutImpulsB$OOB_abserror
resHiAnnoyMedPermImpB$AbsImpuls <- resultsOutImpulsB$conditional_permimp

```

```{r, fig.width=10,fig.height=2}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutImpulsB.conimp <- data.frame('Var_imp'=rev(resultsOutImpulsB$conditional_permimp))

pBar <- ggplot(resultsOutImpulsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutImpulsB.conimp), levels=rownames(resultsOutImpulsB.conimp)), y=Var_imp), fill=mycolours[6], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + ggtitle("Impulsiveness") + theme(text = element_text(family = "serif"))
pBar + coord_flip()

if (saveplots){
  ggsave(filename="PtBHiAnnoyImpulsConPermimp.svg", width=10, height=2, path=outFigPath)
  unlink("PtBHiAnnoyImpulsConPermimp.svg")
}

```
#### SQM and loudness comparison

Now the highest importance SQMs are ranked against each other, controlling for UAS loudness and ambient LAeq.

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASTonLdECMAHMSPowAvgBin", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs1B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(545, 944, 12120, 46484, 165), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSQMs1B$OOB_RMSE
resultsOutSQMs1B$OOB_abserror
resultsOutSQMs1B$Rsquared
```

```{r}

# store results
resHiAnnoyMedFitB['Abs SQMs inc tonal loud', 'RMSE'] <- resultsOutSQMs1B$OOB_RMSE
resHiAnnoyMedFitB['Abs SQMs inc tonal loud', 'Rsquared'] <- resultsOutSQMs1B$Rsquared
resHiAnnoyMedFitB['Abs SQMs inc tonal loud', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                                          which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutSQMs1B$OOB_abserror
resHiAnnoyMedPermImpB$AbsSQMs1 <- resultsOutSQMs1B$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs1B.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs1B$conditional_permimp))

pBar <- ggplot(resultsOutSQMs1B.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs1B.conimp), levels=rownames(resultsOutSQMs1B.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.01, 0.025))

if (saveplots){
  ggsave(filename="PtBHiAnnoyAbsSQMsTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtBHiAnnoyAbsSQMsTonLdConPermimp.svg")
}

```

Repeated without tonal loudness

```{r}
iVars <- c("UASLoudECMAHMSPowAvgBin", "UASEvents", "UASSharpAuresISO3PowAvgMaxLR", "UASTonalAuAvgMaxLR", "UASFluctOV10ExMaxLR", "UASRoughFZ05ExMaxLR", "UASImpulsHMSAvgMaxLR")
resultsOutSQMs2B <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(545, 944, 12120, 46484, 165), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutSQMs2B$OOB_RMSE
resultsOutSQMs2B$OOB_abserror
resultsOutSQMs2B$Rsquared
```

```{r}

# store results
resHiAnnoyMedFitB['Abs SQMs no tonal loud', 'RMSE'] <- resultsOutSQMs2B$OOB_RMSE
resHiAnnoyMedFitB['Abs SQMs no tonal loud', 'Rsquared'] <- resultsOutSQMs2B$Rsquared
resHiAnnoyMedFitB['Abs SQMs no tonal loud', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                                          which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutSQMs2B$OOB_abserror
resHiAnnoyMedPermImpB$AbsSQMs2 <- resultsOutSQMs2B$conditional_permimp

```

```{r, fig.width=10,fig.height=2.4}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutSQMs2B.conimp <- data.frame('Var_imp'=rev(resultsOutSQMs2B$conditional_permimp))

pBar <- ggplot(resultsOutSQMs2B.conimp) + geom_col(aes(x=factor(rownames(resultsOutSQMs2B.conimp), levels=rownames(resultsOutSQMs2B.conimp)), y=Var_imp), fill=mycolours[7], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif"))
pBar + coord_flip(ylim=c(-0.01, 0.025))

if (saveplots){
  ggsave(filename="PtBHiAnnoyAbsSQMsNoTonLdConPermimp.svg", width=10, height=2.4, path=outFigPath)
  unlink("PtBHiAnnoyAbsSQMsNoTonLdConPermimp.svg")
}

```

### Difference variables

Next, the difference metrics are analysed, 

#### Remove ambient only stimuli

Here, the 'ambient only' stimuli are removed, as the analysis cannot handle missing values for dB metrics.

```{r}
stimDataBNum <- stimDataBNum[complete.cases(stimDataBNum),]
stimDataBNum$UASLAeq <- as.numeric(stimDataBNum$UASLAeq)
stimDataBNum$SNRlevel <- as.numeric(stimDataBNum$SNRlevel)
```

```{r}
iVars <- c(names(stimDataBNum)[which(colnames(stimDataBNum)=="LAeqdiffLAF90"):
                               which(colnames(stimDataBNum)=="dImpulsHMS05ExMaxLR")], "SNRlevel", "UASEvents")
resultsOutDiffsB <- multi_crfReg(dataIn=stimDataBNum, iVars=iVars, dVar='HighAnnoyProportion', seeds=c(42870, 1321, 2, 454, 15410), ntree=1000, mtry=as.integer(length(iVars)/1.25), minsplit=10, minbucket=5, nperm=5)

# print model prediction results
resultsOutDiffsB$OOB_RMSE
resultsOutDiffsB$OOB_abserror
resultsOutDiffsB$Rsquared
```

```{r}

# store results
resHiAnnoyMedFitB['Diff vars', 'RMSE'] <- resultsOutDiffsB$OOB_RMSE
resHiAnnoyMedFitB['Diff vars', 'Rsquared'] <- resultsOutDiffsB$Rsquared
resHiAnnoyMedFitB['Diff vars', which(colnames(resHiAnnoyMedFitB) == 'AEq0'):
                            which(colnames(resHiAnnoyMedFitB) == 'AEq100')] <- resultsOutDiffsB$OOB_abserror
resHiAnnoyMedPermImpB$DiffVars <- resultsOutDiffsB$conditional_permimp

```

```{r, fig.width=10,fig.height=9}
par(mai=c(0,3,0,0))

# plot conditional importance
resultsOutDiffsB.conimp <- data.frame('Var_imp'=rev(resultsOutDiffsB$conditional_permimp))

pBar <- ggplot(resultsOutDiffsB.conimp) + geom_col(aes(x=factor(rownames(resultsOutDiffsB.conimp), levels=rownames(resultsOutDiffsB.conimp)), y=Var_imp), fill=mycolours[8], width=0.5) + labs(x="Variable", y="Conditional variable importance (proportion high annoyance)") + theme(text = element_text(family = "serif")) + coord_flip()
pBar

if (saveplots){
  ggsave(filename="PtBHiAnnoyDiffVarsConPermimp.svg", width=10, height=9, path=outFigPath)
  unlink("PtBHiAnnoyDiffVarsConPermimp.svg")
}

```
Save the results outputs to file

```{r}

if (savedata){
  utils::write.csv(resHiAnnoyMedFitB, paste(outDataPath, "\\ptBCRFHiAnnoyOOBFit.csv", sep=""))
  ii <- 0
  temp = list()
  for (res in resHiAnnoyMedPermImpB){
    ii <- ii + 1
    temp[[ii]] <- as.data.frame(resHiAnnoyMedPermImpB[ii])
    names(temp[[ii]]) <- names(resHiAnnoyMedPermImpB[ii])
  }
  openxlsx::write.xlsx(temp, paste(outDataPath, "\\ptBCRFHiAnnoyConPermimp.xlsx",
                                   sep=""),
                       rowNames=TRUE)
}

```

## Part B summary

Summary of annoyance results for Part B

```{r, fig.width=10, fig.height=7}
# combine the annoyance perm importance results

res = transform(merge(x=as.data.frame(resAnnoyMedPermImpB$AbsSQMs1/max(resAnnoyMedPermImpB$AbsSQMs1)),
                      y=as.data.frame(resdAnnoyMedPermImpB$AbsSQMs1/max(resdAnnoyMedPermImpB$AbsSQMs1)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

res = transform(merge(x=res,
                      y=as.data.frame(resHiAnnoyMedPermImpB$AbsSQMs1/max(resHiAnnoyMedPermImpB$AbsSQMs1)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

rownames(res) <- c("UAS events", "UAS fluct. str. F&Z ^10%", "UAS fluct. str. O-V ^10%", "UAS impuls. HMS ^5%", "UAS impuls. mean", "UAS loud. ECMA-412-8 pow. avg.", "UAS rough. F&Z ^5%", "UAS rough. F&Z ^10%", "UAS sharp. Aures+ISO 532-3 pow.avg.", "UAS ton. loud. HMS pow. avg.")
colnames(res) <- c("Annoyance", "Change in annoyance", "Highly Annoyed %")
res[is.na(res)] <- 0

res <- tibble::rownames_to_column(res, var="Variable")

res <- tidyr::pivot_longer(res, cols=-Variable, names_to="Outcome", values_to="Imp")

res <- res[order(res$Imp),]

pBar <- ggplot(res[order(res$Imp), ]) + geom_col(aes(fill=Outcome, y=Imp, x=Variable), colour='grey35',  width=0.75, show.legend=TRUE) + labs(x="Variable", y="Normalised variable importance") + theme(text = element_text(family = "serif"), legend.position = "right") + coord_flip(ylim=c(-0.1, 2.5)) + scale_fill_manual(values=mycolours)
pBar

if (saveplots){
  ggsave(filename="PtBcrfSQMsSummary.svg", width=10, height=7, path=outFigPath)
  unlink("PtBcrfSQMsSummary.svg")
}


```

```{r, fig.width=10, fig.height=7}
# combine the annoyance perm importance results
res = transform(merge(x=as.data.frame(resAnnoyMedPermImpB$AbsSQMs2/max(resAnnoyMedPermImpB$AbsSQMs2)),
                      y=as.data.frame(resdAnnoyMedPermImpB$AbsSQMs2/max(resdAnnoyMedPermImpB$AbsSQMs2)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

res = transform(merge(x=res,
                      y=as.data.frame(resHiAnnoyMedPermImpB$AbsSQMs2/max(resHiAnnoyMedPermImpB$AbsSQMs2)),
                      by.x='row.names',
                      by.y='row.names',
                      all=TRUE),
                row.names=Row.names,
                Row.names=NULL)

rownames(res) <- c("UAS events", "UAS fluct. str. F&Z ^10%", "UAS fluct. str. O-V ^10%", "UAS impuls. HMS ^5%", "UAS impuls. mean", "UAS loud. ECMA-412-8 pow. avg.", "UAS rough. F&Z ^5%", "UAS rough. F&Z ^10%", "UAS sharp. Aures+ISO 532-3 pow.avg.", "UAS tonality Aures mean", "UAS tonality HMS mean")

colnames(res) <- c("Annoyance", "Change in annoyance", "Highly Annoyed %")
res[is.na(res)] <- 0

res <- tibble::rownames_to_column(res, var="Variable")

res <- tidyr::pivot_longer(res, cols=-Variable, names_to="Outcome", values_to="Imp")

res <- res[order(res$Imp),]

pBar <- ggplot(res[order(res$Imp), ]) + geom_col(aes(fill=Outcome, y=Imp, x=Variable), colour='grey35',  width=0.75, show.legend=TRUE) + labs(x="Variable", y="Normalised variable importance") + theme(text = element_text(family = "serif"), legend.position = "right") + coord_flip(ylim=c(-0.1, 2)) + scale_fill_manual(values=mycolours)
pBar

if (saveplots){
  ggsave(filename="PtBcrfSQMsNoTonLdSummary.svg", width=10, height=7, path=outFigPath)
  unlink("PtBcrfSQMsNoTonLdSummary.svg")
}

```
