---
title: "REFMAP listening test 1 analysis: Multi-level linear models for annoyance"
output: html_document
date: "2024-06-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

Load packages

```{r}
library(conflicted)
library(flexplot)
library(lme4)
library(lmerTest)
library(lmtest)
library(stats)
library(ggplot2)
library(openxlsx)
library(performance)
library(rstanarm)
library(MuMIn)
```

Set parameters

```{r}

# plot colour scheme

mycolourlist = list(c(0, 102, 255), c(0, 204, 153), c(255, 0, 102), c(74, 111, 152), c(251, 164, 49), c(204, 153, 255), c(90, 192, 255), c(80, 245, 233), c(255, 90, 192), c(164, 201, 242), c(255, 254, 139), c(255, 243, 255))
mycolours = matrix()

for (ii in 1:length(mycolourlist)){
  mycolours[ii] = rgb(mycolourlist[[ii]][1]/255,
                      mycolourlist[[ii]][2]/255,
                      mycolourlist[[ii]][3]/255)
}

# toggle to save plots
saveplots = TRUE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption="Select output folder to save plots")
}

# toggle to save data
savedata = TRUE

if (savedata){
  # set output plot directory
  if (saveplots==FALSE){
    choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  }
  outDataPath <- utils::choose.dir(caption="Select output folder to save data")
}


```

# Part A analysis

## Import data and wrangle

```{r}

subjDataApath <- utils::choose.files(caption=r"(Select refmap_listest1_testdataA_BySubj.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest1_testdataA_BySubj.csv", "refmap_listest1_testdataA_BySubj.csv"), ncol=2))

subjDataA <- read.csv(subjDataApath, header=TRUE)

```

```{r}
# definition of ordinal variable levels
UASLAeqCatsA <- c("No UAS", "42", "48", "54", "60")
SNRCatsA <- c("No UAS", "-16", "-10", "-4", "2", "8")
UASOpCatsA <- c("No UAS", "Flyby", "Landing", "Takeoff")
UASTypeCatsA <- c("No UAS", "H520", "M300", "T150")

# encode factors
subjDataA$ID. <- factor(subjDataA$ID.)
subjDataA$UASLAeq <- factor(subjDataA$UASLAeq, levels=UASLAeqCatsA, order=TRUE)
subjDataA$SNRlevel <- factor(subjDataA$SNRlevel, levels=SNRCatsA, order=TRUE)
subjDataA$UASOperation <- factor(subjDataA$UASOperation, levels=UASOpCatsA)
subjDataA$UASType <- factor(subjDataA$UASType, levels=UASTypeCatsA)
subjDataA$AmbientEnv <- factor(subjDataA$AmbientEnv, levels=c("Street", "Park"))

# reorder by trial number
subjDataA <- subjDataA[with(subjDataA, order(ID., TrialNumber)), ]

```


## Fit a baseline model

```{r}
control <- lme4::lmerControl(optimizer = 'bobyqa')

# baseline model (no predictors, only clustered intercept)
mBL <- lme4::lmer(Annoyance ~ 1 + (1 | ID.), data=subjDataA,
                        control=control, REML=FALSE)

#mBL_stn <- rstanarm::stan_glmer(Annoyance ~ 1 + (1 | ID.), data=subjDataA, cores=12, iter=4000, seed=2134)

# check the intraclass correlation coefficient and pseudo-Rsquared
performance::icc(mBL)
performance::r2(mBL)

#performance::icc(mBL_stn)
#performance::r2(mBL_stn)

```
## Ambient environment model

Now fit a frequentist model which includes ambient environment category as (i) fixed effect and (ii) mixed effect predictor, and compare with the baseline

```{r, fig.width=8,fig.height=5}
mEnv <- lme4::lmer(Annoyance ~ AmbientEnv + (1 | ID.), data=subjDataA,
                     control=control, REML=FALSE)
mEnv.Env <- lme4::lmer(Annoyance ~ AmbientEnv + (1 + AmbientEnv | ID.), data=subjDataA,
                     control=control, REML=FALSE)

flexplot::compare.fits(Annoyance ~ AmbientEnv | ID., data=subjDataA,
                       model1=mBL, model2=mEnv, clusters=5, re=T)

flexplot::compare.fits(Annoyance ~ AmbientEnv | ID., data=subjDataA,
                       model1=mBL, model2=mEnv.Env, clusters=5, re=T)

flexplot::model.comparison(model1=mEnv, model2=mEnv.Env)
MuMIn::AICc(mEnv, mEnv.Env)

lmtest::lrtest(mEnv, mEnv.Env)
performance::compare_performance(mBL, mEnv, mEnv.Env)

```
## Loudness (fixed) + amb env model
```{r}

# mixed model with HMS loudness as fixed effect, and ambient env as mixed effect
mLoudEnv.Env <- lme4::lmer(Annoyance ~ UASLoudECMAHMSPowAvgBin + AmbientEnv + (1 + AmbientEnv | ID.),
                             data=subjDataA, control=control, REML=FALSE)

flexplot::compare.fits(Annoyance ~ UASLoudECMAHMSPowAvgBin | ID. + AmbientEnv, data=subjDataA,
                       model1=mEnv.Env, model2=mLoudEnv.Env, clusters=5, re=T)

flexplot::model.comparison(model1=mEnv.Env, model2=mLoudEnv.Env)
MuMIn::AICc(mEnv.Env, mLoudEnv.Env)

lmtest::lrtest(mEnv.Env, mLoudEnv.Env)
performance::compare_performance(mBL, mEnv, mEnv.Env, mLoudEnv.Env)
```
## Loudness (mixed) + amb env model

```{r}

# mixed model with HMS loudness and ambient env as mixed effects
mLoudEnv.LoudEnv <- lme4::lmer(Annoyance ~ UASLoudECMAHMSPowAvgBin + AmbientEnv + (1 + AmbientEnv + UASLoudECMAHMSPowAvgBin | ID.),
                                data=subjDataA, control=control, REML=FALSE)

flexplot::compare.fits(Annoyance ~ UASLoudECMAHMSPowAvgBin | ID. + AmbientEnv, data=subjDataA,
                       model1=mLoudEnv.Env, model2=mLoudEnv.LoudEnv, clusters=5, re=T)

flexplot::model.comparison(model1=mLoudEnv.Env, model2=mLoudEnv.LoudEnv)
MuMIn::AICc(mLoudEnv.Env, mLoudEnv.LoudEnv)

lmtest::lrtest(mLoudEnv.Env, mLoudEnv.LoudEnv)
performance::compare_performance(mBL, mEnv, mEnv.Env, mLoudEnv.Env, mLoudEnv.LoudEnv)

```

## Loudness + amb env with interaction model

```{r}

# mixed model with HMS loudness and ambient env as mixed effects, and loudness*ambient as fixed effect
mLoudXEnv.LoudEnv <- lme4::lmer(Annoyance ~ UASLoudECMAHMSPowAvgBin +
                                        AmbientEnv + UASLoudECMAHMSPowAvgBin:AmbientEnv +
                                        (1 +  UASLoudECMAHMSPowAvgBin + AmbientEnv | ID.),
                                      data=subjDataA, control=control, REML=FALSE)

flexplot::compare.fits(Annoyance ~ UASLoudECMAHMSPowAvgBin | ID. + AmbientEnv, data=subjDataA,
                       model1=mLoudEnv.LoudEnv, model2=mLoudXEnv.LoudEnv, clusters=5, re=T)

flexplot::model.comparison(model1=mLoudEnv.LoudEnv, model2=mLoudXEnv.LoudEnv)
MuMIn::AICc(mLoudEnv.LoudEnv, mLoudXEnv.LoudEnv)

lmtest::lrtest(mLoudEnv.LoudEnv, mLoudXEnv.LoudEnv)
performance::compare_performance(mBL, mEnv, mEnv.Env, mLoudEnv.Env,
                                 mLoudEnv.LoudEnv, mLoudXEnv.LoudEnv)


```
## Sound quality models

### Sharpness

```{r}

# mixed model with HMS loudness and ambient env as mixed effects, and sharpness + loudness*ambient as fixed effect
mSLoudXEnv.LoudEnv <- lme4::lmer(Annoyance ~ UASLoudECMAHMSPowAvgBin + UASSharpAuresISO305ExMaxLR +
                                        AmbientEnv + UASLoudECMAHMSPowAvgBin:AmbientEnv +
                                        (1 +  UASLoudECMAHMSPowAvgBin + AmbientEnv | ID.),
                                      data=subjDataA, control=control, REML=FALSE)

flexplot::compare.fits(Annoyance ~ UASLoudECMAHMSPowAvgBin | ID. + AmbientEnv, data=subjDataA,
                       model1=mLoudXEnv.LoudEnv, model2=mSLoudXEnv.LoudEnv, clusters=5, re=T)

flexplot::model.comparison(model1=mLoudXEnv.LoudEnv, model2=mSLoudXEnv.LoudEnv)
MuMIn::AICc(mLoudXEnv.LoudEnv, mSLoudXEnv.LoudEnv)

lmtest::lrtest(mLoudXEnv.LoudEnv, mSLoudXEnv.LoudEnv)
performance::compare_performance(mBL, mEnv, mEnv.Env, mLoudEnv.Env,
                                 mLoudEnv.LoudEnv, mLoudXEnv.LoudEnv, mSLoudXEnv.LoudEnv)



```