---
title: "REFMAP Listening test 2 analysis: Bayesian mixed models for inferential explanation"
output: html_document
date: "2026-05-07"
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(easystats)
library(conflicted)
library(here)
library(brms)
library(bayestestR)
library(tidybayes)
library(bayesplot)
library(tidyverse)
library(DHARMa)
library(tictoc)
library(future)
library(future.apply)
library(mice)
library(marginaleffects)
library(priorsense)
library(posterior)
library(loo)
library(shinystan)
library(shinybrms)
library(ggdist)
library(brmsmargins)
library(viridis)
library(ggnewscale)
library(patchwork)
library(ggpmisc)
library(gginnards)
library(ggridges)

# set package parameters
theme_set(theme_bw())

# CAUTION: calculations in this notebook assume 12 cores available from total of 16
# parallelised processing settings would need to be amended throughout the notebook if
# a different number of cores are available
n_cores <- max(1, parallelly::availableCores() - 4)
future::plan(future::multisession, workers = n_cores)

options(marginaleffects_parallel_inferences = TRUE)
options(marginaleffects_parallel = TRUE)
options(marginaleffects_parallel_packages = c("marginaleffects", "brms"))
options(marginaleffects_posterior_interval = "eti")
options(marginaleffects_posterior_center = mean)

bayesplot::bayesplot_theme_set(bayesplot::theme_default(base_family = "serif", base_size = 16))
bayesplot::bayesplot_theme_update(axis.text = ggplot2::element_text(family = "serif", size = 14))

set.seed(808)

```

## Set parameters

```{r}

# plot colour scheme

mycolourlist = list(c(0, 102, 255), c(0, 204, 153), c(255, 0, 102), c(74, 111, 152), c(251, 164, 49), c(204, 153, 255), c(90, 192, 255), c(80, 245, 233), c(255, 90, 192), c(164, 201, 242), c(255, 254, 139), c(255, 243, 255))
mycolours = matrix()

for (ii in 1:length(mycolourlist)){
  mycolours[ii] = rgb(mycolourlist[[ii]][1]/255,
                      mycolourlist[[ii]][2]/255,
                      mycolourlist[[ii]][3]/255)
}

# toggle to save plots
saveplots = TRUE

if (saveplots){
  # set output plot directory
  choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  outFigPath <- utils::choose.dir(caption=r"(Select output folder to save plots: 03 Experiment\Experiment 2\Analysis\Plots)")
  
  if (!dir.exists(file.path(outFigPath, "svg"))){dir.create(file.path(outFigPath, "svg"))}
  if (!dir.exists(file.path(outFigPath, "pdf"))){dir.create(file.path(outFigPath, "pdf"))}
  if (!dir.exists(file.path(outFigPath, "png"))){dir.create(file.path(outFigPath, "png"))}
  
}

# toggle to save data
savedata = TRUE

if (savedata){
  # set output plot directory
  if (saveplots==FALSE){
    choose.files(caption="Just cancel this", filters=matrix(data=c(" ", " "), ncol=2))  # workaround for bug in RTerm choose.dir
  }
  outDataPath <- utils::choose.dir(caption=r"(Select output folder to save data: 03 Experiment\Experiment 2\Analysis\R)")
}

# set global number of draws and new subjects for Bayesian model predictions 
ndraws_pred <- 500
nnew_pred <- 150

# set flag whether to reloo models with Pareto k > 0.7
reloo_flag = TRUE


```

# Functions

## modelling helpers

```{r}

source(here("src/R/modelling_helpers.R"))

```

## plotting helpers

```{r}

source(here("src/R/plotting_helpers.R"))

```

## brms utilities

```{r}

source(here("src/R/brms_utilities.R"))

```

## avg_comparisons_slopes

Generated by Claude AI (Sonnet 5): https://claude.ai/chat/febecbdd-ea0b-491b-b736-9d2e9a52e55c

```{r}

source(here("src/R/avg_comparisons_slopes.R"))

```

## model performance metrics

```{r}

source(here("src/R/performance_metrics.R"))

```

# Import data

```{r}

subjDataPath <- utils::choose.files(caption=r"(Select refmap_listest2_testdata_BySubj.csv from 03 Experiment\Experiment 2\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest2_testdata_BySubj.csv", "refmap_listest2_testdata_BySubj.csv"), ncol=2))

subjData <- read.csv(subjDataPath, header=TRUE)

stimDataPath <- utils::choose.files(caption=r"(Select refmap_listest2_testdata_ByStim.csv from 03 Experiment\Experiment 2\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest2_testdata_ByStim.csv", "refmap_listest2_testdata_ByStim.csv"), ncol=2))

stimData <- read.csv(stimDataPath, header=TRUE, row.names=1)

```

## wrangle

```{r}

# rename variables for ease
subjData <- subjData |> dplyr::rename(TrialNumber = Trial)

subjData$AmbientEnvCore <- subjData$AmbientEnv |>
  dplyr::recode("Park (high)" = "Park",
                "Highway (low)" = "Highway") |>
  factor(levels=c("Park", "Residential", "Streetside square", "Highway"))

subjData$AmbientVariant <- factor(dplyr::case_when(
  subjData$AmbientEnv == "Park (high)" ~ "ParkHigh",
  subjData$AmbientEnv == "Highway (low)" ~ "HighwayLow",
  TRUE ~ "Standard"
  ), levels = c("Standard", "ParkHigh", "HighwayLow"))

stimData$AmbientEnvCore <- stimData$AmbientEnv |>
  dplyr::recode("Park (high)" = "Park",
                "Highway (low)" = "Highway") |>
  factor(levels=c("Park", "Residential", "Streetside square", "Highway"))

stimData$AmbientVariant <- factor(dplyr::case_when(
  stimData$AmbientEnv == "Park (high)" ~ "ParkHigh",
  stimData$AmbientEnv == "Highway (low)" ~ "HighwayLow",
  TRUE ~ "Standard"
  ), levels = c("Standard", "ParkHigh", "HighwayLow"))

# definition of ordinal variable levels
UASOpCats <- c("Baseline", "Overflight", "Delivery")
UASTypeCats <- c("Baseline", "H520", "T150")
UASStartCats <- c("Baseline", "Left", "Right")
UASProximityCats <- c("Baseline", "Far", "Near")

# encode factors
subjData$ID <- factor(subjData$ID)
subjData$UASOperation <- factor(subjData$UASOperation, levels=UASOpCats)
subjData$UASType <- factor(subjData$UASType, levels=UASTypeCats)
subjData$UASStart <- factor(subjData$UASStart, levels=UASStartCats)
subjData$UASProximity <- factor(subjData$UASProximity, levels=UASProximityCats)
subjData$AmbientEnv <- factor(subjData$AmbientEnv, levels=c("Park", "Residential", "Park (high)",
                                                            "Highway (low)", "Streetside square", "Highway"))
subjData$AAMAttitude <- factor(subjData$AAMAttitude)
subjData$HomeArea <- factor(subjData$HomeArea)
subjData$SoundscapeArea <- factor(subjData$SoundscapeArea)
subjData$Nationality <- factor(subjData$Nationality)
subjData$UKNational <- factor(subjData$UKNational)
subjData$Sex <- factor(subjData$Sex, levels=c("Female", "Male"))


# recode AAM_attitude to 2 groups
subjData <- subjData |> dplyr::mutate(AAM_attitude2 = dplyr::recode_values(AAMAttitude,
                                                                    "Supportive" ~ "Supportive",
                                                                    c("Ambivalent",
                                                                      "Concerned",
                                                                      "Neutral") ~ "Ambiv_Concern_Neutral"))
subjData$AAM_attitude2 <- factor(subjData$AAM_attitude2, levels=c("Supportive", "Ambiv_Concern_Neutral"))

# recode NationGeo to 3 groups
subjData <- subjData |> dplyr::mutate(NationGeo3 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia") ~ "Africa_SAsia",
                                                                 c("EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "NotAnswered",
                                                                   NA, "") ~ "Other"))
subjData$NationGeo3 <- factor(subjData$NationGeo3)

# recode NationGeo to 2 groups
subjData <- subjData |> dplyr::mutate(NationGeo2 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia",
                                                                   "Australasia",
                                                                   "EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "NotAnswered",
                                                                   NA, "") ~ "Other"))
subjData$NationGeo2 <- factor(subjData$NationGeo2)

# recode Area of residence to 2 groups
subjData <- subjData |> dplyr::mutate(Home_Area2 = dplyr::recode_values(HomeArea,
                                                         "Urban" ~ "Urban",
                                                         c("Suburban",
                                                           "Rural") ~ "Suburban_Rural"))
subjData$Home_Area2 <- factor(subjData$Home_Area2)


# recode Area soundscape to 2 groups
subjData <- subjData |> dplyr::mutate(Area_soundscape2 = dplyr::recode_values(SoundscapeArea,
                                                                       c("Calm",
                                                                         "Vibrant") ~ "Pleasant",
                                                                       c("Chaotic",
                                                                         "Monotonous") ~ "Unpleasant"))

subjData$Area_soundscape2 <- factor(subjData$Area_soundscape2, levels=c("Unpleasant", "Pleasant"))

subjData <- subjData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
subjData <- subjData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)

stimData <- stimData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
stimData <- stimData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)

# Log other variables
subjData$PartLoudSHMPowAvgLog <- log(subjData$PartLoudSHMPowAvg)
stimData$PartLoudSHMPowAvgLog <- log(stimData$PartLoudSHMPowAvg)

# reorder by participant ID and trial number
subjData <- subjData[with(subjData, order(ID, TrialNumber)), ]

# add a rescaled dAnnoyance variable
subjData <- subjData |>
  dplyr::mutate(AnnoyanceOrdBetaScl = betaTransform(Annoyance, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyanceOrdBetaScl = betaTransform(dAnnoyance, -10, 10,
                                                     direction='forward', squeeze='none'))

# add a rescaled dAnnoyance variable
stimData <- stimData |>
  dplyr::mutate(AnnoyMeanOrdBetaScl = betaTransform(AnnoyanceMean, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyMeanOrdBetaScl = betaTransform(dAnnoyanceMean, -10, 10,
                                                     direction='forward', squeeze='none'))

# omit ambient-only stimuli
subjDataNoAmb <- subjData |> dplyr::filter(UASStart != "Baseline")
stimDataNoAmb <- stimData |> dplyr::filter(UASStart != "Baseline")

```

## rescaling variables

```{r}

# rescale variables

centre_vars = c("UASLAeqMaxLR", "UASLAEMaxLR", "UASEPNLMaxLR", "UASLAF50ExMaxLR")

out <- standardise_list(list(subjData, subjDataNoAmb, stimData, stimDataNoAmb),
                        vars = centre_vars,
                        scale = FALSE)

subjData <- out[[1]]
subjDataNoAmb <- out[[2]]
stimData <- out[[3]]
stimDataNoAmb <- out[[4]]


out <- standardise_list(list(subjData, subjDataNoAmb),
                        vars = c("TrialNumber"),
                        scale = TRUE)

subjData <- out[[1]]
subjDataNoAmb <- out[[2]]

# rescale trial number variables
subjData <- rbind(subjData |>
                    dplyr::mutate(TrialNumberScl = datawizard::standardise(TrialNumber, scale=TRUE))) |>
  droplevels()

subjDataNoAmb <- rbind(subjDataNoAmb |>
                         dplyr::mutate(TrialNumberScl = datawizard::standardise(TrialNumber, scale=TRUE))) |>
  droplevels()


```

# dAnnoyance

## m0: minimal ordbeta model

### Formula

```{R}

m0formula <- dAnnoyanceOrdBetaScl ~ 1 + TrialNumberScl +
                    UASProximity +
                    UASLAEMaxLRScl + I(log10(UASEvents)) +
                   AmbientEnvCore + UASOperation +
                   AmbientVariant + UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + UASProximity + UASLAEMaxLRScl + AmbientEnvCore +
                      I(log10(UASEvents)) + AmbientVariant +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

m0Data <- subjDataNoAmb[, all.vars(m0formula), drop=FALSE]

```

### run model 0

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

priors0 <- c(
  # mean model
  set_prior("normal(0, 2)", class='b', dpar='mu'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl', dpar='mu'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl', dpar='mu'),

  # precision model
  brms::prior(normal(0, 1), class = 'Intercept', dpar = 'phi'),
  brms::prior(normal(0, 0.5), class = 'b', dpar = 'phi')
)

tic()
m0 <- brms::brm(brms::bf(m0formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0 <- brms::add_criterion(m0, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0))
m0$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0, re_formula=NA))
m0$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0PostCheck <- brms::pp_check(m0, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheck

m0PostCheckEnv <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckEnv

m0PostCheckEnv <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckEnv

m0PostCheckEvt <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckEvt

m0PostCheckType <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckType

m0PostCheckOp <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckOp

m0PostCheckProx <- brms::pp_check(m0, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0PostCheckProx

```


#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))



```

#### performance

```{R}

loo::pareto_k_table(loo::loo(m0))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0)

```

### run model 0_2

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

priors0_2 <- c(
  # mean model
  set_prior("normal(0, 2)", class='b', dpar='mu'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl', dpar='mu'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl', dpar='mu')
)

tic()
m0_2 <- brms::brm(m0formula,
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0_2, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0_2 <- brms::add_criterion(m0_2, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0_2$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0_2))
m0_2$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0_2, re_formula=NA))
m0_2$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0_2, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0_2PostCheck <- brms::pp_check(m0_2, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheck

m0_2PostCheckEnv <- brms::pp_check(m0_2, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheckEnv

m0_2PostCheckEnv <- brms::pp_check(m0_2, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheckEnv

m0_2PostCheckEvt <- brms::pp_check(m0_2, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheckEvt

m0_2PostCheckType <- brms::pp_check(m0_2, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheckType

m0_2PostCheckOp <- brms::pp_check(m0_2, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheckOp

m0_2PostCheckProx <- brms::pp_check(m0_2, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0_2PostCheckProx

```


#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0_2)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0_2), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))

```

#### performance

```{R}

loo::pareto_k_table(loo::loo(m0_2))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0_2)

m0_2_loo <- loo::loo_compare(m0, m0_2, criterion='loo')
m0_2_loo

```

## m0b: medial ordbeta model

### Formula

```{R}

m0bformula <- dAnnoyanceOrdBetaScl ~
  # within-subjects fixed
  1 + TrialNumberScl + UASProximity +
  AmbientEnvCore*UASType + AmbientEnvCore*UASOperation + AmbientVariant +
  UASLAEMaxLRScl*I(log10(UASEvents)) +
  # between subjects fixed
  NationGeo2 + AAM_attitude2 + Home_Area2 +
  Age + Sex + NoiseSensitivity + Area_soundscape2 +
  # random effects
  (1 + UASProximity + UASLAEMaxLRScl + AmbientEnvCore + I(log10(UASEvents)) +
     AmbientVariant + UASOperation + UASType | ID) + (1 | StimID)

```

### run model 0b

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0b <- brms::brm(brms::bf(m0bformula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0b <- brms::add_criterion(m0b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0b))
m0b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0b, re_formula=NA))
m0b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0b, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0bPostCheck <- brms::pp_check(m0b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheck

m0bPostCheckEnv <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckEnv

m0bPostCheckEnv <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckEnv

m0bPostCheckEvt <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckEvt

m0bPostCheckType <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckType

m0bPostCheckOp <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckOp

m0bPostCheckProx <- brms::pp_check(m0b, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0bPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0b)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0b), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0b))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b)

m0b_loo <- loo::loo_compare(m0, m0b, criterion='loo')
m0b_loo

```

## m0c: medial ordbeta model with decorrelated UASProximity

### Formula

```{R}

m0cformula <- dAnnoyanceOrdBetaScl ~
  # within-subjects fixed
  1 + TrialNumberScl + UASProximity +
  AmbientEnvCore*UASType + AmbientEnvCore*UASOperation + AmbientVariant +
  UASLAEMaxLRScl*I(log10(UASEvents)) +
  # between subjects fixed
  NationGeo2 + AAM_attitude2 + Home_Area2 +
  Age + Sex + NoiseSensitivity + Area_soundscape2 +
  # random effects
  (1 + UASLAEMaxLRScl + AmbientEnvCore + I(log10(UASEvents)) +
     AmbientVariant + UASOperation + UASType | ID) +
  (0 + UASProximity | ID) +
  (1 | StimID)

```

### run model 0c

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0c <- brms::brm(brms::bf(m0cformula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0c <- brms::add_criterion(m0c, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0c$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0c))
m0c$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0c, re_formula=NA))
m0c$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0c, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0cPostCheck <- brms::pp_check(m0c, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheck

m0cPostCheckEnv <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckEnv

m0cPostCheckEnv <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckEnv

m0cPostCheckEvt <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckEvt

m0cPostCheckType <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckType

m0cPostCheckOp <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckOp

m0cPostCheckProx <- brms::pp_check(m0c, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0cPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0c)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0c), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0c))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b, m0c)

m0c_loo <- loo::loo_compare(m0, m0b, m0c, criterion='loo')
m0c_loo

```

## m0d: medial ordbeta model with no UASProximity group-level

### Formula

```{R}

m0dformula <- dAnnoyanceOrdBetaScl ~
  # within-subjects fixed
  1 + TrialNumberScl + UASProximity +
  AmbientEnvCore*UASType + AmbientEnvCore*UASOperation + AmbientVariant +
  UASLAEMaxLRScl*I(log10(UASEvents)) +
  # between subjects fixed
  NationGeo2 + AAM_attitude2 + Home_Area2 +
  Age + Sex + NoiseSensitivity + Area_soundscape2 +
  # random effects
  (1 + UASLAEMaxLRScl + AmbientEnvCore + I(log10(UASEvents)) +
     AmbientVariant + UASOperation + UASType | ID) +
  (1 | StimID)

```

### run model 0d

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0d <- brms::brm(brms::bf(m0dformula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0d <- brms::add_criterion(m0d, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0d$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0d))
m0d$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0d, re_formula=NA))
m0d$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0d, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0dPostCheck <- brms::pp_check(m0d, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheck

m0dPostCheckEnv <- brms::pp_check(m0d, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheckEnv

m0dPostCheckEnv <- brms::pp_check(m0d, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheckEnv

m0dPostCheckEvt <- brms::pp_check(m0d, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheckEvt

m0dPostCheckType <- brms::pp_check(m0d, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheckType

m0dPostCheckOp <- brms::pp_check(m0d, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheckOp

m0dPostCheckProx <- brms::pp_check(m0d, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0dPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0d)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0d), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0d))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b, m0c, m0d)

m0d_loo <- loo::loo_compare(m0, m0b, m0c, m0d, criterion='loo')
m0d_loo

```

#### plot calibration

```{r}

# create base datagrid
m0dDataFit <- insight::get_data(m0d)

set.seed(999)
m0dpredMeans <- marginaleffects::avg_predictions(m0d, na.omit(m0dDataFit),
                                                  by=c("StimID"),
                                                re_formula = NULL,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none')) |>
  dplyr::arrange(StimID)

gc()

R2means <- 1 - sum((stimDataNoAmb$dAnnoyanceMean - m0dpredMeans$estimate)^2)/sum((stimDataNoAmb$dAnnoyanceMean - mean(stimDataNoAmb$dAnnoyanceMean))^2)

eRMSE <- epsilonRMSE(measured_data=stimDataNoAmb, predicted_data=m0dpredMeans,
                     measured_target='dAnnoyanceMean', measured_ci_low='dAnnoyanceMeanCI_Low',
                     measured_ci_high='dAnnoyanceMeanCI_High', fitted='estimate')

# using ggplot, plot the predicted fit against the responses in predictMeans
ggplot(data=cbind(m0dpredMeans,
                  response=stimDataNoAmb$dAnnoyanceMean,
                  responseCI_Low=stimDataNoAmb$dAnnoyanceMeanCI_Low,
                  responseCI_High=stimDataNoAmb$dAnnoyanceMeanCI_High)) +
  theme(panel.grid = element_blank(), aspect.ratio=1, text=element_text(family = "serif", size=16),
        axis.text=element_text(family = "serif", size=14)) +
  
  geom_abline(aes(intercept=0, slope=1), colour='grey', alpha=0.5) +
  
  geom_point(mapping=aes(x=response, y=estimate), size=1.75, shape=4, stroke=0.75, colour=mycolours[1], alpha=0.5) +

  geom_errorbar(mapping=aes(x=response, xmin=responseCI_Low, xmax=responseCI_High,
                            y=estimate), width=0, colour=mycolours[1], alpha=0.1) +
  
  geom_errorbar(mapping=aes(x=response, y=estimate, ymin=conf.low, ymax=conf.high), width=0, colour=mycolours[1], alpha=0.1) +

  scale_x_continuous(breaks=seq(-2, 10, by=1), limits=c(-1, 9)) +
  scale_y_continuous(breaks=seq(-2, 10, by=1), limits=c(-1, 9)) +
  
  labs(x="Mean change in annoyance (test)", y="Predicted mean change in annoyance") +
  
  ggplot2::annotate("text", x=0.1, y=6.75, label=deparse(bquote(italic(R)^2 == .(sprintf("%.3f", (round(R2means, 3)))))), family="serif", size=4, hjust = 0, parse=TRUE) +
  ggplot2::annotate("text", x=0.1, y=6, label=paste0("RMSE = ", sprintf("%.3f", round(eRMSE$rmse, 3))), family="serif", size=4, hjust = 0) +
  ggplot2::annotate("text", x = 0.1, y = 5.25, label = paste0("RMSE[epsilon] == ", sprintf("%.3f", round(eRMSE$epsilon_rmse, 3))), 
  family = "serif", size = 4, hjust = 0, parse = TRUE)


```

#### analyse population-averaged effects (not conditional effects) using marginaleffects

```{R}

within_vars_all  <- c("UASProximity", "AmbientEnvCore", "UASType", "UASOperation",
                       "AmbientVariant", "UASLAEMaxLRScl", "UASEvents")
between_vars_all <- c("NationGeo2", "AAM_attitude2", "Home_Area2", "Age", "Sex",
                       "NoiseSensitivity", "Area_soundscape2")

# grid_marg: LAE varies naturally with each real design cell - use for
# descriptive/visual plots and any question not sensitive to the LAE confound
grid_marg <- build_marginal_grid(
  m0d, within_vars = within_vars_all, between_vars = between_vars_all,
  id_var = "ID", stim_var = "StimID", simulate_id = TRUE, simulate_stim = TRUE,
  n_new = nnew_pred, fixed_at_mean = "TrialNumberScl"
)

# grid_fixed_lae: LAE held at its mean - use for any comparison across
# UASType/UASOperation/UASProximity/UASEvents where the LAE confound matters
grid_fixed_lae <- build_marginal_grid(
  m0d,
  within_vars = setdiff(within_vars_all, "UASLAEMaxLRScl"),
  between_vars = between_vars_all,
  id_var = "ID", stim_var = "StimID", simulate_id = TRUE, simulate_stim = TRUE,
  n_new = nnew_pred, fixed_at_mean = c("TrialNumberScl", "UASLAEMaxLRScl")
)

transform_dAnnoy <- \(x) betaTransform(x, -10, 10, direction = 'reverse', squeeze = 'none')


set.seed(999)
env_means <- marginaleffects::avg_predictions(
  m0d, newdata=subset(grid_marg, select=-c(StimID, ID)), by="AmbientEnvCore",
  re_formula=NA, allow_new_levels=TRUE, sample_new_levels="gaussian",
  ndraws=ndraws_pred, transform=transform_dAnnoy
)

env_contrasts <- avg_comparisons_manual(
  m0d, newdata=grid_marg, variable="AmbientEnvCore", comparison_type="pairwise",
  re_formula=NULL, allow_new_levels=TRUE, sample_new_levels="gaussian",
  ndraws=ndraws_pred, seed=999, rope=c(-0.2, 0.2), transform=transform_dAnnoy
)


# counterfactual LAE
lae_step <- seq(min(stimDataNoAmb$UASLAEMaxLRScl), max(stimDataNoAmb$UASLAEMaxLRScl), length.out = 13)
lae_step2 <- c(-10, -8, -6, 4, 6, 8)

shared_rows <- subset(m0DataFit, UASLAEMaxLRScl >= -3 & UASLAEMaxLRScl <= 5)
overlap_lae_scl <- seq(min(shared_rows$UASLAEMaxLRScl), max(shared_rows$UASLAEMaxLRScl), length.out = 5)

grid_env <- build_marginal_grid(m0d, within_vars=c("AmbientEnvCore"),
                                between_vars=NULL,
                                id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred,
                                 fixed_at_mean=c("TrialNumberScl"))
                                
                                
grid_marg <- build_marginal_grid(m0d,
                                 within_vars=c("UASProximity",
                                               "UASType", "UASOperation",
                                               "AmbientEnvCore", "AmbientVariant",
                                               "UASEvents"),
                                 between_vars=c("NationGeo2", "AAM_attitude2",
                                                "Home_Area2", "Age", "Sex",
                                                "NoiseSensitivity",
                                                "Area_soundscape2"),
                                 id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred, counterfactual_vars=list(UASLAEMaxLRScl=lae_step),
                                 fixed_at_mean=c("TrialNumberScl"))

grid_marg2 <- build_marginal_grid(m0d,
                                 within_vars=c("UASProximity",
                                               "UASType", "UASOperation",
                                               "AmbientEnvCore", "AmbientVariant",
                                               "UASEvents"),
                                 between_vars=c("NationGeo2", "AAM_attitude2",
                                                "Home_Area2", "Age", "Sex",
                                                "NoiseSensitivity",
                                                "Area_soundscape2"),
                                 id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred, counterfactual_vars=list(UASLAEMaxLRScl=lae_step2),
                                 fixed_at_mean=c("TrialNumberScl"))


set.seed(999)
m0dpredProx <- marginaleffects::avg_predictions(m0d, newdata=subset(grid_marg,
                                                             UASEvents==1, 
                                                             AmbientVariant=="Standard"),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASProximity",
                                                       "UASType",
                                                       "UASOperation",
                                                       "AmbientEnvCore"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredType <- marginaleffects::avg_predictions(m0d, newdata=subset(grid_marg,
                                                             UASEvents==1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

# force it to match brms's internal string representation
newdata_test <- m0dDataFit
newdata_test$ID <- as.character(newdata_test$ID)
newdata_test$StimID <- as.character(newdata_test$StimID)   # same risk applies here

m0dpredTypeTest <- marginaleffects::avg_predictions(m0d, newdata=subset(newdata_test, UASEvents == 1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredOp <- marginaleffects::avg_predictions(m0d, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "UASOperation",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                              re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredEnv <- marginaleffects::avg_predictions(m0d, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                                re_formula = NULL,
                                               allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredEvt <- marginaleffects::avg_predictions(m0d, newdata=subset(grid_marg,
                                                                 UASProximity=="Far" &
                                                                 UASOperation=="Overflight" &
                                                                   AmbientVariant=="Standard"),
                                            by=c("UASLAEMaxLRScl",
                                                 "AmbientEnvCore",
                                                 "UASEvents",
                                                 "UASOperation"),
                                            re_formula = NULL,
                                            allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                          transform=\(x) betaTransform(x, -10, 10,
                                                                       direction='reverse',
                                                                       squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredEvt2 <- marginaleffects::avg_predictions(m0d, newdata=subset(grid_marg2,
                                                                  UASProximity=="Far" &
                                                                  UASOperation=="Overflight" &
                                                                    AmbientVariant=="Standard"),
                                              by=c("UASLAEMaxLRScl",
                                                   "AmbientEnvCore",
                                                   "UASEvents",
                                                   "UASOperation"),
                                                re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                            transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredAtt <- marginaleffects::avg_predictions(m0d, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "AAM_attitude2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredAoR <- marginaleffects::avg_predictions(m0d, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Home_Area2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredScp <- marginaleffects::avg_predictions(m0d, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Area_soundscape2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredSex <- marginaleffects::avg_predictions(m0d, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Sex"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0dpredNat <- marginaleffects::avg_predictions(m0d, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "NationGeo2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

```

#### analyse contrasts

##### within subjects

```{r}

grid_marg <- build_marginal_grid(m0d,
                                 within_vars=c("UASLAEMaxLRScl",
                                               "UASProximity",
                                               "UASType", "UASOperation",
                                               "AmbientEnvCore", "AmbientVariant",
                                               "UASEvents"),
                                 between_vars=c("NationGeo2", "AAM_attitude2",
                                                "Home_Area2", "Age", "Sex",
                                                "NoiseSensitivity",
                                                "Area_soundscape2"),
                                 id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred, fixed_at_mean=c("TrialNumberScl"))

grid_fixed_lae <- build_marginal_grid(m0d,
                                 within_vars=c("UASProximity",
                                               "UASType", "UASOperation",
                                               "AmbientEnvCore", "AmbientVariant",
                                               "UASEvents"),
                                 between_vars=c("NationGeo2", "AAM_attitude2",
                                                "Home_Area2", "Age", "Sex",
                                                "NoiseSensitivity",
                                                "Area_soundscape2"),
                                 id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred,
                                 fixed_at_mean=c("TrialNumberScl", "UASLAEMaxLRScl"))

m0d_type_within_env <- avg_simple_effects_manual(
    m0d, newdata = grid_marg, variable = "UASType", within_variable = "AmbientEnvCore",
    levels = levels(grid_marg$UASType),
    re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
    ndraws = ndraws_pred, seed = 999,
    rope = c(-0.2, 0.2),
    p_adjust='holm',
    transform = \(x) betaTransform(x, -10, 10, direction = "reverse", squeeze = "none")
  ) |>
  dplyr::mutate(
    AmbientEnvCore = factor(AmbientEnvCore, levels = levels(grid_marg$AmbientEnvCore))
  )
gc()

m0d_type_by_env <- avg_comparisons_cross_manual(
    m0d, newdata = grid_marg, variable1 = "AmbientEnvCore", variable2 = "UASType",
    levels1 = levels(grid_marg$AmbientEnvCore),
    comparison_type1 = "reference",
    levels2 = levels(grid_marg$UASType),
    re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
    ndraws = ndraws_pred, seed = 999,
    rope = c(-0.2, 0.2),
    p_adjust='holm',
    transform = \(x) betaTransform(x, -10, 10, direction = "reverse", squeeze = "none")
  ) |>
  dplyr::mutate(
    AmbientEnvCore = factor(AmbientEnvCore, levels = levels(grid_marg$AmbientEnvCore))
  )
gc()

m0d_op_within_env <- avg_simple_effects_manual(
    m0d, newdata = grid_marg, variable = "UASOperation", within_variable = "AmbientEnvCore",
    levels = levels(grid_marg$UASOperation),
    re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
    ndraws = ndraws_pred, seed = 999,
    rope = c(-0.2, 0.2),
    p_adjust='holm',
    transform = \(x) betaTransform(x, -10, 10, direction = "reverse", squeeze = "none")
  ) |>
  dplyr::mutate(
    AmbientEnvCore = factor(AmbientEnvCore, levels = levels(grid_marg$AmbientEnvCore))
  )
gc()


m0d_op_by_env <- avg_comparisons_cross_manual(
    m0d, newdata = grid_marg, variable1 = "AmbientEnvCore", variable2 = "UASOperation",
    levels1 = levels(grid_marg$AmbientEnvCore),
    comparison_type1 = "reference",
    levels2 = levels(grid_marg$UASOperation),
    re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
    ndraws = ndraws_pred, seed = 999,
    rope = c(-0.2, 0.2),
    p_adjust='holm',
    transform = \(x) betaTransform(x, -10, 10, direction = "reverse", squeeze = "none")
  ) |>
  dplyr::mutate(
    AmbientEnvCore = factor(AmbientEnvCore, levels = levels(grid_marg$AmbientEnvCore))
  )
gc()

m0d_op_within_type <- avg_simple_effects_manual(
    m0d, newdata = grid_marg, variable = "UASOperation", within_variable = "UASType",
    levels = levels(grid_marg$UASOperation),
    re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
    ndraws = ndraws_pred, seed = 999,
    rope = c(-0.2, 0.2),
    p_adjust='holm',
    transform = \(x) betaTransform(x, -10, 10, direction = "reverse", squeeze = "none")
  ) |>
  dplyr::mutate(
    UASType = factor(UASType, levels = levels(grid_marg$UASType))
  )
gc()

m0d_prox_within_type <- avg_simple_effects_manual(m0d, newdata=grid_fixed_lae, variable="UASProximity",
                                                  within_variable="UASType", levels=c("Near", "Far"),
                                    re_formula=NULL,
                                   allow_new_levels=TRUE, sample_new_levels="gaussian",
                                   ndraws=ndraws_pred, seed=999, rope = c(-0.2, 0.2),
                                   p_adjust='holm',
                                   transform=\(x) betaTransform(x, -10, 10,
                                                                direction='reverse',
                                                                squeeze='none'))

```

##### between subjects

```{r}
# contrast analysis for between-subjects variables

contrast_vars <- c("Sex", "NationGeo2", "AAM_attitude2", "Home_Area2",
                    "Area_soundscape2")

m0d_between_contrasts <- purrr::map_dfr(contrast_vars, function(v) {
  res <- avg_comparisons_manual(
    m0d, newdata = grid_marg, variable = v, comparison_type = "pairwise",
    re_formula = NULL, allow_new_levels = TRUE, sample_new_levels = "gaussian",
    ndraws = ndraws_pred,
    transform = \(x) betaTransform(x, -10, 10, direction = 'reverse', squeeze = 'none')
  )
  res$variable <- v
  gc()
  return(res)
}) |>
  as.data.frame() |>
  mutate(
    variable = factor(variable, levels = rev(contrast_vars)),
    # Create the text label string
    y_label = paste(variable, contrast, sep = ": "),
    
    # Reorder the y-axis labels using the underlying numeric levels of 'variable'
    y_label = fct_reorder(y_label, as.numeric(variable))
  )
  

```

#### contrast plots

```{r}

p_simple <- ggplot(m0d_type_within_env, aes(x = AmbientEnvCore, y = estimate,
                                            colour = AmbientEnvCore)) +
  theme(panel.grid = element_blank(),
        text = element_text(family = "serif", size = 16),
        axis.text = element_text(family = "serif", size =12),
        legend.position = "none") +

  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  linewidth = 1, size = 0.8) +

  scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE,
                      begin = 0.2, end = 0.8) +

  scale_y_continuous(breaks = seq(-10, 10, by = 1)) +
  labs(x = NULL, y = expression("Difference in"~bar(Delta*A)~", T150 "~-~"H520"))

p_cross <- ggplot(m0d_type_by_env, aes(x = AmbientEnvCore, y = estimate, colour = AmbientEnvCore)) +
  theme(panel.grid = element_blank(),
        text = element_text(family = "serif", size = 16),
        axis.text = element_text(family = "serif", size = 12),
        legend.position = "none") +

  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, size = 0.8) +

  scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE, begin = 0.2, end = 0.8) +

  scale_y_continuous(breaks = seq(-4, 4, by = 1)) +
  labs(x = paste(unique(m0d_type_by_env$reference1), "(reference)"),
       y = expression(
    atop(
      "Change in T150 "~-~"H520 difference in "~bar(Delta*A)~",",
      "relative to ref"
    )))

p_simple / p_cross # + plot_annotation(tag_levels = "A")

# Forest plot: one row per contrast, point = estimate, whiskers = 95% CI,
# dashed reference line at zero
ggplot(m0d_between_contrasts, aes(x = estimate,
                            y = y_label,
                            colour=variable)) +
  theme(panel.grid = element_blank(),
        text = element_text(family = "serif", size = 16),
        axis.text = element_text(family = "serif", size = 14),
        legend.position = "none") +
  scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE, begin = 0.2, end = 0.8) +

  
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  labs(x = expression("Difference in"~bar(Delta*A)), y = NULL)

p_simple <- ggplot(m0d_op_within_env, aes(x = AmbientEnvCore, y = estimate,
                                            colour = AmbientEnvCore)) +
  theme(panel.grid = element_blank(),
        text = element_text(family = "serif", size = 16),
        axis.text = element_text(family = "serif", size =12),
        legend.position = "none") +

  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  linewidth = 1, size = 0.8) +

  scale_color_discrete(palette = mycolours) +

  scale_y_continuous(breaks = seq(-10, 10, by = 1)) +
  labs(x = NULL, y = expression("Difference in"~bar(Delta*A)~", overflight "~-~"delivery"))

p_simple

p_simple <- ggplot(m0d_op_within_type, aes(x = UASType, y = estimate,
                                            colour = UASType)) +
  theme(panel.grid = element_blank(),
        text = element_text(family = "serif", size = 16),
        axis.text = element_text(family = "serif", size =12),
        legend.position = "none") +

  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  linewidth = 1, size = 0.8) +

  scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE,
                      begin = 0.2, end = 0.8) +

  scale_y_continuous(breaks = seq(-10, 10, by = 1)) +
  labs(x = NULL, y = expression("Difference in"~bar(Delta*A)~", overflight "~-~"delivery"))

p_simple

p_prox_type <- ggplot(m0d_prox_within_type, aes(x = UASType, y = estimate, colour = UASType)) +
    theme(panel.grid = element_blank(),
          text = element_text(family = "serif", size = 16),
          axis.text = element_text(family = "serif", size = 12),
          legend.position = "none") +
    
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
    geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, size = 0.8) +
    
    scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE,
                        begin = 0.2, end = 0.8) +
  
    scale_y_continuous(breaks = seq(-10, 10, by = 0.5), limits = c(-0.5, 1)) +
    labs(x = NULL, y = expression("Difference in"~bar(Delta*A)))

p_prox_type

```

## m0e: medial ordbeta model with no UASProximity population-level

### Formula

```{R}

m0eformula <- dAnnoyanceOrdBetaScl ~
  # within-subjects fixed
  1 + TrialNumberScl +
  AmbientEnvCore*UASType + AmbientEnvCore*UASOperation + AmbientVariant +
  UASLAEMaxLRScl*I(log10(UASEvents)) +
  # between subjects fixed
  NationGeo2 + AAM_attitude2 + Home_Area2 +
  Age + Sex + NoiseSensitivity + Area_soundscape2 +
  # random effects
  (1 + UASLAEMaxLRScl + AmbientEnvCore + I(log10(UASEvents)) +
     AmbientVariant + UASOperation + UASType | ID) +
  (1 | StimID)

```

### run model 0e

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0e <- brms::brm(brms::bf(m0eformula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0e <- brms::add_criterion(m0e, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0e$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0e))
m0e$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0e, re_formula=NA))
m0e$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0e, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0ePostCheck <- brms::pp_check(m0e, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0ePostCheck

m0ePostCheckEnv <- brms::pp_check(m0e, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0ePostCheckEnv

m0ePostCheckEnv <- brms::pp_check(m0e, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0ePostCheckEnv

m0ePostCheckEvt <- brms::pp_check(m0e, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0ePostCheckEvt

m0ePostCheckType <- brms::pp_check(m0e, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0ePostCheckType

m0ePostCheckOp <- brms::pp_check(m0e, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0ePostCheckOp


```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0e)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m0e), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0e))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b, m0c, m0d, m0e)

m0e_loo <- loo::loo_compare(m0, m0b, m0c, m0d, m0e, criterion='loo')
m0e_loo

```

#### plot calibration

```{r}

# create base datagrid
m0eDataFit <- insight::get_data(m0e)

set.seed(999)
m0epredMeans <- marginaleffects::avg_predictions(m0e, na.omit(m0eDataFit),
                                                  by=c("StimID"),
                                                re_formula = NULL,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none')) |>
  dplyr::arrange(StimID)

gc()

R2means <- 1 - sum((stimDataNoAmb$dAnnoyanceMean - m0epredMeans$estimate)^2)/sum((stimDataNoAmb$dAnnoyanceMean - mean(stimDataNoAmb$dAnnoyanceMean))^2)

eRMSE <- epsilonRMSE(measured_data=stimDataNoAmb, predicted_data=m0epredMeans,
                     measured_target='dAnnoyanceMean', measured_ci_low='dAnnoyanceMeanCI_Low',
                     measured_ci_high='dAnnoyanceMeanCI_High', fitted='estimate')

# using ggplot, plot the predicted fit against the responses in predictMeans
ggplot(data=cbind(m0epredMeans,
                  response=stimDataNoAmb$dAnnoyanceMean,
                  responseCI_Low=stimDataNoAmb$dAnnoyanceMeanCI_Low,
                  responseCI_High=stimDataNoAmb$dAnnoyanceMeanCI_High)) +
  theme(panel.grid = element_blank(), aspect.ratio=1, text=element_text(family = "serif", size=16),
        axis.text=element_text(family = "serif", size=14)) +
  
  geom_abline(aes(intercept=0, slope=1), colour='grey', alpha=0.5) +
  
  geom_point(mapping=aes(x=response, y=estimate), size=1.75, shape=4, stroke=0.75, colour=mycolours[1], alpha=0.5) +

  geom_errorbar(mapping=aes(x=response, xmin=responseCI_Low, xmax=responseCI_High,
                            y=estimate), width=0, colour=mycolours[1], alpha=0.1) +
  
  geom_errorbar(mapping=aes(x=response, y=estimate, ymin=conf.low, ymax=conf.high), width=0, colour=mycolours[1], alpha=0.1) +

  scale_x_continuous(breaks=seq(-2, 10, by=1), limits=c(-1, 9)) +
  scale_y_continuous(breaks=seq(-2, 10, by=1), limits=c(-1, 9)) +
  
  labs(x="Mean change in annoyance (test)", y="Predicted mean change in annoyance") +
  
  ggplot2::annotate("text", x=0.1, y=6.75, label=deparse(bquote(italic(R)^2 == .(sprintf("%.3f", (round(R2means, 3)))))), family="serif", size=4, hjust = 0, parse=TRUE) +
  ggplot2::annotate("text", x=0.1, y=6, label=paste0("RMSE = ", sprintf("%.3f", round(eRMSE$rmse, 3))), family="serif", size=4, hjust = 0) +
  ggplot2::annotate("text", x = 0.1, y = 5.25, label = paste0("RMSE[epsilon] == ", sprintf("%.3f", round(eRMSE$epsilon_rmse, 3))), 
  family = "serif", size = 4, hjust = 0, parse = TRUE)


```

#### analyse population-averaged effects (not conditional effects) using marginaleffects

```{R}

# counterfactual LAE
lae_step <- seq(min(stimDataNoAmb$UASLAEMaxLRScl), max(stimDataNoAmb$UASLAEMaxLRScl), length.out = 13)
lae_step2 <- c(-10, -8, -6, 4, 6, 8)

shared_rows <- subset(m0eataFit, UASLAEMaxLRScl >= -3 & UASLAEMaxLRScl <= 5)
overlap_lae_scl <- seq(min(shared_rows$UASLAEMaxLRScl), max(shared_rows$UASLAEMaxLRScl), length.out = 5)


grid_marg <- build_marginal_grid(m0e,
                                 within_vars=c("UASProximity",
                                               "UASType", "UASOperation",
                                               "AmbientEnvCore", "AmbientVariant",
                                               "UASEvents"),
                                 between_vars=c("NationGeo2", "AAM_attitude2",
                                                "Home_Area2", "Age", "Sex",
                                                "NoiseSensitivity",
                                                "Area_soundscape2"),
                                 id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred, counterfactual_vars=list(UASLAEMaxLRScl=lae_step),
                                 fixed_at_mean=c("TrialNumberScl"))

grid_marg2 <- build_marginal_grid(m0e,
                                 within_vars=c("UASProximity",
                                               "UASType", "UASOperation",
                                               "AmbientEnvCore", "AmbientVariant",
                                               "UASEvents"),
                                 between_vars=c("NationGeo2", "AAM_attitude2",
                                                "Home_Area2", "Age", "Sex",
                                                "NoiseSensitivity",
                                                "Area_soundscape2"),
                                 id_var="ID", stim_var="StimID",
                                 simulate_id=T, simulate_stim=T,
                                 n_new=nnew_pred, counterfactual_vars=list(UASLAEMaxLRScl=lae_step2),
                                 fixed_at_mean=c("TrialNumberScl"))


set.seed(999)
m0epredProx <- marginaleffects::avg_predictions(m0e, newdata=subset(grid_marg,
                                                             UASEvents==1, 
                                                             AmbientVariant=="Standard"),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASProximity",
                                                       "UASType",
                                                       "UASOperation",
                                                       "AmbientEnvCore"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredType <- marginaleffects::avg_predictions(m0e, newdata=subset(grid_marg,
                                                             UASEvents==1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

# force it to match brms's internal string representation
newdata_test <- m0eDataFit
newdata_test$ID <- as.character(newdata_test$ID)
newdata_test$StimID <- as.character(newdata_test$StimID)   # same risk applies here

m0epredTypeTest <- marginaleffects::avg_predictions(m0e, newdata=subset(newdata_test, UASEvents == 1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredOp <- marginaleffects::avg_predictions(m0e, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "UASOperation",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                              re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredEnv <- marginaleffects::avg_predictions(m0e, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                                re_formula = NULL,
                                               allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredEvt <- marginaleffects::avg_predictions(m0e, newdata=subset(grid_marg,
                                                                 UASProximity=="Far" &
                                                                 UASOperation=="Overflight" &
                                                                   AmbientVariant=="Standard"),
                                            by=c("UASLAEMaxLRScl",
                                                 "AmbientEnvCore",
                                                 "UASEvents",
                                                 "UASOperation"),
                                            re_formula = NULL,
                                            allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                          transform=\(x) betaTransform(x, -10, 10,
                                                                       direction='reverse',
                                                                       squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredEvt2 <- marginaleffects::avg_predictions(m0e, newdata=subset(grid_marg2,
                                                                  UASProximity=="Far" &
                                                                  UASOperation=="Overflight" &
                                                                    AmbientVariant=="Standard"),
                                              by=c("UASLAEMaxLRScl",
                                                   "AmbientEnvCore",
                                                   "UASEvents",
                                                   "UASOperation"),
                                                re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                            transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredAtt <- marginaleffects::avg_predictions(m0e, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "AAM_attitude2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredAoR <- marginaleffects::avg_predictions(m0e, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Home_Area2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredScp <- marginaleffects::avg_predictions(m0e, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Area_soundscape2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredSex <- marginaleffects::avg_predictions(m0e, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Sex"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m0epredNat <- marginaleffects::avg_predictions(m0e, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "NationGeo2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

```

## m0f: medial ordbeta model with UASProximity interactions

### Formula

```{R}

m0f_formula <- update(m0dformula, . ~ . + UASProximity*UASType + UASProximity*UASOperation)

```

### run model 0f

```{R}

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m0f <- brms::brm(brms::bf(m0f_formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m0Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors0, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m0f <- brms::add_criterion(m0f, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m0f$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m0f))
m0f$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m0f, re_formula=NA))
m0f$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m0f, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m0fPostCheck <- brms::pp_check(m0f, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheck

m0fPostCheckEnv <- brms::pp_check(m0f, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheckEnv

m0fPostCheckEnv <- brms::pp_check(m0f, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheckEnv

m0fPostCheckEvt <- brms::pp_check(m0f, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheckEvt

m0fPostCheckType <- brms::pp_check(m0f, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheckType

m0fPostCheckOp <- brms::pp_check(m0f, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheckOp

m0fPostCheckProx <- brms::pp_check(m0f, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m0fPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m0f)

pplot <- bayesplot::mcmc_pairs(brms::as_draws_matrix(m0f), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))
pplot

```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m0f))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0, m0b, m0c, m0d, m0e, m0f)

m0f_loo <- loo::loo_compare(m0d, m0f, criterion='loo')
m0f_loo

```

```{r}

m0f_prox_within_type <- avg_simple_effects_manual(m0f, newdata=grid_fixed_lae, variable="UASProximity",
                                                  within_variable="UASType", levels=c("Near", "Far"),
                                    re_formula=NULL,
                                   allow_new_levels=TRUE, sample_new_levels="gaussian",
                                   ndraws=ndraws_pred, seed=999, rope = c(-0.2, 0.2),
                                   p_adjust='holm',
                                   transform=\(x) betaTransform(x, -10, 10,
                                                                direction='reverse',
                                                                squeeze='none'))


m0f_prox_within_op <- avg_simple_effects_manual(m0f, newdata=grid_fixed_lae, variable="UASProximity",
                                                  within_variable="UASOperation",
                                    re_formula=NULL,
                                   allow_new_levels=TRUE, sample_new_levels="gaussian",
                                   ndraws=ndraws_pred, seed=999, rope = c(-0.2, 0.2),
                                   p_adjust='holm',
                                   transform=\(x) betaTransform(x, -10, 10,
                                                                direction='reverse',
                                                                squeeze='none'))

p_prox_type <- ggplot(m0f_prox_within_type, aes(x = UASType, y = estimate, colour = UASType)) +
    theme(panel.grid = element_blank(),
          text = element_text(family = "serif", size = 16),
          axis.text = element_text(family = "serif", size = 12),
          legend.position = "none") +
    
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
    geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, size = 0.8) +
    
    scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE,
                        begin = 0.2, end = 0.8) +
  
    scale_y_continuous(breaks = seq(-10, 10, by = 0.5), limits = c(-0.5, 1)) +
    labs(x = NULL, y = expression("Difference in"~bar(Delta*A)))

p_prox_type

p_prox_op <- ggplot(m0f_prox_within_op, aes(x = UASOperation, y = estimate, colour = UASOperation)) +
    theme(panel.grid = element_blank(),
          text = element_text(family = "serif", size = 16),
          axis.text = element_text(family = "serif", size = 12),
          legend.position = "none") +
    
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
    geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1, size = 0.8) +
    
    scale_color_viridis(option = "plasma", direction = 1, discrete = TRUE,
                        begin = 0.2, end = 0.8) +
  
    scale_y_continuous(breaks = seq(-10, 10, by = 0.5), limits = c(-0.5, 1)) +
    labs(x = NULL, y = expression("Difference in"~bar(Delta*A)))

p_prox_op

```

## m1: maximal ordbeta model

### Formula

```{R}

m1formula <- dAnnoyanceOrdBetaScl ~ 1 + TrialNumberScl +
                    UASProximity +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnvCore*UASOperation +
                   UASLAEMaxLRScl*AmbientEnvCore*UASType +
                   AmbientVariant*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NoiseSensitivity + Area_soundscape2 +
                   (1 + UASProximity + UASLAEMaxLRScl + AmbientEnvCore +
                      I(log10(UASEvents)) + AmbientVariant +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

m1Data <- subjDataNoAmb[, all.vars(m1formula), drop=FALSE]

```

### run model 1

```{r}

chains <- 4

future::plan(future::multisession, workers = chains)

priors1 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(gamma(2, 0.1), class='phi')
)

tic()
m1Priors <- brms::brm(m1formula,
                 data=m1Data,
                 family=ordbeta(link='logit'),
                 future=TRUE, backend='cmdstanr', init=0,
                 prior=priors1, control=list(adapt_delta=0.95),
                 sample_prior='only', seed=808,
                 chains=chains, iter=2000, warmup=1000)
toc()

m1PriorCheck <- brms::pp_check(m1Priors, ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PriorCheck

tic()
m1 <- brms::brm(m1formula, data=m1Data,
                family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1, control=list(adapt_delta=0.95),
               threads = threading(threads = 3, static = TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1 <- brms::add_criterion(m1, criterion=c('loo', 'loo_R2'),
                          cores=n_cores,
                          reloo=reloo_flag,
                          overwrite=TRUE,
                          chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                          backend='cmdstanr',
                          future_args=list(future.seed=TRUE))
toc()

m1$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1))
m1$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1, re_formula=NA))
m1$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1PostCheck <- brms::pp_check(m1, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheck

m1PostCheckEnv <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckEnv

m1PostCheckEnv <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckEnv

m1PostCheckEvt <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckEvt

m1PostCheckType <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckType

m1PostCheckOp <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckOp

m1PostCheckProx <- brms::pp_check(m1, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1PostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m1)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m1), pars = c("b_UASLAEMaxLRScl",
                                                          "b_UASOperationDelivery",
                                                          "b_UASTypeT150", "b_UASProximityNear",
                                                          "b_AmbientEnvCoreResidential",
                                                          "b_AmbientEnvCoreStreetsidesquare",
                                                          "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))



```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m1))

# make a table of the bayes_R2 values and quantiles for each model
get_Br2_table(m0d, m1)

m1_loo <- loo::loo_compare(m0d, m1, criterion='loo')
m1_loo

```

### run model 1b

```{R}

priors1b <- c(
  # mean model
  set_prior("normal(0, 2)", class='b', dpar='mu'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl', dpar='mu'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents', dpar='mu'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl', dpar='mu'),
  # precision model
  brms::prior(normal(0, 1), class = 'Intercept', dpar = 'phi'),
  brms::prior(normal(0, 0.5), class = 'b', dpar = 'phi')
)

chains <- 4

future::plan(future::multisession, workers = chains)

tic()
m1b <- brms::brm(brms::bf(m1formula, phi ~ 1 + AmbientEnvCore + UASOperation +
                            UASType + I(log10(UASEvents)) + (1 | ID)),
                data=m1Data, family=ordbeta(link='logit'),
               future=TRUE, backend='cmdstanr', init=0,
               prior = priors1b, control=list(adapt_delta=0.95),
               threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
               seed=808, chains=chains, iter=2000, warmup=1000)
toc()

future::plan(future::multisession, workers = 6)

tic()
m1b <- brms::add_criterion(m1b, criterion=c('loo', 'loo_R2'),
                           cores=n_cores,
                           reloo=reloo_flag,
                           overwrite=TRUE,
                           chains=2, iter=1500, warmup=750,  # check workers*chains = n_cores
                           backend='cmdstanr',
                           future_args=list(future.seed=TRUE))
toc()

m1b$criteria$loo_R2_summary <- as.data.frame(brms::loo_R2(m1b))
m1b$criteria$bayes_R2_marginal <- as.data.frame(brms::bayes_R2(m1b, re_formula=NA))
m1b$criteria$bayes_R2_conditional <- as.data.frame(brms::bayes_R2(m1b, re_formula=NULL))

```

#### check posterior predictive distribution

```{r}

m1bPostCheck <- brms::pp_check(m1b, ndraws=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheck

m1bPostCheckEnv <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='AmbientEnvCore') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckEnv

m1bPostCheckEnv <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='AmbientVariant') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckEnv

m1bPostCheckEvt <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASEvents') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckEvt

m1bPostCheckType <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASType') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckType

m1bPostCheckOp <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASOperation') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckOp

m1bPostCheckProx <- brms::pp_check(m1b, type='dens_overlay_grouped', ndraws=100, group='UASProximity') +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
m1bPostCheckProx

```

#### diagnostics

```{R}

# collinearity check
performance::check_collinearity(m1b)

bayesplot::mcmc_pairs(brms::as_draws_matrix(m1b), pars = c("b_UASLAEMaxLRScl",
                                                           "b_UASOperationDelivery",
                                                           "b_UASTypeT150", "b_UASProximityNear",
                                                           "b_AmbientEnvCoreResidential",
                                                           "b_AmbientEnvCoreStreetsidesquare",
                                                           "b_AmbientEnvCoreHighway"),
                               off_diag_args=list(alpha=0.3, size=0.5))

```

#### compare performance

```{R}

loo::pareto_k_table(loo::loo(m1b))

get_Br2_table(m0d, m1, m1b)

m1b_loo <- loo::loo_compare(m0d, m1, m1b, criterion='loo')
m1b_loo

```

### analyse m1b results

#### visualise posterior draws for population level effects

```{R, fig.width=8, fig.height=6}

m1b_bCI_range <- bayestestR::hdi(m1b, ci = c(0.5, 0.89, 0.95))

# plot spi for within-subjects factors only
m1b_bCI_wsf <- m1b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASProximityNear", 
                                 "b_UASTypeT150", 
                                 "b_UASOperationDelivery",
                                 "b_AmbientEnvCoreResidential",
                                 "b_AmbientEnvCoreStreetsidesquare",
                                 "b_AmbientEnvCoreHighway",
                                 "b_AmbientVariantParkHigh",
                                 "b_AmbientVariantHighwayLow"))
p_m1b_bCI_wsf <- plot(m1b_bCI_wsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1b_bCI_wsf

filename <- "dAnnoyMnCatModbCI_brmsOb_wsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects factor interactions only
m1b_bCI_wsfi <- m1b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_AmbientEnvCoreResidential:UASOperationDelivery",
                                 "b_AmbientEnvCoreStreetsidesquare:UASOperationDelivery",
                                 "b_AmbientEnvCoreHighway:UASOperationDelivery",
                                 "b_AmbientEnvCoreResidential:UASTypeT150",
                                 "b_AmbientEnvCoreStreetsidesquare:UASTypeT150",
                                 "b_AmbientEnvCoreHighway:UASTypeT150",
                                 "b_UASTypeT150:AmbientVariantParkHigh",
                                 "b_UASTypeT150:AmbientVariantHighwayLow",
                                 "b_UASOperationDelivery:UASTypeT150"))
p_m1b_bCI_wsfi <- plot(m1b_bCI_wsfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1b_bCI_wsfi

filename <- "dAnnoyMnCatModbCI_brmsOb_wsfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariates only
m1b_bCI_wsc <- m1b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl", "b_Ilog10UASEvents", "b_TrialNumberScl"))
p_m1b_bCI_wsc <- plot(m1b_bCI_wsc, show_intercept=F) +
    theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1b_bCI_wsc

filename <- "dAnnoyMnCatModbCI_brmsOb_wsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=8, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=8, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for within-subjects covariate-factor interactions only
m1b_bCI_wscfi <- m1b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_UASLAEMaxLRScl:AmbientEnvCoreResidential",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreStreetsidesquare",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreHighway",
                                 "b_UASLAEMaxLRScl:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreResidential:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreStreetsidesquare:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreHighway:UASOperationDelivery",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreResidential:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreStreetsidesquare:UASTypeT150",
                                 "b_UASLAEMaxLRScl:AmbientEnvCoreHighway:UASTypeT150",
                                 "b_UASLAEMaxLRScl:Ilog10UASEvents"))
p_m1b_bCI_wscfi <- plot(m1b_bCI_wscfi, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Within-subjects covariate-factor interactions",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1b_bCI_wscfi

filename <- "dAnnoyMnCatModbCI_brmsOb_wscfi"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=14, height=7,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=14, height=7, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}


# plot spi for between-subjects factors only
m1b_bCI_bsf <- m1b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_NationGeo2UK", "b_AAM_attitude2Ambiv_Concern_Neutral",
                                 "b_Home_Area2Urban", "b_SexMale", 
                                 "b_Area_soundscape2Unpleasant"))
p_m1b_bCI_bsf <- plot(m1b_bCI_bsf, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects factors",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1b_bCI_bsf

filename <- "dAnnoyMnCatModbCI_brmsOb_bsf"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=9, height=5,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=9, height=5, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# plot spi for between-subjects covariates only
m1b_bCI_bsc <- m1b_bCI_range |>
  dplyr::filter(Parameter %in% c("b_Age", "b_NoiseSensitivity"))
p_m1b_bCI_bsc <- plot(m1b_bCI_bsc, show_intercept=F) +
  theme(panel.grid=element_blank(), text=element_text(family='serif', size=16)) +
  scale_fill_manual(values=mycolours) +
  labs(title="Between-subjects covariates",
       x="Coefficient posterior distribution",
       y=NULL)
p_m1b_bCI_bsc

filename <- "dAnnoyMnCatModbCI_brmsOb_bsc"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### analyse population-averaged effects (not conditional effects) using marginaleffects

```{R}
# create base datagrid
m1bDataFit <- insight::get_data(m1b)
m1bDataFit <- m1bDataFit |> dplyr::mutate(ID=as.character(ID),
                                          StimID=as.character(StimID))

# get unique combinations of the predictors
base_unique <- m1bDataFit |>
    dplyr::distinct(ID, UASProximity, UASType, UASEvents, AmbientEnvCore, AmbientVariant, UASOperation,
                    NationGeo2, AAM_attitude2, Home_Area2,
                    Age, Sex, NoiseSensitivity, Area_soundscape2,
                    .keep_all = TRUE) |>
    dplyr::group_by(ID, UASProximity, UASType, UASEvents, AmbientEnvCore, AmbientVariant, UASOperation) |>
    dplyr::ungroup()
# include mean trial number
base_unique$TrialNumberScl <- mean(m1bDataFit$TrialNumberScl)

# expand grid over LAE
lae_step <- seq(min(stimDataNoAmb$UASLAEMaxLRScl), max(stimDataNoAmb$UASLAEMaxLRScl), length.out = 13)
base_expanded <- marginaleffects::datagrid(
  newdata = base_unique,
  UASLAEMaxLRScl = lae_step,
  grid_type = "counterfactual"
)

lae_step2 <- c(-10, -8, -6, 4, 6, 8)
base_expanded2 <- marginaleffects::datagrid(
  newdata = base_unique,
  UASLAEMaxLRScl = lae_step2,
  grid_type = "counterfactual"
)

# set up marginal grids with new subject and stimulus IDs
grid_marg <- base_expanded[rep(seq_len(nrow(base_expanded)), each = nnew_pred), ]
new_idx <- rep(seq_len(nnew_pred), times = nrow(base_expanded))
grid_marg$ID     <- paste0("new_id_", new_idx)
grid_marg$StimID <- paste0("new_stim_", new_idx)

grid_marg2<- base_expanded2[rep(seq_len(nrow(base_expanded2)), each = nnew_pred), ]
new_idx2 <- rep(seq_len(nnew_pred), times = nrow(base_expanded2))
grid_marg2$ID     <- paste0("new_id_", new_idx2)
grid_marg2$StimID <- paste0("new_stim_", new_idx2)

set.seed(999)
m1bpredProx <- marginaleffects::avg_predictions(m1b, newdata=subset(grid_marg,
                                                             UASEvents==1, 
                                                             AmbientVariant=="Standard"),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASProximity",
                                                       "UASType",
                                                       "UASOperation",
                                                       "AmbientEnvCore"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredType <- marginaleffects::avg_predictions(m1b, newdata=subset(grid_marg,
                                                             UASEvents==1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                                ndraws=ndraws_pred,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

# force it to match brms's internal string representation
newdata_test <- m1bDataFit
newdata_test$ID <- as.character(newdata_test$ID)
newdata_test$StimID <- as.character(newdata_test$StimID)   # same risk applies here

m1bpredTypeTest <- marginaleffects::avg_predictions(m1b, newdata=subset(newdata_test, UASEvents == 1),
                                                  by=c("UASLAEMaxLRScl",
                                                       "UASType",
                                                       "AmbientEnvCore",
                                                       "UASEvents"),
                                                re_formula = NULL,
                                                transform=\(x) betaTransform(x, -10, 10,
                                                                             direction='reverse',
                                                                             squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredOp <- marginaleffects::avg_predictions(m1b, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "UASOperation",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                              re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredEnv <- marginaleffects::avg_predictions(m1b, newdata=subset(grid_marg,
                                                        UASEvents==1),
                                                by=c("UASLAEMaxLRScl",
                                                     "AmbientEnvCore",
                                                     "UASEvents"),
                                                re_formula = NULL,
                                               allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                              transform=\(x) betaTransform(x, -10, 10,
                                                                           direction='reverse',
                                                                           squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredEvt <- marginaleffects::avg_predictions(m1b, newdata=subset(grid_marg,
                                                                 UASProximity=="Far" &
                                                                 UASOperation=="Overflight" &
                                                                   AmbientVariant=="Standard"),
                                            by=c("UASLAEMaxLRScl",
                                                 "AmbientEnvCore",
                                                 "UASEvents",
                                                 "UASOperation"),
                                            re_formula = NULL,
                                            allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                          transform=\(x) betaTransform(x, -10, 10,
                                                                       direction='reverse',
                                                                       squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredEvt2 <- marginaleffects::avg_predictions(m1b, newdata=subset(grid_marg2,
                                                                  UASProximity=="Far" &
                                                                  UASOperation=="Overflight" &
                                                                    AmbientVariant=="Standard"),
                                              by=c("UASLAEMaxLRScl",
                                                   "AmbientEnvCore",
                                                   "UASEvents",
                                                   "UASOperation"),
                                                re_formula = NULL,
                                              allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                            transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredAtt <- marginaleffects::avg_predictions(m1b, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "AAM_attitude2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredAoR <- marginaleffects::avg_predictions(m1b, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Home_Area2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredScp <- marginaleffects::avg_predictions(m1b, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Area_soundscape2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredSex <- marginaleffects::avg_predictions(m1b, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "Sex"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

set.seed(999)
m1bpredNat <- marginaleffects::avg_predictions(m1b, newdata=grid_marg,
                                             by=c("UASLAEMaxLRScl", "NationGeo2"),
                                                re_formula = NULL,
                                                allow_new_levels = TRUE,
                                                sample_new_levels = "gaussian",
                                               ndraws=ndraws_pred,
                                             transform=\(x) betaTransform(x, -10, 10,
                                                                         direction='reverse',
                                                                         squeeze='none'))

gc()  # garbage collect

```

#### visualise plots of PA effects

```{R}

p1 <- ggplot(data=subset(m1bpredType, UASEvents==1)) +
               theme(panel.grid = element_blank(), aspect.ratio=1.35,
                     text = element_text(family = "serif", size=16),
                     axis.text=element_text(family = "serif", size=14)) +
               
               geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyanceMean,
                                                  colour=UASType, shape=UASType),
                          alpha=0.35, size=2) +
               
               geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASType),
                           alpha=0.15) +
               
               geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASType), linewidth=1) +
               
               scale_color_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
               scale_fill_viridis(option='plasma', direction=-1, discrete=TRUE, begin = 0.2, end = 0.8) +
               scale_shape_manual(values=c(10, 11, 12)) +
               
               guides(colour=guide_legend(title="UAS type", reverse=FALSE),
                      fill=guide_legend(title="UAS type", reverse=FALSE),
                      shape=guide_legend(title="UAS type", reverse=FALSE)) +
             
               rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                              stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
               
               scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-6, 8)) +
               
               labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance") +
               facet_wrap(vars(AmbientEnvCore))

p2 <- ggplot(data=subset(m1bpredOp, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                                                 colour=UASOperation, shape=UASOperation),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=UASOperation),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=UASOperation), linewidth=1) +
              
              scale_color_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='mako', discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(9, 6, 2)) +
              
              guides(colour=guide_legend(title="UAS operation", reverse=TRUE),
                     fill=guide_legend(title="UAS operation", reverse=TRUE),
                     shape=guide_legend(title="UAS operation", reverse=TRUE)) +
              
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance") +
              facet_grid(rows = vars(AmbientEnv))

p3 <- ggplot(data=subset(m1bpredEnv, UASEvents==1)) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14),
                    axis.title.x=element_blank(),
                    axis.text.x=element_blank(),
                    axis.ticks.x=element_blank()) +
              
              geom_point(data=subset(stimDataNoAmb, UASEvents==1), aes(x=UASLAEMaxLRScl, y=dAnnoyanceMean,
                                                 colour=AmbientEnvCore, shape=AmbientEnvCore),
                         alpha=0.35, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AmbientEnvCore),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AmbientEnvCore), linewidth=1) +
              
              scale_color_viridis(option='magma', direction=-1, discrete=TRUE, begin=0.2, end=0.8) +
              scale_fill_viridis(option='magma', direction=-1, discrete=TRUE, begin=0.2, end=0.8) +
              scale_shape_manual(values=c(1, 3, 5, 7)) +
              
              guides(colour=guide_legend(title="Amb. env.", reverse=FALSE),
                     fill=guide_legend(title="Amb. env.", reverse=FALSE),
                     shape=guide_legend(title="Amb. env.", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(y="Mean change in annoyance")

p4 <- ggplot(data=subset(m1bpredEvt, AmbientEnv=='Park' & UASOperation=='Overflight')) +
              theme(panel.grid = element_blank(), aspect.ratio=1.35,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' & UASOperation=='Overflight'),
                         aes(x=UASLAEMaxLRScl, y=dAnnoyMean,
                             colour=factor(UASEvents), shape=factor(UASEvents)),
                         alpha=0.55, size=2) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=factor(UASEvents)),
                          alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=factor(UASEvents)), linewidth=1) +
              
              scale_color_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_fill_viridis(option='viridis', direction=1, discrete=TRUE, begin = 0.2, end = 0.8) +
              scale_shape_manual(values=c(4, 5, 7, 8)) +
              
              guides(colour=guide_legend(title="UAS events", reverse=TRUE),
                     fill=guide_legend(title="UAS events", reverse=TRUE),
                     shape=guide_legend(title="UAS events", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(min(2, min(m1bpredEvt$conf.low)), 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

(p1 | p2) + (p3 / p4)

filename <- "PtsABdAnnoyMnCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

# add faint dashed grey major grid lines to p1, p2, p3, p4 and remove minor grid lines and point data
p1b <- p1 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                  panel.grid.minor = element_blank())
p1b <- gginnards::delete_layers(p1b, "GeomPoint")
p2b <- p2 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p2b <- gginnards::delete_layers(p2b, "GeomPoint")
p3b <- p3 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p3b <- gginnards::delete_layers(p3b, "GeomPoint")
p4b <- p4 + theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                 panel.grid.minor = element_blank())
p4b <- gginnards::delete_layers(p4b, "GeomPoint")

(p1b | p2b) + (p3b / p4b)

filename <- "PtsABdAnnoyMnCatModGrid_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p3c <- p3 + theme(axis.title.x=element_text(family = "serif", size=14),
                  axis.text.x=element_text(family = "serif", size=14),
                  axis.ticks.x=element_line(colour="black", linewidth=1)) + 
        labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)))

filename <- "PtsABdAnnoyMnCatModEnv_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=5, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=5, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p5 <- ggplot(data=subset(m1bpredEvt2, UASOperation=="Overflight" & AmbientEnv=="Park")) +
              theme(panel.grid = element_blank(), aspect.ratio=0.8,
                    text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_point(data=subset(stimDataNoAmb, AmbientEnv=='Park' &
                                       UASOperation=='Overflight' & SessionPart=='B'),
                         aes(x=UASEvents, y=dAnnoyMean,
                             colour=UASLAEMaxLR, shape=UASType),
                         alpha=0.35, size=2) +
  
              scale_color_viridis(option='inferno', direction=1, discrete=FALSE, begin = 0.2, end = 0.8,
                                  breaks=c(73, 79)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE)) +
  
              ggnewscale::new_scale_color() +
  
              geom_ribbon(aes(x=UASEvents, ymin=conf.low, ymax=conf.high, fill=factor(UASLAEMaxLRScl)),
                          alpha=0.05) +
  
              geom_line(aes(x=UASEvents, y=estimate, colour=factor(UASLAEMaxLRScl)), linewidth=1, alpha=0.5) +

              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.2, end = 0.8,
                                   labels=function(x) format(round(as.numeric(x) +
                                                                   mean(stimDataNoAmb$UASLAEMaxLR) -
                                                                   mean(stimDataNoAmb$UASLAEMaxLRScl),
                                                                   0),
                                                             nsmall = 0)) +
              scale_shape_manual(values=c(10, 11, 12)) +
              
              guides(colour=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     fill=guide_legend(title=expression(paste(UAS~italic(L)[AE]~","~dB)), reverse=TRUE),
                     shape=guide_legend(title="UAS type", reverse=FALSE)) +
            
              scale_x_continuous(breaks=c(1, 3, 5, 9), labels=c(1, 3, 5, 9)) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(2, 7)) +
              
              labs(x="Number of UAS Overflight events", y="Mean change in annoyance")

p5

filename <- "PtsABdAnnoyMnCatModEvt2_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4, path=file.path(outFigPath, "svg"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

p6 <- ggplot(data=m1bpredAtt) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=AAM_attitude2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=AAM_attitude2), linewidth=1) +
              
              scale_color_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='rocket', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="AAM attitude", reverse=TRUE),
                     fill=guide_legend(title="AAM attitude", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p7 <- ggplot(data=m1bpredAoR) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Home_Area2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Home_Area2), linewidth=1) +
              
              scale_color_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='mako', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Area of residence", reverse=FALSE),
                     fill=guide_legend(title="Area of residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p8 <- ggplot(data=m1bpredScp) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Area_soundscape2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Area_soundscape2), linewidth=1) +
              
              scale_color_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='turbo', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Soundscape at residence", reverse=FALSE),
                     fill=guide_legend(title="Soundscape at residence", reverse=FALSE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p9 <- ggplot(data=m1bpredSex) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=Sex), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=Sex), linewidth=1) +
              
              scale_color_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='inferno', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="Sex", reverse=TRUE),
                     fill=guide_legend(title="Sex", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")

p10 <- ggplot(data=m1bpredNat) +
              theme(panel.grid.major = element_line(colour = alpha("grey90", alpha=0.5), linetype='dashed'),
                    panel.grid.minor = element_blank(),
                    aspect.ratio=1.35, text = element_text(family = "serif", size=16),
                    axis.text=element_text(family = "serif", size=14)) +
              
              geom_ribbon(aes(x=UASLAEMaxLRScl, ymin=conf.low, ymax=conf.high, fill=NationGeo2), alpha=0.15) +
              
              geom_line(aes(x=UASLAEMaxLRScl, y=estimate, colour=NationGeo2), linewidth=1) +
              
              scale_color_viridis(option='cividis', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              scale_fill_viridis(option='cividis', direction=1, discrete=TRUE, begin = 0.1, end = 0.8) +
              
              guides(colour=guide_legend(title="National region", reverse=TRUE),
                     fill=guide_legend(title="National region", reverse=TRUE)) +
            
              rescaleTicks(stimDataNoAmb$UASLAEMaxLR,
                             stimDataNoAmb$UASLAEMaxLRScl, sep=5) +
              scale_y_continuous(breaks=seq(-10, 10, by=1), limits=c(-2, 8)) +
              
              labs(x=expression(paste(UAS~italic(L)[AE],",",~dB)), y="Mean change in annoyance")


(p6 + p7 + p8) / (p9 + p10)

filename <- "PtsABdAnnoyMnAttAoRScpSexNatCatMod_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=15, height=8,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=15, height=8, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```

#### visualise posterior distributions of group level effects

```{r}

m1b_sd_draws <- as.data.frame(m1b) %>%
    dplyr::select(starts_with("sd_")) %>%
    tidyr::pivot_longer(cols = everything(), names_to = "Parameter", values_to = "Value") %>%
    dplyr::mutate(Parameter = gsub("sd_", "", Parameter)) # Clean up label names

# 2. Plot using ridges with a shared x-axis and normalized curve heights
ggplot(m1b_sd_draws, aes(x = Value, y = Parameter, fill = Parameter)) +
     theme(legend.position = "none",
            panel.grid.major.y = element_blank(),
            text = element_text(family = "serif", size=16)) +
    # stat_density_ridges normalizes the peak height of each curve individually
    ggridges::stat_density_ridges(aes(height = after_stat(density)), 
                        geom = "density_ridges", 
                        alpha = 1, 
                        scale = 1.5,) + # Controls how much curves can overlap vertically
    # Adds the 50%, 89% and 95% credible intervals right beneath each curve
    tidybayes::stat_pointinterval(aes(y = as.numeric(as.factor(Parameter)) - 0.1), 
                       .width = c(0.5, 0.89, 0.95)) +
    scale_fill_manual(values = mycolours) +
    labs(x = "Estimated variation (sd scale)",
         y = "Group parameter")

filename <- "PtsABdAnnoyMnCatModSD_brmsOb"

if (saveplots){
  ggsave(filename=paste(filename, ".svg", sep=""), width=6, height=4,
         path=file.path(outFigPath, "svg"), system_fonts = list('serif'="Times New Roman"))
  unlink(paste(filename, ".svg", sep=""))

  ggsave(filename=paste(filename, ".pdf", sep=""), width=6, height=4, path=file.path(outFigPath, "pdf"))
  unlink(paste(filename, ".pdf", sep=""))
}

```








































