---
title: "REFMAP Listening test 1 Parts A & B analysis: Bayesian mixed models for inferential explanation"
output: html_document
date: "2026-05-07"
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load packages
library(easystats)
library(conflicted)
library(brms)
library(bayestestR)
library(tidybayes)
library(bayesplot)
library(tidyverse)
library(DHARMa)
library(tictoc)
library(future)
library(mice)
library(marginaleffects)
library(priorsense)
library(posterior)
library(loo)
library(shinystan)
library(shinybrms)
library(ggdist)

# set package parameters
theme_set(theme_bw())

n_cores <- max(1, parallel::detectCores() - 4)
future::plan(future::multisession, workers = n_cores)

options(marginaleffects_parallel_inferences = TRUE)
options(marginaleffects_parallel_packages = c("marginaleffects", "brms"))

set.seed(808)

```

# Functions

## Prior predictive distribution ppd_ridgeplot
Adapted from: https://bruno.nicenboim.me/posts/posts/2026-01-09-ordinal-models/index.html

```{r}

ppd_ridgeplot <- function(fit, title = "Prior Predictive Distribution", 
                          subtitle = NULL, ndraws = 500) {
  
  yrep <- brms::posterior_predict(fit, ndraws = ndraws)

  # extract observed response categories from model
  response_name <- all.vars(fit$formula$formula)[1]
  
  observed_y <- fit$data[[response_name]]

  # preserve ordinal ordering
  response_levels <- sort(unique(observed_y))

  proportions_per_draw <- lapply(seq_len(nrow(yrep)), function(i) {
    props <- table(factor(yrep[i, ], levels = response_levels)) / ncol(yrep)
    data.frame(
      draw = i,
      response = factor(response_levels,
                        levels = response_levels,
                        ordered = TRUE),
      proportion = as.numeric(props)
    )
  })
  
  ppd_data <- do.call(rbind, proportions_per_draw)
  
  # reference line for equal occupancy
  equal_prob <- 1 / length(response_levels)
  
  ggplot(ppd_data, aes(x = proportion, y = response)) +
    ggridges::geom_density_ridges(fill = "steelblue", alpha = 0.7, scale = 0.9, stat = "binline") +
    scale_x_continuous(breaks = seq(0, 1, by = 0.2), limits = c(0, 1)) +
    geom_vline(xintercept = equal_prob, linetype = "dashed") +
    labs(title = title,
         subtitle = subtitle,
         x = "Predicted category proportion",
         y = "Response category") +
    theme_minimal(base_size = 12) +
    coord_flip()

}

```

## Beta distribution transform from arbitrary scale to (0, 1) or back again

```{r}

betaTransform <- function(x, scaleMin, scaleMax,
                          direction=c('forward', 'reverse')[1],
                          squeeze=c('none', 'basic', 'smithson')[1],
                          basic_val=1e-6){
  "Squeeze algorithm is from:
  Smithson, M & Verkuilen, J, 2006. A better lemon squeezer? Maximum-likelihood
  regression with beta-distributed dependent variables. Psychological Methods,
  11(1), 54-71."
  
  if (direction == 'forward') {
    # transform from original scale to (0,1)
    x_scale <- (x - scaleMin) / (scaleMax - scaleMin)
    
    if (squeeze == 'smithson') {
      
      N = length(x_scale)
      x_out <- (x_scale*(N - 1) + 0.5) / N
      
    } else if (squeeze == 'basic') {
      
      x_out <- x_scale*(1 - 2*basic_val) + basic_val
      
    } else {
      
      x_out <- x_scale
      
    }

  } else if (direction == 'reverse') {
    # transform from (0, 1) back to original scale
    x_scale <- x * (scaleMax - scaleMin) + scaleMin
    
    if (squeeze == 'smithson') {
      
      N = length(x_scale)
      x_out <- (x_scale*N - 0.5)/(N - 1)
      
    } else if (squeeze == 'basic') {
      
      x_out <- (x_scale - basic_val)/(1 - 2*basic_val)
      
    } else {
      
      x_out <- x_scale
      
    }

  } else {
    
    stop("Invalid direction argument: must be 'forward' or 'reverse'")
    
  }
  
  return(x_out)
  
}


```

# Import data and wrangle

## Parts A & B combined

```{r}

subjDataPath <- utils::choose.files(caption=r"(Select refmap_listest1_testdata_BySubj.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest1_testdata_BySubj.csv", "refmap_listest1_testdata_BySubj.csv"), ncol=2))

subjData <- read.csv(subjDataPath, header=TRUE)

stimDataPath <- utils::choose.files(caption=r"(Select refmap_listest1_testdata_ByStim.csv from 03 Experiment\Experiment 1\Analysis\PostProcess)",
                                     filters=matrix(data=c("refmap_listest1_testdata_ByStim.csv", "refmap_listest1_testdata_ByStim.csv"), ncol=2))

stimData <- read.csv(stimDataPath, header=TRUE, row.names=1)

```

```{r}
# definition of ordinal variable levels
UASLAeqCatsA <- c("Baseline", "42", "48", "54", "60")
SNRCatsA <- c("Baseline", "-16", "-10", "-4", "2", "8")
UASOpCatsA <- c("Baseline", "Overflight", "Landing", "Takeoff")
UASTypeCatsA <- c("Baseline", "H520", "M300", "T150")

# encode factors
subjData$ID <- factor(subjData$ID)
subjData$UASLAeq <- factor(subjData$UASLAeq, levels=UASLAeqCatsA, order=TRUE)
subjData$SNRlevel <- factor(subjData$SNRlevel, levels=SNRCatsA, order=TRUE)
subjData$UASOperation <- factor(subjData$UASOperation, levels=UASOpCatsA)
subjData$UASType <- factor(subjData$UASType, levels=UASTypeCatsA)
subjData$AmbientEnv <- factor(subjData$AmbientEnv, levels=c("Park", "Street"))
subjData$AAM_attitude <- factor(subjData$AAM_attitude)
subjData$Home_Area <- factor(subjData$Home_Area)
subjData$Area_soundscape <- factor(subjData$Area_soundscape)
subjData$NationGeo <- factor(subjData$NationGeo)

# For Age column in subjData, replace "No answer" with NA, and then convert to numeric using dplyr and pipe
subjData <- subjData |> dplyr::mutate(Age = case_when(Age == "No answer" ~ NA_character_, TRUE ~ Age)) |>
  dplyr::mutate(Age = as.numeric(Age))

# recode AAM_attitude to 3 groups
subjData <- subjData |> dplyr::mutate(AAM_attitude3 = dplyr::recode_values(AAM_attitude,
                                                                    "Supportive" ~ "Supportive",
                                                                    c("Ambivalent",
                                                                      "Concerned") ~ "Ambiv_Concern",
                                                                      "Neutral" ~ "Neutral"))
subjData$AAM_attitude3 <- factor(subjData$AAM_attitude3, levels=c("Supportive", "Ambiv_Concern", "Neutral"))

# recode AAM_attitude to 2 groups
subjData <- subjData |> dplyr::mutate(AAM_attitude2 = dplyr::recode_values(AAM_attitude,
                                                                    "Supportive" ~ "Supportive",
                                                                    c("Ambivalent",
                                                                      "Concerned",
                                                                      "Neutral") ~ "Ambiv_Concern_Neutral"))
subjData$AAM_attitude2 <- factor(subjData$AAM_attitude2, levels=c("Supportive", "Ambiv_Concern_Neutral"))

# recode AAM_attitude to 2 other groups
subjData <- subjData |> dplyr::mutate(AAM_attitude2_2 = dplyr::recode_values(AAM_attitude,
                                                                    c("Supportive",
                                                                      "Ambivalent") ~ "Support_Ambiv",
                                                                    c("Concerned",
                                                                      "Neutral") ~ "Concern_Neutral"))

subjData$AAM_attitude2_2 <- factor(subjData$AAM_attitude2_2, levels=c("Support_Ambiv", "Concern_Neutral"))

# recode NationGeo to 4 groups
subjData <- subjData |> dplyr::mutate(NationGeo4 = dplyr::recode_values(NationGeo,
                                                               "UK" ~ "UK",
                                                               c("Africa",
                                                                 "SouthAsia") ~ "Africa_SAsia",
                                                               c("Australasia",
                                                                 "EastAsia",
                                                                 "Europe",
                                                                 "MidEast",
                                                                 "SouthAmerica") ~ "Other",
                                                               "" ~ "Unspecified"))
subjData$NationGeo4 <- factor(subjData$NationGeo4)

# recode NationGeo to 3 groups
subjData <- subjData |> dplyr::mutate(NationGeo3 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia") ~ "Africa_SAsia",
                                                                 c("Australasia",
                                                                   "EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "") ~ "Other"))
subjData$NationGeo3 <- factor(subjData$NationGeo3)

# recode NationGeo to 2 groups
subjData <- subjData |> dplyr::mutate(NationGeo2 = dplyr::recode_values(NationGeo,
                                                                 "UK" ~ "UK",
                                                                 c("Africa",
                                                                   "SouthAsia",
                                                                   "Australasia",
                                                                   "EastAsia",
                                                                   "Europe",
                                                                   "MidEast",
                                                                   "SouthAmerica",
                                                                   "") ~ "Other"))
subjData$NationGeo2 <- factor(subjData$NationGeo2)


subjData$NationGeo3 <- factor(subjData$NationGeo3)

# recode Area of residence to 2 groups
subjData <- subjData |> dplyr::mutate(Home_Area2 = dplyr::recode_values(Home_Area,
                                                         "Urban" ~ "Urban",
                                                         c("Suburban",
                                                           "Rural") ~ "Suburban_Rural"))
subjData$Home_Area2 <- factor(subjData$Home_Area2)


# recode Area soundscape to 2 groups
subjData <- subjData |> dplyr::mutate(Area_soundscape2 = dplyr::recode_values(Area_soundscape,
                                                                       c("Calm",
                                                                         "Monotonous") ~ "Uneventful",
                                                                       c("Chaotic",
                                                                         "Vibrant") ~ "Eventful"))

subjData$Area_soundscape2 <- factor(subjData$Area_soundscape2)

# rescale trial number variables separately for each session part
subjData <- rbind(subjData[subjData$SessionPart == "A", ] |> dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)),
                    subjData[subjData$SessionPart == "B", ] |> dplyr::mutate(PartTrialNumberScl = datawizard::standardise(PartTrialNumber, scale=TRUE)))
subjData <- subjData |> dplyr::mutate(TrialNumberScl = datawizard::standardise(TrialNumber, scale=TRUE))

# relocate new columns
subjData <- subjData |> dplyr::relocate(TrialNumberScl, PartTrialNumberScl, .after=PartTrialNumber)

# rescale variables
subjData <- subjData |> dplyr::mutate(UASLAeqMaxLRScl = datawizard::standardise(UASLAeqMaxLR, scale=FALSE))
subjData <- subjData |> dplyr::mutate(UASLAEMaxLRScl = datawizard::standardise(UASLAEMaxLR, scale=FALSE))
subjData <- subjData |> dplyr::mutate(UASEPNLMaxLRScl = datawizard::standardise(UASEPNLMaxLR, scale=FALSE))
subjData <- subjData |> dplyr::mutate(LAELAF50diffScl = datawizard::standardise(LAELAF50diff, scale=FALSE))
subjData <- subjData |> dplyr::mutate(LAELAeqdiffScl = datawizard::standardise(LAELAeqdiff, scale=FALSE))
subjData <- subjData |> dplyr::mutate(EPNLLAeqdiffScl = datawizard::standardise(EPNLLAeqdiff, scale=FALSE))
subjData <- subjData |> dplyr::mutate(UASDisc0p5LAEMaxLRScl = datawizard::standardise(UASDisc0p5LAEMaxLR, scale=FALSE))
subjData <- subjData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
subjData <- subjData |> dplyr::mutate(UASLoudECMAPowAvgBinScl = datawizard::standardise(UASLoudECMAPowAvgBin, scale=FALSE))
subjData <- subjData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
subjData <- subjData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)
subjData <- subjData |> dplyr::mutate(AmbLAeqMaxLRScl = datawizard::standardise(AmbLAeqMaxLR, scale=FALSE))
subjData <- subjData |> dplyr::mutate(AmbLAF50ExMaxLRScl = datawizard::standardise(AmbLAF50ExMaxLR, scale=FALSE))

stimData <- stimData |> dplyr::mutate(UASLAeqMaxLRScl = datawizard::standardise(UASLAeqMaxLR, scale=FALSE))
stimData <- stimData |> dplyr::mutate(UASLAEMaxLRScl = datawizard::standardise(UASLAEMaxLR, scale=FALSE))
stimData <- stimData |> dplyr::mutate(UASEPNLMaxLRScl = datawizard::standardise(UASEPNLMaxLR, scale=FALSE))
stimData <- stimData |> dplyr::mutate(LAELAF50diffScl = datawizard::standardise(LAELAF50diff, scale=FALSE))
stimData <- stimData |> dplyr::mutate(LAELAeqdiffScl = datawizard::standardise(LAELAeqdiff, scale=FALSE))
stimData <- stimData |> dplyr::mutate(EPNLLAeqdiffScl = datawizard::standardise(EPNLLAeqdiff, scale=FALSE))
stimData <- stimData |> dplyr::mutate(UASDisc0p5LAEMaxLRScl = datawizard::standardise(UASDisc0p5LAEMaxLR, scale=FALSE))
stimData <- stimData |> dplyr::mutate(UASDisc0p5PAEMaxLR = 2e-5*10^(UASDisc0p5LAEMaxLR/20))
stimData <- stimData |> dplyr::mutate(UASLoudECMAPowAvgBinScl = datawizard::standardise(UASLoudECMAPowAvgBin, scale=FALSE))
stimData <- stimData |> dplyr::mutate(IntermitRatioC2MaxLRScl = IntermitRatioC2MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC3MaxLRScl = IntermitRatioC3MaxLR/100)
stimData <- stimData |> dplyr::mutate(IntermitRatioC5MaxLRScl = IntermitRatioC5MaxLR/100)
stimData <- stimData |> dplyr::mutate(AmbLAeqMaxLRScl = datawizard::standardise(AmbLAeqMaxLR, scale=FALSE))
stimData <- stimData |> dplyr::mutate(AmbLAF50ExMaxLRScl = datawizard::standardise(AmbLAF50ExMaxLR, scale=FALSE))


# convert detectability dB to log variables
subjData <- subjData |> dplyr::mutate(Detect0p1IntMaxLRLog = Detect0p1dBIntMaxLR/10)
subjData <- subjData |> dplyr::mutate(Detect0p5IntMaxLRLog = Detect0p5dBIntMaxLR/10)
subjData <- subjData |> dplyr::mutate(Detect0p1MaxMaxLRLog = Detect0p1dBMaxMaxLR/10)
subjData <- subjData |> dplyr::mutate(Detect0p5MaxMaxLRLog = Detect0p5dBMaxMaxLR/10)
subjData <- subjData |> dplyr::mutate(Detect0p1IntMaxLRLogScl = datawizard::standardise(Detect0p1IntMaxLRLog, scale=FALSE))
subjData <- subjData |> dplyr::mutate(Detect0p5IntMaxLRLogScl = datawizard::standardise(Detect0p5IntMaxLRLog, scale=FALSE))
subjData <- subjData |> dplyr::mutate(Detect0p1MaxMaxLRLogScl = datawizard::standardise(Detect0p1MaxMaxLRLog, scale=FALSE))
subjData <- subjData |> dplyr::mutate(Detect0p5MaxMaxLRLogScl = datawizard::standardise(Detect0p5MaxMaxLRLog, scale=FALSE))


stimData <- stimData |> dplyr::mutate(Detect0p1IntMaxLRLog = Detect0p1dBIntMaxLR/10)
stimData <- stimData |> dplyr::mutate(Detect0p5IntMaxLRLog = Detect0p5dBIntMaxLR/10)
stimData <- stimData |> dplyr::mutate(Detect0p1MaxMaxLRLog = Detect0p1dBMaxMaxLR/10)
stimData <- stimData |> dplyr::mutate(Detect0p5MaxMaxLRLog = Detect0p5dBMaxMaxLR/10)
stimData <- stimData |> dplyr::mutate(Detect0p1IntMaxLRLogScl = datawizard::standardise(Detect0p1IntMaxLRLog, scale=FALSE))
stimData <- stimData |> dplyr::mutate(Detect0p5IntMaxLRLogScl = datawizard::standardise(Detect0p5IntMaxLRLog, scale=FALSE))
stimData <- stimData |> dplyr::mutate(Detect0p1MaxMaxLRLogScl = datawizard::standardise(Detect0p1MaxMaxLRLog, scale=FALSE))
stimData <- stimData |> dplyr::mutate(Detect0p5MaxMaxLRLogScl = datawizard::standardise(Detect0p5MaxMaxLRLog, scale=FALSE))

# Log other variables
subjData$PartLoudMGLT05ExLog <- log(subjData$PartLoudMGLT05Ex)
subjData$PartLoudMGST05ExLog <- log(subjData$PartLoudMGST05Ex)
subjData$PartLoudMGLTPowAvgLog <- log(subjData$PartLoudMGLTPowAvg)
subjData$PartLoudMGSTPowAvgLog <- log(subjData$PartLoudMGSTPowAvg)

stimData$PartLoudMGLT05ExLog <- log(stimData$PartLoudMGLT05Ex)
stimData$PartLoudMGST05ExLog <- log(stimData$PartLoudMGST05Ex)
stimData$PartLoudMGLTPowAvgLog <- log(stimData$PartLoudMGLTPowAvg)
stimData$PartLoudMGSTPowAvgLog <- log(stimData$PartLoudMGSTPowAvg)

# reorder by participant ID and trial number
subjData <- subjData[with(subjData, order(ID, TrialNumber)), ]

# re-encode Annoyance variables as ordinal
subjData <- subjData |> dplyr::mutate(AnnoyanceOrd=factor(Annoyance,
                                                          levels=seq(0, 10, by=1),
                                                          ordered=TRUE),
                                      dAnnoyanceOrd=factor(dAnnoyance,
                                                           levels=seq(-10, 10, by=1),
                                                           ordered=TRUE))


# add a rescaled dAnnoyance variable
subjData <- subjData |>
  dplyr::mutate(AnnoyanceOrdBetaScl = betaTransform(Annoyance, 0, 10,
                                                    direction='forward', squeeze='none'),
                dAnnoyanceOrdBetaScl = betaTransform(dAnnoyance, -10, 10,
                                                     direction='forward', squeeze='none'))

# omit ambient-only stimuli
subjDataNoAmb <- subjData |> dplyr::filter(UASLAeq != "Baseline")
stimDataNoAmb <- stimData |> dplyr::filter(UASLAeq != "Baseline")

# filter data to exclude the missing age participant and the missing response data
subjDataNoAmb.cc <- subjDataNoAmb |> dplyr::filter(!is.na(Age) & !is.na(TrialNumber))

# now drop any unused levels
subjDataNoAmb <- droplevels(subjDataNoAmb)
stimDataNoAmb <- droplevels(stimDataNoAmb)
subjDataNoAmb.cc <- droplevels(subjDataNoAmb.cc)

```

## impute missing age data

```{R}

# first create a participant-level dataset
subj_dat <- subjData |> dplyr::select(ID, Age) |> dplyr::distinct()

# create a median imputation for missing age data
subj_dat.med <- subj_dat |> dplyr::mutate(Age = ifelse(is.na(Age),
                                                   median(Age, na.rm=TRUE),
                                                   Age))

# now merge the imputed age data back into the main dataset
subjData.med <- subjData |> dplyr::select(-Age) |> dplyr::left_join(subj_dat.med, by="ID")

# now filter the dataset to exclude ambient-only stimuli
subjDataNoAmb.med <- subjData.med |> dplyr::filter(UASLAeq != "Baseline") |>
  droplevels()

# use multiple imputation to impute missing age data
imp_data <- mice::mice(subj_dat, m=5, method='pmm', seed=808)

completed_list <- mice::complete(imp_data, action='all')

# merge the completed datasets back into a main dataset list and filter baseline
subjData.imp <- lapply(completed_list,
                       function(df) {subjData |>
                           dplyr::select(-Age) |>
                           dplyr::left_join(df, by="ID")})

subjDataNoAmb.imp <- lapply(subjData.imp,
                            function(df) {subjData |>
                                dplyr::filter(UASLAeq != "Baseline") |>
                                droplevels()
                            } )

```

# Annoyance

## Model 0 formula

```{R}

model0formula <- AnnoyanceOrd ~ 1 + SessionPart + TrialNumberScl +
                    UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

```

## Model 0a: maximal model for annoyance, complete cases

```{r}

emp_thresh0a <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb.cc$AnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh0a <- emp_thresh0a[is.finite(emp_thresh0a)]

priors0a <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh0a,", 1)"), class = "Intercept", coef = 1:length(emp_thresh0a))
)

# extract the data for the model
model0aData <- subjDataNoAmb.cc[, all.vars(model0formula), drop=FALSE]

tic()
model0aPriors <- brms::brm(model0formula,
                 data=model0aData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0a,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

model0a_ppd <- ppd_ridgeplot(model0aPriors, ndraws = 100)
model0a_ppd

model0aPriorCheck <- brms::pp_check(model0aPriors, type='bars', ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
model0aPriorCheck

tic()
model0a <- brms::brm(model0formula,
                 data=model0aData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0a,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

model0aPostCheck <- brms::pp_check(model0a, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model0aPostCheck

```

## Model 0b: maximal model for annoyance, median imputed

```{r}

emp_thresh0b <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb$AnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh0b <- emp_thresh0b[is.finite(emp_thresh0b)]

priors0b <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh0b,", 1)"), class = "Intercept", coef = 1:length(emp_thresh0b))
)

# extract the data for the model
model0bData <- subjDataNoAmb.med[, all.vars(model0formula), drop=FALSE]

tic()
model0bPriors <- brms::brm(model0formula,
                 data=model0bData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0b,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

model0b_ppd <- ppd_ridgeplot(model0bPriors, ndraws = 100)
model0b_ppd

model0bPriorCheck <- brms::pp_check(model0bPriors, type='bars', ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
model0bPriorCheck

tic()
model0b <- brms::brm(model0formula,
                 data=model0bData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0b,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

model0bPostCheck <- brms::pp_check(model0b, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model0bPostCheck

```

## Model 0c: maximal model for annoyance, multiple imputed

```{r}

emp_thresh0c <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb$AnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh0c <- emp_thresh0c[is.finite(emp_thresh0c)]

priors0c <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.2, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh0c,", 1)"), class = "Intercept", coef = 1:length(emp_thresh0c))
)

# extract the data for the model
model0cData <- lapply(subjDataNoAmb.imp,
                      function(df) {df[, all.vars(model0formula), drop=FALSE]})

tic()
model0cPriors <- brms::brm_multiple(model0formula,
                 data=model0cData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior=priors0c,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

model0c_ppd <- ppd_ridgeplot(model0cPriors, ndraws = 100)
model0c_ppd

model0cPriorCheck <- brms::pp_check(model0cPriors, type='bars', ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
model0cPriorCheck

tic()
model0c <- brms::brm_multiple(model0formula,
                 data=model0cData,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior = priors0c,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

model0cPostCheck <- brms::pp_check(model0c, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model0cPostCheck

```

# dAnnoyance

## Priors

```{r}

# redefine the response for the subsetted data to drop unused levels
subjDataNoAmb.cc$dAnnoyanceOrd <- droplevels(subjDataNoAmb.cc$dAnnoyanceOrd)

# empirical distribution converted into threshold centres for the cumulative logit model
emp_thresh1 <- round(qlogis(cumsum(prop.table(table(subjDataNoAmb.cc$dAnnoyanceOrd)))), 2)
# truncate emp_thresh to remove infinite values
emp_thresh1 <- emp_thresh[is.finite(emp_thresh1)]

priors1 <- c(
  set_prior("normal(0, 2)", class='b'),
  brms::prior(normal(0.25, 1), class='b', coef='UASLAEMaxLRScl'),
  brms::prior(normal(1.5, 1), class='b', coef='Ilog10UASEvents'),
  brms::prior(normal(0.1, 1), class='b', coef='TrialNumberScl'),
  brms::prior(normal(0.1, 1), class='b', coef='SessionPartB'),
  brms::prior_string(paste0("normal(", emp_thresh1,", 1)"), class = "Intercept", coef = 1:length(emp_thresh1))
)

```

## Model 1: maximal model

```{r}

model1formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID) +
                     (1 | StimID)

tic()
model1Priors <- brms::brm(model1formula,
                 data=subjDataNoAmb.cc,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior = priors1,
                 sample_prior='only', seed=808,
                 chains=4, iter=2000, warmup=1000)
toc()

model1_ppd <- ppd_ridgeplot(model1Priors, ndraws = 100)
model1_ppd

model1PriorCheck <- brms::pp_check(model1Priors, type='bars', ndraws = 100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Mean change in annoyance")
model1PriorCheck

tic()
model1 <- brms::brm(model1formula,
                 data=subjDataNoAmb.cc,
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior = priors1,
                 threads=threading(threads=3, static=TRUE),  # check threads*chains = n_cores
                 seed=808, chains=4, iter=2000, warmup=1000)
toc()

model1 <- brms::add_criterion(model1, criterion=c('loo', 'loo_R2'), cores=n_cores)

model1PostCheck <- brms::pp_check(model1, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model1PostCheck

```

## Model 2: omit stimID random effect

```{r}

model2formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) +
                      UASOperation + UASType | ID)

tic()
model2 <- brms::brm(model2formula,
                 data=insight::get_data(model1),
                 family=cumulative(link='logit'),
                 future=TRUE, backend='cmdstanr', prior = priors1,
                 threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores,
                 seed=303, chains=4, iter=2000, warmup=1000)
toc()

model2 <- brms::add_criterion(model2, criterion=c('loo', 'loo_R2'), cores=n_cores)

model2PostCheck <- brms::pp_check(model2, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model2PostCheck

```

## Model 1 and 2 comparison

```{r}

loo::loo(model1)
loo::loo(model2)

model1.2_loo <- loo::loo_compare(model1, model2, criterion='loo')
model1.2_loo

#        elpd_diff se_diff
# model1  0.0       0.0   
# model2 -3.8       2.2

```

## Model 2 analysis

```{r}

# visualise the effects of the main predictors in model2

tidybayes::spread_draws(model2, b_UASLAEMaxLRScl, b_Ilog10UASEvents, b_UASTypeM300,
                        b_UASTypeT150, b_UASOperationLanding, b_UASOperationTakeoff, b_AmbientEnvStreet)


```

## Model 3: omit group slopes for UASOperation and UASType

```{r}
model3formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) | ID)

tic()
model3 <- brms::brm(model3formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=707, chains=4, iter=2000, warmup=1000)
toc()

model3 <- brms::add_criterion(model3, criterion=c('loo', 'loo_R2'), cores=n_cores)

model3PostCheck <- brms::pp_check(model3, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model3PostCheck

```

## Model 1-3 comparison

```{r}

loo::loo(model1)
loo::loo(model2)
loo::loo(model3)

model1.2.3_loo <- loo::loo_compare(model1, model2, model3, criterion='loo')
model1.2.3_loo




```

## Model 4: omit group slope for UASEvents

```{r}

model4formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv | ID)


tic()
model4 <- brms::brm(model4formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=999, chains=4, iter=2000, warmup=1000)
toc()

model4 <- brms::add_criterion(model4, criterion=c('loo', 'loo_R2'), cores=n_cores)

model4PostCheck <- brms::pp_check(model4, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model4PostCheck

```

## Models 1-4 comparison

```{r}

loo::loo(model1)
loo::loo(model2)
loo::loo(model3)
loo::loo(model4)

model1.2.3.4_loo <- loo::loo_compare(model1, model2, model3, model4, criterion='loo')
model1.2.3.4_loo

#         elpd_diff se_diff
# model1    0.0       0.0 
# model2   -36.6       9.7 
# model3  -206.7      20.3 
# model4  -813.2      39.4

```

## Model 5: omit group slope for AmbientEnv

```{r}

model5formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + UASLAEMaxLRScl | ID)


tic()
model5 <- brms::brm(model5formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=118, chains=4, iter=2000, warmup=1000)
toc()

model5 <- brms::add_criterion(model5, criterion=c('loo', 'loo_R2'), cores=n_cores)

model5PostCheck <- brms::pp_check(model5, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model5PostCheck

```

## Models 1-5 comparison

```{r}

loo::loo(model1)
loo::loo(model2)
loo::loo(model3)
loo::loo(model4)
loo::loo(model5)

model1.2.3.4.5_loo <- loo::loo_compare(model1, model2, model3, model4, model5, criterion='loo')
model1.2.3.4.5_loo

#         elpd_diff se_diff
# model1a    0.0       0.0 
# model1b   -4.8       2.6 
# model2   -36.6       9.7 
# model3  -206.7      20.3 
# model4  -813.2      39.4 

```

## Model 6: omit group slope for UASLAEMaxLRScl but retain AmbientEnv

```{r}

model6formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv  | ID)


tic()
model6 <- brms::brm(model6formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=111, chains=4, iter=2000, warmup=1000)
toc()

model6 <- brms::add_criterion(model6, criterion=c('loo', 'loo_R2'), cores=n_cores)

model6PostCheck <- brms::pp_check(model6, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model6PostCheck

```

## Models 1-6 comparison

```{r}

loo::loo(model1)
loo::loo(model2)
loo::loo(model3)
loo::loo(model4)
loo::loo(model5)


model1.2.3.4.5.6_loo <- loo::loo_compare(model1, model2, model3, model4, model5,
                                         model6, criterion='loo')
model1.2.3.4.5.6_loo

#         elpd_diff se_diff
# model1a    0.0       0.0 
# model1b   -4.8       2.6 
# model2   -36.6       9.7 
# model3  -206.7      20.3 
# model5  -274.6      24.5 
# model4  -813.2      39.4 

```

## Model 7: omit group slope for UASLAEMaxLRScl and AmbientEnv but retain UASEvents

```{r}

model7formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + I(log10(UASEvents)) | ID)


tic()
model7 <- brms::brm(model7formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=57132, chains=4, iter=2000, warmup=1000)
toc()

model6 <- brms::add_criterion(model7, criterion=c('loo', 'loo_R2'), cores=n_cores)

model7PostCheck <- brms::pp_check(model7, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model7PostCheck

```

## Models 1-7 comparison

```{r}

loo::loo(model1)
loo::loo(model2)
loo::loo(model3)
loo::loo(model4)
loo::loo(model5)
loo::loo(model6)
loo::loo(model7)

model1.2.3.4.5.6.7_loo <- loo::loo_compare(model1, model2, model3,
                                               model4, model5, model6, model7, criterion='loo')
model1.2.3.4.5.6.7_loo

#         elpd_diff se_diff
# model1a    0.0       0.0 
# model1b   -3.5       1.6 
# model2   -13.8       7.9 
# model3  -187.7      18.6  (1 + UASLAEMaxLRScl + AmbientEnv | ID)
# model5  -255.5      22.3  (1 + AmbientEnv | ID)
# model6  -723.2      35.8  (1 + I(UASEvents^-1) | ID)
# model4  -788.4      36.3  (1 + UASLAEMaxLRScl | ID)

model3Vs5_loo <- loo::loo_compare(model3, model5, criterion='loo')
model3Vs5_loo

```

## Model 8: omit group slope for UASLAEMaxLRScl

```{r}

model8formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   Age + Sex + NSSTotal + Area_soundscape2 +
                   (1 + AmbientEnv + I(log10(UASEvents)) | ID)

tic()
model8 <- brms::brm(model8formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=985416, chains=4, iter=2000, warmup=1000)
toc()

model8 <- brms::add_criterion(model8, criterion=c('loo', 'loo_R2'), cores=n_cores)

model8PostCheck <- brms::pp_check(model8, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model8PostCheck

```

## Models 1-8 comparison

```{r}

loo::loo(model1)
loo::loo(model2)
loo::loo(model3)
loo::loo(model4)
loo::loo(model5)
loo::loo(model6)
loo::loo(model7)
loo::loo(model8)

model1.2.3.4.5.6.7.8_loo <- loo::loo_compare(model1, model2, model3,
                                               model4, model5, model6, model7,
                                             model8, criterion='loo')
model1.2.3.4.5.6.7.8_loo

#         elpd_diff se_diff
# model1a    0.0       0.0 (1 + UASLAEMaxLRScl + AmbientEnv + I(UASEvents^-1) + UASOperation + UASType | ID) + (1 | StimID)
# model1b   -4.8       2.6 (1 + UASLAEMaxLRScl + AmbientEnv + I(UASEvents^-1) + UASOperation + UASType | ID)
# model2   -36.6       9.7 (1 + UASLAEMaxLRScl + AmbientEnv + I(UASEvents^-1) | ID)
# model7  -104.8      15.8  (1 + AmbientEnv + I(UASEvents^-1) | ID)
# model3  -206.7      20.3 (1 + UASLAEMaxLRScl + AmbientEnv | ID)
# model5  -274.6      24.5 (1 + AmbientEnv | ID)
# model6  -746.2      38.8 (1 + I(UASEvents^-1) | ID)
# model4  -813.2      39.4 (1 + UASLAEMaxLRScl | ID)

```

## Model 9: omit between-subjects effects expected to be negligible

```{r}

model9formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 + Home_Area2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv + I(log10(UASEvents)) | ID)

tic()
model9 <- brms::brm(model9formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model9 <- brms::add_criterion(model9, criterion=c('loo', 'loo_R2'), cores=n_cores)

model9PostCheck <- brms::pp_check(model9, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model9PostCheck

```

## Model 1 & 9 comparison

```{r}

loo::loo(model1)
loo::loo(model9)

model1.9_loo <- loo::loo_compare(model1, model9, criterion='loo')
model1.9_loo

#         elpd_diff se_diff
# model1a   0.0       0.0  
# model8  -12.4       7.9  

```

## Model 10: omit further between-subjects effects expected to have minor effects

```{r}

model10formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 + AAM_attitude2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv +
                      I(log10(UASEvents)) | ID)


tic()
model10 <- brms::brm(model10formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model10 <- brms::add_criterion(model10, criterion=c('loo', 'loo_R2'), cores=n_cores)

model10PostCheck <- brms::pp_check(model10, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model10PostCheck

```

## Model 1, 9 and 10 comparison

```{r}

loo::loo(model1)
loo::loo(model9)
loo::loo(model10)

model1.9.10_loo <- loo::loo_compare(model1, model9, model10, criterion='loo')
model1.9.10_loo

#         elpd_diff se_diff
# model1a   0.0       0.0  
# model8  -12.4       7.9  
# model9  -12.4       7.9    

```

## Model 11: omit NationGeo2 and Home_Area2 between-subjects effects

```{r}

model11formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   AAM_attitude2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv +
                      I(log10(UASEvents)) | ID)


tic()
model11 <- brms::brm(model11formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model11 <- brms::add_criterion(model11, criterion=c('loo', 'loo_R2'), cores=n_cores)

model11PostCheck <- brms::pp_check(model11, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model11PostCheck

```

## Model 1 & 9-11 comparison

```{r}

loo::loo(model1)
loo::loo(model9)
loo::loo(model10)
loo::loo(model11)

model1.9.10.11_loo <- loo::loo_compare(model1, model9, model10, model11, criterion='loo')
model1.9.10.11_loo

#         elpd_diff se_diff
# model1a   0.0       0.0  
# model8  -12.4       7.9  
# model9  -12.4       7.9  
# model10 -13.5       7.9   

```

## Model 12: omit all between-subjects effects

```{r}

model12formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   (1 + UASLAEMaxLRScl + AmbientEnv +
                      I(log10(UASEvents)) | ID)


tic()
model12 <- brms::brm(model12formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model12 <- brms::add_criterion(model12, criterion=c('loo', 'loo_R2'), cores=n_cores)

model12PostCheck <- brms::pp_check(model12, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model12PostCheck

```

## Model 1 & 9-12 comparison

```{r}

loo::loo(model1)
loo::loo(model9)
loo::loo(model10)
loo::loo(model11)
loo::loo(model12)

model1.9.10.11.12_loo <- loo::loo_compare(model1, model9,
                                              model10, model11, model12, criterion='loo')
model1.9.10.11.12_loo

#         elpd_diff se_diff
# model1a   0.0       0.0  (NationGeo2 + AAM_attitude3 + Home_Area2 + Age + Sex + NSSTotal + NativeLang + Area_soundscape + PANAS_positive + PANAS_negative)
# model8  -12.4       7.9  (NationGeo2 + AAM_attitude3 + Home_Area2 + Age + NSSTotal + Area_soundscape)
# model9  -12.4       7.9  (NationGeo2 + AAM_attitude3 + Home_Area2)
# model11 -12.7       7.9  ()
# model10 -13.5       7.9  (AAM_attitude3)

```

## Model 13: retain Home_Area between-subjects effect

```{r}

model13formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                    Home_Area2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv +
                      I(log10(UASEvents)) | ID)

tic()
model13 <- brms::brm(model13formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model13 <- brms::add_criterion(model13, criterion=c('loo', 'loo_R2'), cores=n_cores)

model13PostCheck <- brms::pp_check(model13, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model13PostCheck

```

## Model 1 & 9-13 comparison

```{r}

loo::loo(model1)
loo::loo(model9)
loo::loo(model10)
loo::loo(model11)
loo::loo(model12)
loo::loo(model13)

model1.9.10.11.12.13_loo <- loo::loo_compare(model1, model9,
                                              model10, model11, model12,
                                             model13, criterion='loo')
model1.9.10.11.12.13_loo

#         elpd_diff se_diff
# model1a   0.0       0.0  
# model8  -36.0       9.7  
# model12 -36.0       9.8  
# model9  -36.4       9.7  
# model11 -36.5       9.8  
# model10 -36.8       9.7  

```

## Model 14: retain NationGeo between-subjects effect

```{r}

model14formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   NationGeo2 +
                   (1 + UASLAEMaxLRScl + AmbientEnv +
                      I(log10(UASEvents)) | ID)


tic()
model14 <- brms::brm(model14formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model14 <- brms::add_criterion(model14, criterion=c('loo', 'loo_R2'), cores=n_cores)

model14PostCheck <- brms::pp_check(model14, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model14PostCheck

```

## Model 1 & 9-14 comparison

```{r}

loo::loo(model1)
loo::loo(model9)
loo::loo(model10)
loo::loo(model11)
loo::loo(model12)
loo::loo(model13)
loo::loo(model14)

model1.9.10.11.12.13.14_loo <- loo::loo_compare(model1, model9,
                                              model10, model11, model12, model13,
                                              model14, criterion='loo')
model1.9.10.11.12.13.14_loo

```

## Model 15: retain Sex between-subjects effect

```{r}

model15formula <- dAnnoyanceOrd ~ 1 + TrialNumberScl +
                      SessionPart +
                   UASLAEMaxLRScl*I(log10(UASEvents)) +
                   UASLAEMaxLRScl*AmbientEnv*UASOperation +
                   UASLAEMaxLRScl*AmbientEnv*UASType +
                   UASOperation*UASType +
                   Sex +
                   (1 + UASLAEMaxLRScl + AmbientEnv +
                      I(log10(UASEvents)) | ID)


tic()
model15 <- brms::brm(model15formula,
                   data=insight::get_data(model1),
                   family=cumulative(link='logit'),
                   future=TRUE, backend='cmdstanr', prior = priors1,
                   threads=threading(threads=3, static=TRUE), # check threads*chains = n_cores
                   seed=1678, chains=4, iter=2000, warmup=1000)
toc()

model15 <- brms::add_criterion(model15, criterion=c('loo', 'loo_R2'), cores=n_cores)

model15PostCheck <- brms::pp_check(model15, type='bars', ndraw=100) +
  theme(panel.grid=element_blank(), text=element_text(family='serif')) +
  labs(x="Ordinal category index")
model15PostCheck

```

## Model 1 & 9-15 comparison

```{r}

loo::loo(model1)
loo::loo(model9)
loo::loo(model10)
loo::loo(model11)
loo::loo(model12)
loo::loo(model13)
loo::loo(model14)
loo::loo(model15)

model1.9.10.11.12.13.14.15_loo <- loo::loo_compare(model1, model9,
                                              model10, model11, model12, model13,
                                              model14, model15, criterion='loo')
model1.9.10.11.12.13.14.15_loo

```

## model 16: 



























